### 2018-02-12 tex/manuscript.tex
add files for manuscript

%% Submissions for peer-review must enable line-numbering 
%% using the lineno option in the \documentclass command.
%%
%% Preprints and camera-ready submissions do not need 
%% line numbers, and should have this option removed.
%%
%% Please note that the line numbering option requires
%% version 1.1 or newer of the wlpeerj.cls file, and
%% the corresponding author info requires v1.2

\documentclass[fleqn,10pt,lineno]{wlpeerj} % for journal submissions
% \documentclass[fleqn,10pt]{wlpeerj} % for preprint submissions

\usepackage{gensymb}
\usepackage{wasysym}
\usepackage{textgreek}
\usepackage{textcomp}
\newcommand{\td}{\textdegree~}
\newcommand{\x}{$\times$~}

\title{Descriptions of four new species of \textit{Minyomerus} Horn, 1876 (Coleoptera: Curculionid\ae), with notes on their distribution and phylogeny}

\author[1]{M. Andrew Jansen}
\author[2]{Nico M. Franz}
\affil[1]{School of Life Sciences, 427 E Tyler Mall, PO Box 874501, Tempe, AZ 85287}
\affil[2]{ASU Natural History Collections, 734 W Alameda Dr, Tempe, AZ 85282}
\corrauthor[1]{M. Andrew Jansen}{majanse1@asu.edu}

% \keywords{Keyword1, Keyword2, Keyword3}

\begin{abstract}
Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text.
\end{abstract}

\begin{document}

\flushbottom
\maketitle
\thispagestyle{empty}

\section*{Introduction}
	\#
\section*{Materials and methods}
	\paragraph{Natural history observations} 
		Members of the genus Minyomerus are typically found on a variety of host plants, as indicated following each species account.
		Many species are likely generalists with regards to their host plant spectrum. 
		Adult weevils are most commonly observed on the leaves and branches of the host where they feed on the leaf tissue. Eggs, larvae, and pupae remain unknown. 
		The larvae are probably root feeders, as observed in the tanymecine genus Tanymecus Germar, 1817 (Howden 1975). 
		They typically inhabit arid regions, especially deserts, throughout southwestern North America, including the Mojave, Sonoran, Chihuahuan, and Great Basin Deserts. 
		They also occur in semi-arid regions of the Great Plains, on the Colorado Plateau, and throughout Baja California, Mexico. 
		The adults apparently disperse without flight, as the hind wings and associated flight structures of all species in the genus are greatly reduced and not readily apparent after dissections.
		In several species only females are known, and some are putatively considered parthenogenetic, as indicated in the respective descriptions.

	\paragraph{Acquisition of museum specimens} 
		Georeferencing of localities was performed with Google Earth (Google Inc. 2009–2015) and reported in decimal degrees.
		Taxonomic names for associated host plants are used in accordance with Munz and Keck (1973) and SEINet (2015).
		The set of existing \textit{Minyomerus} [JF2015] specimens used in the revision of Jansen and Franz 2015 was supplemented with material from the following collections, using the codens of Arnett et al. (1993):

		\begin{description}[itemsep=-1ex]
			\item[\texttt{CMNC}] Canadian Museum of Nature Collection, Ottawa, Ontario, Canada
			\item[\texttt{TAMU}] Texas A \& M University, College Station, Texas, USA
			\item[\texttt{USNM}] National Museum of Natural History, Washington, D.C., USA
		\end{description}

	\paragraph{Morphological analysis}
		The herein utilized systematic and descriptive approach follows Franz (2010a, 2010b, 2012).
		Terminology for exterior morphology is in general accordance with Torre-Bueno (Nichols 1989).
		Additional morphological terms specific to (entimine) weevils were used as follows:
			Ting (1936) and Morimoto and Kojima (2003) for mouthparts;
			Thompson (1992) for tibial apices and abdominal segments;
			and Oberprieler et al. (2014) and Howden (1995) for male and female terminalia.
		All measurements were taken using a Leica M205 C stereomicroscope and attached computer running the software Leica Application Suite (LAS), version 4.1.0.
		The overall body length and width were measured in dorsal view as the maximum distance between the apex of the rostrum and the apex of the elytra, and the maximum width of the elytra, respectively.
		The length of the rostrum was measured in dorsal view as the distance extending from the apex of the epistoma to the anterior margin of the eyes.
		The width of the rostrum was measured in dorsal view as the maximum distance between the dorsal margins of the rostrum near the point of antennal insertion.
		The length of the pronotum was measured in dorsal view as the length along the midline from the anterior margin to the posterior margin.
		The width of the elytra was measured in dorsal view as the maximum distance between the lateral margin and the elytral suture.
		Other length and width measurements were performed in dorsal orientation, as the maximum length and width of the corresponding structure (profemur, protibia, elytron, and aedeagus).
		Images of mouthparts and terminalia were produced with the Leica microscope equipment, whereas habitus photographs were created with a Visionary Digital Passport II sytem using a Canon EOS Mark 5D II camera.

		Species of Minyomerus [JF2015] recognized in this revision were delimited through application of the phylogenetic species concept sensu Wheeler and Platnick (2000).
		Species descriptions follow the inferred phylogenetic sequence (see details below).
		The genus-level description for Minyomerus [JF2015] highlights characters present in all members and accounts for their apparent variability.
		Consequently, the species descriptions represent unique and complementary accounts of the character states observed in each species, including their variability, and excepting characters that are invariate within the genus as specified in the higher-level description of Minyomerus.
		Likewise, descriptions of males in the genus- and species-level accounts emphasize characters that are variable and sufficiently different from those of the females to merit recognition.
		Some redundancy occurs between genus and species descriptions when discussing characters that vary widely within single species, and also between species descriptions where a character exhibits considerable variation in some species yet is invariant in others.
		The key to identifying species of Minyomerus is arranged with emphasis being placed on the most readily observable diagnostic characters.
		The revision is arranged with the species descriptions appearing first, followed by the key to species, and then by the phylogenetic results.

	\paragraph{Phylogenetic analysis}
		The morphological cladistic analysis includes 22 terminal taxa; with 17 ingroup and 5 outgroup terminals.
		Following resolution of species identities and boundaries, the ingroup terminals were represented by six species previously assigned to Minyomerus sec. O’Brien and Wibmer (1982), Piscatopus griseus sec. Sleeper (1960), and ten newly recognized species.
		The lack of prior phylogenetic analyses of Minyomerus and closely related lineages made it necessary to sample outgroups fairly broadly while remaining focused on North American lineages that are are putative close relatives of the ingroup (Nixon and Carpenter 1993).
		The tribe Tanymecini [non-focal] is cosmopolitan, with the subtribe Tanymecina [non-focal] containing the majority of New World species diversity in the tribe (Alonzo-Zarazaga and Lyal 1999).
		Accordingly, four outgroup terminals are represented by species belonging to separate genera in the Tanymecina [non-focal]; viz. Pandeleteius cinereus (Horn, 1876) [non-focal], Pandeleteinus subcancer Howden, 1969 [non-focal], Isodrusus debilis Sharp, 1911 [non-focal], and Isodacrys buchanani Howden, 1961 [non-focal].
		Because generic relationships in the Tanymecini [non-focal] remain unresolved, it was deemed prudent to find a relatively far-removed taxon to root the cladogram that would nevertheless display states that are applicable to the ingroup for all characters under consideration (Rieppel 2007; Franz 2014).
		For this purpose we select the North American species Sitona californicus (Fahraeus, 1840) [non-focal], representing the tribe Sitonini Gistel, 1856 [non-focal].
		The character matrix was edited and phylogenetic results reviewed and reconnected to the input using the WinDada and WinClados interfaces of WinClada (Nixon 2002).
		The character sequence follows that of the taxonomic descriptions.
		The most parsimonious tree and character state optimizations were inferred under parsimony using NONA (Goloboff 1999).
		An unconstrained heuristic search of tree space for the 22-terminal matrix was conducted using the commands: hold 100001, mult*1000, hold/100, with mult*max* selected.
		Bootstrap support was inferred in WinClada using the parameters of 1000 replications, hold 1000, hold/100, mult*10, “Don’t do max*”, and “Save consensus”.
		Finally, Bremer support values (Bremer 1994) were calculated in NONA using the commands hold 20000, suboptimal 20, and bsupport 20.
	\paragraph{Species distribution modeling}
		We used the modeling program Maxent, Version 3.3, to generate habitat models for the species of Minyomerus [JF 2015] (Figs 50–52) based on the documented occurrence records (Phillips et al. 2004, 2006; Elith et al. 2011).
		The default settings “Max number background points”, set to 100,000, and “Iterations” set to 10 and with cross-validation, were applied to leverage all available locality data.
		However, no models could be created for three species with single documented localities; and only a single-iteration habitat model could be generated for a fourth species due to limited information data.
		We selected 19 bioclimatic variables and elevation as Environmental Layers in Maxent, obtained from WorldClim (see Hijmans et al. 2005 and the associated website for further detail on variables).
		The layers were downloaded by tile (zones 11–13 and 21–23), with a 30 arc-second resolution (projected using WSG 84) to provide adequate coverage of the full distribution of Minyomerus [JF2015].
		These tiles were assembled, by layer, into composite maps of six tiles each, using QGIS, Version 2.8.1 ‘Wien’, prior to species distribution modeling (Quantum GIS Development Team 2015).
		After modeling, the raster files of the predictive probabilities were imported into GIS.
		Each file was designated a specific color, and each pixel in the raster grid was assigned a linearly interpolated saturation of that color, with increasing saturation denoting an increased probability of successful prediction of species presence at that point.
		Pixels with a value below 0.50 were rendered transparent so that the model only shows regions with a greater than 50\% chance of successful prediction.
		The raster files were clipped to remove extraneous predicted regions based on: (1) predictive probability (i.e., removing large areas with only transparent pixels) and (2) geographic extent (accounting for endemicity).
		For instance, species endemic to Baja California Sur, Mexico, do not require a predictive model for bioclimatically similar habitats in Canada.
		The actual (documented) occurrence records are laid over the modeled habitat ranges as colored circles on the respetive maps (Figs 50–52), along with vector layers of country and state borders (Hijmans et al. 2012).
\section*{Descriptions of new species}
	\subsection*{\textit{Minyomerus ampullaceus} - sp. n.}
		\subsubsection*{Diagnosis}
			\#
		\subsubsection*{Description of female}
			\paragraph{Habitus}
				Length \# mm, width \# mm, length/width ratio \#, widest at anterior \# of elytra.
				Integument orange-brown to black. 
				Scales with variously interspersed colors ranging from slightly off-white to beige to yellow. 
				Setae recumbent to sub-recumbent, white to brown in color.
			\paragraph{Manidbles}
				Partially covered with white, slightly opalescent scales, with 3 longer setae, and 1 shorter seta between these.
			\paragraph{Rostrum}
				Length \# mm, anterior portion \# broader than long, rostrum/pronotum length ratio \#, rostrum length/width ratio \#.
				Separation of rostrum from head generally obscure. 
				Dorsal outline of rostrum nearly square, anterior half of dorsal surface mesally concave, posterior half coarsely but shallowly punctate to rugose. 
				Rostrum in lateral view nearly square; apical margin broadly bisinuate and emarginate, with 2 pairs of large vibrissae. 
				Nasal plate defined by Y-shaped, impressed lines, convex, integument partially covered with white scales.
				Margins of mandibular incision directed \#\td outward dorsally in frontal view. 
				Ventrolateral sulci strongly defined, beginning as a narrow sulcus posteriad of insertion point of mandibles, running parallel to scrobe, terminating in a ventral fovea.
			\paragraph{Antennae}
				Small tooth formed by overhanging dorsal margin of scrobe directly ventrad of margin of eye.
				Scape extending to posterior 1/3 of eye.
				Funicular segments V-VII and club missing.
			\paragraph{Head}
				Eyes globular, anterodorsal margin of each eye feebly impressed, posterior margin elevated from lateral surface of head; eyes separated in dorsal view by 4\x their anterior-posterior length, set off from anterior prothoracic margin by 1/3 of their anterior-posterior length. 
				Head without any transverse post-ocular impression.
			\paragraph{Pronotum}
				Length/width ratio \#; widest near midpoint. 
				Anterior margin slightly arcuate, lateral margins curved and widening into a bulge just anteriad of midpoint of pronotum, posterior margin straight, with a slight mesal incurvature. 
				Pronotum in lateral view with setae that reach beyond anterior margin by 1/2 of their length; these setae becoming evenly longer and more erect laterally, reaching a maximum length equal to 1/2 of length of eye. 
				Anterolateral margin with a reduced tuft of 6-7 post-ocular vibrissae present, emerging near ventral 1/2 of eye, and stopping just below ventral margin of eye; vibrissae sub-equal in length at 1/3 of anterior-posterior length of eye, except for three vibrissae achieving a maximum length similar to anterior-posterior length of eye.
			\paragraph{Scutellum}
				Exposed, margins straight.
			\paragraph{Pleurites}
				Metepisternum hidden by elytron.
			\paragraph{Thoracic sterna}
				Mesocoxal cavities separated by 1/4\x width of mesocoxal cavity. 
				Metasternum with transverse sulcus not apparent; metacoxal cavities widely separated by ca. 2\x their width.
			\paragraph{Legs}
				Profemur/pronotum length ratio \#; profemur with distal 1/5 produced ventrally as a rounded projection covering tibial joint; condyle of tibial articulation occupying 4/5 of distal surface and 1/5 length of femur. 
				Protibia/profemur length ratio \#; protibial apex with ventral setal comb recessed in an incurved groove; mucro present as a large, black, sub-triangular, medially-projected tooth, which is approximately equilateral and whose sides are subequal in length to surrounding setae. 
				Protarsus with tarsomere III 1.25\x as long as II; wider than long. 
				Metatibial apex with almond shaped convexity ringed by 10 short, spiniform setae.
			\paragraph{Elytra}
				Length/width ratio \#; widest at anterior 1/3; anterior margins jointly 1.75\x wider than posterior margin of pronotum and strongly produced dorsally from margin of pronotum; lateral margins evenly rounded until posterior 1/3, more strongly rounded and converging thereafter. 
				Posterior declivity angled at nearly 85\td to main body axis. Elytra with 10 complete striae; striae shallow; punctures faint beneath appressed scales, separated by 5-7\x their diameter; intervals very slightly elevated.
			\paragraph{Abdominal sterna}
				Ventrite III anteromesally incurved around a fovea located mesally on anterior margin, posterior margin elevated and set off from IV along lateral 1/3s of its length. 
				Sternum VII mesally 1/2\x as long as wide; anterior margin weakly curved.
			\paragraph{Tergum}
				Pygidium (tergum VIII) sub-conical; posterior margin emarginate; medial 1/3 of anterior 3/5 of pygidum less sclerotized.		
			\paragraph{Sternum VIII}
				Anterior laminar edges each incurved forming a 115\td angle with lateral margin, this angle distinctly sclerotized; posterior 1/2 of lamina porose throughout, laminar arms more sclerotized medially; posterior edge evenly, moderately arcuate.
			\paragraph{Ovipositor}
				Coxites in dorsal view slightly longer than broad, with a medial region that is weakly sclerotized.
			\paragraph{Spermatheca}
				Comma-shaped; collum expanded to form a long, cylindrical projection, subequal in length to ramus, 1/3\x width of corpus, angled at 45\td to corpus, apically with a reduced hood-shaped projection; ramus elongate, bulbous, slightly wider than thickness of corpus, basally constricted to form a short stalk; corpus not greatly swollen; cornu sub-equal in length to corpus and collum, recurved distally to form in inner angle of 60\td to corpus, straight and gradually narrowing along basal 2/3, with apical 1/3 abruptly narrowed, angled at 45\td to coprus, and tapering to a slight knob.
		\subsubsection*{Description of male}
			Male not available or known.
		\subsubsection*{Comments}
			Due to the limited number of specimens of this species, dissections of mouthparts could not be performed.
		\subsubsection*{Etymology}
			Named in reference to the shape of the body in dorsal view, which appears bottle-shaped due to the large elytra and comparatively cylindrical pronotum; ampullaceus = flasklike; Latin adjective \citep{brown1956}.
		\subsubsection*{Material examined}
			\paragraph{Holotype}
				\female~``Carlsbad, N.M.; Geococcyx calif; 144640'' (\texttt{\textbf{USNM}}).
		\subsection*{Distribution}
			\#
		\subsubsection*{Natural history}
			No host plant associations have been documented.
			The label indicates "Geococcyx calif"; this is presumably a reference to \textit{Geococcyx californianus} (Lesson, 1829) [Cuculidae], the Greater Roadrunner, although it is unclear if the specimen was found on or near one of these birds (either living, dead, or in a nest).
			\textit{Minyomerus} species are only known to be phytophagous, not parasitic, phoretic, or necrophagous, so we believe that this specimen was most likely found in a nest, and was present there only incidentally because the nest was constructed in the host plant of this specimen \citep{jansen2015}.
			It is unknown whether this species is parthenogenetic.

	\subsection*{\textit{Minyomerus franko} - sp. n.}
		\subsubsection*{Diagnosis}
			\#
		\subsubsection*{Description of female}
			\paragraph{Habitus}
				Length \# mm, width \# mm, length/width ratio \#, widest at anterior 1/3-1/4 of elytra.
				Integument orange-brown to black. 
				Scales with variously interspersed colors ranging from slightly off-white or beige to manila/tan to dark coffee brown, in some specimens appearing semi-translucent (in others opaque). 
				Setae linear to slightly apically explanate, appearing minutely spatulate, sub-recumbent to sub-erect, white or brown in color.
			\paragraph{Manidbles}
				Covered with white scales, with 3 longer setae, and 1-2 shorter setae between these.
			\paragraph{Maxillae}
				Cardo bifurcate at base with an inner angle typically between 90–120\td, arms of equal length, inner (mesal) arm nearly 1.5\x thicker than outer arm, both arms of bifurcation equal in length to apically outcurved arm, glabrous. 
				Stipes sub-quadrate, roughly equal in length to each bifurcation of cardo, with a single lateral seta. 
				Galeo-lacinial complex nearly extending to apex of maxillary palpomere II; complex mesally membranous, laterally sclerotized, with sharp demarcation of sclerotized region separating palpiger from galeo-lacinial complex; setose in membranous area just adjacent to sclerotized
region, setae covering 2/3 of dorsal surface area; dorsally with 7 apicomesal lacinial teeth; ventrally with 4 reduced lacinial teeth. 
				Palpiger with a single lateral seta, otherwise glabrous and evenly sclerotized throughout.
			\paragraph{Maxillary palps}
				I apically oblique, apical end forming a 45\td angle with base, with 2 apical setae; II sub-cylindrical, with 1 apical seta.
			\paragraph{Labium}
				Prementum roughly trapezoidal; apical margins angulate, ventral margin gently sinuate, dorsal margin straight; lateral margins feebly incurved near posterior margin; basal margin arcuate.
				Labial palps 3-segmented, I with apical 2/3 projecting beyond margin of prementum, exceeding apex of ligula; III slightly longer than II.
			\paragraph{Rostrum}
				Length \# mm, anterior portion \# broader than long, rostrum/pronotum length ratio \#, rostrum length/width ratio \#.
				Separation of rostrum from head generally obscure. 
				Dorsal outline of rostrum sub-rectangular, anterior half of dorsal surface feebly impressed, posterior half coarsely but shallowly punctate to rugose. 
				Rostrum in lateral view nearly square; apical margin bisinuate and emarginate , with 2 large vibrissae. 
				Nasal plate defined by broad, V-shaped, shallowly impressed lines, anteromesally slightly convex, integument partially covered with white scales. 
				Margins of mandibular incision directed \#\td outward dorsally in frontal view. 
				Ventrolateral sulci weakly defined (or entirely absent in some specimens) as a broad concavity dorsad of insertion point of mandibles, running parallel to scrobe, becoming flatter posteriorly and disappearing ventrally.
				Dorsal surface of rostrum with  short, linear, median fovea.
				Rostrum ventrally lacking sulci at corners of oral cavity.
			\paragraph{Antennae}
				Small tooth formed by overhanging dorsal margin of scrobe anterior to margin of eye by 1/5 of length of eye.
				Scape nearly extending to posterior 1/4 of eye.
				Terminal funicular antennomere lacking appressed scales, having instead a covering of apically-directed pubescence with interspersed sub-erect setae.
				Club nearly 3\x as long as wide.
			\paragraph{Head}
				Eyes globular to slightly elongate, slanted ca. 35\td antero-ventrally; eyes separated in dorsal view by 4\x their anterior-posterior length, set off from anterior prothoracic margin by 1/3 of their anterior-posterior length. 
				Head without any transverse post-ocular impression.
			\paragraph{Pronotum}
				Length/width ratio \#; widest near anterior 1/3, between anterior constriction and midpoint. 
				Anterior margin arcuate, lateral margins curved and widening into a slight bulge just anteriad of midpoint of pronotum, posterior margin straight, with a slight mesal incurvature. 
				Pronotum in lateral view with setae that reach just beyond anterior margin, angled laterally at 45-80\td to longitudinal axis, and strikingly long; these setae becoming evenly longer and more angled laterally, reaching a maximum length nearly equal to length of eye. 
				Anterolateral margin with a reduced tuft of 5 post-ocular vibrissae present, emerging near ventral 1/2 of eye, and stopping just below ventral margin of eye; vibrissae sub-equal in length at 1/3\x anterior-posterior length of eye, except for one vibrissa achieving a maximum length similar to anterior-posterior length of eye.
			\paragraph{Scutellum}
				Narrowly exposed, with visible area approximately equal to length of appressed scales, margins straight.
			\paragraph{Pleurites}
				Metepisternum nearly hidden by elytron except for triangular extension.
			\paragraph{Thoracic sterna} 
				Mesocoxal cavities separated by 1/3\x width of mesocoxal cavity. 
				Metasternum with transverse sulcus not apparent; metacoxal cavities widely separated by ca. 2\x their width.
			\paragraph{Legs}
				Profemur/pronotum length ratio \#; profemur with distal 1/5 produced ventrally as a sub-rectangular projection covering tibial joint; condyle of tibial articulation occupying 4/5 of distal surface and 1/5 length of femur. 
				Protibia/profemur length ratio \#; protibial apex with ventral setal comb recessed in a subtly incurved groove; mucro present as a large, black, sub-triangular, medially-projected tooth, which is approximately equilateral and whose sides are subequal in length to surrounding setae. 
				Protarsus with tarsomere III 2\x as long as II; wider than long. 
				Metatibial apex with almond shaped convexity ringed by 8-9 short, spiniform setae.
			\paragraph{Elytra}
				Length/width ratio \#; widest at anterior 1/3-1/4; anterior margins jointly 1.5\x wider than posterior margin of pronotum; lateral margins subparallel to slightly rounded after anterior 1/3, more strongly rounded and converging in posterior 1/3. 
				Posterior declivity angled at 70-85\td to main body axis. Elytra with 10 complete striae; striae shallow; punctures faint beneath appressed scales, separated by 5-7\x their diameter; intervals very slightly elevated.
			\paragraph{Abdominal sterna}
				Ventrite III anteromesally incurved around a fovea located mesally on anterior margin, posterior margin elevated and set off from IV along lateral 1/3s of its length. 
				Sternum VII mesally 1/2\x as long as wide; setae darkening, lengthening, and becoming more erect in posterior 2/3; anterior margin weakly curved.
			\paragraph{Tergum}
				Pygidium (tergum VIII) sub-cylindrical; medial 1/3 of anterior 2/3 of pygidum less sclerotized.
			\paragraph{Sternum VIII}
				Anterior laminar edges each incurved forming a 140\td angle with lateral margin; slightly less sclerotized medially between arms of bifurcation; posterior edge subtly incurved medially.
			\paragraph{Ovipositor}
				Coxites 1.5\x as long as broad, glabrous; styli 1/2\x as long as coxites. Genital chamber apically sclerotized.
			\paragraph{Spermatheca}
				Comma-shaped; collum short, apically with a large, hood-shaped projection angled at ca. 60\td to ramus, nearly equal in length and contiously aligned with curvature of bulb of ramus; collum sub-contiguous with, and angled at 90\td to ramus; ramus elongate, sub-cylindrical to slightly bulbous, 4/5\x thickness of corpus; corpus swollen, 1.25\x thicknes of ramus and 1.5\x thickness of cornu; cornu elongate, strongly recurved in basal 1/3, nearly straight thereafter and narrowing apically, abruptly narrowed in apical 1/3 with apex angled at 30\td to corpus.
		\subsubsection*{Description of male}
			Similar to female, except where noted.
			\paragraph{Habitus}
				Length \# mm, width \# mm, length/width ratio \#. Rostrum length \# mm, rostrum/pronotum length ratio \#, rostrum length/width ratio \#. Pronotum length/width ratio \#. Profemur/pronotum length ratio \#, protibia/profemur length ratio \#. Elytra length/width ratio \#.
			\paragraph{Elytra}
				Elytral declivity more angulate than female on average, forming an 80\td angle to main body axis, but otherwise as in female.
			\paragraph{Abdominal sterna}
				Sternum VII 2/5-1/2 \x as long as wide, posterior margin arcuate mesally.
			\paragraph{Tergum}
				Pygidium (tergum VIII) with posterior 1/3 punctate; anterior 2/3 rugose.
			\paragraph{Sternum IX}
				Spiculum gastrale 2\x length of aedeagal pedon. Laminar alae located on lateral 1/4 of posterior margin.
			\paragraph{Aedeagus}
				Length/width ratio \#; lateral margins very slightly converging posteriorly, abruptly constricted and more strongly converging in apical 1/5.
				Pedon in lateral view becoming gradually narrower posteriorly in anterior 1/2, ventral margins in posterior 1/2 abruptly curving to meet dorsal margins at a rounded apical point.
				Flagellum with large, elonage, tortuous apical sclerite, sclerite nearly as long as pedon, with complex, asymmetrical interior structure.
		\subsubsection*{Etymology}
			Named in reference to the long, somewhat unkempt, erect setae on the anterior margin of the pronotum; franko = free; Old High-German adjective \citep{brown1956}.
		\subsubsection*{Material examined}
			\paragraph{Holotype}
				\female~``MEX: S.L.P 1 km N.; Entronque El Huizache; 1493 m 2.VI.87; R. Anderson, \underline{\smash{Sphaeralcea}}; \underline{\smash{hastula}} A. Gray'' (\texttt{\textbf{CMNC}}).
			\paragraph{Paratypes}
				Same label information as female holotype (\texttt{\textbf{CMNC}}:  1 \female, 1 \male; \texttt{\textbf{TAMU}}: 2 \male);
				``MEXICO: S.L.P; 19.6 mi. n. Huizache; July 25, 1976; Peigler, Gruetzmacher,; R\&M Murray, Schaffner'' (\texttt{\textbf{CMNC}}: 1 \male);
				``MEXICO: San Luis Potosi; Entronque el Hulzache; 2 June 1987; R. Turnbow'' (\texttt{\textbf{CMNC}}: 1 \female, 1 \male);
				``MEXICO:Tamaulipas; 8.8 mi. ne. Jaumave; October 10, 1973; Gaumer \& Clark'' (\texttt{\textbf{TAMU}}: 2\female);
				``9 mi east Santo; Domingo, S.L.P.,; Mexico~~~XI-14-68; Veryl V. Board'' (\texttt{\textbf{TAMU}}: 2 \male).
		\subsubsection*{Distribution}
			\#
		\subsubsection*{Natural history}
			Associated with spear globemallow [\textit{Sphaeralcea hastulata} A. Gray; Malvaceae].

	\subsection*{\textit{Minyomerus sculptilis} - sp. n.}
		\subsubsection*{Diagnosis}
		\subsubsection*{Description of female}
			\paragraph{Habitus}
				Length \# mm, width \# mm, length/width ratio \#, widest at anterior 1/5 of elytra.
				Integument orange-brown to black.
				Scales with variously interspersed colors ranging from slightly off-white or beige to golden brown to dark coffee brown.
				Setae sub-recumbent to sub-erect, white to brown in color.
			\paragraph{Manidbles}
				Covered with white scales, with 3 longer setae, and 1 shorter seta between these.
			\paragraph{Rostrum}
				Length \# mm, anterior portion \# broader than long, rostrum/pronotum length ratio \#, rostrum length/width ratio \#.
				Separation of rostrum from head generally obscure. 
				Dorsal outline of rostrum nearly square, anterior half of dorsal surface mesally concave, posterior half coarsely but shallowly punctate to rugose. 
				Rostrum in lateral view nearly square; apical margin bisinuate and emarginate, with 2 pairs of large vibrissae. 
				Nasal plate defined by Y-shaped, impressed lines, convex, integument covered with white scales.
				Margins of mandibular incision directed \#\td outward dorsally in frontal view. 
				Ventrolateral sulci strongly defined, beginning as a narrow sulcus posteriad of insertion point of mandibles, running parallel to scrobe, terminating in a ventral fovea.
			\paragraph{Antennae}
				Dorsal margin of scrobe overhanging broadly (not forming a minute tooth).
				Funicle slightly longer than scape.
				Scape extending Brassicaceae  to posterior 1/4 of eye.
				Club nearly 3\x as long as wide.
			\paragraph{Head}
				Eyes globular, anterodorsal margin of each eye impressed, posterior margin slightly elevated from lateral surface of head; eyes separated in dorsal view by 5\x their anterior-posterior length, set off from anterior prothoracic margin by 1/4 of their anterior-posterior length.
				Head between eyes rugose and slightly bulging.
			\paragraph{Pronotum}
				Length/width ratio \#; widest near anterior 2/5.
				Anterior margin arcuate, subtly incurved mesally, and somewhat produced dorsally; anterior constriction broad, posterior margin slightly arcuate.
				Pronotum in lateral view with setae that reach beyond anterior margin; these setae becoming slightly longer and more erect laterally.
				Anterolateral margin with a reduced tuft of 3-6 post-ocular vibrissae present, emerging near ventral 1/2 of eye, and stopping just below ventral margin of eye; vibrissae varying in length from 1/2\x anterior-posterior length of eye to a maximum length similar to anterior-posterior length of eye.
			\paragraph{Scutellum}
				Exposed, margins straight.
			\paragraph{Pleurites}
				Metepisternum nearly hidden by elytron except for triangular extension.
			\paragraph{Thoracic sterna} 
				Mesocoxal cavities separated by 1/3\x width of mesocoxal cavity. 
				Metasternum with transverse sulcus not apparent; metacoxal cavities widely separated by ca. 2\x their width.
			\paragraph{Legs}
				Profemur/pronotum length ratio \#; profemur with distal 1/6 produced ventrally as a slightly rounded, sub-rectangular projection covering tibial joint; condyle of tibial articulation occupying 4/5 of distal surface and 1/6 length of femur. 
				Protibia/profemur length ratio \#; protibial apex with ventral setal comb recessed in a subtly incurved groove; mucro not apparent. 
				Protarsus with tarsomere III 1.5\x as long as II; wider than long. 
				Metatibial apex with almond shaped convexity ringed by 10-12 short, spiniform setae.
			\paragraph{Elytra}
				Length/width ratio \#; widest at anterior 1/5; anterior margins jointly 1.5-2\x wider than posterior margin of pronotum; lateral margins gently converging after anterior 1/5, more strongly converging in posterior 1/4. 
				Posterior declivity angled at 65-70\td to main body axis. Elytra with 10 complete striae; striae broadly sculpted; punctures faint beneath appressed scales, separated by 5-7\x their diameter; intervals elevated, with every second interval, beginning at elytral suture, more strongly raised than adjacent intervals.
			\paragraph{Abdominal sterna}
				Ventrite III anteromesally incurved around a fovea located mesally on anterior margin, posterior margin elevated and set off from IV along lateral 1/3s of its length. 
				Sternum VII mesally 2/3\x as long as wide; anterior margin straight.
			\paragraph{Tergum}
				Pygidium sub-cylindrical; medial 1/2 of anterior 3/5 of pygidium less sclerotized.
			\paragraph{Sternum VIII}
				Anterior laminar edges of spiculum ventrale each incurved forming a 125\td angle with lateral margin; lamina more sclerotized medially; posterior margin medially incurved.
			\paragraph{Ovipositor}
				Coxites as long as broad; styli as long as coxites, glabrous.
			\paragraph{Spermatheca}
				S-shaped; collum short, apically with a large, hood-shaped projection roughly aligned with central axis of corpus, nearly equal in length to bulb of ramus; collum sub-contiguous with, and angled at 30\td to ramus; ramus elongate, sub-cylindrical to slightly bulbous, 3/4\x thickness of corpus, with a short stalk oriented at ca. 45\td to the corpus; corpus swollen, 1.3\x thicknes of ramus; cornu short, 2.5-3\x length or ramus, recurved and strongly arched in basal 1/2, forming an inner angle of ca. 80\td, feebly sinuate thereafter, with apical 1/2 expanded, then abruptly constricted near apical 1/4 to a fine point.
		\subsubsection*{Description of male}
			Similar to female, except where noted.
			\paragraph{Habitus}
				Length \# mm, width \# mm, length/width ratio \#. Rostrum length \# mm, rostrum/pronotum length ratio \#, rostrum length/width ratio \#. Pronotum length/width ratio \#. Profemur/pronotum length ratio \#, protibia/profemur length ratio \#. Elytra length/width ratio \#.
			\paragraph{Elytra}
				Elytral declivity slightly less angulate than female, forming a 60\td angle to main body axis, but otherwise as in female.
			\paragraph{Abdominal sterna}
				Sternum VII 1/2 \x as long as wide, posterior margin feebly arcuate mesally.
			\paragraph{Tergum}
				Pygidium (tergum VIII) with mesal 1/3 of posterior margin subtly incurved; posterior 2/3 punctate; anterior 1/3 rugose.
			\paragraph{Sternum VIII}
				Consisting of 2 sub-triangular sclerites; antero-laterally with a sharply-pointed projection as long as anterior-posterior length of triangular portion of sclerite.
			\paragraph{Aedeagus}
				Length/width ratio \#; lateral margins parallel, more strongly converging in region of ostium. 
				In lateral view, width of pedon even throughout in anterior 2/3, ventral margins in posterior 1/3 becoming straight towards apex, then curving to meet dorsal margins at a sharp apical point; apex acutely angulate. 
				Flagellum without apparent sclerite.
		\subsubsection*{Comments}
			Due to the limited number of specimens of this species, dissections of mouthparts could not be performed.
		\subsubsection*{Etymology}
			Named in reference to the elevated elytral intervals, which give this species a sculpted appearance; sculptilis = sculpted; Latin adjective \citep{brown1956}.
		\subsubsection*{Material examined}
			\paragraph{Holotype}
				\female~``Burley, Idaho; \#7, 5-20-32; \underline{A.} \underline{tridentata}; David E. Fox'' (\texttt{\textbf{USNM}}).
			\paragraph{Paratypes}
				``Milner, Idaho; \#5a, 7-9-31; S. pestifer; David E. Fox'' (\texttt{\textbf{USNM}}: 1 \female);
				``Hazelton, Ida; \#10~~~4/29/30; N. altissma'' (\texttt{\textbf{USNM}}: 1 \male)
		\subsubsection*{Distribution}
			\#
		\subsubsection*{Natural history}
			Associated with big sagebrush [\textit{Artemisia tridentata} Nutt.; Asteraceae], tumbleweed [\textit{Salsola tragus} L.; Amaranthaceae], tall tumblemustard [\textit{Sisymbrium altissimum} L.; Brassicaceae].

	\subsection*{\textit{Minyomerus tylotos} - sp. n.}
		\subsubsection*{Diagnosis}
		\subsubsection*{Description of female}
			\paragraph{Habitus}
				Length \# mm, width \# mm, length/width ratio \#, widest at anterior 1/6 of elytra.
				Integument orange-brown to black. 
				Scales with variously interspersed colors ranging from slightly off-white or beige to manila/tan to dark coffee brown, in some specimens appearing semi-translucent (in others opaque).
				Setae linear to apically explanate, appearing minutely spatulate, sub-recumbent to sub-erect, tan to brown in color.
			\paragraph{Manidbles}
				Covered with white scales, with 2-3 longer setae, and 1-3 shorter setae between these.
			\paragraph{Maxillae}
				Cardo bifurcate at base with an inner angle of ca. 90\td, arms roughly equal in length and width, arms of bifurcation equal in length to apically outcurved arm. 
				Stipes subrectangular, 1.5\x wider than long, roughly equal in width to inner arm of bifurcation of cardo, glabrous. 
				Galeo-lacinial complex nearly extending to apex of maxillary palpomere I; complex mesally membranous, laterally sclerotized, with sharp demarcation of sclerotized region separating palpiger from galeo-lacinial complex; setose in membranous area just adjacent to sclerotized region, setae covering 1/2 of dorsal surface area; dorsally with 5 apicomesal lacinial teeth; ventrally with 3 reduced lacinial teeth. 
				Palpiger with a single lateral seta, otherwise glabrous, anterior 1/2 membranous, posteriorly sclerotized.
			\paragraph{Maxillary palps}
				I apically oblique, apical end forming a 45\td angle with base, with 2 apical setae; II sub-cylindrical, with 1 apical seta.
			\paragraph{Labium}
				Prementum roughly pentagonal; apical margins arcuate, medially angulate; lateral margins feebly incurved; basal margin arcuate. 
				Labial palps 3-segmented, I with apical 1/2 projecting beyond margin of prementum, reaching apex of ligula; III slightly
longer than II.
			\paragraph{Rostrum}
				Length \# mm, anterior portion \# broader than long, rostrum/pronotum length ratio \#, rostrum length/width ratio \#.
				Separation of rostrum from head generally obscure. 
				Dorsal outline of rostrum nearly square, anterior half of dorsal surface feebly impressed, posterior half coarsely but shallowly punctate to rugose. 
				Rostrum in lateral view nearly square; apical margin strongly bisinuate and emarginate, appearing medially notched, with 2 large vibrissae. 
				Nasal plate lacking distinct impressions, having instead a poorly defined anteromesal convexity, integument completely and evenly covered with white scales. 
				Margins of mandibular incision directed \#\td outward dorsally in frontal view. 
				Ventrolateral sulci weakly defined as a broad concavity dorsad of insertion point of mandibles, running parallel to scrobe, becoming flatter posteriorly and disappearing ventrally.
				Dorsal surface of rostrum with median fovea short and linear, or punctate.
				Rostrum ventrally with subparallel sulci beginning at corners of oral cavity and continuing halfway to back of head.
			\paragraph{Antennae}
				Minute tooth formed by overhanging dorsal margin of scrobe anterior to margin of eye by 1/3 of length of eye.
				Scape extending to posterior margin of eye.
				Terminal funicular antennomere lacking appressed scales, having instead a covering of apically-directed pubescence with interspersed sub-erect setae.
				Club nearly 3\x as long as wide.
			\paragraph{Head}
				Eyes globular and somewhat elongate, strongly impressed, slanted ca. 45\td antero-ventrally; eyes separated in dorsal view by 4\x their anterior-posterior length, set off from anterior prothoracic margin by 1/4 of their anterior-posterior length. 
				Head between eyes punctate and protuberant.
			\paragraph{Pronotum}
				Length/width ratio \#; widest near anterior 2/5; somewhat globular. 
				Anterior margin arcuate, but feebly incurved mesally, lateral margins evenly curved and widening into a bulge just anteriad of midpoint of pronotum, posterior margin straight, with a slight mesal incurvature. 
				Pronotum in lateral view with transverse ventrolateral sulci strongly excavated and distinctly sculptured; with short, recumbent to suberect setae that barely attain or reach just beyond anterior margin; these setae becoming shorter and more erect laterally, reaching a maximum length nearly equal to length of eye; dorsally, these setae become uniquely apically explanate, with a longitudinal, medial, ridgelike portion that tapers to either side apicolaterally.
				Anterolateral margin with a single ocular vibrissa present, emerging near ventral margin of eye; vibrissa achieving a maximum length of 2/5 of anterior-posterior length of eye.
			\paragraph{Scutellum}
				Not exposed.
			\paragraph{Pleurites}
				Metepisternum nearly hidden by elytron except for triangular extension.
			\paragraph{Thoracic sterna} 
				Mesocoxal cavities separated by 1/3\x width of mesocoxal cavity. 
				Metasternum with transverse sulcus not apparent; metacoxal cavities widely separated by ca. 3\x their width.
			\paragraph{Legs}
				Profemur/pronotum length ratio \#; profemur with distal 1/5 produced ventrally as a sub-rectangular projection covering tibial joint; condyle of tibial articulation occupying 4/5 of distal surface and 1/5 length of femur. 
				Protibia/profemur length ratio \#; protibial apex with ventral setal comb recessed in a subtly incurved groove; mucro present as an acute, medially-projected tooth, which is approximately equal in length to surrounding setae. 
				Protarsus with tarsomere III 2\x as long as II; wider than long. 
				Metatibial apex with weakly projecting, poorly defined, narrow convexity laterally flanged by 5 short, spiniform setae.
			\paragraph{Elytra}
				Length/width ratio \#; widest at anterior 1/6; anterior margins jointly 1.5-2\x wider than posterior margin of pronotum; lateral margins nearly straight and subparallel after anterior 1/5, converging in posterior 1/3. 
				Posterior declivity angled at 70-75\td to main body axis. Elytra with 10 complete striae; striae broadly sculpted; punctures broad and faint beneath appressed scales, separated by 4-5\x their diameter; intervals elevated.
			\paragraph{Abdominal sterna}
				Ventrite III anteromesally incurved around a fovea located mesally on anterior margin, posterior margin elevated and set off from IV along lateral 3/8s of its length. 
				Sternum VII mesally 2/3\x as long as wide; setae slightly lengthening, and becoming medially directed in posterior 1/3; anterior margin weakly curved; posterior margin distinctly incurved mesally, appearing broadly notched; surface of sternite concave, appearing broadly foveate, immediately anteriad of marginal incurvature.
			\paragraph{Tergum}
				Tergum VII mesally incurved.
				Pygidium sub-cylindrical; medial 1/3 of anterior 2/3 of pygidium less sclerotized, with a patch of very short, fine setae.
			\paragraph{Sternum VIII}
				Anterior laminar edges each incurved forming a 130\td angle with lateral margin; slightly less sclerotized medially between arms; posterior margin medially incurved.
			\paragraph{Ovipositor}
				Coxites as long as broad; styli with 3 setae near the base.
			\paragraph{Spermatheca}
				?-shaped; collum short, apically with a large, angulate, hood-shaped projection angled at 45\td to corpus, sub-equal in length to ramus and contiously aligned with curvature of bulb of ramus; collum sub-contiguous with, and angled at ca. 60\td to ramus; ramus basally elongate and constricted, forming a stalk, 1/3\x length of collum, bulbous apically, 3\x thicker than stalk; corpus not swollen, of equal thickness to collum and cornu; cornu elongate, apically, gradually narrowed, strongly recurved in basal 1/3, straight along mesal 1/3, and curved near apical 1/3 such that apex is parallel to collum and corpus.
		\subsubsection*{Description of male}
			Not available or known.
		\subsubsection*{Comments}
		\subsubsection*{Etymology}
			Named in reference to the short, apically explanate setae interspersed throughout the dorsum, which give this species a distinctly ``knobbed'' appearance; tylotos = knobby; Greek adjective \citep{brown1956}.
		\subsubsection*{Material examined}
			\paragraph{Holotype}
				\female~``H. O. Canyon,; Davis Mts., Texas; Jeff Davis County; VII-20-1968, 6200'; J. E. Hafernik'' (\texttt{\textbf{TAMU}}).
			\paragraph{Paratypes}
				``24 mi. wsw. Ft. Davis; Jeff Davis Co., Texas; August 17, 1969; Board \& Hafernik'' (\texttt{\textbf{TAMU}}: 1 \female);
				``USA Texas Jeff Davis Co.; 4.1 mi. S. Fort Davis; sweeping grasses-weeds; 4750' . 19.VII.82; R.S. Anderson'' (\texttt{\textbf{CMNC}}: 1 \female)
		\subsubsection*{Distribution}
			\#
		\subsubsection*{Natural history}
			No host plant associations have been documented.
			It is unknown whether this species is parthenogenetic.

\section*{Checklist of species}
	\#
\section*{Identification key}
	\#
\section*{Phylogenetic placement of new species}
	\#
\section*{Acknowledgments}

\newpage
\bibliography{references} 
%just references in windows, use references.bib in linux
\end{document}

### 2018-03-01 tex/manuscript.tex
subsubsection, not subsection
Added a brief intro and edited methods

@@
 \section*{Introduction}
-	\#
+	The weevil genus \textit{Minyomerus} Horn, 1876 is currently assigned to the tribe Tanymecini Lacordaire, 1863 (Curculionidae: Entiminae). 
+	The genus was recently revised and includes a total of 17 described species distributed throughout the desert and plains regions of North America.
+	Since the publication of the monographic revision of \textit{Minyomerus}, we have discovered four additional undescribed species, known to us only from limited numbers of specimens, yet falling neatly into the generic delimitation of \textit{Minyomerus} \textit{sensu} Jansen and Franz 2015.
+	Here we describe these species and provide images of the holotypes and of dissected genitalia for the purpose of identification.
+	We additionally conduct a morphological phylogenetic analysis of the genus to clarify the placement of these new taxa within \textit{Minyomerus}, based on the analysis provided in our previous work.
+	An emended identification key to the species of \textit{Minyomerus} is given along with information on the geographic distribution of the herein described species.
+	Where possible, we make note of host-plant records and briefly consider the historical biogeographic relationships of the new species.
+	A more extensive discussion of the habits, distribution, and delimitation of the genus (and all of its constituent species) can found in the generic revision.
+
 \section*{Materials and methods}
+	The keen reader will note a certain similarity between the methods used in this manuscript with those of Jansen and Franz 2015. 
+	Rather than merely referencing the monograph as a source of inspiration, we feel it is better to provide a fully transparent and updated accounting of the methods used to generate the species descriptions, distribution maps, and phylogeny herein.
+	Most notably, we retain the format of the species descriptions, whereby we emphasize only those characters that vary significantly from the generic description, as explained below.
 	\paragraph{Natural history observations} 
-		Members of the genus Minyomerus are typically found on a variety of host plants, as indicated following each species account.
-		Many species are likely generalists with regards to their host plant spectrum. 
-		Adult weevils are most commonly observed on the leaves and branches of the host where they feed on the leaf tissue. Eggs, larvae, and pupae remain unknown. 
-		The larvae are probably root feeders, as observed in the tanymecine genus Tanymecus Germar, 1817 (Howden 1975). 
-		They typically inhabit arid regions, especially deserts, throughout southwestern North America, including the Mojave, Sonoran, Chihuahuan, and Great Basin Deserts. 
-		They also occur in semi-arid regions of the Great Plains, on the Colorado Plateau, and throughout Baja California, Mexico. 
-		The adults apparently disperse without flight, as the hind wings and associated flight structures of all species in the genus are greatly reduced and not readily apparent after dissections.
-		In several species only females are known, and some are putatively considered parthenogenetic, as indicated in the respective descriptions.
+		Members of the genus \textit{Minyomerus} may be found on a variety of host plants, as indicated following each description.
+		While many species appear to be generalists, the adults are consistently observed on the leaves and branches of the host feeding on the leaf tissue; all other life stages remain unknown.
+		Members of this genus are commonly found in deserts throughout western North America, including the Mojave, Sonoran, Chihuahuan, and Great Basin Deserts. 
+		Furthermore, the range of the genus extends through the semi-arid regions of the Great Plains, the Colorado Plateau, and Baja California, Mexico. 
+		The adults are flightless, as the hind wings and associated flight structures of all species are either greatly reduced or not readily apparent in dissection.
 
@@
 		Georeferencing of localities was performed with Google Earth (Google Inc. 2009–2015) and reported in decimal degrees.
-		Taxonomic names for associated host plants are used in accordance with Munz and Keck (1973) and SEINet (2015).
-		The set of existing \textit{Minyomerus} [JF2015] specimens used in the revision of Jansen and Franz 2015 was supplemented with material from the following collections, using the codens of Arnett et al.
+		Taxonomic names for associated host plants are used in accordance with Munz and Keck (1973) and SEINet (2017).
+		The existing set of \textit{Minyomerus} specimens used in the revision of Jansen and Franz 2015 was supplemented with material from the following collections, using the codens of Arnett et al.
 (1993):
@@
 	\paragraph{Morphological analysis}
-		The herein utilized systematic and descriptive approach follows Franz (2010a, 2010b, 2012).
+		Our systematic and descriptive approach is complementary to Jansen and Franz 2015, which in turn follows Franz (2010a, 2010b, 2012).
 		Terminology for exterior morphology is in general accordance with Torre-Bueno (Nichols 1989).
@@
 			and Oberprieler et al. (2014) and Howden (1995) for male and female terminalia.
-		All measurements were taken using a Leica M205 C stereomicroscope and attached computer running the software Leica Application Suite (LAS), version 4.1.0.
-		The overall body length and width were measured in dorsal view as the maximum distance between the apex of the rostrum and the apex of the elytra, and the maximum width of the elytra, respectively.
-		The length of the rostrum was measured in dorsal view as the distance extending from the apex of the epistoma to the anterior margin of the eyes.
-		The width of the rostrum was measured in dorsal view as the maximum distance between the dorsal margins of the rostrum near the point of antennal insertion.
-		The length of the pronotum was measured in dorsal view as the length along the midline from the anterior margin to the posterior margin.
-		The width of the elytra was measured in dorsal view as the maximum distance between the lateral margin and the elytral suture.
-		Other length and width measurements were performed in dorsal orientation, as the maximum length and width of the corresponding structure (profemur, protibia, elytron, and aedeagus).
-		Images of mouthparts and terminalia were produced with the Leica microscope equipment, whereas habitus photographs were created with a Visionary Digital Passport II sytem using a Canon EOS Mark 5D II camera.
 
-		Species of Minyomerus [JF2015] recognized in this revision were delimited through application of the phylogenetic species concept sensu Wheeler and Platnick (2000).
-		Species descriptions follow the inferred phylogenetic sequence (see details below).
-		The genus-level description for Minyomerus [JF2015] highlights characters present in all members and accounts for their apparent variability.
-		Consequently, the species descriptions represent unique and complementary accounts of the character states observed in each species, including their variability, and excepting characters that are invariate within the genus as specified in the higher-level description of Minyomerus.
-		Likewise, descriptions of males in the genus- and species-level accounts emphasize characters that are variable and sufficiently different from those of the females to merit recognition.
-		Some redundancy occurs between genus and species descriptions when discussing characters that vary widely within single species, and also between species descriptions where a character exhibits considerable variation in some species yet is invariant in others.
-		The key to identifying species of Minyomerus is arranged with emphasis being placed on the most readily observable diagnostic characters.
-		The revision is arranged with the species descriptions appearing first, followed by the key to species, and then by the phylogenetic results.
+		Measurements were taken with a Leica M205 C stereomicroscope and associated software, Leica Application Suite (LAS), version 4.1.0.
+		Overall body length and width were measured in dorsal view as the maximum distance between the rostral and elytral apices, and the maximum width of both elytra, respectively.
+		Rostral length was measured in dorsal view as the distance between the epistomal apex and the anterior margin of the eyes.
+		Rostral width was measured in dorsal view as the maximum distance between the dorsal margins of the rostrum near the point of antennal insertion.
+		Pronotal length was measured in dorsal view as the length along the midline between the anterior and posterior margins.
+		The width of an individual elytron was measured in dorsal view as the maximum distance between the lateral margin and the elytral suture.
+		Other length and width measurements were also performed in dorsal orientation, using the maximum length and width of the corresponding structure (profemur, protibia, elytron, and aedeagus).
+		Images of mouthparts and terminalia were produced with the Leica microscope equipment, while habitus photographs were created with a Visionary Digital Passport II sytem using a Canon EOS Mark 5D II camera.
+
+		Herein recognized species of \textit{Minyomerus}  were delimited through application of the phylogenetic species concept \textit{sensu} Wheeler and Platnick (2000).
+		Species descriptions are in alphabetical order, rather than phylogetic order, for ease of use.
+		The species descriptions in this manuscript represent unique and complementary accounts of the character states observed in each species, including their variability, but except those characters invariant within the genus as specified in the higher-level description of \textit{Minyomerus}.
+		Likewise, descriptions of males emphasize characters that are variable and sufficiently different from those of the females to merit recognition.
+		The key to identifying species of \textit{Minyomerus} is arranged with emphasis being placed on the most readily observable diagnostic characters.
+		This manuscript is arranged with the species descriptions appearing first, followed by the key to species, and then by the phylogenetic results.
 
 	\paragraph{Phylogenetic analysis}
-		The morphological cladistic analysis includes 22 terminal taxa; with 17 ingroup and 5 outgroup terminals.
+		The morphological cladistic analysis includes 26 terminal taxa; with 21 ingroup and 5 outgroup terminals.
 		Following resolution of species identities and boundaries, the ingroup terminals were represented by six species previously assigned to Minyomerus sec.
@@
 	\paragraph{Species distribution modeling}
-		We used the modeling program Maxent, Version 3.3, to generate habitat models for the species of Minyomerus [JF 2015] (Figs 50–52) based on the documented occurrence records (Phillips et al.
+		We used the modeling program Maxent, Version 3.4, to generate habitat models for the species of Minyomerus [JF 2015] (Figs 50–52) based on the documented occurrence records (Phillips et al.
 2004, 2006; Elith et al.
@@
 		The default settings “Max number background points”, set to 100,000, and “Iterations” set to 10 and with cross-validation, were applied to leverage all available locality data.
-		However, no models could be created for three species with single documented localities; and only a single-iteration habitat model could be generated for a fourth species due to limited information data.
+		However, no models could be created for one species a single documented locality.
 		We selected 19 bioclimatic variables and elevation as Environmental Layers in Maxent, obtained from WorldClim (see Hijmans et al. 2005 and the associated website for further detail on variables).
@@
 				\female~``Carlsbad, N.M.; Geococcyx calif; 144640'' (\texttt{\textbf{USNM}}).
-		\subsection*{Distribution}
+		\subsubsection*{Distribution}
 			\#

### 2018-03-04 tex/manuscript.tex
Added checklist and finalized cladistics

@@
 \section*{Introduction}
-	The weevil genus \textit{Minyomerus} Horn, 1876 is currently assigned to the tribe Tanymecini Lacordaire, 1863 (Curculionidae: Entiminae). 
+	The weevil genus \textit{Minyomerus} Horn, 1876 is currently assigned to the tribe Tanymecini Lacordaire, 1863, subtribe Tanymecina Lacoirdaire, 1863 (Curculionidae: Entiminae). 
 	The genus was recently revised and includes a total of 17 described species distributed throughout the desert and plains regions of North America.
-	Since the publication of the monographic revision of \textit{Minyomerus}, we have discovered four additional undescribed species, known to us only from limited numbers of specimens, yet falling neatly into the generic delimitation of \textit{Minyomerus} \textit{sensu} Jansen and Franz 2015.
+	Since the publication of our monographic revision of \textit{Minyomerus}, we have discovered four additional undescribed species, known to us only from limited numbers of specimens, yet falling neatly into the generic delimitation of \textit{Minyomerus} \textit{sensu} Jansen and Franz 2015.
 	Here we describe these species and provide images of the holotypes and of dissected genitalia for the purpose of identification.
@@
 \section*{Materials and methods}
-	The keen reader will note a certain similarity between the methods used in this manuscript with those of Jansen and Franz 2015. 
-	Rather than merely referencing the monograph as a source of inspiration, we feel it is better to provide a fully transparent and updated accounting of the methods used to generate the species descriptions, distribution maps, and phylogeny herein.
-	Most notably, we retain the format of the species descriptions, whereby we emphasize only those characters that vary significantly from the generic description, as explained below.
+	The keen reader will note the alignment of the methods used in this manuscript with those of Jansen and Franz 2015. 
+	For convenience and transparency, we provide an updated account of the methods used to generate the species descriptions, distribution maps, and phylogeny herein.
+	Most importantly, we retain the format of the species descriptions, whereby we emphasize only those characters that vary significantly from the generic description, as explained below.
+
 	\paragraph{Natural history observations} 
@@
 		Members of this genus are commonly found in deserts throughout western North America, including the Mojave, Sonoran, Chihuahuan, and Great Basin Deserts. 
-		Furthermore, the range of the genus extends through the semi-arid regions of the Great Plains, the Colorado Plateau, and Baja California, Mexico. 
+		Furthermore, the range of the genus extends through the semi-arid regions of the Great Plains, the Colorado Plateau, and Baja California, M\'{e}xico. 
 		The adults are flightless, as the hind wings and associated flight structures of all species are either greatly reduced or not readily apparent in dissection.
@@
 		Species descriptions are in alphabetical order, rather than phylogetic order, for ease of use.
-		The species descriptions in this manuscript represent unique and complementary accounts of the character states observed in each species, including their variability, but except those characters invariant within the genus as specified in the higher-level description of \textit{Minyomerus}.
+		The species descriptions in this manuscript represent unique and complementary accounts of the character states observed in each species, including their variability, but excepting those characters invariant within the genus as specified in the higher-level description of \textit{Minyomerus}.
 		Likewise, descriptions of males emphasize characters that are variable and sufficiently different from those of the females to merit recognition.
@@
 		The morphological cladistic analysis includes 26 terminal taxa; with 21 ingroup and 5 outgroup terminals.
-		Following resolution of species identities and boundaries, the ingroup terminals were represented by six species previously assigned to Minyomerus sec.
-O’Brien and Wibmer (1982), Piscatopus griseus sec.
-Sleeper (1960), and ten newly recognized species.
-		The lack of prior phylogenetic analyses of Minyomerus and closely related lineages made it necessary to sample outgroups fairly broadly while remaining focused on North American lineages that are are putative close relatives of the ingroup (Nixon and Carpenter 1993).
-		The tribe Tanymecini [non-focal] is cosmopolitan, with the subtribe Tanymecina [non-focal] containing the majority of New World species diversity in the tribe (Alonzo-Zarazaga and Lyal 1999).
-		Accordingly, four outgroup terminals are represented by species belonging to separate genera in the Tanymecina [non-focal]; viz.
-Pandeleteius cinereus (Horn, 1876) [non-focal], Pandeleteinus subcancer Howden, 1969 [non-focal], Isodrusus debilis Sharp, 1911 [non-focal], and Isodacrys buchanani Howden, 1961 [non-focal].
-		Because generic relationships in the Tanymecini [non-focal] remain unresolved, it was deemed prudent to find a relatively far-removed taxon to root the cladogram that would nevertheless display states that are applicable to the ingroup for all characters under consideration (Rieppel 2007; Franz 2014).
-		For this purpose we select the North American species Sitona californicus (Fahraeus, 1840) [non-focal], representing the tribe Sitonini Gistel, 1856 [non-focal].
-		The character matrix was edited and phylogenetic results reviewed and reconnected to the input using the WinDada and WinClados interfaces of WinClada (Nixon 2002).
+		The ingroup terminals were represented by 17 species previously assigned to \textit{Minyomerus} sec. Jansen and Franz (2015) and four newly recognized species.
+		In keeping with our previous analysis, we sampled outgroups fairly broadly while remaining focused on North American lineages that are putative close relatives of the ingroup (Jansen and Franz 2015, Nixon and Carpenter 1993).
+		Although the tribe Tanymecini [non-focal] is cosmopolitan, the majority of New World species diversity in the tribe may be found in the subtribe Tanymecina [non-focal] (Alonzo-Zarazaga and Lyal 1999).
+		Thus, four of the five outgroup terminals are represented by species belonging to separate genera in the Tanymecina [non-focal]; viz.
+Isodacrys buchanani Howden, 1961 [non-focal], Isodrusus debilis Sharp, 1911 [non-focal], Pandeleteinus subcancer Howden, 1969 [non-focal], and Pandeleteius cinereus (Horn, 1876) [non-focal].
+		Because generic relationships in the Tanymecini [non-focal] remain unresolved, we selected a relatively far-removed taxon to root the cladogram that would nevertheless display states applicable to the ingroup for characters under consideration (Rieppel 2007; Franz 2014).
+		To this end we used the North American species Sitona californicus (Fahraeus, 1840) [non-focal], of the tribe Sitonini Gistel, 1856 [non-focal].
+
+		The character matrix was edited and phylogenetic results viewed using the WinDada and WinClados interfaces of WinClada, respectively (Nixon 2002).
 		The character sequence follows that of the taxonomic descriptions.
 		The most parsimonious tree and character state optimizations were inferred under parsimony using NONA (Goloboff 1999).
-		An unconstrained heuristic search of tree space for the 22-terminal matrix was conducted using the commands: hold 100001, mult*1000, hold/100, with mult*max* selected.
-		Bootstrap support was inferred in WinClada using the parameters of 1000 replications, hold 1000, hold/100, mult*10, “Don’t do max*”, and “Save consensus”.
-		Finally, Bremer support values (Bremer 1994) were calculated in NONA using the commands hold 20000, suboptimal 20, and bsupport 20.
+		An unconstrained heuristic search was conducted using the commands: \texttt{hold 100001}, \texttt{mult*1000}, \texttt{hold/100}, with \texttt{mult*max*} selected.
+		Bootstrap support was inferred in WinClada using the parameters of \texttt{1000 replications}, \texttt{hold 1000}, \texttt{hold/100}, \texttt{mult*10}, \texttt{Don’t do max*}, and \texttt{Save consensus}.
+		Finally, Bremer support values (Bremer 1994) were calculated in NONA using the commands: \texttt{hold 20000}, \texttt{suboptimal 20}, and \texttt{bsupport 20}.
+
 	\paragraph{Species distribution modeling}
-		We used the modeling program Maxent, Version 3.4, to generate habitat models for the species of Minyomerus [JF 2015] (Figs 50–52) based on the documented occurrence records (Phillips et al.
+		We used the modeling program Maxent, Version 3.4, to generate habitat models for the species of Minyomerus [JF 2015] (Figs.~\#) based on documented occurrence records (Phillips et al.
 2004, 2006; Elith et al.
 2011).
-		The default settings “Max number background points”, set to 100,000, and “Iterations” set to 10 and with cross-validation, were applied to leverage all available locality data.
-		However, no models could be created for one species a single documented locality.
-		We selected 19 bioclimatic variables and elevation as Environmental Layers in Maxent, obtained from WorldClim (see Hijmans et al. 2005 and the associated website for further detail on variables).
-		The layers were downloaded by tile (zones 11–13 and 21–23), with a 30 arc-second resolution (projected using WSG 84) to provide adequate coverage of the full distribution of Minyomerus [JF2015].
-		These tiles were assembled, by layer, into composite maps of six tiles each, using QGIS, Version 2.8.1 ‘Wien’, prior to species distribution modeling (Quantum GIS Development Team 2015).
-		After modeling, the raster files of the predictive probabilities were imported into GIS.
-		Each file was designated a specific color, and each pixel in the raster grid was assigned a linearly interpolated saturation of that color, with increasing saturation denoting an increased probability of successful prediction of species presence at that point.
-		Pixels with a value below 0.50 were rendered transparent so that the model only shows regions with a greater than 50\% chance of successful prediction.
+		The default settings were adjusted to \texttt{Max number background points = 100,000} and \texttt{Iterations = 10}.
+		Cross-validation was used to leverage all available locality data; however, no models could be created for species with two or fewer documented localities.
+		We selected 19 bioclimatic variables and elevation as Environmental Layers in Maxent, obtained from WorldClim (see Hijmans et al. 2005).
+		The layers were downloaded by tile (zones 11–13 and 21–23), with a 30 arc-second resolution (projected using WSG 84) to provide adequate coverage of the full distribution of the genus.
+		Layerwise assembly of tiles was done using QGIS, Version 2.18.16 `Las Palmas', creating composite maps of six tiles each to use in species distribution modeling (Quantum GIS Development Team 2017).
+
+		The rasterized predictive probabilities were imported into QGIS, where each file was designated a specific color. 
+		Each pixel in the raster was assigned a linearly interpolated saturation of that color, with increasing saturation denoting an increased probability of successful prediction of species presence at that point.
+		Pixels with a value below 0.50 were rendered transparent so that the maps only show regions with a greater than 50\% chance of successful prediction.
 		The raster files were clipped to remove extraneous predicted regions based on: (1) predictive probability (i.e., removing large areas with only transparent pixels) and (2) geographic extent (accounting for endemicity).
-		For instance, species endemic to Baja California Sur, Mexico, do not require a predictive model for bioclimatically similar habitats in Canada.
-		The actual (documented) occurrence records are laid over the modeled habitat ranges as colored circles on the respetive maps (Figs 50–52), along with vector layers of country and state borders (Hijmans et al.
+		For example, a species endemic to the Snake River Valley of Idaho does not require a predictive model for bioclimatically similar habitats in the Chihuahuan Desert.
+		Documented occurrence records are laid over the modeled habitat ranges as colored circles on their respective maps (Figs.~\#), along with vector layers of country (white) and state (gray) borders (Hijmans et al.
 2012).
+
 \section*{Descriptions of new species}
@@
 		\subsubsection*{Diagnosis}
-			\#
+			\textit{Minyomerus ampullaceus} is best differentiated from other congenerics by its unique body shape, which most prominently features a strongly constricted, sub-cylindrical pronotum and greatly protuberant elytra; this combination gives the species a distinctly flask- or bottle-shaped appearance.
+			Due to the relatively poor condition of the scales and setae of the holotype, color and setation cannot be reliably used for identification.
+			Fortunately, the elytra themselves are unique in shape, and diagnostic, together nearly 2\x the width of the pronotum at their widest point, and nearly 3/4 as wide as long in dorsal view.
+			In lateral view the anterior and posterior declivities of the elytra are strongly abrupt, and nearly vertical; most notably, the anterior magin of the elytra projects strongly and characteristically dorsad of its articulation with the posterior pronotal margin.
+			The spermatheca is also quite distinct, having a highly elongate projection of the corpus aligned with midline of the ramus, which is basally tapered and angled at nearly 45\td to the corpus.
 		\subsubsection*{Description of female}
@@
 				Setae recumbent to sub-recumbent, white to brown in color.
-			\paragraph{Manidbles}
+			\paragraph{Mandibles}
 				Partially covered with white, slightly opalescent scales, with 3 longer setae, and 1 shorter seta between these.
@@
 				Profemur/pronotum length ratio \#; profemur with distal 1/5 produced ventrally as a rounded projection covering tibial joint; condyle of tibial articulation occupying 4/5 of distal surface and 1/5 length of femur.
-				Protibia/profemur length ratio \#; protibial apex with ventral setal comb recessed in an incurved groove; mucro present as a large, black, sub-triangular, medially-projected tooth, which is approximately equilateral and whose sides are subequal in length to surrounding setae.
+				Protibia/profemur length ratio \#; protibial apex with ventral setal comb recessed in an incurved groove; mucro present as a large, black, sub-triangular, medially-projected tooth, which is approximately equilateral and whose sides are sub-equal in length to surrounding setae.
 				Protarsus with tarsomere III 1.25\x as long as II; wider than long. 
@@
 			\paragraph{Elytra}
-				Length/width ratio \#; widest at anterior 1/3; anterior margins jointly 1.75\x wider than posterior margin of pronotum and strongly produced dorsally from margin of pronotum; lateral margins evenly rounded until posterior 1/3, more strongly rounded and converging thereafter.
+				Length/width ratio \#; widest at anterior 1/3; anterior margins jointly almost 2\x wider than posterior margin of pronotum and strongly produced dorsally from margin of pronotum; lateral margins evenly rounded until posterior 1/3, more strongly rounded and converging thereafter.
 				Posterior declivity angled at nearly 85\td to main body axis.
@@
 			\paragraph{Spermatheca}
-				Comma-shaped; collum expanded to form a long, cylindrical projection, subequal in length to ramus, 1/3\x width of corpus, angled at 45\td to corpus, apically with a reduced hood-shaped projection; ramus elongate, bulbous, slightly wider than thickness of corpus, basally constricted to form a short stalk; corpus not greatly swollen; cornu sub-equal in length to corpus and collum, recurved distally to form in inner angle of 60\td to corpus, straight and gradually narrowing along basal 2/3, with apical 1/3 abruptly narrowed, angled at 45\td to coprus, and tapering to a slight knob.
+				Comma-shaped; collum expanded to form a long, cylindrical projection, sub-equal in length to ramus, 1/3\x width of corpus, angled at 45\td to corpus, apically with a reduced hood-shaped projection; ramus elongate, bulbous, slightly wider than thickness of corpus, basally constricted to form a short stalk; corpus not greatly swollen; cornu sub-equal in length to corpus and collum, recurved distally to form in inner angle of 60\td to corpus, straight and gradually narrowing along basal 2/3, with apical 1/3 abruptly narrowed, angled at 45\td to coprus, and tapering to a slight knob.
 		\subsubsection*{Description of male}
@@
 		\subsubsection*{Distribution}
-			\#
+			This species is known only from Carlsbad, New Mexico (USA), from an unspecified locality; the location of the city is shown in Fig.~\#.
 		\subsubsection*{Natural history}
 			No host plant associations have been documented.
-			The label indicates "Geococcyx calif"; this is presumably a reference to \textit{Geococcyx californianus} (Lesson, 1829) [Cuculidae], the Greater Roadrunner, although it is unclear if the specimen was found on or near one of these birds (either living, dead, or in a nest).
+			The label indicates ``Geococcyx calif''; this is presumably a reference to \textit{Geococcyx californianus} (Lesson, 1829) [Cuculidae], the Greater Roadrunner, although it is unclear if the specimen was found on or near one of these birds (either living, dead, or in a nest).
 			\textit{Minyomerus} species are only known to be phytophagous, not parasitic, phoretic, or necrophagous, so we believe that this specimen was most likely found in a nest, and was present there only incidentally because the nest was constructed in the host plant of this specimen \citep{jansen2015}.
@@
 		\subsubsection*{Diagnosis}
-			\#
+			\textit{Minyomerus franko} is readily distinguished from other congenerics by the strikingly long setae of the anterior margin of the pronotum, which project laterally up to 80\td from the longitudinal axis of the body and achieve a maximum length at least equaling the diameter of the eye.
+			In addition, the setae lining the dorsal margin of the ocular impression are elongate and reach a length equal to 1/2 - 3/4\x the diameter of the eye.
+			The spermatheca has a short, somewhat bulbous corpus, with the ramus sub-equal in size and perpendicular to the corpus, and the collum is strongly recurved along the basal 1/3 of its length.
+			The aedeagus is relatively short and wide, and is abruptly constricted in the apical 1/5 of its length, thereafter tapered to a rounded point.
 		\subsubsection*{Description of female}
@@
 				Setae linear to slightly apically explanate, appearing minutely spatulate, sub-recumbent to sub-erect, white or brown in color.
-			\paragraph{Manidbles}
+			\paragraph{Mandibles}
 				Covered with white scales, with 3 longer setae, and 1-2 shorter setae between these.
@@
 				Profemur/pronotum length ratio \#; profemur with distal 1/5 produced ventrally as a sub-rectangular projection covering tibial joint; condyle of tibial articulation occupying 4/5 of distal surface and 1/5 length of femur.
-				Protibia/profemur length ratio \#; protibial apex with ventral setal comb recessed in a subtly incurved groove; mucro present as a large, black, sub-triangular, medially-projected tooth, which is approximately equilateral and whose sides are subequal in length to surrounding setae.
+				Protibia/profemur length ratio \#; protibial apex with ventral setal comb recessed in a subtly incurved groove; mucro present as a large, black, sub-triangular, medially-projected tooth, which is approximately equilateral and whose sides are sub-equal in length to surrounding setae.
 				Protarsus with tarsomere III 2\x as long as II; wider than long. 
@@
 			\paragraph{Elytra}
-				Length/width ratio \#; widest at anterior 1/3-1/4; anterior margins jointly 1.5\x wider than posterior margin of pronotum; lateral margins subparallel to slightly rounded after anterior 1/3, more strongly rounded and converging in posterior 1/3.
+				Length/width ratio \#; widest at anterior 1/3-1/4; anterior margins jointly 1.5\x wider than posterior margin of pronotum; lateral margins sub-parallel to slightly rounded after anterior 1/3, more strongly rounded and converging in posterior 1/3.
 				Posterior declivity angled at 70-85\td to main body axis.
@@
 		\subsubsection*{Distribution}
-			\#
+			This species has been found in San Luis Potos\'{i} and Tamaulipas (M\'{e}xico).
+			It is likely to be found throughout the Chihuahuan Desert and arid regions of south-central M\'{e}xico based on habitat similarity (Fig.~\#).
 		\subsubsection*{Natural history}
@@
 		\subsubsection*{Diagnosis}
+			\textit{Minyomerus sculptilis} is best distinguished from other congenerics by a combination of characters, as follows.
+			The interspersed setae on the body are linear and either brown or white.
+			The anterior margin of the pronotum bears a reduced tuft of post-ocular vibrissae.
+			The head is barely elevated between the eyes.
+			The ventrolateral sulci of  the rostrum are well defined.
+			The lateral face of each elytron has the intervals raised and well sculpted in appearance.
+			The spermatheca is distinct and has an elongate, annulate, basally tapered ramus, which is slightly thinner than corpus.
+			The cornu is strongly recurved in the basal half, giving it a uniquely sinuate appearance.
+			Both the corpus and cornu terminate in large, hood-shaped, explanate projections equal in size to the ramus.
+			The aedeagus is elongate, acutely angulate, and narrowing towards the apex more strongly in the region of the ostium.
 		\subsubsection*{Description of female}
@@
 				Setae sub-recumbent to sub-erect, white to brown in color.
-			\paragraph{Manidbles}
+			\paragraph{Mandibles}
 				Covered with white scales, with 3 longer setae, and 1 shorter seta between these.
@@
 		\subsubsection*{Distribution}
-			\#
+			This species has been found in three localities along the Snake River in Idaho (USA), and is thought to be endemic to the Snake River Valley (Fig.~\#).
 		\subsubsection*{Natural history}
@@
 		\subsubsection*{Diagnosis}
+			\textit{Minyomerus tylotos} is most readily distinguished from other congenerics by a combination of characters, as follows.
+			The nasal plate lacks distinct impressions, having instead a poorly defined anteromesal convexity completely and evenly covered with white scales.
+			The frons is protuberant and moderately punctate.
+			The entire body, including the legs, head, and venter, are clothed with brown, linear to minutely apically expanded setae, which are of similar length throughout and appear distinctly undifferentiated and uniform across body regions.
+			The body is somewhat bulky, with the pronotum protuberant laterally and globular in dorsal view.
+			The setae lining the anterodorsal margin of the pronotum uniquely apically explanate, with a longitudinal, medial, ridge-like portion that tapers to either side apicolaterally (visible at high magnification).
+			The lateral margins of the elytra are protuberant anteriorly and sub-parallel along the between anterior 1/5 and posterior 1/3 of their length.
+			The spermatheca has the corpus narrow throughout, equal in thickness to the collum.
+			The ramus is basally stalked and apically bulbous.
+			The collum exhibits a double-bend, and is recurved.
 		\subsubsection*{Description of female}
@@
 				Setae linear to apically explanate, appearing minutely spatulate, sub-recumbent to sub-erect, tan to brown in color.
-			\paragraph{Manidbles}
+			\paragraph{Mandibles}
 				Covered with white scales, with 2-3 longer setae, and 1-3 shorter setae between these.
@@
 				Cardo bifurcate at base with an inner angle of ca. 90\td, arms roughly equal in length and width, arms of bifurcation equal in length to apically outcurved arm. 
-				Stipes subrectangular, 1.5\x wider than long, roughly equal in width to inner arm of bifurcation of cardo, glabrous. 
+				Stipes sub-rectangular, 1.5\x wider than long, roughly equal in width to inner arm of bifurcation of cardo, glabrous. 
 				Galeo-lacinial complex nearly extending to apex of maxillary palpomere I; complex mesally membranous, laterally sclerotized, with sharp demarcation of sclerotized region separating palpiger from galeo-lacinial complex; setose in membranous area just adjacent to sclerotized region, setae covering 1/2 of dorsal surface area; dorsally with 5 apicomesal lacinial teeth; ventrally with 3 reduced lacinial teeth.
@@
 				Dorsal surface of rostrum with median fovea short and linear, or punctate.
-				Rostrum ventrally with subparallel sulci beginning at corners of oral cavity and continuing halfway to back of head.
+				Rostrum ventrally with sub-parallel sulci beginning at corners of oral cavity and continuing halfway to back of head.
 			\paragraph{Antennae}
@@
 				Anterior margin arcuate, but feebly incurved mesally, lateral margins evenly curved and widening into a bulge just anteriad of midpoint of pronotum, posterior margin straight, with a slight mesal incurvature.
-				Pronotum in lateral view with transverse ventrolateral sulci strongly excavated and distinctly sculptured; with short, recumbent to suberect setae that barely attain or reach just beyond anterior margin; these setae becoming shorter and more erect laterally, reaching a maximum length nearly equal to length of eye; dorsally, these setae become uniquely apically explanate, with a longitudinal, medial, ridgelike portion that tapers to either side apicolaterally.
+				Pronotum in lateral view with transverse ventrolateral sulci strongly excavated and distinctly sculptured; with short, recumbent to sub-erect setae that barely attain or reach just beyond anterior margin; these setae becoming shorter and more erect laterally, reaching a maximum length nearly equal to length of eye; dorsally, these setae become uniquely apically explanate, with a longitudinal, medial, ridge-like portion that tapers to either side apicolaterally.
 				Anterolateral margin with a single ocular vibrissa present, emerging near ventral margin of eye; vibrissa achieving a maximum length of 2/5 of anterior-posterior length of eye.
@@
 			\paragraph{Elytra}
-				Length/width ratio \#; widest at anterior 1/6; anterior margins jointly 1.5-2\x wider than posterior margin of pronotum; lateral margins nearly straight and subparallel after anterior 1/5, converging in posterior 1/3.
+				Length/width ratio \#; widest at anterior 1/6; anterior margins jointly 1.5-2\x wider than posterior margin of pronotum; lateral margins nearly straight and sub-parallel after anterior 1/5, converging in posterior 1/3.
 				Posterior declivity angled at 70-75\td to main body axis.
@@
 			Not available or known.
-		\subsubsection*{Comments}
 		\subsubsection*{Etymology}
@@
 		\subsubsection*{Distribution}
-			\#
+			This species has been found in three localities near the Davis Mountains in Jeff Davis County and in nearby Presidio County, Texas (USA).
+			Habitat models (Figs.~\#) predict that this represents the northeastern extent of its range, indicating a strong likelihood that it is present in other parts of the northern Chihuahuan desert, especially in the state of Chihuahua (M\'{e}xico).
 		\subsubsection*{Natural history}
@@
 \section*{Checklist of species}
-	\#
+	\begin{tabbing}
+		\quad \= \quad \= = \= \kill
+		\textit{Minyomerus} Horn, 1876: 17\\
+				\> \> = \textit{Elissa} Casey, 1888: 271\\
+				\> \> \> (synonymized by Kissinger, 1964: 30)\\
+				\> \> = \textit{Pseudelissa} Casey, 1888: 273\\
+				\> \> \> (synonymized by Pierce, 1909: 359)\\
+				\> \> = \textit{Piscatopus} Sleeper, 1960: 84\\
+				\> \> \> (synonymized by Jansen and Franz, 2015: 12)\\
+			\> \textit{microps} (Say, 1831: 9) [redescribed by Jansen and Franz, 2015: 45]\\
+				\> \> = \textit{Minyomerus innocuus} Horn, 1876: 18\\
+				\> \> \> [former type of \textit{Minyomerus}, designated by Pierce, 1913: 400]\\
+				\> \> \> (synonymized by Jansen and Franz, 2015: 45)\\
+				\> \> = \textit{Thylacites microps} Say, 1831: 9\\
+				\> \> \> (transferred to \textit{Minyomerus} on the authority of Buchanan \textit{in litt.}\\
+				\> \> \> by Blackwelder and Blackwelder, 1948: 46)\\
+				\> \> = \textit{Thylacites microsus} Boheman, 1833: 523\\
+				\> \> \> (synonymized by LeConte, 1859: 286)\\
+			\> \textit{aeriballux} Jansen and Franz, 2015: 52\\
+			\> \textit{ampullaceus} \textbf{sp. nov.}\\
+			\> \textit{bulbifrons} Jansen and Franz, 2015: 81\\
+			\> \textit{caseyi} (Sharp, 1891: 151) [redescribed by Jansen and Franz, 2015: 66]\\
+				\> \> = \textit{Pseudelissa caseyi} Sharp, 1891: 151\\
+				\> \> \> (genus synonymized by Pierce, 1909: 359)\\
+			\> \textit{conicollis} Green, 1920: 194 [redescribed by Jansen and Franz, 2015: 33]\\
+			\> \textit{constrictus} (Casey, 1888: 272) [redescribed by Jansen and Franz, 2015: 22]\\
+				\> \> = \textit{Elissa constricta} Casey, 1888: 272\\
+				\> \> \> (genus synonymized by Kissinger, 1964: 30)\\
+			\> \textit{cracens} Jansen and Franz, 2015: 61\\
+			\> \textit{franko} \textbf{sp. nov.}\\
+			\> \textit{gravivultus} Jansen and Franz, 2015: 92\\
+			\> \textit{griseus} (Sleeper, 1960: 84) [redescribed by Jansen and Franz, 2015: 96]\\
+				\> \> = \textit{Piscatopus griseus} Sleeper, 1960: 84\\
+				\> \> \> (genus synonymized by Jansen and Franz, 2015: 96)\\
+			\> \textit{imberbus} Jansen and Franz, 2015: 18\\
+			\> \textit{languidus} Horn, 1876: 18 [redescribed by Jansen and Franz, 2015: 40]\\
+				\> \> = \textit{Pseudelissa cinerea} Casey, 1888: 274\\
+				\> \> \> (synonymized by Pierce, 1909: 359)\\
+			\> \textit{laticeps} (Casey, 1888) [redescribed by Jansen and Franz, 2015: 27]\\
+				\> \> = \textit{Elissa laticeps} Casey, 1888: 272\\
+				\> \> \> (genus synonymized by Kissinger, 1964: 30)\\
+			\> \textit{politus} Jansen and Franz, 2015: 86\\
+			\> \textit{puticulatus} Jansen and Franz, 2015: 75\\
+			\> \textit{reburrus} Jansen and Franz, 2015: 57\\
+			\> \textit{rutellirostris} Jansen and Franz, 2015: 103\\
+			\> \textit{sculptilis} \textbf{sp. nov.}\\
+			\> \textit{trisetosus} Jansen and Franz, 2015: 71\\
+			\> \textit{tylotos} \textbf{sp. nov.}\\
+	\end{tabbing}
+
 \section*{Identification key}

### 2018-03-14 tex/manuscript.tex
finalized tree, most of manuscript, refs

@@
 \usepackage{textcomp}
+\usepackage{array}
+\usepackage{xtab}
+\usepackage{dcolumn}
+\usepackage{multirow}
+\newcolumntype{m}[1]{D{.}{~}{#1}}
 \newcommand{\td}{\textdegree~}
 \newcommand{\x}{$\times$~}
+\newcommand{\breakfill}{\dotfill\newline\penalty0\hbox{}\nobreak\dotfill}
 
-\title{Descriptions of four new species of \textit{Minyomerus} Horn, 1876 (Coleoptera: Curculionid\ae), with notes on their distribution and phylogeny}
+\title{Descriptions of four new species of \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz, 2015 (Coleoptera: Curculionid{\ae}), with notes on their distribution and phylogeny}
 
@@
 
-% \keywords{Keyword1, Keyword2, Keyword3}
+%\keywords{Biogeography, cladistics, concept taxonomy, desert, Entiminae, \textit{Minyomerus}, new species, provenance, weevils} - KEYWORDS PROVIDED DURING SUBMISSION.
 
 \begin{abstract}
-Dummy abstract text.
-Dummy abstract text.
-Dummy abstract text.
-Dummy abstract text.
-Dummy abstract text.
-Dummy abstract text.
-Dummy abstract text.
-Dummy abstract text.
-Dummy abstract text.
-Dummy abstract text.
-Dummy abstract text.
+	This contribution adopts the taxonomic concept annotation and alignment approach. 
+	Accordingly, and where indicated, previous and newly inferred meanings of taxonomic names are individuated according to one specific source.
+	Articulations among these concepts and pairwise, logically consistent alignments of original and revisionary classifications are also provided, in addition to conventional nomenclatural provenance information.
+	Descriptions of four species belonging to the broad-nosed weevil genera \textit{Minyomerus} Horn, 1876 sec.
+Jansen \& Franz, 2015 (Curculionidae [non-focal]: Entiminae [non-focal]: Tanymecini [non-focal]) are presented.
+	Prior to this study, \textit{Minyomerus} sec. Jansen \& Franz, 2015 contained 17 species species distributed throughout the desert and plains regions of North America.
+	We thoroughly describe these four species as new to science: \textit{M.
+ampullaceus} sec.
+Jansen \& Franz (2015) (henceforth: [JF2015]), sp.
+n., \textit{M.
+franko} [JF2015], sp.
+n., \textit{M.
+sculptilis} [JF2015], sp.
+n., and \textit{M.
+tylotos} [JF2015], sp.
+n.
+	A cladistic analysis using 52 morphological characters of 26 terminal taxa (5/21 outgroup/ingroup) yielded a single most-parsimonious cladogram (L = 99, CI = 60, RI = 80). 
+	The analysis supports the monophyly of Minyomerus [JF2015] with eight unreversed synapomorphies, in corroboration of prior work.
+	Accordingly, each of the four new species is placed within \textit{Minyomerus} [JF2015], and their species-group placement, possible biogeographic origins, and natural history are discussed in detail.
 \end{abstract}
@@
 \section*{Introduction}
-	The weevil genus \textit{Minyomerus} Horn, 1876 is currently assigned to the tribe Tanymecini Lacordaire, 1863, subtribe Tanymecina Lacoirdaire, 1863 (Curculionidae: Entiminae). 
-	The genus was recently revised and includes a total of 17 described species distributed throughout the desert and plains regions of North America.
-	Since the publication of our monographic revision of \textit{Minyomerus}, we have discovered four additional undescribed species, known to us only from limited numbers of specimens, yet falling neatly into the generic delimitation of \textit{Minyomerus} \textit{sensu} Jansen and Franz 2015.
-	Here we describe these species and provide images of the holotypes and of dissected genitalia for the purpose of identification.
-	We additionally conduct a morphological phylogenetic analysis of the genus to clarify the placement of these new taxa within \textit{Minyomerus}, based on the analysis provided in our previous work.
-	An emended identification key to the species of \textit{Minyomerus} is given along with information on the geographic distribution of the herein described species.
-	Where possible, we make note of host-plant records and briefly consider the historical biogeographic relationships of the new species.
-	A more extensive discussion of the habits, distribution, and delimitation of the genus (and all of its constituent species) can found in the generic revision.
+	The weevil genus \textit{Minyomerus} Horn, 1876 [JF2015] is currently assigned to the tribe Tanymecini Lacordaire, 1863 [non-focal], subtribe Tanymecina Lacoirdaire, 1863 [non-focal] (Curculionid{\ae} [non-focal]: Entimin{\ae} [non-focal] - higher-level classification in accordance with \citealt{alonso1999} and \citealt{bouchard2011}).
+	A recent phylogenetic revision of the genus recognized a total of 17 described species distributed throughout the desert and plains regions of North America \citep{jansen2015}.
+
+	Members of the genus \textit{Minyomerus} [JF2015] are phytophagous, and may be found on a variety of host plants, especially the creosote bush (\textit{Larrea tridentata} (DC.) Coville [non-focal; Zygophyllaceae [non-focal]), broomweed (\textit{Gutierrezia lagasca} [non-focal; Asteraceae [non-focal), sagebrush (\textit{Artemisia} Linnaeus [non-focal]; Asteraceae [non-focal]), and occasionally on other various Asteraceae [non-focal] \citep{jansen2015}.
+	While many species appear to be generalists, the adults are consistently observed on the leaves and branches of the host feeding on the leaf tissue; all other life stages remain unknown.
+	Species of this genus are commonly found in deserts throughout western North America, including the Mojave, Sonoran, Chihuahuan, and Great Basin Deserts; however, their range extends throughout the semi-arid regions of the Great Plains, the Colorado Plateau, and Baja California, M\'{e}xico \citep{obrien1982, jansen2015}.
+	The adults are flightless, as the hind wings and associated flight structures of all species are either greatly reduced or not readily apparent in dissection.
+
+	\textit{Minyomerus} [JF2015] belongs to the broad-nosed weevils, subfamily Entimin{\ae} [non-focal], on the basis of having a short, broad rostrum and dehiscent mandibular process \citep{marvaldi1997, anderson2002, oberprieler2007, oberprieler2014, marvaldi2014}.
+	They are clothed in appressed, circular scales, generally in earth-tones from white to dark brown, with sub-recumbent to erect, interspersed setiform scales (`set{\ae}') arranged in rows on the elytral intervals, and can range in length from 2.8 to 6.0 mm \citep{jansen2015}.
+	The genus has been classified in the tribe Tanymecini [non-focal] based on the presence of post-ocular vibriss{\ae} that project anteriorly from the anterior prothoracic margin, although the exact placement and sister taxa of this genus within the tribe are currently unknown \citep{howden1959, howden1970, howden1982, jansen2015}.
+
+	The genus is diagnosed by a unique combination of synapomorphic traits, described by \citet{jansen2015}, and as follows:
+
+	\begin{enumerate}[itemsep=-0.4em]
+		\item The integument is covered by appressed scales that are sub-circular and overlap posteriorly.
+		\item The nasal plate is present as a broad, scale-covered, chevron-shaped ridge demarcating the epistoma.
+		\item A sulcus posteriad of nasal plate is present.
+		\item The scrobe is sub-equal in length to the funicle and club combined.
+		\item The head is directed slightly ventrally.
+		\item The metatibial apex lacks setiform bristles yet displays bristles that are shorter to sub-equal in length to the surrounding set{\ae} and conical to lamelliform.
+		\item The mesotarsi are slightly shorter than the mesotibi{\ae}.
+		\item All tarsi lack pads of setiform set{\ae} but have stout, spiniform set{\ae}.
+	\end{enumerate}
+
+	The following additional characters are useful for identifying members of \textit{Minyomerus} [JF2015], especially when differentiating the former from other genera of Tanymecini [non-focal] that may be found together in the same desert habitats, viz.
+\textit{Isodrusus} Sharp, 1911 [non-focal], \textit{Isodacrys} Sharp, 1911 [non-focal], and \textit{Pandeleteinus} Champion, 1911 [non-focal] (see also \citealt{anderson2002}):
+
+	\begin{enumerate} [itemsep=-0.4em]
+		\item The intercoxal process of the prosternum is medially divided into two halves, with the procox{\ae} apparently contiguous in most.
+		\item The elytral humeri are rounded rather than angled and protruding.
+		\item The profemora are not dilated and lack spines.
+		\item The protibi{\ae} are ventrally excavated by a longitudinal groove or concavity.
+		\item A distinct scrobe is present and directed ventrad of the eye, with a more or less apparent tooth formed by an overhang of the dorsal margin.
+	\end{enumerate}
+
+	Following the publication of a monographic revision of \textit{Minyomerus} [JF2015], we have discovered four additional undescribed species, known to us only from limited numbers of specimens, yet well circumscribed by the generic delimitation of the genus.
+	As such, the addition of these new species \emph{does not} alter the definition of the genus (see Phylogenetic results), and we retain the taxonomic concept previously specified by \citet{jansen2015} when referring to this definition.
+	For ease of legibility, especially when discussing differences in clade composition when comparing between this and previous work, we use the notation [JF2015] and [JF2018] to specify taxon concepts sec.
+Jansen \& Franz, 2015 and sec.
+Jansen \& Franz, 2018, respectively.
+	Specifically, all clades inferred in this work will be designated according to the concept [JF2018], \emph{unless} there is perfect congruence (viz.
+synapomorphies and clade composition) with a clade previously resolved by \citet{jansen2015}, in which case the identifier [JF2015] will be retained.
+	While this is the case for all of the previously described species, and a few select clades, we differentiate the newly inferred clade corresponding to the genus, and including the herein described species, as \textit{Minyomerus} [JF2018].
+
+	Here we describe the four newly found species and provide images of the holotypes and of dissected genitalia for the purpose of identification.
+	We additionally conduct a morphological phylogenetic analysis of the genus to clarify the placement of these new taxa within \textit{Minyomerus} [JF2015], based on the analysis provided in our previous work.
+	An emended identification key to the species of \textit{Minyomerus} [JF2015] is given along with an updated checklist of the genus.
+	Where possible, we make note of host-plant records and briefly consider the geographic distribution of the herein described species.
+	A more extensive discussion of the habits, distribution, and delimitation of the genus (and all of its constituent species) can found in the generic revision \citep{jansen2015}.
 
 \section*{Materials and methods}
-	The keen reader will note the alignment of the methods used in this manuscript with those of Jansen and Franz 2015. 
-	For convenience and transparency, we provide an updated account of the methods used to generate the species descriptions, distribution maps, and phylogeny herein.
+	In order to maximize the compatibility of the new species accounts with the higher-level generic account of \textit{Minyomerus} [JF2015], the methods used in this manuscript are aligned with those of \citet{jansen2015}.
+	Here we provide an updated account of the procedures used to generate the species descriptions, distribution maps, and phylogeny herein.
 	Most importantly, we retain the format of the species descriptions, whereby we emphasize only those characters that vary significantly from the generic description, as explained below.
 
-	\paragraph{Natural history observations} 
-		Members of the genus \textit{Minyomerus} may be found on a variety of host plants, as indicated following each description.
-		While many species appear to be generalists, the adults are consistently observed on the leaves and branches of the host feeding on the leaf tissue; all other life stages remain unknown.
-		Members of this genus are commonly found in deserts throughout western North America, including the Mojave, Sonoran, Chihuahuan, and Great Basin Deserts. 
-		Furthermore, the range of the genus extends through the semi-arid regions of the Great Plains, the Colorado Plateau, and Baja California, M\'{e}xico. 
-		The adults are flightless, as the hind wings and associated flight structures of all species are either greatly reduced or not readily apparent in dissection.
-
-	\paragraph{Acquisition of museum specimens} 
-		Georeferencing of localities was performed with Google Earth (Google Inc. 2009–2015) and reported in decimal degrees.
-		Taxonomic names for associated host plants are used in accordance with Munz and Keck (1973) and SEINet (2017).
-		The existing set of \textit{Minyomerus} specimens used in the revision of Jansen and Franz 2015 was supplemented with material from the following collections, using the codens of Arnett et al.
-(1993):
+	\subsection*{Acquisition of museum specimens} 
+		The existing set of \textit{Minyomerus} [JF2015] specimens used in the revision of \citet{jansen2015} was supplemented with material from the following collections, using the codens of \citet{arnett1993}:
 
@@
 
-	\paragraph{Morphological analysis}
-		Our systematic and descriptive approach is complementary to Jansen and Franz 2015, which in turn follows Franz (2010a, 2010b, 2012).
-		Terminology for exterior morphology is in general accordance with Torre-Bueno (Nichols 1989).
-		Additional morphological terms specific to (entimine) weevils were used as follows:
-			Ting (1936) and Morimoto and Kojima (2003) for mouthparts;
-			Thompson (1992) for tibial apices and abdominal segments;
-			and Oberprieler et al. (2014) and Howden (1995) for male and female terminalia.
+			Georeferencing of localities was performed with Google Earth \citep{google2018} and reported in decimal degrees.
+		Taxonomic names for associated host plants, as noted following each species account, are used in accordance with \citet{munz1973} and \citet{seinet2018}.
+
+	\subsection*{Morphological analysis}
+		Our systematic and descriptive approach is complementary to \citet{jansen2015}, which in turn follows \citet{franz2010a, franz2010b, franz2012}.
+		Terminology for exterior morphology is in general accordance with \citet{torre1989}.
+		Additional morphological terms specific to (entimine [non-focal]) weevils were used as follows:
+			\citet{ting1936} and \citet{morimoto2003} for mouthparts;
+			\citet{thompson1992} for tibial apices and abdominal segments;
+			and \citet{oberprieler2014} and \citet{howden1995} for male and female terminalia.
 
@@
 		The width of an individual elytron was measured in dorsal view as the maximum distance between the lateral margin and the elytral suture.
-		Other length and width measurements were also performed in dorsal orientation, using the maximum length and width of the corresponding structure (profemur, protibia, elytron, and aedeagus).
+		Other length and width measurements were also performed in dorsal orientation, using the maximum length and width of the corresponding structure (profemur, protibia, elytron, and {\ae}deagus).
 		Images of mouthparts and terminalia were produced with the Leica microscope equipment, while habitus photographs were created with a Visionary Digital Passport II sytem using a Canon EOS Mark 5D II camera.
 
-		Herein recognized species of \textit{Minyomerus}  were delimited through application of the phylogenetic species concept \textit{sensu} Wheeler and Platnick (2000).
+		Herein recognized species of \textit{Minyomerus} [JF2015] were delimited through application of the phylogenetic species concept \textit{sensu} \citet{wheeler2000}.
 		Species descriptions are in alphabetical order, rather than phylogetic order, for ease of use.
-		The species descriptions in this manuscript represent unique and complementary accounts of the character states observed in each species, including their variability, but excepting those characters invariant within the genus as specified in the higher-level description of \textit{Minyomerus}.
+		As in \citet{jansen2015}, the species descriptions in this manuscript represent unique and complementary accounts of the character states observed in each species, including their variability, but excepting those characters invariant within the genus as specified in the higher-level description of \textit{Minyomerus} [JF2015].
 		Likewise, descriptions of males emphasize characters that are variable and sufficiently different from those of the females to merit recognition.
-		The key to identifying species of \textit{Minyomerus} is arranged with emphasis being placed on the most readily observable diagnostic characters.
+		The key to identifying species of \textit{Minyomerus} [JF2015] is arranged with emphasis being placed on the most readily observable diagnostic characters.
 				This manuscript is arranged with the species descriptions appearing first, followed by the key to species, and then by the phylogenetic results.
 
-	\paragraph{Phylogenetic analysis}
+	\subsection*{Phylogenetic analysis}
 		The morphological cladistic analysis includes 26 terminal taxa; with 21 ingroup and 5 outgroup terminals.
-		The ingroup terminals were represented by 17 species previously assigned to \textit{Minyomerus} sec. Jansen and Franz (2015) and four newly recognized species.
-		In keeping with our previous analysis, we sampled outgroups fairly broadly while remaining focused on North American lineages that are putative close relatives of the ingroup (Jansen and Franz 2015, Nixon and Carpenter 1993).
-		Although the tribe Tanymecini [non-focal] is cosmopolitan, the majority of New World species diversity in the tribe may be found in the subtribe Tanymecina [non-focal] (Alonzo-Zarazaga and Lyal 1999).
+		The ingroup terminals were represented by 17 species previously assigned to \textit{Minyomerus} [JF2015] and four newly recognized species.
+		In keeping with our previous analysis, we sampled outgroups fairly broadly while remaining focused on North American lineages that are putative close relatives of the ingroup \citep{jansen2015, nixon1993}.
+
+		Although the tribe Tanymecini [non-focal] is cosmopolitan, the majority of New World species diversity in the tribe may be found in the subtribe Tanymecina [non-focal] \citep{alonso1999}.
 		Thus, four of the five outgroup terminals are represented by species belonging to separate genera in the Tanymecina [non-focal]; viz.
-Isodacrys buchanani Howden, 1961 [non-focal], Isodrusus debilis Sharp, 1911 [non-focal], Pandeleteinus subcancer Howden, 1969 [non-focal], and Pandeleteius cinereus (Horn, 1876) [non-focal].
-		Because generic relationships in the Tanymecini [non-focal] remain unresolved, we selected a relatively far-removed taxon to root the cladogram that would nevertheless display states applicable to the ingroup for characters under consideration (Rieppel 2007; Franz 2014).
-		To this end we used the North American species Sitona californicus (Fahraeus, 1840) [non-focal], of the tribe Sitonini Gistel, 1856 [non-focal].
+\textit{Isodacrys buchanani} Howden, 1961 [non-focal], \textit{Isodrusus debilis} Sharp, 1911 [non-focal], \textit{Pandeleteinus subcancer} Howden, 1969 [non-focal], and \textit{Pandeleteius cinereus} (Horn, 1876) [non-focal].
+		Because generic relationships in the Tanymecini [non-focal] remain unresolved, we selected a relatively far-removed taxon to root the cladogram that would nevertheless display states applicable to the ingroup for characters under consideration \citep{rieppel2007, franz2014}.
+		To this end we used the North American species \textit{Sitona californicus} (Fahr{\ae}us, 1840) [non-focal], of the tribe Sitonini Gistel, 1856 [non-focal].
 
-		The character matrix was edited and phylogenetic results viewed using the WinDada and WinClados interfaces of WinClada, respectively (Nixon 2002).
+		The character matrix was edited and phylogenetic results viewed using the WinDada and WinClados interfaces of WinClada, respectively \citep{nixon2002}.
 		The character sequence follows that of the taxonomic descriptions.
-		The most parsimonious tree and character state optimizations were inferred under parsimony using NONA (Goloboff 1999).
+		The most parsimonious tree and character state optimizations were inferred under parsimony using NONA \citep{goloboff1999}.
 		An unconstrained heuristic search was conducted using the commands: \texttt{hold 100001}, \texttt{mult*1000}, \texttt{hold/100}, with \texttt{mult*max*} selected.
 		Bootstrap support was inferred in WinClada using the parameters of \texttt{1000 replications}, \texttt{hold 1000}, \texttt{hold/100}, \texttt{mult*10}, \texttt{Don’t do max*}, and \texttt{Save consensus}.
-		Finally, Bremer support values (Bremer 1994) were calculated in NONA using the commands: \texttt{hold 20000}, \texttt{suboptimal 20}, and \texttt{bsupport 20}.
+		Finally, Bremer support values \citep{bremer1994} and relative fit difference \citep{goloboff2001} were calculated in NONA using the commands: \texttt{hold 1001}, \texttt{sub 20}, \texttt{bs} for Bremer support values, and \texttt{bs*} for relative fit difference, respectively \citep{goloboff2008}.
 
-	\paragraph{Species distribution modeling}
-		We used the modeling program Maxent, Version 3.4, to generate habitat models for the species of Minyomerus [JF 2015] (Figs.~\#) based on documented occurrence records (Phillips et al.
-2004, 2006; Elith et al.
-2011).
+		The motivation for providing Bremer support values and relative fit difference comes from their respective interpretations, based on how the measures are calculated, \textit{per} \citet{goloboff2001}.
+		Both of these indices rely on summation of the number of favorable and contradictory characters when comparing a most-parsimonious tree to a suboptimal tree. 
+		If the step length of the $i^{\text{th}}$ character ($I$) of $n$ total characters on the most-parsimonious tree ($L_{MPT}$) is less than its corresponding step length on the suboptimal tree ($L_{SUB}$), the character is designated as favorable ($f_{i}$), but if the opposite is true, the character is designated as contradictory ($c_{i}$), and expressed formally:
+		\begin{equation}
+		I = 
+			\begin{cases}
+				f_{i} & L_{MPT} < L_{SUB}\\
+				c_{i} & L_{MPT} > L_{SUB}
+			\end{cases}
+		\end{equation}
+		Where the number of favorable ($F$) and contradictory ($C$) characters are defined, respectively, as:
+		\begin{align}
+			F = \sum_{n = 0}^{i}{f_{i}}\\
+			C = \sum_{n = 0}^{i}{c_{i}}
+		\end{align}
+		Bremer support values (bsv) and relative fit difference (rfd) are then calculated simply as:
+		\begin{align}
+			\text{bsv} & = F - C\\
+			\text{rfd} & = \frac{F - C}{F} \times 100
+		\end{align}
+
+		The Bremer support value for a node thus indicates how many more characters support a node than contradict it, while the relative fit difference indicates what proportion of the favorable characters are represented by the Bremer support value.
+		Whereas the Bremer support value is as large as the number of characters supporting the node, in excess of the contradicting characters, the relative fit difference can only vary from 0 to 100, as a proportion of the number of supporting characters.
+		By providing both measures, one may quickly discriminate, for example, between a node supported by 4 characters but contradicted by 1 character (bsv = 3, rfd = 75), and a node supported by 10 characters but contradicted by 7 characters (bsv = 3, rfd = 30).
+
+	\subsection*{Species distribution modeling}
+		We used the modeling program Maxent, Version 3.4, to generate habitat models for the species of Minyomerus [JF2015] (Figs.~\#) based on documented occurrence records \citep{phillips2004, phillips2006, elith2011}.
 		The default settings were adjusted to \texttt{Max number background points = 100,000} and \texttt{Iterations = 10}.
 		Cross-validation was used to leverage all available locality data; however, no models could be created for species with two or fewer documented localities.
-		We selected 19 bioclimatic variables and elevation as Environmental Layers in Maxent, obtained from WorldClim (see Hijmans et al. 2005).
+		We selected 19 bioclimatic variables and elevation as Environmental Layers in Maxent, obtained from WorldClim \citep{hijmans2005}.
 		The layers were downloaded by tile (zones 11–13 and 21–23), with a 30 arc-second resolution (projected using WSG 84) to provide adequate coverage of the full distribution of the genus.
-		Layerwise assembly of tiles was done using QGIS, Version 2.18.16 `Las Palmas', creating composite maps of six tiles each to use in species distribution modeling (Quantum GIS Development Team 2017).
+		Layerwise assembly of tiles was done using QGIS, Version 2.18.16 `Las Palmas', creating composite maps of six tiles each to use in species distribution modeling \citep{qgis2018}.
 
@@
 		For example, a species endemic to the Snake River Valley of Idaho does not require a predictive model for bioclimatically similar habitats in the Chihuahuan Desert.
-		Documented occurrence records are laid over the modeled habitat ranges as colored circles on their respective maps (Figs.~\#), along with vector layers of country (white) and state (gray) borders (Hijmans et al.
-2012).
+		Documented occurrence records are laid over the modeled habitat ranges as colored circles on their respective maps (Figs.~\#), along with vector layers of country (white) and state (gray) borders \citep{hijmans2012}.
 
 \section*{Descriptions of new species}
-	\subsection*{\textit{Minyomerus ampullaceus} - sp. n.}
+	\subsection*{\textit{Minyomerus ampullaceus} Jansen \& Franz sec. Jansen \& Franz, 2018; sp. n.}
 		\subsubsection*{Diagnosis}
 			\textit{Minyomerus ampullaceus} is best differentiated from other congenerics by its unique body shape, which most prominently features a strongly constricted, sub-cylindrical pronotum and greatly protuberant elytra; this combination gives the species a distinctly flask- or bottle-shaped appearance.
-			Due to the relatively poor condition of the scales and setae of the holotype, color and setation cannot be reliably used for identification.
-			Fortunately, the elytra themselves are unique in shape, and diagnostic, together nearly 2\x the width of the pronotum at their widest point, and nearly 3/4 as wide as long in dorsal view.
-			In lateral view the anterior and posterior declivities of the elytra are strongly abrupt, and nearly vertical; most notably, the anterior magin of the elytra projects strongly and characteristically dorsad of its articulation with the posterior pronotal margin.
+			Due to the relatively poor condition of the scales and set{\ae} of the holotype, color and setation cannot be reliably used for identification.
+			Fortunately, the elytra themselves are unique in shape, and diagnostic, together nearly 2\x the width of the pronotum at their widest point, and nearly 3/4\x as wide as long in dorsal view.
+			In lateral view the anterior and posterior declivities of the elytra are strongly abrupt, and nearly vertical; most notably, the anterior margin of the elytra projects strongly and characteristically dorsad of its articulation with the posterior pronotal margin.
 			The spermatheca is also quite distinct, having a highly elongate projection of the corpus aligned with midline of the ramus, which is basally tapered and angled at nearly 45\td to the corpus.
@@
 				Scales with variously interspersed colors ranging from slightly off-white to beige to yellow. 
-				Setae recumbent to sub-recumbent, white to brown in color.
+				Set{\ae} recumbent to sub-recumbent, white to brown in color.
 			\paragraph{Mandibles}
-				Partially covered with white, slightly opalescent scales, with 3 longer setae, and 1 shorter seta between these.
+				Partially covered with white, slightly opalescent scales, with 3 longer set{\ae}, and 1 shorter seta between these.
 			\paragraph{Rostrum}
@@
 				Dorsal outline of rostrum nearly square, anterior half of dorsal surface mesally concave, posterior half coarsely but shallowly punctate to rugose. 
-				Rostrum in lateral view nearly square; apical margin broadly bisinuate and emarginate, with 2 pairs of large vibrissae. 
+				Rostrum in lateral view nearly square; apical margin broadly bisinuate and emarginate, with 2 pairs of large vibriss{\ae}. 
 				Nasal plate defined by Y-shaped, impressed lines, convex, integument partially covered with white scales.
@@
 				Ventrolateral sulci strongly defined, beginning as a narrow sulcus posteriad of insertion point of mandibles, running parallel to scrobe, terminating in a ventral fovea.
-			\paragraph{Antennae}
+			\paragraph{Antenn{\ae}}
 				Small tooth formed by overhanging dorsal margin of scrobe directly ventrad of margin of eye.
@@
 				Anterior margin slightly arcuate, lateral margins curved and widening into a bulge just anteriad of midpoint of pronotum, posterior margin straight, with a slight mesal incurvature. 
-				Pronotum in lateral view with setae that reach beyond anterior margin by 1/2 of their length; these setae becoming evenly longer and more erect laterally, reaching a maximum length equal to 1/2 of length of eye.
-				Anterolateral margin with a reduced tuft of 6-7 post-ocular vibrissae present, emerging near ventral 1/2 of eye, and stopping just below ventral margin of eye; vibrissae sub-equal in length at 1/3 of anterior-posterior length of eye, except for three vibrissae achieving a maximum length similar to anterior-posterior length of eye.
+				Pronotum in lateral view with set{\ae} that reach beyond anterior margin by 1/2 of their length; these set{\ae} becoming evenly longer and more erect laterally, reaching a maximum length equal to 1/2 of length of eye.
+				Anterolateral margin with a reduced tuft of 6-7 post-ocular vibriss{\ae} present, emerging near ventral 1/2 of eye, and stopping just below ventral margin of eye; vibriss{\ae} sub-equal in length at 1/3 of anterior-posterior length of eye, except for three vibriss{\ae} achieving a maximum length similar to anterior-posterior length of eye.
 			\paragraph{Scutellum}
@@
 				Profemur/pronotum length ratio \#; profemur with distal 1/5 produced ventrally as a rounded projection covering tibial joint; condyle of tibial articulation occupying 4/5 of distal surface and 1/5 length of femur.
-				Protibia/profemur length ratio \#; protibial apex with ventral setal comb recessed in an incurved groove; mucro present as a large, black, sub-triangular, medially-projected tooth, which is approximately equilateral and whose sides are sub-equal in length to surrounding setae.
+				Protibia/profemur length ratio \#; protibial apex with ventral setal comb recessed in an incurved groove; mucro present as a large, black, sub-triangular, medially-projected tooth, which is approximately equilateral and whose sides are sub-equal in length to surrounding set{\ae}.
 				Protarsus with tarsomere III 1.25\x as long as II; wider than long. 
-				Metatibial apex with almond shaped convexity ringed by 10 short, spiniform setae.
+				Metatibial apex with almond shaped convexity ringed by 10 short, spiniform set{\ae}.
 			\paragraph{Elytra}
@@
 				Posterior declivity angled at nearly 85\td to main body axis.
-Elytra with 10 complete striae; striae shallow; punctures faint beneath appressed scales, separated by 5-7\x their diameter; intervals very slightly elevated.
+Elytra with 10 complete stri{\ae}; stri{\ae} shallow; punctures faint beneath appressed scales, separated by 5-7\x their diameter; intervals very slightly elevated.
 			\paragraph{Abdominal sterna}
@@
 			No host plant associations have been documented.
-			The label indicates ``Geococcyx calif''; this is presumably a reference to \textit{Geococcyx californianus} (Lesson, 1829) [Cuculidae], the Greater Roadrunner, although it is unclear if the specimen was found on or near one of these birds (either living, dead, or in a nest).
+			The label indicates ``Geococcyx calif''; this is presumably a reference to \textit{Geococcyx californianus} (Lesson, 1829 [non-focal]; Cuculid{\ae} [non-focal]), the Greater Roadrunner, although it is unclear if the specimen was found on or near one of these birds (either living, dead, or in a nest).
 			\textit{Minyomerus} species are only known to be phytophagous, not parasitic, phoretic, or necrophagous, so we believe that this specimen was most likely found in a nest, and was present there only incidentally because the nest was constructed in the host plant of this specimen \citep{jansen2015}.
@@
 
-	\subsection*{\textit{Minyomerus franko} - sp. n.}
+	\subsection*{\textit{Minyomerus franko} Jansen \& Franz sec. Jansen \& Franz, 2018; sp. n.}
 		\subsubsection*{Diagnosis}
-			\textit{Minyomerus franko} is readily distinguished from other congenerics by the strikingly long setae of the anterior margin of the pronotum, which project laterally up to 80\td from the longitudinal axis of the body and achieve a maximum length at least equaling the diameter of the eye.
-			In addition, the setae lining the dorsal margin of the ocular impression are elongate and reach a length equal to 1/2 - 3/4\x the diameter of the eye.
+			\textit{Minyomerus franko} is readily distinguished from other congenerics by the strikingly long set{\ae} of the anterior margin of the pronotum, which project laterally up to 80\td from the longitudinal axis of the body and achieve a maximum length at least equaling the diameter of the eye.
+			In addition, the set{\ae} lining the dorsal margin of the ocular impression are elongate and reach a length equal to 1/2 - 3/4\x the diameter of the eye.
 			The spermatheca has a short, somewhat bulbous corpus, with the ramus sub-equal in size and perpendicular to the corpus, and the collum is strongly recurved along the basal 1/3 of its length.
-			The aedeagus is relatively short and wide, and is abruptly constricted in the apical 1/5 of its length, thereafter tapered to a rounded point.
+			The {\ae}deagus is relatively short and wide, and is abruptly constricted in the apical 1/5 of its length, thereafter tapered to a rounded point.
 		\subsubsection*{Description of female}
@@
 				Scales with variously interspersed colors ranging from slightly off-white or beige to manila/tan to dark coffee brown, in some specimens appearing semi-translucent (in others opaque). 
-				Setae linear to slightly apically explanate, appearing minutely spatulate, sub-recumbent to sub-erect, white or brown in color.
+				Set{\ae} linear to slightly apically explanate, appearing minutely spatulate, sub-recumbent to sub-erect, white or brown in color.
 			\paragraph{Mandibles}
-				Covered with white scales, with 3 longer setae, and 1-2 shorter setae between these.
-			\paragraph{Maxillae}
+				Covered with white scales, with 3 longer set{\ae}, and 1-2 shorter set{\ae} between these.
+			\paragraph{Maxill{\ae}}
 				Cardo bifurcate at base with an inner angle typically between 90–120\td, arms of equal length, inner (mesal) arm nearly 1.5\x thicker than outer arm, both arms of bifurcation equal in length to apically outcurved arm, glabrous.
@@
 				Galeo-lacinial complex nearly extending to apex of maxillary palpomere II; complex mesally membranous, laterally sclerotized, with sharp demarcation of sclerotized region separating palpiger from galeo-lacinial complex; setose in membranous area just adjacent to sclerotized
-region, setae covering 2/3 of dorsal surface area; dorsally with 7 apicomesal lacinial teeth; ventrally with 4 reduced lacinial teeth. 
+region, set{\ae} covering 2/3 of dorsal surface area; dorsally with 7 apicomesal lacinial teeth; ventrally with 4 reduced lacinial teeth. 
 				Palpiger with a single lateral seta, otherwise glabrous and evenly sclerotized throughout.
 			\paragraph{Maxillary palps}
-				I apically oblique, apical end forming a 45\td angle with base, with 2 apical setae; II sub-cylindrical, with 1 apical seta.
+				I apically oblique, apical end forming a 45\td angle with base, with 2 apical set{\ae}; II sub-cylindrical, with 1 apical seta.
 			\paragraph{Labium}
@@
 				Dorsal outline of rostrum sub-rectangular, anterior half of dorsal surface feebly impressed, posterior half coarsely but shallowly punctate to rugose. 
-				Rostrum in lateral view nearly square; apical margin bisinuate and emarginate , with 2 large vibrissae. 
+				Rostrum in lateral view nearly square; apical margin bisinuate and emarginate , with 2 large vibriss{\ae}. 
 				Nasal plate defined by broad, V-shaped, shallowly impressed lines, anteromesally slightly convex, integument partially covered with white scales. 
@@
 				Rostrum ventrally lacking sulci at corners of oral cavity.
-			\paragraph{Antennae}
+			\paragraph{Antenn{\ae}}
 				Small tooth formed by overhanging dorsal margin of scrobe anterior to margin of eye by 1/5 of length of eye.
 				Scape nearly extending to posterior 1/4 of eye.
-				Terminal funicular antennomere lacking appressed scales, having instead a covering of apically-directed pubescence with interspersed sub-erect setae.
+				Terminal funicular antennomere lacking appressed scales, having instead a covering of apically-directed pubescence with interspersed sub-erect set{\ae}.
 				Club nearly 3\x as long as wide.
@@
 				Anterior margin arcuate, lateral margins curved and widening into a slight bulge just anteriad of midpoint of pronotum, posterior margin straight, with a slight mesal incurvature. 
-				Pronotum in lateral view with setae that reach just beyond anterior margin, angled laterally at 45-80\td to longitudinal axis, and strikingly long; these setae becoming evenly longer and more angled laterally, reaching a maximum length nearly equal to length of eye.
-				Anterolateral margin with a reduced tuft of 5 post-ocular vibrissae present, emerging near ventral 1/2 of eye, and stopping just below ventral margin of eye; vibrissae sub-equal in length at 1/3\x anterior-posterior length of eye, except for one vibrissa achieving a maximum length similar to anterior-posterior length of eye.
+				Pronotum in lateral view with set{\ae} that reach just beyond anterior margin, angled laterally at 45-80\td to longitudinal axis, and strikingly long; these set{\ae} becoming evenly longer and more angled laterally, reaching a maximum length nearly equal to length of eye.
+				Anterolateral margin with a reduced tuft of 5 post-ocular vibriss{\ae} present, emerging near ventral 1/2 of eye, and stopping just below ventral margin of eye; vibriss{\ae} sub-equal in length at 1/3\x anterior-posterior length of eye, except for one vibrissa achieving a maximum length similar to anterior-posterior length of eye.
 			\paragraph{Scutellum}
@@
 				Profemur/pronotum length ratio \#; profemur with distal 1/5 produced ventrally as a sub-rectangular projection covering tibial joint; condyle of tibial articulation occupying 4/5 of distal surface and 1/5 length of femur.
-				Protibia/profemur length ratio \#; protibial apex with ventral setal comb recessed in a subtly incurved groove; mucro present as a large, black, sub-triangular, medially-projected tooth, which is approximately equilateral and whose sides are sub-equal in length to surrounding setae.
+				Protibia/profemur length ratio \#; protibial apex with ventral setal comb recessed in a subtly incurved groove; mucro present as a large, black, sub-triangular, medially-projected tooth, which is approximately equilateral and whose sides are sub-equal in length to surrounding set{\ae}.
 				Protarsus with tarsomere III 2\x as long as II; wider than long. 
-				Metatibial apex with almond shaped convexity ringed by 8-9 short, spiniform setae.
+				Metatibial apex with almond shaped convexity ringed by 8-9 short, spiniform set{\ae}.
 			\paragraph{Elytra}
@@
 				Posterior declivity angled at 70-85\td to main body axis.
-Elytra with 10 complete striae; striae shallow; punctures faint beneath appressed scales, separated by 5-7\x their diameter; intervals very slightly elevated.
+Elytra with 10 complete stri{\ae}; stri{\ae} shallow; punctures faint beneath appressed scales, separated by 5-7\x their diameter; intervals very slightly elevated.
 			\paragraph{Abdominal sterna}
 				Ventrite III anteromesally incurved around a fovea located mesally on anterior margin, posterior margin elevated and set off from IV along lateral 1/3s of its length. 
-				Sternum VII mesally 1/2\x as long as wide; setae darkening, lengthening, and becoming more erect in posterior 2/3; anterior margin weakly curved.
+				Sternum VII mesally 1/2\x as long as wide; set{\ae} darkening, lengthening, and becoming more erect in posterior 2/3; anterior margin weakly curved.
 			\paragraph{Tergum}
@@
 			\paragraph{Sternum IX}
-				Spiculum gastrale 2\x length of aedeagal pedon. Laminar alae located on lateral 1/4 of posterior margin.
-			\paragraph{Aedeagus}
+				Spiculum gastrale 2\x length of {\ae}deagal pedon. Laminar al{\ae} located on lateral 1/4 of posterior margin.
+			\paragraph{{\AE}deagus}
 				Length/width ratio \#; lateral margins very slightly converging posteriorly, abruptly constricted and more strongly converging in apical 1/5.
@@
 		\subsubsection*{Etymology}
-			Named in reference to the long, somewhat unkempt, erect setae on the anterior margin of the pronotum; franko = free; Old High-German adjective \citep{brown1956}.
+			Named in reference to the long, somewhat unkempt, erect set{\ae} on the anterior margin of the pronotum; franko = free; Old High-German adjective \citep{brown1956}.
 		\subsubsection*{Material examined}
 			\paragraph{Holotype}
-				\female~``MEX: S.L.P 1 km N.; Entronque El Huizache; 1493 m 2.VI.87; R. Anderson, \underline{\smash{Sphaeralcea}}; \underline{\smash{hastula}} A. Gray'' (\texttt{\textbf{CMNC}}).
+				\female~``MEX: S.L.P 1 km N.; Entronque El Huizache; 1493 m 2.VI.87; R. Anderson, \underline{\smash{Sph{\ae}ralcea}}; \underline{\smash{hastula}} A. Gray'' (\texttt{\textbf{CMNC}}).
 			\paragraph{Paratypes}
@@
 		\subsubsection*{Natural history}
-			Associated with spear globemallow [\textit{Sphaeralcea hastulata} A. Gray; Malvaceae].
+			Associated with spear globemallow (\textit{Sph{\ae}ralcea hastulata} A. Gray [non-focal]; Malvace{\ae} [non-focal]).
 
-	\subsection*{\textit{Minyomerus sculptilis} - sp. n.}
+	\subsection*{\textit{Minyomerus sculptilis} Jansen \& Franz sec. Jansen \& Franz, 2018; sp. n.}
 		\subsubsection*{Diagnosis}
-			\textit{Minyomerus sculptilis} is best distinguished from other congenerics by a combination of characters, as follows.
-			The interspersed setae on the body are linear and either brown or white.
-			The anterior margin of the pronotum bears a reduced tuft of post-ocular vibrissae.
+			\textit{Minyomerus sculptilis} is best distinguished from other congenerics, especially \textit{Minyomerus imberbus} Jansen \& Franz, 2015 [JF2015], by a combination of characters, as follows.
+			The interspersed set{\ae} on the body are linear and either brown or white.
+			The anterior margin of the pronotum bears a reduced tuft of post-ocular vibriss{\ae}.
 			The head is barely elevated between the eyes.
@@
 			Both the corpus and cornu terminate in large, hood-shaped, explanate projections equal in size to the ramus.
-			The aedeagus is elongate, acutely angulate, and narrowing towards the apex more strongly in the region of the ostium.
+			The {\ae}deagus is elongate, acutely angulate, and narrowing towards the apex more strongly in the region of the ostium.
 		\subsubsection*{Description of female}
@@
 				Scales with variously interspersed colors ranging from slightly off-white or beige to golden brown to dark coffee brown.
-				Setae sub-recumbent to sub-erect, white to brown in color.
+				Set{\ae} sub-recumbent to sub-erect, white to brown in color.
 			\paragraph{Mandibles}
-				Covered with white scales, with 3 longer setae, and 1 shorter seta between these.
+				Covered with white scales, with 3 longer set{\ae}, and 1 shorter seta between these.
 			\paragraph{Rostrum}
@@
 				Dorsal outline of rostrum nearly square, anterior half of dorsal surface mesally concave, posterior half coarsely but shallowly punctate to rugose. 
-				Rostrum in lateral view nearly square; apical margin bisinuate and emarginate, with 2 pairs of large vibrissae. 
+				Rostrum in lateral view nearly square; apical margin bisinuate and emarginate, with 2 pairs of large vibriss{\ae}. 
 				Nasal plate defined by Y-shaped, impressed lines, convex, integument covered with white scales.
@@
 				Ventrolateral sulci strongly defined, beginning as a narrow sulcus posteriad of insertion point of mandibles, running parallel to scrobe, terminating in a ventral fovea.
-			\paragraph{Antennae}
+			\paragraph{Antenn{\ae}}
 				Dorsal margin of scrobe overhanging broadly (not forming a minute tooth).
 				Funicle slightly longer than scape.
-				Scape extending Brassicaceae  to posterior 1/4 of eye.
+				Scape extending Brassicace{\ae}  to posterior 1/4 of eye.
 				Club nearly 3\x as long as wide.
@@
 				Anterior margin arcuate, subtly incurved mesally, and somewhat produced dorsally; anterior constriction broad, posterior margin slightly arcuate.
-				Pronotum in lateral view with setae that reach beyond anterior margin; these setae becoming slightly longer and more erect laterally.
-				Anterolateral margin with a reduced tuft of 3-6 post-ocular vibrissae present, emerging near ventral 1/2 of eye, and stopping just below ventral margin of eye; vibrissae varying in length from 1/2\x anterior-posterior length of eye to a maximum length similar to anterior-posterior length of eye.
+				Pronotum in lateral view with set{\ae} that reach beyond anterior margin; these set{\ae} becoming slightly longer and more erect laterally.
+				Anterolateral margin with a reduced tuft of 3-6 post-ocular vibriss{\ae} present, emerging near ventral 1/2 of eye, and stopping just below ventral margin of eye; vibriss{\ae} varying in length from 1/2\x anterior-posterior length of eye to a maximum length similar to anterior-posterior length of eye.
 			\paragraph{Scutellum}
@@
 				Protarsus with tarsomere III 1.5\x as long as II; wider than long. 
-				Metatibial apex with almond shaped convexity ringed by 10-12 short, spiniform setae.
+				Metatibial apex with almond shaped convexity ringed by 10-12 short, spiniform set{\ae}.
 			\paragraph{Elytra}
@@
 				Posterior declivity angled at 65-70\td to main body axis.
-Elytra with 10 complete striae; striae broadly sculpted; punctures faint beneath appressed scales, separated by 5-7\x their diameter; intervals elevated, with every second interval, beginning at elytral suture, more strongly raised than adjacent intervals.
+Elytra with 10 complete stri{\ae}; stri{\ae} broadly sculpted; punctures faint beneath appressed scales, separated by 5-7\x their diameter; intervals elevated, with every second interval, beginning at elytral suture, more strongly raised than adjacent intervals.
 			\paragraph{Abdominal sterna}
@@
 				Consisting of 2 sub-triangular sclerites; antero-laterally with a sharply-pointed projection as long as anterior-posterior length of triangular portion of sclerite.
-			\paragraph{Aedeagus}
+			\paragraph{{\AE}deagus}
 				Length/width ratio \#; lateral margins parallel, more strongly converging in region of ostium. 
@@
 		\subsubsection*{Distribution}
-			This species has been found in three localities along the Snake River in Idaho (USA), and is thought to be endemic to the Snake River Valley (Fig.~\#).
+			This species has been found in three localities along the Snake River in Idaho (USA), and is thought to be endemic to the Snake River Plain (Fig.~\#).
 		\subsubsection*{Natural history}
-			Associated with big sagebrush [\textit{Artemisia tridentata} Nutt.; Asteraceae], tumbleweed [\textit{Salsola tragus} L.; Amaranthaceae], tall tumblemustard [\textit{Sisymbrium altissimum} L.; Brassicaceae].
+			Associated with big sagebrush (\textit{Artemisia tridentata} Nutt.
+[non-focal]; Asterace{\ae} [non-focal]), tumbleweed (\textit{Salsola tragus} L.
+[non-focal]; Amaranthace{\ae} [non-focal]), tall tumblemustard (\textit{Sisymbrium altissimum} L.
+[non-focal]; Brassicace{\ae} [non-focal]).
 
-	\subsection*{\textit{Minyomerus tylotos} - sp. n.}
+	\subsection*{\textit{Minyomerus tylotos} Jansen \& Franz sec. Jansen \& Franz, 2018; sp. n.}
 		\subsubsection*{Diagnosis}
@@
 			The frons is protuberant and moderately punctate.
-			The entire body, including the legs, head, and venter, are clothed with brown, linear to minutely apically expanded setae, which are of similar length throughout and appear distinctly undifferentiated and uniform across body regions.
+			The entire body, including the legs, head, and venter, are clothed with brown, linear to minutely apically expanded set{\ae}, which are of similar length throughout and appear distinctly undifferentiated and uniform across body regions.
 			The body is somewhat bulky, with the pronotum protuberant laterally and globular in dorsal view.
-			The setae lining the anterodorsal margin of the pronotum uniquely apically explanate, with a longitudinal, medial, ridge-like portion that tapers to either side apicolaterally (visible at high magnification).
+			The set{\ae} lining the anterodorsal margin of the pronotum uniquely apically explanate, with a longitudinal, medial, ridge-like portion that tapers to either side apicolaterally (visible at high magnification).
 			The lateral margins of the elytra are protuberant anteriorly and sub-parallel along the between anterior 1/5 and posterior 1/3 of their length.
@@
 				Scales with variously interspersed colors ranging from slightly off-white or beige to manila/tan to dark coffee brown, in some specimens appearing semi-translucent (in others opaque).
-				Setae linear to apically explanate, appearing minutely spatulate, sub-recumbent to sub-erect, tan to brown in color.
+				Set{\ae} linear to apically explanate, appearing minutely spatulate, sub-recumbent to sub-erect, tan to brown in color.
 			\paragraph{Mandibles}
-				Covered with white scales, with 2-3 longer setae, and 1-3 shorter setae between these.
-			\paragraph{Maxillae}
+				Covered with white scales, with 2-3 longer set{\ae}, and 1-3 shorter set{\ae} between these.
+			\paragraph{Maxill{\ae}}
 				Cardo bifurcate at base with an inner angle of ca. 90\td, arms roughly equal in length and width, arms of bifurcation equal in length to apically outcurved arm. 
 				Stipes sub-rectangular, 1.5\x wider than long, roughly equal in width to inner arm of bifurcation of cardo, glabrous. 
-				Galeo-lacinial complex nearly extending to apex of maxillary palpomere I; complex mesally membranous, laterally sclerotized, with sharp demarcation of sclerotized region separating palpiger from galeo-lacinial complex; setose in membranous area just adjacent to sclerotized region, setae covering 1/2 of dorsal surface area; dorsally with 5 apicomesal lacinial teeth; ventrally with 3 reduced lacinial teeth.
+				Galeo-lacinial complex nearly extending to apex of maxillary palpomere I; complex mesally membranous, laterally sclerotized, with sharp demarcation of sclerotized region separating palpiger from galeo-lacinial complex; setose in membranous area just adjacent to sclerotized region, set{\ae} covering 1/2 of dorsal surface area; dorsally with 5 apicomesal lacinial teeth; ventrally with 3 reduced lacinial teeth.
 				Palpiger with a single lateral seta, otherwise glabrous, anterior 1/2 membranous, posteriorly sclerotized.
 			\paragraph{Maxillary palps}
-				I apically oblique, apical end forming a 45\td angle with base, with 2 apical setae; II sub-cylindrical, with 1 apical seta.
+				I apically oblique, apical end forming a 45\td angle with base, with 2 apical set{\ae}; II sub-cylindrical, with 1 apical seta.
 			\paragraph{Labium}
@@
 				Dorsal outline of rostrum nearly square, anterior half of dorsal surface feebly impressed, posterior half coarsely but shallowly punctate to rugose. 
-				Rostrum in lateral view nearly square; apical margin strongly bisinuate and emarginate, appearing medially notched, with 2 large vibrissae. 
+				Rostrum in lateral view nearly square; apical margin strongly bisinuate and emarginate, appearing medially notched, with 2 large vibriss{\ae}. 
 				Nasal plate lacking distinct impressions, having instead a poorly defined anteromesal convexity, integument completely and evenly covered with white scales. 
@@
 				Rostrum ventrally with sub-parallel sulci beginning at corners of oral cavity and continuing halfway to back of head.
-			\paragraph{Antennae}
+			\paragraph{Antenn{\ae}}
 				Minute tooth formed by overhanging dorsal margin of scrobe anterior to margin of eye by 1/3 of length of eye.
 				Scape extending to posterior margin of eye.
-				Terminal funicular antennomere lacking appressed scales, having instead a covering of apically-directed pubescence with interspersed sub-erect setae.
+				Terminal funicular antennomere lacking appressed scales, having instead a covering of apically-directed pubescence with interspersed sub-erect set{\ae}.
 				Club nearly 3\x as long as wide.
@@
 				Anterior margin arcuate, but feebly incurved mesally, lateral margins evenly curved and widening into a bulge just anteriad of midpoint of pronotum, posterior margin straight, with a slight mesal incurvature.
-				Pronotum in lateral view with transverse ventrolateral sulci strongly excavated and distinctly sculptured; with short, recumbent to sub-erect setae that barely attain or reach just beyond anterior margin; these setae becoming shorter and more erect laterally, reaching a maximum length nearly equal to length of eye; dorsally, these setae become uniquely apically explanate, with a longitudinal, medial, ridge-like portion that tapers to either side apicolaterally.
+				Pronotum in lateral view with transverse ventrolateral sulci strongly excavated and distinctly sculptured; with short, recumbent to sub-erect set{\ae} that barely attain or reach just beyond anterior margin; these set{\ae} becoming shorter and more erect laterally, reaching a maximum length nearly equal to length of eye; dorsally, these set{\ae} become uniquely apically explanate, with a longitudinal, medial, ridge-like portion that tapers to either side apicolaterally.
 				Anterolateral margin with a single ocular vibrissa present, emerging near ventral margin of eye; vibrissa achieving a maximum length of 2/5 of anterior-posterior length of eye.
@@
 				Profemur/pronotum length ratio \#; profemur with distal 1/5 produced ventrally as a sub-rectangular projection covering tibial joint; condyle of tibial articulation occupying 4/5 of distal surface and 1/5 length of femur.
-				Protibia/profemur length ratio \#; protibial apex with ventral setal comb recessed in a subtly incurved groove; mucro present as an acute, medially-projected tooth, which is approximately equal in length to surrounding setae.
+				Protibia/profemur length ratio \#; protibial apex with ventral setal comb recessed in a subtly incurved groove; mucro present as an acute, medially-projected tooth, which is approximately equal in length to surrounding set{\ae}.
 				Protarsus with tarsomere III 2\x as long as II; wider than long. 
-				Metatibial apex with weakly projecting, poorly defined, narrow convexity laterally flanged by 5 short, spiniform setae.
+				Metatibial apex with weakly projecting, poorly defined, narrow convexity laterally flanged by 5 short, spiniform set{\ae}.
 			\paragraph{Elytra}
@@
 				Posterior declivity angled at 70-75\td to main body axis.
-Elytra with 10 complete striae; striae broadly sculpted; punctures broad and faint beneath appressed scales, separated by 4-5\x their diameter; intervals elevated.
+Elytra with 10 complete stri{\ae}; stri{\ae} broadly sculpted; punctures broad and faint beneath appressed scales, separated by 4-5\x their diameter; intervals elevated.
 			\paragraph{Abdominal sterna}
 				Ventrite III anteromesally incurved around a fovea located mesally on anterior margin, posterior margin elevated and set off from IV along lateral 3/8s of its length. 
-				Sternum VII mesally 2/3\x as long as wide; setae slightly lengthening, and becoming medially directed in posterior 1/3; anterior margin weakly curved; posterior margin distinctly incurved mesally, appearing broadly notched; surface of sternite concave, appearing broadly foveate, immediately anteriad of marginal incurvature.
+				Sternum VII mesally 2/3\x as long as wide; set{\ae} slightly lengthening, and becoming medially directed in posterior 1/3; anterior margin weakly curved; posterior margin distinctly incurved mesally, appearing broadly notched; surface of sternite concave, appearing broadly foveate, immediately anteriad of marginal incurvature.
 			\paragraph{Tergum}
 				Tergum VII mesally incurved.
-				Pygidium sub-cylindrical; medial 1/3 of anterior 2/3 of pygidium less sclerotized, with a patch of very short, fine setae.
+				Pygidium sub-cylindrical; medial 1/3 of anterior 2/3 of pygidium less sclerotized, with a patch of very short, fine set{\ae}.
 			\paragraph{Sternum VIII}
@@
 			\paragraph{Ovipositor}
-				Coxites as long as broad; styli with 3 setae near the base.
+				Coxites as long as broad; styli with 3 set{\ae} near the base.
 			\paragraph{Spermatheca}
@@
 		\subsubsection*{Etymology}
-			Named in reference to the short, apically explanate setae interspersed throughout the dorsum, which give this species a distinctly ``knobbed'' appearance; tylotos = knobby; Greek adjective \citep{brown1956}.
+			Named in reference to the short, apically explanate set{\ae} interspersed throughout the dorsum, which give this species a distinctly ``knobbed'' appearance; tylotos = knobby; Greek adjective \citep{brown1956}.
 		\subsubsection*{Material examined}
@@
 				\> \> = \textit{Piscatopus} Sleeper, 1960: 84\\
-				\> \> \> (synonymized by Jansen and Franz, 2015: 12)\\
-			\> \textit{microps} (Say, 1831: 9) [redescribed by Jansen and Franz, 2015: 45]\\
+				\> \> \> (synonymized by Jansen \& Franz, 2015: 12)\\
+			\> \textit{microps} (Say, 1831: 9) [redescribed by Jansen \& Franz, 2015: 45]\\
 				\> \> = \textit{Minyomerus innocuus} Horn, 1876: 18\\
 				\> \> \> [former type of \textit{Minyomerus}, designated by Pierce, 1913: 400]\\
-				\> \> \> (synonymized by Jansen and Franz, 2015: 45)\\
+				\> \> \> (synonymized by Jansen \& Franz, 2015: 45)\\
 				\> \> = \textit{Thylacites microps} Say, 1831: 9\\
@@
 				\> \> \> (synonymized by LeConte, 1859: 286)\\
-			\> \textit{aeriballux} Jansen and Franz, 2015: 52\\
+			\> \textit{{\ae}riballux} Jansen \& Franz, 2015: 52\\
 			\> \textit{ampullaceus} \textbf{sp. nov.}\\
-			\> \textit{bulbifrons} Jansen and Franz, 2015: 81\\
-			\> \textit{caseyi} (Sharp, 1891: 151) [redescribed by Jansen and Franz, 2015: 66]\\
+			\> \textit{bulbifrons} Jansen \& Franz, 2015: 81\\
+			\> \textit{caseyi} (Sharp, 1891: 151) [redescribed by Jansen \& Franz, 2015: 66]\\
 				\> \> = \textit{Pseudelissa caseyi} Sharp, 1891: 151\\
 				\> \> \> (genus synonymized by Pierce, 1909: 359)\\
-			\> \textit{conicollis} Green, 1920: 194 [redescribed by Jansen and Franz, 2015: 33]\\
-			\> \textit{constrictus} (Casey, 1888: 272) [redescribed by Jansen and Franz, 2015: 22]\\
+			\> \textit{conicollis} Green, 1920: 194 [redescribed by Jansen \& Franz, 2015: 33]\\
+			\> \textit{constrictus} (Casey, 1888: 272) [redescribed by Jansen \& Franz, 2015: 22]\\
 				\> \> = \textit{Elissa constricta} Casey, 1888: 272\\
 				\> \> \> (genus synonymized by Kissinger, 1964: 30)\\
-			\> \textit{cracens} Jansen and Franz, 2015: 61\\
+			\> \textit{cracens} Jansen \& Franz, 2015: 61\\
 			\> \textit{franko} \textbf{sp. nov.}\\
-			\> \textit{gravivultus} Jansen and Franz, 2015: 92\\
-			\> \textit{griseus} (Sleeper, 1960: 84) [redescribed by Jansen and Franz, 2015: 96]\\
+			\> \textit{gravivultus} Jansen \& Franz, 2015: 92\\
+			\> \textit{griseus} (Sleeper, 1960: 84) [redescribed by Jansen \& Franz, 2015: 96]\\
 				\> \> = \textit{Piscatopus griseus} Sleeper, 1960: 84\\
-				\> \> \> (genus synonymized by Jansen and Franz, 2015: 96)\\
-			\> \textit{imberbus} Jansen and Franz, 2015: 18\\
-			\> \textit{languidus} Horn, 1876: 18 [redescribed by Jansen and Franz, 2015: 40]\\
+				\> \> \> (genus synonymized by Jansen \& Franz, 2015: 96)\\
+			\> \textit{imberbus} Jansen \& Franz, 2015: 18\\
+			\> \textit{languidus} Horn, 1876: 18 [redescribed by Jansen \& Franz, 2015: 40]\\
 				\> \> = \textit{Pseudelissa cinerea} Casey, 1888: 274\\
 				\> \> \> (synonymized by Pierce, 1909: 359)\\
-			\> \textit{laticeps} (Casey, 1888) [redescribed by Jansen and Franz, 2015: 27]\\
+			\> \textit{laticeps} (Casey, 1888: 272) [redescribed by Jansen \& Franz, 2015: 27]\\
 				\> \> = \textit{Elissa laticeps} Casey, 1888: 272\\
 				\> \> \> (genus synonymized by Kissinger, 1964: 30)\\
-			\> \textit{politus} Jansen and Franz, 2015: 86\\
-			\> \textit{puticulatus} Jansen and Franz, 2015: 75\\
-			\> \textit{reburrus} Jansen and Franz, 2015: 57\\
-			\> \textit{rutellirostris} Jansen and Franz, 2015: 103\\
+			\> \textit{politus} Jansen \& Franz, 2015: 86\\
+			\> \textit{puticulatus} Jansen \& Franz, 2015: 75\\
+			\> \textit{reburrus} Jansen \& Franz, 2015: 57\\
+			\> \textit{rutellirostris} Jansen \& Franz, 2015: 103\\
 			\> \textit{sculptilis} \textbf{sp. nov.}\\
-			\> \textit{trisetosus} Jansen and Franz, 2015: 71\\
+			\> \textit{trisetosus} Jansen \& Franz, 2015: 71\\
 			\> \textit{tylotos} \textbf{sp. nov.}\\
@@
 \section*{Identification key}
-	\#
-\section*{Phylogenetic placement of new species}
-	\#
+	\begin{xtabular}{@{}
+                p{\dimexpr.1\textwidth-\tabcolsep\relax}
+                p{\dimexpr.9\textwidth-\tabcolsep\relax}@{}}
+
+		{1} & {Procox{\ae} apparently separate, with intercoxal processes touching or very nearly so}{\dotfill}{\textbf{2}}\\
+		{--} & {Procox{\ae} apparently contiguous, with intercoxal processes short and not touching}{\dotfill}{\textbf{3}}\\
+
+		{2~(1)} & {Rostrum approximately square and as wide as head in dorsal view; ramus of spermatheca basally narrow, forming a stalk that tapers into an apical bulb}{\breakfill}{\textbf{\textit{Minyomerus rutellirostris} Jansen \& Franz, 2015 [JF2015]}}\\
+		{--} & {Rostrum approximately trapezoidal and narrower than the head in dorsal view; ramus of spermatheca cylindrical, somewhat bulbous, and basally constricted}{\breakfill}{\textbf{\textit{Minyomerus griseus} (Sleeper, 1960) [JF2015]}}\\
+
+		{3~(1)} & {Anterior margin of pronotum bearing a full, well-developed tuft of 10 or more ocular vibriss{\ae}; anterolateral margins of prementum explanate, angular, and posteriorly declivous, with a distinctly hexagonal appearance}{\dotfill}{\textbf{4}}\\
+		{--} & {Ocular vibriss{\ae} reduced in number or length; anterior margins of prementum not explanate and declivous, typically with a pentagonal appearance}{\dotfill}{\textbf{5}}\\
+
+		{4~(3)} & {Head very wide and only somewhat swollen between eyes; rostrum ca.
+4\x wider than long in dorsal view; pronotum in dorsal view cylindrical; elytral set{\ae} short, brown, and sub-recumbent; ramus of spermatheca stalked and with apical bulb abruptly constricted, not tapering at point of connection to stalk}{\dotfill}{\textbf{\textit{Minyomerus laticeps} (Casey, 1888) [JF2015]}}\\
+		{--} & {Head and rostrum typical (rostrum 2-3\x wider than long in dorsal view); pronotum in dorsal view somewhat globular, with a strong anterior constriction; elytral set{\ae} short and setiform, especially near disk; spermatheca without basal stalk}{\breakfill}{\textbf{\textit{Minyomerus constrictus} (Casey, 1888) [JF2015]}}\\
+
+		{5~(3)} & {Metatibial apex strongly convex, with set{\ae} similar in length to those of remainder of leg, somewhat lighter in color and translucent, and slightly lamelliform; head somewhat conical in form, rounded between the eyes; elytral set{\ae} copious, not in uniform rows on intervals, instead appearing in offset rows, especially near elytral suture and declivity}{\dotfill}{\textbf{6}}\\
+		{--} & {Metatibial apex oblique or weakly convex, with set{\ae} short and conical in appearance; head roughly quadrate; elytral set{\ae} in relatively uniform rows on elytra, not strongly offset}{\dotfill}{\textbf{7}}\\
+
+		{6~(5)} & {Elytral stri{\ae} deeply and distinctly punctate, appearing pin-striped; elytra without obvious humeri, gradually widening posteriorly; ramus of spermatheca elongate, annulate, and sub-apically situated on corpus}{\dotfill}{\mbox{\textbf{\textit{Minyomerus {\ae}riballux} Jansen \& Franz, 2015 [JF2015]}}}\\
+		{--} & {Elytral stri{\ae} punctate, with punctures somewhat obscured by appressed scales; elytra somewhat pyriform, with weak, but obviously present humeri; ramus of spermatheca elongate, somewhat swollen, and sub-apically situated on corpus}{\breakfill}{\textbf{\textit{Minyomerus reburrus} Jansen \& Franz, 2015 [JF2015]}}\\
+
+		{7~(5)} & {Elytra very strongly convex in lateral view; anterior margin of pronotum wider than posterior margin; spermatheca comma-shaped, with ramus reduced, apically flattened and sub-contiguous with the collum; {\ae}deagal pedon membranous ventrally, and not fully sclerotized}{\breakfill}{\textbf{\textit{Minyomerus conicollis} Green, 1920 [JF2015]}}\\
+		{--} & {Elytra only somewhat convex to nearly flat in lateral view; anterior margin of pronotum similar in length to posterior margin; spermatheca variable; {\ae}deagal pedon fully sclerotized}{\breakfill}{\textbf{8}}\\
+
+		{8~(7)} & {Body shape distinctly flask-like, with strongly constricted, sub-cylindrical pronotum and greatly protuberant elytra; in dorsal view, elytra nearly 2\x width of pronotum at maximum width and nearly 3/4\x as wide as long; in lateral view, anterior and posterior declivities of elytra abrupt and nearly vertical, with anterior elytral margin projecting strongly and characteristically dorsad of articulation with posterior pronotal margin; corpus of spermatheca with highly elongate projection aligned with midline of the ramus, which is basally tapered and angled at nearly 45\td to corpus}{\dotfill}{\textbf{\textit{Minyomerus ampullaceus} [JF2018], sp.
+n.}}\\
+		{--} & {Body shape usually narrow; elytra typically not more than 1.5\x width of pronotum and typically not more than 2/3\x as wide as long in dorsal view; elytral declivities in lateral view variable, but anterior margin never abruptly and strongly projected dorsad of posterior pronotal margin; spermatheca variable, but never with elongate projection aligned with midline of ramus}{\dotfill}{\textbf{9}}\\
+
+		{9~(8)} & {Set{\ae} of elytral disc a mix of shorter, brown set{\ae} and longer, more erect, white set{\ae}}{\dotfill}{\textbf{10}}\\
+		{--} & {Set{\ae} of elytral disc uniform}{\dotfill}{\textbf{12}}\\
+
+		{10~(9)} & {Anterior margin of pronotum bearing strikingly long set{\ae}, which project laterally up to 80\td from longitudinal body axis and at least equal to diameter of eye;	spermatheca with short, somewhat bulbous corpus, ramus sub-equal in size and perpendicular to corpus, and collum strongly recurved along basal 1/3 of its length; {\ae}deagal pedon relatively short and wide, and abruptly constricted in apical 1/5, thereafter tapered to rounded point}{\breakfill}{\textbf{\textit{Minyomerus franko} [JF2018], sp.
+n.}}\\
+		{--} & {Anterior margin of pronotum bearing set{\ae} more strongly directed anteriorly and never as long as diameter of eye; spermatheca variable; {\ae}deagal pedon, where known, narrow and expanded laterally in region of ostium}{\dotfill}{\textbf{11}}\\
+
+		{11~(10)} & {Set{\ae} apically explanate, appearing somewhat spatulate; corpus of spermatheca uniquely elongate, ramus short and cylindrical}{\dotfill}{\textbf{\textit{Minyomerus caseyi} (Sharp, 1891) [JF2015]}}\\
+		{--} & {Set{\ae} linear; corpus of spermatheca typical, ramus bulbous and basally constricted}{\breakfill}{\textbf{\textit{Minyomerus trisetosus} Jansen \& Franz, 2015 [JF2015]}}\\
+
+		{12~(9)} & {Anterior margin of pronotum lined with linear set{\ae} that extend anteriorly beyond margin by half their length}{\dotfill}{\textbf{13}}\\
+		{--} & {Anterior margin of pronotum lacking set{\ae}, or with set{\ae} that do not extend far beyond margin}{\breakfill}{\textbf{14}}\\
+
+		{13~(12)} & {Lateral margins of gular cavity strongly rounded, never straight, and slightly longer than posterior margin; frons weakly projected between eyes; appressed scales on elytra without opalescent sheen; nasal plate with or without metallic reflections; lamina of spiculum ventrale sclerotized throughout}{\dotfill}{\textbf{\textit{Minyomerus languidus} Horn, 1876 [JF2015]}}\\
+		{--} & {Lateral margins of gular cavity nearly straight, and not longer than posterior margin; frons strongly projected between eyes; appressed scales with strong opalescent sheen; nasal plate with metallic reflections; lamina of spiculum ventrale with a membranous region present medially between laminar arm}{\dotfill}{\textbf{\textit{Minyomerus gravivultus} Jansen \& Franz, 2015 [JF2015]}}\\
+
+		{14~(12)} & {Elytra each 4-5\x as long as broad in dorsal view, strongly punctate; elytra constricted anteriad of humeri, narrower than the pronotum, widening thereafter near the humeri; spermatheca with the corpus somewhat bulbous, and the ramus either flattened somewhat or slightly elongate}{\breakfill}{\textbf{\textit{Minyomerus cracens} Jansen \& Franz, 2015 [JF2015]}}\\
+		{--} & {Elytra not so elongate, variably punctate; elytra lacking basal constriction; spermatheca variable}{\dotfill}{\textbf{15}}\\
+
+		{15~(14)} & {Elytral stri{\ae} with large, obvious punctures}{\dotfill}{\textbf{16}}\\
+		{--} & {Elytral stri{\ae} without evident punctures}{\dotfill}{\textbf{17}}\\
+
+		{16~(15)} & {Frons strongly protuberant; elytra in lateral view convex dorsally; spermatheca with corpus possessing an annulate, rectate projection nearly 1/2\x length of ramus; {\ae}deagal pedon evenly curving towards apex; {\ae}deagal flagellum with spiriform apical sclerite that spirals counterclockwise and of equal length to {\ae}deagal pedon}{\breakfill}{\textbf{\textit{Minyomerus bulbifrons} Jansen \& Franz, 2015 [JF2015]}}\\
+		{--} & {Frons not so protuberant; elytra in lateral view nearly flat dorsally; spermatheca with corpus possessing an annulate, rectate projection nearly 2/3\x length of the ramus; {\ae}deagal pedon narrow and elongate; {\ae}deagal flagellum with very minute apical sclerite}{\breakfill}{\textbf{\textit{Minyomerus puticulatus} Jansen \& Franz, 2015 [JF2015]}}\\
+
+		{17~(15)} & {Frons strongly protruding in lateral view by ca. 2\x diameter of eye}{\dotfill}{\textbf{18}}\\
+		{--} & {Frons not or weakly protruding in lateral view by 1.5\x diameter of eye or less}{\dotfill}{\textbf{19}}\\
+
+		{18~(17)} & {Nasal plate defined by inversely V-shaped, impressed lines; spermatheca with the ramus elongate and apically swollen, corpus possessing an annulate, rectate projection nearly 1/2\x length of the ramus, and cornu evenly recurved throughout its length; {\ae}deagal flagellum with a spiriform apical sclerite that spirals clockwise and of equal length to pedon}{\breakfill}{\textbf{\textit{Minyomerus politus} Jansen \& Franz, 2015 [JF2015]}}\\
+		{--} & {Nasal plate lacking distinct impressions; spermatheca with ramus basally tapered with a short stalk, corpus narrow and lacking an annulate rectate bulb, and cornu with an abrupt apical curve; males not known}{\dotfill}{\textbf{\textit{Minyomerus tylotos} [JF2018], sp.
+n.}}\\
+
+		{19~(17)} & {Ventrolateral sulci weakly defined as a notch ventrad of antennal insertion, or absent entirely; intervals broadly sculpted and raised, and stri{\ae} not punctate; body generally robust in overall quality; appressed scales uniformly beige and gray, with a
+distinctly ‘crusty’ appearance; spematheca with ramus and collum appearing
+as two subcontiguous, apically invaginated bulbs}{\dotfill}{\textbf{\textit{Minyomerus microps} (Say, 1831) [JF2015]}}\\
+		{--} & {Ventrolateral sulci deeply and distinctly defined along their entire length; intervals, if raised, only sculpted along lateral faces of elytra, not on disk; body usually not markedly robust; appressed scales either translucent or otherwise typical of genus, not beige and crusted; spermatheca distincly sinuate, with well defined, protruding ramus}{\dotfill}{\textbf{20}}\\
+
+		{20~(19)} & {Elytra with very minute set{\ae}, only perceptible at high magnification; lateral faces of elytra with intervals not noticeably raised; ramus of spermatheca elongate, cylindrical, and slightly thinner than corpus, cornu strongly recurved in basal half with uniquely sinuate appearance, both corpus and cornu with hood-like projections shorter than ramus; males not known}{\breakfill}{\textbf{\textit{Minyomerus imberbus} Jansen \& Franz, 2015 [JF2015]}}\\
+		{--} & {Elytra with easily visible, linear set{\ae}; lateral faces of elytra with intervals raised; ramus of spermatheca bulbous, basally tapered, and similar in width to corpus, cornu strongly recurved, but short in basal half with uniquely sinuate appearance, both corpus and cornu with hood-like projections longer than ramus; {\ae}deagal pedon narrow and cylindrical, apically tapered}{\breakfill}{\textbf{\textit{Minyomerus sculptilis} [JF2018], sp.
+n.}}\\
+	\end{xtabular}
+
+\section*{Phylogenetic results}
+	A matrix of 52 characters was assembled for the 26 terminal taxa (Tab. 1).
+	These characters are comprised of all 46 characters included in the revision of \textit{Minyomerus} [JF2015], plus an additional 6 characters intended to identify putative sister taxa to the newly described species.
+	Parsimony analysis returned a single, most-parsimonious cladogram (henceforth MPT) with a length (L) of 99 steps, a consistency index (CI) of 60 and a retention index (RI) of 80 \citep{farris1989}.
+	TNT (Tree Analysis Using New Technology) was used to confirm that the shortest tree had been found \citep{goloboff2008}.
+	The most-parsimonious cladogram is shown in Fig.~\#, with relative and absolute Bremer support values (see also \# Methods: Phylogenetic analysis) mapped along the left side of each branch; nodes with bootstrap support above 0.95 are marked with a ``*'' symbol to the right of each node.
+
+	The characters, states, and preferred optimizations are described in this section.
+	Characters relating to placement of the herein described taxa are discussed in detail in the Discussion (\#) section, along with changes in species group composition and tree topology from \citet{jansen2015}.
+	 For all characters not resolved as unreversed synapomorphies, both the individual consistency (ci) and retention (ri) indices are provided.
+	Characters are numbered in accordance with descriptive sequence used in the species accounts.
+	A ``–'' symbol indicates inapplicable (character, state), whereas a ``?'' symbol indicates missing information, e.g., due to the unavailability of male specimens or insufficient specimens on hand to permit full dissections.
+	Characters 9, 27, 39, 45 - 47, 49, and 51 were mapped onto the preferred phylogeny using ACCTRAN optimization (see \citealt{agnarsson2008}), and the remaining characters had an unambiguous optimization.
+
+	\begin{table}[h!]
+  	\begin{center}
+    	\caption{\textbf{Taxon/character matrix used for for cladistic analysis}.
+Includes all species of \textit{Minyomerus} [JF2015], newly designated species, and select outgroup taxa.
+All multistate characters coded as additive, except for character 33.
+The symbol ``–'' denotes inapplicable character states, whereas ``?'' denotes missing information (see also text).}
+    	\label{tab::table1}
+    	\ttfamily
+    	\footnotesize
+    	\begin{tabular}{m{11.10}|l}
+      	\toprule
+      	\multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Taxon{\textbackslash}Character}}} 
+      														& ~~~~0~~~~~1~~~~~1~~~~~2~~~~~2~~~~~3~~~~~3~~~~~4~~~~~4~~~~~5~~~\\
+      														& ~~~~5~~~~~0~~~~~5~~~~~0~~~~~5~~~~~0~~~~~5~~~~~0~~~~~5~~~~~0~~~\\
+      	\midrule
+      	Sitona.californicus       & 00-00~?????~00000~00000~00000~00000~00---~-0---~--???~?????~??\\
+      	Pandeleteius.cinereus     & 11000~?????~01000~00001~01000~00100~00000~000-0~00???~?????~??\\
+      	Pandeleteinus.subcancer   & 11000~?????~01000~00001~01010~00100~00000~000-0~00???~?????~??\\
+				Isodrusus.debilis         & 11000~?????~01000~00001~01011~00100~00000~000-0~00???~?????~??\\
+				Isodacrys.buchanani       & 11000~?????~01000~00001~01011~00101~00000~000-0~00???~?????~??\\
+				Minyomerus.constrictus    & 21100~00010~02110~01002~00011~11211~00000~00000~00000~01010~00\\
+				Minyomerus.laticeps       & 21100~00010~02110~01002~00011~11211~00000~00000~00000~01010~00\\
+				Minyomerus.imberbus       & 21100~?????~02010~11002~10011~11211~01001~00000~00???~?????~??\\
+				Minyomerus.sculptilis     & 21100~?????~02010~11002~10011~11211~01001~00000~00001~00000~10\\
+				Minyomerus.conicollis     & 21100~00000~02010~11002~10011~10211~00001~10000~01000~00000~00\\
+				Minyomerus.languidus      & 21000~11100~02010~11002~10011~10211~00001~10000~?????~?????~??\\
+				Minyomerus.microps        & 21001~11101~02110~11002~10011~10211~00001~10000~10???~?????~??\\
+				Minyomerus.tylotos        & 21001~11101~02110~11002~10011~10211~00001~10000~00???~?????~??\\
+				Minyomerus.cracens        & 21000~11101~02020~11112~10011~11211~00001~10001~00000~10010~10\\
+				Minyomerus.ampullaceus    & 21000~?????~02020~11??2~10011~11211~00001~11001~00???~?????~??\\
+				Minyomerus.{\textnormal{\textit{{\ae}}}}riballux  
+																	& 22000~11101~12020~11012~10011~20211~00001~11001~10000~00000~01\\
+				Minyomerus.reburrus       & 22000~11101~12020~11112~10011~20211~00001~11021~00???~?????~??\\
+				Minyomerus.franko         & 21110~10100~02020~11002~10011~11211~00001~10011~10010~00000~01\\
+				Minyomerus.caseyi         & 21110~00101~02020~11112~10011~11211~00001~10101~10010~10010~01\\
+				Minyomerus.trisetosus     & 21110~00101~02020~11012~10011~10211~00001~10101~10???~?????~??\\
+				Minyomerus.gravivultus    & 21100~11101~02120~11002~10011~10211~00111~10000~??010~00000~11\\
+				Minyomerus.griseus        & 21100~10101~02120~01002~10111~11211~00111~10000~00010~01100~10\\
+				Minyomerus.rutellirostris & 21100~10101~02120~11002~10111~11211~00111~10000~00010~01100~10\\
+				Minyomerus.puticulatus    & 21000~11101~02020~11012~10011~11211~10101~10010~01011~01000~11\\
+				Minyomerus.bulbifrons     & 21000~11101~02021~11112~10011~10211~10101~10000~01110~01001~01\\
+				Minyomerus.politus        & 21000~?????~02021~11112~10011~10211~10101~10010~01111~01001~11\\
+      	\bottomrule
+    	\end{tabular}
+  	\end{center}
+	\end{table}
+
+	\begin{enumerate}
+		\item Habitus, form of appressed scales: (0) elongate pyriform, not overlapping; (1) sub-circular to polygonal, variously overlapping non-linearly; (2) sub-circular and only overlapping posteriorly.
+Coded as additive due to alignment of character states with the preferred phylogeny.
+Coding as non-additive in isolation or in unison with other additive multistate characters does not affect polarization of the character/states or alter the phylogeny.
+State 1 is a synapomorphy for the tanymecine clade [non-focal], whereas state 2 is a synapomorphy for \textit{Minyomerus} [JF2018].
+
+		\item Habitus, arrangement of elytral set{\ae}: (0) variously interspersed; (1) arranged in single-file rows on elytral intervals; (2) arranged non-uniformly on elytral intervals.
+Coded as additive due to alignment of character states with the preferred phylogeny.
+Coding as non-additive in isolation or in unison with other additive multistate characters does not affect polarization of the character/states or alter the phylogeny.
+State 1 is a synapomorphy for the tanymecine clade [non-focal], whereas state 2 is a synapomorphy the \textit{M.
+{\ae}riballux} - \textit{M.
+reburrus} clade [JF2018].
+
+		\item Habitus, lateral elytral set{\ae} and ventral set{\ae} differentiated from set{\ae} of elytral disc: (0) absent; (1) present.
+Homoplasy for \textit{Minyomerus} [JF2018], with a reversal (state 0) in the \textit{M.
+languidus} – \textit{M.
+politus} clade [JF2018], subsequent convergent gain (state 1) in the \textit{M.
+franko} - \textit{M.
+politus} clade, and convergent reversal (state 0) in the \textit{M.
+puticulatus} – \textit{M.
+politus} clade [JF2018] (ci = 25; ri = 70).
+
+	 	\item Habitus, rows of elytral set{\ae} with larger white set{\ae} randomly interspersed among smaller brown set{\ae}: (0) absent; (1) present.
+Synapomorphy for the \textit{M.
+franko} – \textit{M.
+trisetosus} clade [JF2018].
+Changed from \citet{jansen2015}, where \textit{M.
+rutellirostris} [JF2015] was previously coded as having this character; however, the white elytral set{\ae} of this species are not randomly interspersed, but follow a distinct, and uniquely derived, pattern where every other interval contains a row of such set{\ae}.
+
+	 	\item Habitus, elytra and pronotum generally large, protuberant, and sculpted in appearance along dorsal and lateral faces: (0) absent; (1) present.
+Synapomorphy for the \textit{M.
+microps} – \textit{M.
+tylotos} clade [JF2018].
+
+	 	\item Prementum, anterior margin forming a distinct face that continues to lateral margins: (0) absent; (1) present.
+Synapomorphy for the \textit{M.
+languidus} – \textit{M.
+politus} clade [JF2018], with a single reversal in the \textit{M.
+caseyi} – \textit{M.
+trisetosus} clade [JF2018] (ci = 50; ri = 75).
+
+	 	\item Prementum, strongly ligulate and with margins nearly straight, appearing pentagonal: (0) absent; (1) present.
+Synapomorphy for the \textit{M.
+languidus} – \textit{M.
+politus} clade [JF2018], with independent reversals in the \textit{M.
+franko} – \textit{M.
+trisetosus} clade [JF2018] and \textit{M.
+griseus} – \textit{M.
+rutellirostris} clade [JF2018], respectively (ci = 33; ri = 71).
+
+	 	\item Prementum, anterolateral margins simple, unexpanded: (0) absent; (1) present. Synapomorphy for the \textit{M. languidus} – \textit{M. politus} clade [JF2018].
+
+	 	\item Prementum, anterolateral margins explanate, angular, and posteriorly declivous, with a distinctly hexagonal appearance: (0) absent; (1) present.
+ACCTRAN optimization preferred (see \citealt{agnarsson2008}), therefore inferred as a synapomorphy for the \textit{M.
+constrictus} – \textit{M.
+laticeps} clade [JF2018].
+
+	 	\item Prementum, exposure of palpomere I: (0) exposed, visible beyond ligula and anterior margin of prementum in ventral view; (1) hidden, fully covered or only minutely exposed beyond ligula and anterior margin of prementum in ventral view.
+Synapomorphy for the \textit{M.
+microps} – \textit{M.
+politus} clade [JF2018], with a single reversal in \textit{M.
+franko} [JF2018] (ci = 50; ri = 75).
+
+	 	\item Rostrum, form in dorsal view: (0) approximately quadrate; (1) somewhat conical, medially convex. Synapomorphy for the \textit{M. {\ae}riballux} – \textit{M. reburrus} clade [JF2018].
+
+	 	\item Rostrum, form of nasal plate and demarcation of epistoma: (0) with three parallel, longitudinal carin{\ae}, and surface planar between these; (1) with a sharp, narrow, chevron-shaped carina demarcating epistoma; (2) with a broad, scale-covered, chevron-shaped carina demarcating epistoma.
+Coded as additive due to alignment of character states with preferred phylogeny.
+Coding as non-additive in isolation or in unison with other additive multistate characters does not affect polarization of the character/states or alter the phylogeny.
+State 1 is a synapomorphy for the tanymecine clade [non-focal], whereas state 2 is a synapomorphy for \textit{Minyomerus} [JF2018].
+
+	 	\item Rostrum, sulcus posteriad of nasal plate weakly impressed: (0) absent; (1) present.
+Convergently present in the \textit{M.
+constrictus} – \textit{M.
+laticeps} clade [JF2018], the \textit{M.
+microps} - \textit{M.
+tylotos} clade [JF2018], and the \textit{M.
+gravivultus} – \textit{M.
+rutellirostris} clade [JF2015] (ci = 33; ri = 60).
+
+	 	\item Rostrum, form of sulcus posteriad of nasal plate: (0) absent; (1) sulcus present, broad, and weakly punctate; (2) sulcus present, more strongly punctate.
+Coded as additive due to alignment of character states with preferred phylogeny.
+Coding as non-additive in isolation or in unison with other additive multistate characters does not affect polarization of the character/states or alter the phylogeny.
+Synapomorphy for \textit{Minyomerus} [JF2018] (state 1) and the \textit{M.
+cracens} – \textit{M.
+politus} clade [JF2018] (state 2), respectively.
+
+	 	\item Head, frons very strongly projected beyond anterior margin of eye, by 2\x anterior-posterior length of eye: (0) absent; (1) present.
+Synapomorphy for the \textit{M.
+bulbifrons} – \textit{M.
+politus} clade [JF2018].
+
+	 	\item Head, frons with posterior transverse constriction: (0) absent; (1) present.
+Synapomorphy for the \textit{M.
+imberbus} – \textit{M.
+politus} clade [JF2018], with a single reversal in \textit{M.
+griseus} [JF2015] (ci = 50, ri = 85).
+
+	 	\item Antenna, length of scrobe relative to funicle and club: (0) scrobe shorter than funicle and club combined; (1) scrobe subequal in length to funicle and club combined.
+Synapomorphy for \textit{Minyomerus} [JF2018].
+
+	 	\item Antenna, terminal funicular segment entirely without thin, nearly setiform scales: (0) absent; (1) present.
+Convergently present in \textit{M.
+cracens} [JF2015], \textit{M.
+reburrus} [JF2015], \textit{M.
+caseyi} [JF2015], and the \textit{M.
+bulbifrons} – \textit{M.
+politus} clade [JF2018] (ci = 25; ri = 25).
+
+	 	\item Antenna, terminal funicular segment at least partially clothed with broad scales: (0) absent; (1) present.
+Synapomorphy for the \textit{M.
+cracens} – \textit{M.
+politus} clade [JF2018] with independent reversals in \textit{M.
+franko} [JF2018] and the \textit{M.
+gravivultus} – \textit{M.
+rutellirostris} clade [JF2015] (ci = 33; ri = 71).
+
+	 	\item Head, angle of base in relation to prothorax: (0) directed anteriorly, in line with main body axis; (1) directed strongly ventrally; (2) directed slightly ventrally.
+Coded as additive due to alignment of character states with preferred phylogeny.
+Coding as non-additive in isolation or in unison with other additive multistate characters does not affect polarization of the character/states or alter the phylogeny.
+State 1 is a synapomorphy for the tanymecine clade [non-focal], whereas state 2 is a synapomorphy for \textit{Minyomerus} [JF2018].
+
+	 	\item Pronotum, condition of post-ocular vibriss{\ae}: (0) present in a well-developed tuft of 10 or more setae; (1) present in a reduced tuft of 3-7 set{\ae}.
+Synapomorphy for the \textit{M.
+imberbus} - \textit{M.
+politus} clade.
+
+	 	\item Prosternum, intercoxal process complete, undivided: (0) absent; (1) present.
+Synapomorphy for the tanymecine clade [non-focal], with a single reversal for \textit{Minyomerus} [JF2018] (ci = 50; ri = 66).
+
+	 	\item Prosternum, intercoxal process divided at midpoint between cox{\ae}, but both anterior and posterior processes extending completely between procox{\ae} and contiguous with each other: (0) absent; (1) present.
+Synapomorphy for the \textit{M.
+griseus} – \textit{M.
+rutellirostris} clade [JF2015].
+
+	 	\item Legs, fore femora not swollen in comparison to other legs: (0) absent; (1) present. Synapomorphy for the \textit{P. subcancer} – \textit{M. politus} clade [non-focal].
+
+	 	\item Legs, sculpture of ventral surface of protibi{\ae}: (0) evenly convex throughout; (1) with a longitudinal groove or concavity.
+Synapomorphy for the \textit{I.
+debilis}–\textit{M.
+politus} clade [JF2018].
+
+	 	\item Legs, setation of metatibial apex: (0) bristles at least as long as surrounding set{\ae} and setiform; (1) bristles shorter than surrounding set{\ae} and conical; (2) bristles sub-equal in length to surrounding set{\ae} and somewhat lamelliform.
+Coded as additive due to alignment of character states with preferred phylogeny, and the appearance of being a transformation series.
+Coding as non-additive in isolation or in unison with other additive multistate characters does not affect polarization of the character/states or alter the phylogeny.
+Synapomorphy for \textit{Minyomerus} [JF2018] (state 1) and the \textit{M.
+{\ae}riballux} – \textit{M.
+reburrus} clade [JF2018] (state 2), respectively.
+
+	 	\item Legs, curvature of metatibial apex: (0) convex ; (1) oblique.
+ACCTRAN optimization preferred (see \citealt{agnarsson2008}), therefore inferred as a synapomorphy for \textit{Minyomerus} [JF2018] with a reversal (state 0) in the \textit{M.
+conicollis} - \textit{M.
+politus} clade [JF2018], then a convergent gain (state 1) in the \textit{M.
+cracens} – \textit{M.
+politus} clade [JF2018], with independent reversals (state 0) in the \textit{M.
+{\ae}riballux} – \textit{M.
+reburrus} clade [JF2018], \textit{M.
+trisetosus} [JF2015], \textit{M.
+gravivultus} [JF2015], and the \textit{M.
+bulbifrons} - \textit{M.
+politus} clade [JF2018] (ci = 14; ri = 40).
+
+		\item Legs, relative length of mesotarsi to mesotibi{\ae}: (0) tarsi much shorter than tibi{\ae}; (1) tarsi at least equal in length to tibi{\ae}; (2) tarsi slightly shorter than tibi{\ae}.
+Coded as additive due to alignment of character states with preferred phylogeny.
+Coding as non-additive in isolation or in unison with other additive multistate characters does not affect polarization of the character/states or alter the phylogeny.
+State 1 is a synapomorphy for the tanymecine clade [non-focal], whereas state 2 is a synapomorphy for \textit{Minyomerus} [JF2018].
+
+		\item Legs, tarsi ventrally spinose: (0) absent; (1) present. Synapomorphy for \textit{Minyomerus} [JF2018].
+
+		\item Elytra, humeral angle rounded, not projected: (0) absent; (1) present. Synapomorphy for the \textit{I. buchanani} – \textit{M. politus} clade [non-focal].
+
+		\item Female terminalia, spermatheca with apical cylindrical bulb on corpus: (0) absent; (1) present. Synapomorphy for the \textit{M. puticulatus} – \textit{M. politus} clade [JF2018].
+
+		\item Female terminalia, corpus of spermatheca sinuate: (0) absent; (1) present. Synapomorphy for the \textit{M. imberbus} - \textit{M. sculptilis} clade [JF2018].
+
+		\item Female terminalia, lamina of spiculum ventrale less sclerotized between laminar arms: (0) absent; (1) present.
+Coded as inapplicable for \textit{S.
+californicus} [non-focal], as laminar arms are not apparent.
+Synapomorphy for the \textit{M.
+gravivultus} – \textit{M.
+politus} clade [JF2018].
+
+		\item Female terminalia, lamina of spiculum ventrale with laminar arms bifurcating around a membranous region: (0) absent; (1) present.
+Coded as inapplicable for \textit{S.
+californicus} [non-focal], as laminar arms are not apparent.
+Synapomorphy for the \textit{M.
+gravivultus} – \textit{M.
+rutellirostris} clade [JF2015].
+
+		\item Female terminalia, lamina of spiculum ventrale with style basally divided or obscured, not mesally intact: (0) absent; (1) present.
+Coded as inapplicable for \textit{S.
+californicus} [non-focal], as laminar arms are not apparent.
+Synapomorphy for the \textit{M.
+imberbus} – \textit{M.
+politus} clade [JF2018].
+
+		\item Female terminalia, lamina of spiculum ventrale with laminar arms clearly bifurcating.
+(0) absent; (1) present.
+Coded as inapplicable for \textit{S.
+californicus} [non-focal], as laminar arms are not apparent.
+Synapomorphy for the \textit{M.
+conicollis} – \textit{M.
+politus} clade [JF2018].
+
+		\item Female terminalia, laminar arms narrowly bifurcating basally, thereafter sub-parallel mesally: (0) absent; (1) present.
+Synapomorphy for the \textit{M.
+ampullaceus} - \textit{M.
+reburrus} clade [JF2018].
+
+		\item Female terminalia, coxites of ovipositor with a lateral, anteriorly-directed, recurved, alate process: (0) absent; (1) present.
+Coded as inapplicable for \textit{S.
+californicus} [non-focal], as coxites of ovipositor are not apparent.
+Synapomorphy for the \textit{M.
+caseyi} – \textit{M.
+trisetosus} clade [JF2018].
+
+		\item Female terminalia, relative length of styli to coxites of ovipositor: (0) Similar in size; (1) distinctly shortened; (2) highly reduced, appearing minute.
+Coded as non-additive, due to strong differences in structure of coxites and styli in state 2; inapplicable for outgroup taxa, as styli of ovipositor are not apparent.
+ACCTRAN optimization preferred (see \citealt{agnarsson2008}), therefore inferred as convergent gains in \textit{M.
+franko} [JF2018] and the \textit{M.
+puticulatus} – \textit{M.
+politus} clade [JF2018] (state 1), with a single reversal in \textit{M.
+bulbifrons} [JF2015] (state 0).
+Autapomorphy for \textit{M.
+reburrus} [JF2015] (state 2) (ci = 50, ri = 0).
+
+		\item Female terminalia, condition of medial, anteriorly-directed, sclerotized process of coxites of ovipositor: (0) fully developed; (1) reduced and inapparent.
+Coded as inapplicable for \textit{S.
+californicus} [non-focal], as coxites of ovipositor are not apparent.
+Synapomorphy for the \textit{M.
+cracens} – \textit{M.
+politus} clade [JF2018], with a single reversal in the \textit{M.
+gravivultus} - \textit{M.
+politus} clade [JF2018] (ci = 50, ri = 83).
+
+		\item Female terminalia, anterior margin of tergum VII entirely free of sclerotized band: (0) absent; (1) present.
+Coded as inapplicable for \textit{S.
+californicus} [non-focal], as the tergum VII is evenly sclerotized throughout.
+Convergently present in \textit{M.
+microps} [JF2015], \textit{M.
+{\ae}riballux} [JF2015], and the \textit{M.
+franko} – \textit{M.
+trisetosus} clade [JF2018] (ci = 33; ri = 50).
+
+		\item Female terminalia, anterior margin of tergum VII sclerotized fully, appearing as an obviously complete band: (0) absent; (1) present.
+Coded as inapplicable for \textit{S.
+californicus} [non-focal], as the tergum VII is evenly sclerotized throughout.
+Convergently present in \textit{M.
+conicollis} [JF2015] and the \textit{M.
+puticulatus} – \textit{M.
+politus} clade [JF2018] (ci = 50; ri = 66).
+
+		\item Male terminalia, apical sclerite of {\ae}deagal flagellum elongate-spiriform: (0) absent; (1) present. Synapomorphy for the \textit{M. bulbifrons} – \textit{M. politus} clade [JF2018].
+
+		\item Male terminalia, style of spiculum gastrale with an anterior ventral flange: (0) absent; (1) present. Synapomorphy for the \textit{M. franko} – \textit{M. politus} clade [JF2018].
+
+		\item Male terminalia, lamina of spiculum gastrale longer than broad and anteriorly extended along syle: (0) absent; (1) present.
+ACCTRAN optimization preferred (see \citealt{agnarsson2008}), therefore inferred as convergent gains in the \textit{M.
+imberbus} - \textit{M.
+sculptilis} clade [JF2018] and the \textit{M.
+puticulatus} – \textit{M.
+politus} clade [JF2018], with a reversal in \textit{M.
+bulbifrons} [JF2015] (ci = 33; ri = 0).
+
+		\item Male terminalia, sub-triangular sclerites of sternum VIII with a medial process: (0) absent; (1) present.
+ACCTRAN optimization preferred (see \citealt{agnarsson2008}), therefore inferred as convergent gains in \textit{M.
+cracens} [JF2015] and the \textit{M.
+caseyi} – \textit{M.
+trisetosus} clade [JF2018] (ci = 50, ri = 0).
+
+		\item Male terminalia, curvature of posterior margin of tergum VII: (0) evenly arcuate; (1) medially incurved.
+ACCTRAN optimization preferred (see \citealt{agnarsson2008}), therefore convergently present in the \textit{M.
+constrictus} – \textit{M.
+laticeps} clade [JF2018] and the \textit{M.
+gravivultus} – \textit{M.
+politus} clade [JF2018] with a reversal in \textit{M.
+gravivultus} [JF2015] (ci = 33; ri = 66).
+
+		\item Male terminalia, tergum VII approximately 4\x as long as broad: (0) absent; (1) present. Synapomorphy for the \textit{M. griseus} – \textit{M. rutellirostris} clade [JF2018].
+
+		\item Male terminalia, {\ae}deagal pedon expanded laterally around ostium: (0) absent; (1) present.
+ACCTRAN optimization preferred (see \citealt{agnarsson2008}), therefore convergently present in the \textit{M.
+constrictus} – \textit{M.
+laticeps} clade [JF2018], \textit{M.
+cracens}, and the \textit{M.
+caseyi} –\textit{ M.
+trisetosus} clade [JF2018] (ci = 33; ri = 33).
+
+		\item Male terminalia, {\ae}deagal pedon broad basally, evenly tapering toward apex: (0) absent; (1) present. Synapomorphy for the \textit{M. bulbifrons} – \textit{M. politus} clade [JF2018].
+
+		\item Male terminalia, {\ae}deagal pedon medially sclerotized along dorsum: (0) absent; (1) present.
+ACCTRAN optimization preferred (see \citealt{agnarsson2008}), therefore convergently present in the \textit{M.
+imberbus} - \textit{M.
+sculptilis} clade [JF2018], \textit{M.
+cracens}, [JF2015] and the \textit{M.
+gravivultus} – \textit{M.
+politus} clade [JF2018], with a reversal in \textit{M.
+bulbifrons} [JF2015] (ci = 25; ri = 50).
+
+		\item Male terminalia, width of connection between apodemes of {\ae}deagal tegmen: (0) wider than base of apodeme; (1) narrower than base of apodeme.
+Synapomorphy for the \textit{M.
+ampullaceus} – \textit{M.
+politus} clade [JF2018] , with a single reversal in the \textit{M.
+griseus} – \textit{M.
+rutellirostris clade} [JF2018] (ci = 50; ri = 83).
+	\end{enumerate}
+
+\section*{Discussion}
+	\subsection*{Parallels with prior work}
+		The most-parsimonious cladogram of this work (Fig.~\#) exhibits important differences compared to that of \citet{jansen2015} with respect relationships between species groups, in large part due to the unique character combinations present in the newly-added taxa (need citation \#).
+		Nonetheless, we resolve three key clades with strong support, also inferred by and in corroboration with \citet{jansen2015}, as follows:
+		\begin{enumerate}
+			\item The genus \textit{Minyomerus} [JF2018] is well-supported by the same eight synapomorphies identified by \citet{jansen2015}, as specified in the Introduction of this manuscript (Bremer support value [henceforth: bsv] = 10, relative fit difference [henceforth: rfd] = 95; Bootstrap [henceforth: boot] = 100).
+			\item The species \textit{M.
+griseus} [JF2015], formerly of the monotypic genus \textit{Piscatopus} sec.
+Sleeper (1960), forms a well-supported clade with \textit{M.
+rutellirostris} [JF2015] (bsv = 4, rfd = 77, boot = 96).
+These taxa jointly share the same two synapomorphies (chars.
+23:1 and 48:1) provided in \citet{jansen2015}: (1) the intercoxal process is divided at the midpoint between the cox{\ae}, but has both the anterior and posterior processes extending completely between the procox{\ae} and contiguous with each other; and (2) the male tergum VII is nearly 4\x as long as broad, respectively.
+In addition, the \textit{M.
+gravivultus} - \textit{M.
+griseus} [JF2015] clade (bsv = 3, rfd = 60), as resolved in the current cladogram, is perfectly congruent with that of \citet{jansen2015}.
+This clade is nested within \textit{Minyomerus} [JF2018], in support of the classificatory emendations made by \citet{jansen2015}, whereby the genus \textit{Piscatopus} sec.
+Sleeper (1960) was invalidated as a junior synonym of \textit{Minyomerus} [JF2015].
+			\item The genus \textit{Minyomerus} [JF2018] is nested within a well-supported clade of Tanymecini [non-focal] (boot = 100).
+However we note, in agreement with \citet{jansen2015}, that significant further work is needed to assess the phylogenetic relationships between all genera presently assigned to the Tanymecini [non-focal] \citep{alonso1999}.
+		\end{enumerate}
+
+	\subsection*{Intrageneric relationships}
+		While some species groups inferred by \citet{jansen2015} remain intact, but with different character alignment, internal topology, or their placement within the genus, others are entirely different; we identify these major topological and compositional phylogenetic differences here.
+
+		Within \textit{Minyomerus} [JF2018], and beginning at the basal-most node and proceeding nodewise apically, the first major incongruence with \textit{Minyomerus} [JF2015] is the placement of \textit{M.
+imberbus} [JF2015].
+		This species was sister to the \textit{M.
+constrictus} - \textit{M.
+laticeps} [JF2015] clade (corresponding to ``\textit{Elissa}'' sec.
+Casey (1888), but see \citealt{jansen2015}), forming a clade sister to the \textit{M.
+conicollis} - \textit{M.
+rutellirostriss} clade [JF2015].
+		By contrast, the present analysis places \textit{M.
+imberbus} [JF2015] in a clade with \textit{M.
+sculptilis} [JF2015] (see also \# below), sister to \textit{M.
+conicollis} - \textit{M.
+politus} [JF2018] clade.
+		The inferred \textit{M.
+imberbus} - \textit{M.
+politus} [JF2018] clade (bsf = 2, rfd = 50) is supported by three synapomorphies: (1) presence of a transverse constriction across the posterior of the frons (char 16: 1); (2) presence of a reduced tuft of post-ocular vibriss{\ae} (char.
+21: 1); and (3) a mesally obscure lamina of the spiculum ventrale in the female (char.
+35: 1).
+
+		The MPT of the current analysis is thereafter topologically identical to that of \citet{jansen2015} until the \textit{M.
+cracens} - \textit{M.
+politus} [JF2018] clade, and the \textit{M.
+ampullaceus} - \textit{M.
+politus} clade, which correspond compositionally and topologically to the \textit{M.
+{\ae}riballux} - \textit{M.
+rutellirostris} [JF2015] clade, respectively.
+		In \textit{Minyomerus} [JF2015], \textit{M.
+cracens} was placed sister to the \textit{M.
+caseyi} - \textit{M.
+trisetosus} [JF2015] clade, forming a clade sister to the \textit{M.
+{\ae}riballus} - \textit{M.
+reburrus} [clade]; this larger \textit{M.
+{\ae}riballux} - \textit{M.
+trisetosus} [JF2015] clade was then sister to the \textit{M.
+puticulatus} - \textit{M.
+rutellirostris} [2015] clade.
+		We instead resolve \textit{M.
+cracens} [JF2015] as sister to the \textit{M.
+ampullaceus} - \textit{M.
+politus} [JF2018] clade, inclusively supported by three synapomorphies: (1) presence of a strongly punctate sulcus posteriad of the nasal plate (char.
+14: 2); (2) presence of broad scales on the terminal funicular segment of the antenn{\ae}(char.
+19: 1); and (3) absence of a medial, anteriorly-directed, sclerotized process on the coxites of the ovipositor (char.
+40: 1).
+
+		Moreover, the \textit{M.
+ampullaceus} - \textit{M.
+politus} [JF2018] clade approximately corresponds to the topological position of the \textit{M.
+{\ae}riballux} - \textit{M.
+rutellirostris} [JF2015] clade and exhibits comparatively different internal relationships between species groups, while maintaining similar composition and topology within these groups.
+		Specifically, the relative positions of the \textit{M.
+{\ae}riballux} - \textit{M.
+reburrus} [JF2015] clade and the \textit{M.
+caseyi} - \textit{M.
+trisetosus} [JF2015] have changed from being sister clades (excepting the placement of \textit{M.
+cracens} [JF2015]), such that the \textit{M.
+ampullaceus} - \textit{M.
+reburrus} [JF2018] clade is correspondingly inferred as sister to the clade comprised of the \textit{M.
+franko} - \textit{M.
+trisetosus} [JF2018] clade and the \textit{M.
+gravivultus} - \textit{M.
+politus} [JF2018] clade, the latter of which has not changed in composition or internal topology.
+
+		The \textit{M.
+ampullaceus} - \textit{M.
+politus} [JF2018] clade is supported by a single synapomorphy: the width of the connection between the apodemes of the {\ae}deagal tegmen is narrower than the base of the apodeme (char.
+52: 1).
+		Within this clade, the position of the \textit{M.
+franko} - \textit{M.
+politus} [JF2018] clade as separate from and sister to the \textit{M.
+ampullaceus} - \textit{M.
+reburrus} [JF2018] clade, is supported by a single synapomorphy and a single homoplasious character, namely: (1) presence of an anterior ventral flange on the style of the spiculum gastrale (char.
+44: 1, synapomorphy), and (2) differentiation of the set{\ae} on the lateral portion of the elytra and on the venter from the set{\ae} on the elytral disc (char.
+3: 1, homoplasy).
+
+	\subsection*{Phylogenetic placement of newly described species}
+		The clades within \textit{Minyomerus} [JF2018] not addressed in the preceding section are identical in topology and composition to those of \textit{Minyomerus} [JF2015], except for the addition of newly described species.
+		Here we describe explicitly the phylogenetic placement of these species, and the characters supporting these newly-inferred relationships.
+		We additionally discuss, where possible, similarities in biogeographic extent of each species with putative sister taxa, based on the results of species distribution modeling.
+
+		\subsubsection*{Minyomerus sculptilis \textnormal{\bfseries[JF2018]}}
+			\textit{M. sculptilis} [JF2018] is inferred as sister to \textit{M. imberbus} [JF2015].
+			The resulting \textit{M.
+imberbus} - \textit{M.
+sculptilis} [JF2018] clade (bsv = 3, rfd = 72) is supported by a single synapomorphy and two homoplasious characters: (1) corpus of spermatheca sinuate (char.
+32: 1, synapomorphy); (2) lamina of spiculum gastrale in male longer than broad and anteriorly extended along style (char.
+45: 1, homoplasy); and (3) {\ae}deagal pedon medially sclerotized along dorsum (char.
+51: 1, homoplasy).
+			In addition to these characters, \textit{M.
+sculptilis} [JF2018] and \textit{M.
+imberbus} generally share very similar exterior morphology, which can make separating these two species difficult, especially in old, damaged, or worn specimens.
+
+			While \textit{M.
+sculptilis} [JF2018] is associated with big sagebrush (\textit{Artemisia tridentata} Nutt.
+[non-focal]; Asterace{\ae} [non-focal]), tumbleweed (\textit{Salsola tragus} L.
+[non-focal]; Amaranthace{\ae} [non-focal]), tall tumblemustard (\textit{Sisymbrium altissimum} L.
+[non-focal]; Brassicace{\ae} [non-focal]), its sister taxon \textit{M.
+imberbus} [JF2015] is associated with budsage (\textit{Artemisia spinescens} D.C.Eaton [non-focal]; Asteraceae [non-focal]).
+			It is possible that the divergence of these two species may have been driven, in part, by the difference in host-plant preference between related species of \textit{Artemesia}, but given the generalist feeding habits of congenerics, and the limited data available on these species, we do not consider it very likely.
+			Conversely, their divergence may have resulted from a vicariance event, based on their present-day biogeographic distributions, which are separated by the eastern extension of the Columbia Plateau; \textit{M.
+sculptilis} [JF2018] appears to be endemic to the Snake River Plain to the north, while \textit{M.
+imberbus} [JF2015] has been found in the Great Basin Desert to the south.
+
+		\subsubsection*{Minyomerus tylotos \textnormal{\bfseries[JF2018]}}	
+			\textit{M. tylotos} [JF2018] is inferred as the sister to \textit{M. microps} [JF2015], the type species of \textit{Minyomerus} [JF2015].
+			The resulting \textit{M.
+tylotos} - \textit{M.
+microps} [JF2018] clade (bsv = 3, rfd = 73) is supported by a single synapomorphy and a single homoplasious character: (1) elytra and pronotum generally large, protuberant, and sculpted in appearance along dorsal and lateral faces (char.
+5: 1, synapomorphy); and (2) sulcus posteriad of nasal plate broad and weakly punctate (char.
+13: 1, homoplasy).
+			In addition to these characters, \textit{M. tylotos} [JF2018] and \textit{M. microps} share a similar gestalt and uniform setation.
+
+			\textit{M.
+tylotos} [JF2018] appears to be endemic to northern Chihuahuan Desert, while \textit{M.
+microps} [JF2015] is widely distributed to the north throughout the Great Plains and along the Missouri River.
+			We consider it likely that \textit{M.
+microps} [JF2015] represents a northern radiation of the common ancestor of this clade, while \textit{M.
+tylotos} [JF2018] represents the ancestral distribution to the south, based on the hypothesized origin of \textit{Minyomerus} [JF2015] in the Chihuahuan Desert posited by \citet{jansen2015} (see also \citealt{wilson2010}).
+
+		\subsubsection*{Minyomerus ampullaceus \textnormal{\bfseries[JF2018]}}
+			\textit{M. ampullaceus} [JF2018] is inferred as sister to the \textit{M. {\ae}riballux} - \textit{M. reburrus} [JF2015] clade.
+			The resulting \textit{M.
+ampullaceus} - \textit{M.
+reburrus} [JF2018] clade (bsv = 1, rfd = 50) is supported by a single synapomorphy: lamina of spiculum ventrale with laminar arms basally bifurcating and sub-parallel mesally thereafter (char.
+37: 1).
+			The placement of this species is tentatively based on the characteristics of a single, worn specimen, and may be subject to change if more data become available regarding the disposition of the habitus and mouthparts.
+
+			Nonetheless, the biogeographic distributions of the species in the \textit{M.
+ampullaceus} - \textit{M.
+reburrus} [JF2018] clade exhibit overlap; \textit{M.
+ampullaceus} [JF2018] is documented from Carlsbad, NM, in the western parts of the distributions of \textit{M.
+{\ae}riballux} [JF2015] and \textit{M.
+reburrus} [JF2015].
+			The divergence of the latter two species is thought to be a result of their habitat and host plant preference, given their overlapping ranges, as \textit{M.
+{\ae}riballux} [JF2015] is found in very sandy soils and on dune systems, while \textit{M.
+reburrus} [JF2015] prefers arid grasslands.
+			Without additional distribution or host plant data for \textit{M.
+ampullaceus} [JF2018], it is impossible to speculate whether the only documented locality for this species represents the center or edge of its range.
+			However, this locality does overlap with the known range of its sister clade, suggesting that the divergence of \textit{M.
+ampullaceus} [JF2018] from the \textit{M.
+ampullaceus} - \textit{M.
+reburrus} [JF2018] clade was not a vicariance event.
+
+		\subsubsection*{Minyomerus franko \textnormal{\bfseries[JF2018]}}
+			\textit{M. franko} [JF2018] is inferred as sister to the \textit{M. caseyi} - \textit{M. trisetosus} [JF2018] clade.
+			The resulting \textit{M.
+franko} - \textit{M.
+trisetosus} [JF2018] clade (bsv = 4, rfd = 63) is supported by a single synapomorphy and two homoplasious characters: (1) rows of set{\ae} on elytral intervals comprised of larger white set{\ae} randomly interspersed among smaller brown set{\ae}(char.
+4: 1, synapomorphy); (2) prementum lacking strong ligula and straight margins, not appearing pentagonal (char.
+7: 0, homoplasy); and (3) anterior margin of female tergum VII entirely free of sclerotized band (char.
+41: 1, homoplasy).
+			In addition to these characters, members of the \textit{M.
+franko} - \textit{M.
+trisetosus} [2018] clade share a generally similar gestalt, especially as pertains to the overall shape of the head and rostrum, and the articulation between the pronotum and elytra in dorsal and lateral view.
+			Furthermore, the interspersed white elytral set{\ae} of these three species all exhibit varying degrees of apical expansion, and can appear moderately to greatly explanate or spatulate in at least some, but not all, specimens of these species.
+
+			While \textit{M.
+franko} [JF2018] has been documented on spear globemallow (\textit{Sph{\ae}ralcea hastulata} A.
+Gray [non-focal]; Malvace{\ae} [non-focal]), \textit{M.
+trisetosus} [JF2015] is associated with broomweed (\textit{Xanthocephalum} [non-focal]; Asteraceae [non-focal]), creosote bush (\textit{Larrea tridentata} (DC.) Coville [non-focal]; Zygophyllaceae [non-focal]), and snakeweed (\textit{Gutierrezia} [non-focal]; Asteraceae [non-focal]); \textit{M.
+caseyi} has no known plant associations.
+			It is possible that the divergence of \textit{M.
+franko} [2018] may have resulted from a difference in host-plant preference, but, as stated previously, this is unlikely given the generalist feeding habits of congenerics, and the limited data available on this species.
+
+			Alternatively, the speciation sequence in the \textit{M. franko} - \textit{M. trisetosus} [JF2018] clade may correspond to vicariance events.
+			\textit{M.
+trisetosus} [JF2015] inhabits a broad swath of the northern Chihuahuan Desert, while \textit{M.
+franko} [2018] and \textit{M.
+caseyi} [2015] are exclusively encountered in the southern Chihuahuan Desert.
+			MaxEnt predicts overlapping species distributions for the latter species; however, the documented localities of these two species pertain to distinct biogeographic regions.
+			Specifically, \textit{M.
+franko} [JF2018] has only been collected in the valleys of the Sierra Madre Oriental range, while \textit{M.
+caseyi} is found along the western edge of this range, in the eastern portion of the Central Mexican Plateau.
+			Additional field data are needed to clarify the spatial extents of these species' distributions to draw more robust inferences regarding their endemicity within these regions.
+
 \section*{Acknowledgments}
+	The authors are grateful to Robert Anderson (CMNC), Ed Riley and John Oswald (TAMU), and Lourdes Chamorro (USNM) for their assistance and provision of specimens of \textit{Minyomerus} [JF2018] used in this manuscript.
+	The authors also thank Salvatore Anzaldo, Andrew Johnston, Sangmi Lee and other ASUHIC members for their assistance in procuring, treating, and maintaining specimen loans upon entry into the ASUHIC.
+	This research was funded in part by the National Science Foundation (DEB-1155984) and the United States Department of Agriculture – Agricultural Research Service (Agreement 58-1275-1-335).
+
+\section*{To Do}
+	\begin{description}[itemsep=-0.4em]
+		\item[Saturday] Insert figures and tables after text, with references, labels, captions, and links in-text.
+		\item[Saturday] Proofread for ligatures, italicizing, sec. notation, spelling, grammar.
+		\item[Saturday] Send to Nico for sec. notation, concept taxonomy, and revisions.
+		\item[Saturday] Insert tables and figures; arrange plates as needed.
+		\item[Monday] Take and insert measurements.
+		\item[Unspec.] Submit names to zoobank.
+		\item[Unspec.] Upload matrix data to dryad.
+		\item[Unspec.] Upload pre-prints to bioR{\textchi}iv.
+	\end{description}
 

### 2018-03-15 tex/manuscript.tex
rough draft complete with figs
still need to insert measurements

@@
 \usepackage{multirow}
+\usepackage{nameref}
 \newcolumntype{m}[1]{D{.}{~}{#1}}
@@
 \newcommand{\breakfill}{\dotfill\newline\penalty0\hbox{}\nobreak\dotfill}
+\makeatletter
+\def\ttl@useclass#1#2{%
+  \@ifstar
+    {\ttl@labelfalse\@dblarg{#1{#2}}}
+    {\ttl@labelfalse\@dblarg{#1{#2}}}}
+\makeatother
+\usepackage[counterclockwise]{rotating}
+\graphicspath{{figures/}}
+\extrafloats{50}
 
@@
 
-\section*{Introduction}
+\section*{Introduction}\label{sec:intro}
 	The weevil genus \textit{Minyomerus} Horn, 1876 [JF2015] is currently assigned to the tribe Tanymecini Lacordaire, 1863 [non-focal], subtribe Tanymecina Lacoirdaire, 1863 [non-focal] (Curculionid{\ae} [non-focal]: Entimin{\ae} [non-focal] - higher-level classification in accordance with \citealt{alonso1999} and \citealt{bouchard2011}).
@@
 	Following the publication of a monographic revision of \textit{Minyomerus} [JF2015], we have discovered four additional undescribed species, known to us only from limited numbers of specimens, yet well circumscribed by the generic delimitation of the genus.
-	As such, the addition of these new species \emph{does not} alter the definition of the genus (see Phylogenetic results), and we retain the taxonomic concept previously specified by \citet{jansen2015} when referring to this definition.
+	As such, the addition of these new species \emph{does not} alter the definition of the genus (see \textbf{\nameref{sec:results}}), and we retain the taxonomic concept previously specified by \citet{jansen2015} when referring to this definition.
 	For ease of legibility, especially when discussing differences in clade composition when comparing between this and previous work, we use the notation [JF2015] and [JF2018] to specify taxon concepts sec.
@@
 
-\section*{Materials and methods}
+\section*{Materials and Methods}\label{sec:methods} 
 	In order to maximize the compatibility of the new species accounts with the higher-level generic account of \textit{Minyomerus} [JF2015], the methods used in this manuscript are aligned with those of \citet{jansen2015}.
@@
 
-	\subsection*{Acquisition of museum specimens} 
+	\subsection*{Acquisition of museum specimens}\label{ssec:museum} 
 		The existing set of \textit{Minyomerus} [JF2015] specimens used in the revision of \citet{jansen2015} was supplemented with material from the following collections, using the codens of \citet{arnett1993}:
@@
 
-	\subsection*{Morphological analysis}
+	\subsection*{Morphological analysis}\label{ssec:morph} 
 		Our systematic and descriptive approach is complementary to \citet{jansen2015}, which in turn follows \citet{franz2010a, franz2010b, franz2012}.
@@
 
-	\subsection*{Phylogenetic analysis}
+	\subsection*{Phylogenetic analysis}\label{ssec:phylo} 
 		The morphological cladistic analysis includes 26 terminal taxa; with 21 ingroup and 5 outgroup terminals.
@@
 
-	\subsection*{Species distribution modeling}
-		We used the modeling program Maxent, Version 3.4, to generate habitat models for the species of Minyomerus [JF2015] (Figs.~\#) based on documented occurrence records \citep{phillips2004, phillips2006, elith2011}.
+	\subsection*{Species distribution modeling}\label{ssec:dismo} 
+		We used the modeling program Maxent, Version 3.4, to generate habitat models for the species of Minyomerus [JF2015] (Figs.~\ref{fig:map_summary}-\ref{fig:map_sculptilis}) based on documented occurrence records \citep{phillips2004, phillips2006, elith2011}.
 		The default settings were adjusted to \texttt{Max number background points = 100,000} and \texttt{Iterations = 10}.
@@
 		For example, a species endemic to the Snake River Valley of Idaho does not require a predictive model for bioclimatically similar habitats in the Chihuahuan Desert.
-		Documented occurrence records are laid over the modeled habitat ranges as colored circles on their respective maps (Figs.~\#), along with vector layers of country (white) and state (gray) borders \citep{hijmans2012}.
-
-\section*{Descriptions of new species}
-	\subsection*{\textit{Minyomerus ampullaceus} Jansen \& Franz sec. Jansen \& Franz, 2018; sp. n.}
+		Documented occurrence records are laid over the modeled habitat ranges as colored circles on their respective maps (Figs.~\ref{fig:map_amptyl}-\ref{fig:map_sculptilis}), along with vector layers of country (white) and state (gray) borders \citep{hijmans2012}.
+
+\section*{Descriptions of New Species}\label{sec:nsp} 
+	\subsection*{\textit{Minyomerus ampullaceus} Jansen \& Franz sec. Jansen \& Franz, 2018; sp. n.}\label{ssec:amp}
+		Figures~\ref{fig:ampullaceus_F_dorsal}-\ref{fig:ampullaceus_lamina}
 		\subsubsection*{Diagnosis}
@@
 		\subsubsection*{Distribution}
-			This species is known only from Carlsbad, New Mexico (USA), from an unspecified locality; the location of the city is shown in Fig.~\#.
+			This species is known only from Carlsbad, New Mexico (USA), from an unspecified locality; the location of the city is shown in Fig.~\ref{fig:map_amptyl}.
 		\subsubsection*{Natural history}
@@
 
-	\subsection*{\textit{Minyomerus franko} Jansen \& Franz sec. Jansen \& Franz, 2018; sp. n.}
+	\subsection*{\textit{Minyomerus franko} Jansen \& Franz sec. Jansen \& Franz, 2018; sp. n.}\label{ssec:franko}
+		Figures~\ref{fig:franko_F_dorsal}-\ref{fig:franko_aedeagus_lateral}
 		\subsubsection*{Diagnosis}
@@
 			This species has been found in San Luis Potos\'{i} and Tamaulipas (M\'{e}xico).
-			It is likely to be found throughout the Chihuahuan Desert and arid regions of south-central M\'{e}xico based on habitat similarity (Fig.~\#).
+			It is likely to be found throughout the Chihuahuan Desert and arid regions of south-central M\'{e}xico based on habitat similarity (Fig.~\ref{fig:map_franko}).
 		\subsubsection*{Natural history}
@@
 
-	\subsection*{\textit{Minyomerus sculptilis} Jansen \& Franz sec. Jansen \& Franz, 2018; sp. n.}
+	\subsection*{\textit{Minyomerus sculptilis} Jansen \& Franz sec. Jansen \& Franz, 2018; sp. n.}\label{ssec:sculpt}
+		Figures~\ref{fig:sculptilis_F_dorsal}-\ref{fig:sculptilis_aedeagus_lateral}
 		\subsubsection*{Diagnosis}
@@
 		\subsubsection*{Distribution}
-			This species has been found in three localities along the Snake River in Idaho (USA), and is thought to be endemic to the Snake River Plain (Fig.~\#).
+			This species has been found in three localities along the Snake River in Idaho (USA), and is thought to be endemic to the Snake River Plain (Fig.~\ref{fig:map_sculptilis}).
 		\subsubsection*{Natural history}
@@
 
-	\subsection*{\textit{Minyomerus tylotos} Jansen \& Franz sec. Jansen \& Franz, 2018; sp. n.}
+	\subsection*{\textit{Minyomerus tylotos} Jansen \& Franz sec. Jansen \& Franz, 2018; sp. n.}\label{ssec:tylotos}
+		Figures~\ref{fig:tylotos_F_dorsal}-\ref{fig:tylotos_lamina}
 		\subsubsection*{Diagnosis}
@@
 			This species has been found in three localities near the Davis Mountains in Jeff Davis County and in nearby Presidio County, Texas (USA).
-			Habitat models (Figs.~\#) predict that this represents the northeastern extent of its range, indicating a strong likelihood that it is present in other parts of the northern Chihuahuan desert, especially in the state of Chihuahua (M\'{e}xico).
+			Habitat models (Figs.~\ref{fig:map_amptyl}) predict that this represents the northeastern extent of its range, indicating a strong likelihood that it is present in other parts of the northern Chihuahuan desert, especially in the state of Chihuahua (M\'{e}xico).
 		\subsubsection*{Natural history}
@@
 
-\section*{Checklist of species}
+\section*{Checklist of Species}\label{sec:checklist}
 	\begin{tabbing}
@@
 
-\section*{Identification key}
+\section*{Identification Key}\label{sec:idkey}
 	\begin{xtabular}{@{}
@@
 
-\section*{Phylogenetic results}
-	A matrix of 52 characters was assembled for the 26 terminal taxa (Tab. 1).
+\section*{Phylogenetic Results}\label{sec:results}
+	A matrix of 52 characters was assembled for the 26 terminal taxa (Tab.~\ref{tab:table1}).
 	These characters are comprised of all 46 characters included in the revision of \textit{Minyomerus} [JF2015], plus an additional 6 characters intended to identify putative sister taxa to the newly described species.
@@
 	TNT (Tree Analysis Using New Technology) was used to confirm that the shortest tree had been found \citep{goloboff2008}.
-	The most-parsimonious cladogram is shown in Fig.~\#, with relative and absolute Bremer support values (see also \# Methods: Phylogenetic analysis) mapped along the left side of each branch; nodes with bootstrap support above 0.95 are marked with a ``*'' symbol to the right of each node.
+	The most-parsimonious cladogram is shown in Fig.~\ref{fig:tree}, with relative and absolute Bremer support values (see also \textbf{\nameref{sec:methods}: \nameref{ssec:phylo}}) mapped along the left side of each branch; nodes with bootstrap support above 0.95 are marked with a ``*'' symbol to the right of each node.
 
 	The characters, states, and preferred optimizations are described in this section.
-	Characters relating to placement of the herein described taxa are discussed in detail in the Discussion (\#) section, along with changes in species group composition and tree topology from \citet{jansen2015}.
+	Characters relating to placement of the herein described taxa are discussed in detail in the \textbf{\nameref{sec:disc}} section, along with changes in species group composition and tree topology from \citet{jansen2015}.
 	 For all characters not resolved as unreversed synapomorphies, both the individual consistency (ci) and retention (ri) indices are provided.
@@
 The symbol ``–'' denotes inapplicable character states, whereas ``?'' denotes missing information (see also text).}
-    	\label{tab::table1}
+    	\label{tab:table1}
     	\ttfamily
@@
 
-\section*{Discussion}
-	\subsection*{Parallels with prior work}
-		The most-parsimonious cladogram of this work (Fig.~\#) exhibits important differences compared to that of \citet{jansen2015} with respect relationships between species groups, in large part due to the unique character combinations present in the newly-added taxa (need citation \#).
+\section*{Discussion}\label{sec:disc}
+	\subsection*{Parallels with prior work}\label{ssec:same}
+		The most-parsimonious cladogram of this work (Fig.~\ref{fig:tree}) exhibits important differences compared to that of \citet{jansen2015} with respect relationships between species groups, in large part due to the unique character combinations present in the newly-added taxa \citep{rieppel2007, franz2014}.
 		Nonetheless, we resolve three key clades with strong support, also inferred by and in corroboration with \citet{jansen2015}, as follows:
@@
 
-	\subsection*{Intrageneric relationships}
+	\subsection*{Intrageneric relationships}\label{ssec:diff}
 		While some species groups inferred by \citet{jansen2015} remain intact, but with different character alignment, internal topology, or their placement within the genus, others are entirely different; we identify these major topological and compositional phylogenetic differences here.
@@
 imberbus} [JF2015] in a clade with \textit{M.
-sculptilis} [JF2015] (see also \# below), sister to \textit{M.
+sculptilis} [JF2015] (see below: \textbf{\nameref{ssec:place}}), sister to \textit{M.
 conicollis} - \textit{M.
@@
 
-	\subsection*{Phylogenetic placement of newly described species}
+	\subsection*{Phylogenetic placement of newly described species}\label{ssec:place}
 		The clades within \textit{Minyomerus} [JF2018] not addressed in the preceding section are identical in topology and composition to those of \textit{Minyomerus} [JF2015], except for the addition of newly described species.
 		Here we describe explicitly the phylogenetic placement of these species, and the characters supporting these newly-inferred relationships.
-		We additionally discuss, where possible, similarities in biogeographic extent of each species with putative sister taxa, based on the results of species distribution modeling.
+		We additionally discuss, where possible, similarities in biogeographic extent of each species with putative sister taxa, based on the results of species distribution modeling (see Figs.~\ref{fig:map_summary}-\ref{fig:map_sculptilis}).
 
@@
 \section*{To Do}
-	\begin{description}[itemsep=-0.4em]
-		\item[Saturday] Insert figures and tables after text, with references, labels, captions, and links in-text.
-		\item[Saturday] Proofread for ligatures, italicizing, sec. notation, spelling, grammar.
-		\item[Saturday] Send to Nico for sec. notation, concept taxonomy, and revisions.
-		\item[Saturday] Insert tables and figures; arrange plates as needed.
-		\item[Monday] Take and insert measurements.
-		\item[Unspec.] Submit names to zoobank.
-		\item[Unspec.] Upload matrix data to dryad.
-		\item[Unspec.] Upload pre-prints to bioR{\textchi}iv.
-	\end{description}
+	\begin{enumerate}[itemsep=-0.4em]
+		\item Insert measurements.
+		\item Submit names to zoobank.
+		\item Upload matrix data to dryad.
+		\item Upload pre-prints to bioR{\textchi}iv.
+	\end{enumerate}
 
@@
 %just references in windows, use references.bib in linux
+
+\newpage
+
+%M. ampullaceus
+\begin{figure}[h]
+	\begin{sideways}
+		\centering
+		\includegraphics[height=\textwidth]{ampullaceus_F_dorsal.jpg}
+	\end{sideways}
+	\caption{\textbf{Dorsal habitus of \textit{M. ampullaceus} [JF2018].} Image of female (\female) holotype.}
+	\label{fig:ampullaceus_F_dorsal}
+\end{figure}
+
+\begin{figure}[h]
+	\begin{sideways}
+		\centering
+		\includegraphics[height=\textwidth]{ampullaceus_F_lateral.jpg}
+	\end{sideways}
+	\caption{\textbf{Lateral habitus of \textit{M. ampullaceus} [JF2018].} Image of female (\female) holotype.}
+	\label{fig:ampullaceus_F_lateral}
+\end{figure}
+
+\begin{figure}[h]
+	\begin{sideways}
+		\centering
+		\includegraphics[height=\textwidth]{ampullaceus_F_ventral.jpg}
+	\end{sideways}
+	\caption{\textbf{Ventral habitus of \textit{M. ampullaceus} [JF2018].} Image of female (\female) holotype.}
+	\label{fig:ampullaceus_F_ventral}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{ampullaceus_F_frontal.jpg}
+	\caption{\textbf{Head and rostrum of \textit{M. ampullaceus} [JF2018].} Frontal view of female (\female) holotype.}
+	\label{fig:ampullaceus_F_frontal}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{ampullaceus_spermatheca.jpg}
+	\caption{\textbf{Spermatheca of \textit{M. ampullaceus} [JF2018].} Genitalia of female (\female) holotype.}
+	\label{fig:ampullaceus_spermatheca}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{ampullaceus_lamina.jpg}
+	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. ampullaceus} [JF2018].} Sternum VIII of female (\female) holotype.}
+	\label{fig:ampullaceus_lamina}
+\end{figure}
+
+%M. franko
+\begin{figure}[h]
+	\begin{sideways}
+		\centering
+		\includegraphics[height=\textwidth]{franko_F_dorsal.jpg}
+	\end{sideways}
+	\caption{\textbf{Dorsal habitus of \textit{M. franko} [JF2018].} Image of female (\female) holotype.}
+	\label{fig:franko_F_dorsal}
+\end{figure}
+
+\begin{figure}[h]
+	\begin{sideways}
+		\centering
+		\includegraphics[height=\textwidth]{franko_F_lateral.jpg}
+	\end{sideways}
+	\caption{\textbf{Lateral habitus of \textit{M. franko} [JF2018].} Image of female (\female) holotype.}
+	\label{fig:franko_F_lateral}
+\end{figure}
+
+\begin{figure}[h]
+	\begin{sideways}
+		\centering
+		\includegraphics[height=\textwidth]{franko_F_ventral.jpg}
+	\end{sideways}
+	\caption{\textbf{Ventral habitus of \textit{M. franko} [JF2018].} Image of female (\female) holotype.}
+	\label{fig:franko_F_ventral}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{franko_F_frontal.jpg}
+	\caption{\textbf{Head and rostrum of \textit{M. franko} [JF2018].} Frontal view of female (\female) holotype.}
+	\label{fig:franko_F_frontal}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{franko_maxilla.jpg}
+	\caption{\textbf{Maxilla of \textit{M. franko} [JF2018].} Dextral maxilla of female (\female) paratype.}
+	\label{fig:franko_maxilla}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{franko_prementum.jpg}
+	\caption{\textbf{Prementum of \textit{M. franko} [JF2018].} Labium of female (\female) paratype.}
+	\label{fig:franko_prementum}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{franko_spermatheca.jpg}
+	\caption{\textbf{Spermatheca of \textit{M. franko} [JF2018].} Genitalia of female (\female) paratype.}
+	\label{fig:franko_spermatheca}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{franko_lamina.jpg}
+	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. franko} [JF2018].} Sternum VIII of female (\female) paratype.}
+	\label{fig:franko_lamina}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\begin{sideways}
+		\includegraphics[width=0.95\textheight]{franko_aedeagus_dorsal.jpg}
+	\end{sideways}
+	\caption{\textbf{Dorsal view of {\ae}deagus of \textit{M. franko} [JF2018].} Genitalia of male (\male) paratype.}
+	\label{fig:franko_aedeagus_dorsal}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\begin{sideways}
+		\includegraphics[width=0.95\textheight]{franko_aedeagus_lateral.jpg}
+	\end{sideways}
+	\caption{\textbf{Lateral view of {\ae}deagus of \textit{M. franko} [JF2018].} Genitalia of male (\male) paratype.}
+	\label{fig:franko_aedeagus_lateral}
+\end{figure}
+
+%M. sculptilis
+\begin{figure}[h]
+	\begin{sideways}
+		\centering
+		\includegraphics[height=\textwidth]{sculptilis_F_dorsal.jpg}
+	\end{sideways}
+	\caption{\textbf{Dorsal habitus of \textit{M. sculptilis} [JF2018].} Image of female (\female) holotype.}
+	\label{fig:sculptilis_F_dorsal}
+\end{figure}
+
+\begin{figure}[h]
+	\begin{sideways}
+		\centering
+		\includegraphics[height=\textwidth]{sculptilis_F_lateral.jpg}
+	\end{sideways}
+	\caption{\textbf{Lateral habitus of \textit{M. sculptilis} [JF2018].} Image of female (\female) holotype.}
+	\label{fig:sculptilis_F_lateral}
+\end{figure}
+
+\begin{figure}[h]
+	\begin{sideways}
+		\centering
+		\includegraphics[height=\textwidth]{sculptilis_F_ventral.jpg}
+	\end{sideways}
+	\caption{\textbf{Ventral habitus of \textit{M. sculptilis} [JF2018].} Image of female (\female) holotype.}
+	\label{fig:sculptilis_F_ventral}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{sculptilis_F_frontal.jpg}
+	\caption{\textbf{Head and rostrum of \textit{M. sculptilis} [JF2018].} Frontal view of female (\female) holotype.}
+	\label{fig:sculptilis_F_frontal}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{sculptilis_spermatheca.jpg}
+	\caption{\textbf{Spermatheca of \textit{M. sculptilis} [JF2018].} Genitalia of female (\female) paratype.}
+	\label{fig:sculptilis_spermatheca}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{sculptilis_lamina.jpg}
+	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. sculptilis} [JF2018].} Sternum VIII of female (\female) paratype.}
+	\label{fig:sculptilis_lamina}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\begin{sideways}
+		\includegraphics[width=0.95\textheight]{sculptilis_aedeagus_dorsal.jpg}
+	\end{sideways}
+	\caption{\textbf{Dorsal view of {\ae}deagus of \textit{M. sculptilis} [JF2018].} Genitalia of male (\male) paratype.}
+	\label{fig:sculptilis_aedeagus_dorsal}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\begin{sideways}
+		\includegraphics[width=0.95\textheight]{sculptilis_aedeagus_lateral.jpg}
+	\end{sideways}
+	\caption{\textbf{Lateral view of {\ae}deagus of \textit{M. sculptilis} [JF2018].} Genitalia of male (\male) paratype.}
+	\label{fig:sculptilis_aedeagus_lateral}
+\end{figure}
+
+%M. tylotos
+\begin{figure}[h]
+	\begin{sideways}
+		\centering
+		\includegraphics[height=\textwidth]{tylotos_F_dorsal.jpg}
+	\end{sideways}
+	\caption{\textbf{Dorsal habitus of \textit{M. tylotos} [JF2018].} Image of female (\female) holotype.}
+	\label{fig:tylotos_F_dorsal}
+\end{figure}
+
+\begin{figure}[h]
+	\begin{sideways}
+		\centering
+		\includegraphics[height=\textwidth]{tylotos_F_lateral.jpg}
+	\end{sideways}
+	\caption{\textbf{Lateral habitus of \textit{M. tylotos} [JF2018].} Image of female (\female) holotype.}
+	\label{fig:tylotos_F_lateral}
+\end{figure}
+
+\begin{figure}[h]
+	\begin{sideways}
+		\centering
+		\includegraphics[height=\textwidth]{tylotos_F_ventral.jpg}
+	\end{sideways}
+	\caption{\textbf{Ventral habitus of \textit{M. tylotos} [JF2018].} Image of female (\female) holotype.}
+	\label{fig:tylotos_F_ventral}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{tylotos_F_frontal.jpg}
+	\caption{\textbf{Head and rostrum of \textit{M. tylotos} [JF2018].} Frontal view of female (\female) holotype.}
+	\label{fig:tylotos_F_frontal}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{tylotos_prementum.jpg}
+	\caption{\textbf{Prementum of \textit{M. tylotos} [JF2018].} Labium of female (\female) paratype.}
+	\label{fig:tylotos_prementum}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{tylotos_spermatheca.jpg}
+	\caption{\textbf{Spermatheca of \textit{M. tylotos} [JF2018].} Genitalia of female (\female) paratype.}
+	\label{fig:tylotos_spermatheca}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{tylotos_lamina.jpg}
+	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. tylotos} [JF2018].} Sternum VIII of female (\female) paratype.}
+	\label{fig:tylotos_lamina}
+\end{figure}
+
+%phylogeny
+\begin{figure}[h]
+	\centering
+	\begin{sideways}
+		\includegraphics[height=0.75\textwidth]{tree.pdf}
+	\end{sideways}
+	\caption{\textbf{Preferred phylogeny.} Single most parsimonious cladogram representing the preferred phylogeny of species of \textit{Minyomerus} [JF2018], and select outgroup taxa (L = 99, CI = 60, RI = 80).
+Characters 9, 27, 39, 45 - 47, 49, and 51 are mapped under ACCTRAN optimization; all others are unambiguously optimized.
+Black squares indicate non-homoplasious character state changes, whereas white squares indicate homoplasious character state changes.
+The numbers above and below the squares represent character numbers and states, respectively.
+Bremer support (upper value) and relative fit difference (lower value) values can be found at the left ends of the branches.
+A ``*'' symbol at the right end of a branch indicates Bootstrap support greater than 0.95.}
+	\label{fig:tree}
+\end{figure}
+
+%distribution maps
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{summary.pdf}
+	\caption{\textbf{Summary map of distributions of new species of \textit{Minyomerus} [JF2018].} Combined occurrence record and Maxent habitat modeling map for four newly-described species of \textit{Minyomerus} [JF2018], as indicated in the legend.}
+	\label{fig:map_summary}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{tylotos_ampullaceus.pdf}
+	\caption{\textbf{Distributions of \textit{M.
+ampullaceus} [JF2018] and \textit{M.
+tylotos} [JF2018].} Combined occurrence record and Maxent habitat modeling map for \textit{M.
+ampullaceus} [JF2018] and \textit{M.
+tylotos} [JF2018], as indicated in the legend.}
+	\label{fig:map_amptyl}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{franko.pdf}
+	\caption{\textbf{Distributions of \textit{M. franko} [JF2018].} Combined occurrence record and Maxent habitat modeling map for \textit{M. franko} [JF2018], as indicated in the legend.}
+	\label{fig:map_franko}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\begin{sideways}
+		\includegraphics[height=0.8\textwidth]{sculptilis.pdf}
+		\end{sideways}
+	\caption{\textbf{Distributions of \textit{M. sculptilis} [JF2018].} Combined occurrence record and Maxent habitat modeling map for \textit{M. sculptilis} [JF2018], as indicated in the legend.}
+	\label{fig:map_sculptilis}
+\end{figure}
 \end{document}

### 2018-03-17 tex/manuscript.tex
commented out 5 figs that need to be added

@@
 			\paragraph{Habitus}
-				Length \# mm, width \# mm, length/width ratio \#, widest at anterior \# of elytra.
+				Length \# mm, width \# mm, length/width ratio \#, widest at anterior 1/3 of elytra.
 				Integument orange-brown to black. 
@@
 			\paragraph{Rostrum}
-				Length \# mm, anterior portion \# broader than long, rostrum/pronotum length ratio \#, rostrum length/width ratio \#.
+				Length \# mm, anterior portion 1.5-2\x broader than long, rostrum/pronotum length ratio \#, rostrum length/width ratio \#.
 				Separation of rostrum from head generally obscure. 
@@
 			\paragraph{Rostrum}
-				Length \# mm, anterior portion \# broader than long, rostrum/pronotum length ratio \#, rostrum length/width ratio \#.
+				Length \# mm, anterior portion 1.75-2.25\x broader than long, rostrum/pronotum length ratio \#, rostrum length/width ratio \#.
 				Separation of rostrum from head generally obscure. 
@@
 			\paragraph{Rostrum}
-				Length \# mm, anterior portion \# broader than long, rostrum/pronotum length ratio \#, rostrum length/width ratio \#.
+				Length \# mm, anterior portion ca. 1.5\x broader than long, rostrum/pronotum length ratio \#, rostrum length/width ratio \#.
 				Separation of rostrum from head generally obscure. 
@@
 			\paragraph{Rostrum}
-				Length \# mm, anterior portion \# broader than long, rostrum/pronotum length ratio \#, rostrum length/width ratio \#.
+				Length \# mm, anterior portion 2.25-2.5\x broader than long, rostrum/pronotum length ratio \#, rostrum length/width ratio \#.
 				Separation of rostrum from head generally obscure. 
@@
 	\begin{sideways}
-		\includegraphics[height=0.75\textwidth]{tree.pdf}
+		%\includegraphics[height=0.75\textwidth]{tree.pdf}
 	\end{sideways}
@@
 	\centering
-	\includegraphics[width=\textwidth]{summary.pdf}
+	%\includegraphics[width=\textwidth]{summary.pdf}
 	\caption{\textbf{Summary map of distributions of new species of \textit{Minyomerus} [JF2018].} Combined occurrence record and Maxent habitat modeling map for four newly-described species of \textit{Minyomerus} [JF2018], as indicated in the legend.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{tylotos_ampullaceus.pdf}
+	%\includegraphics[width=\textwidth]{tylotos_ampullaceus.pdf}
 	\caption{\textbf{Distributions of \textit{M.
@@
 	\centering
-	\includegraphics[width=\textwidth]{franko.pdf}
+	%\includegraphics[width=\textwidth]{franko.pdf}
 	\caption{\textbf{Distributions of \textit{M. franko} [JF2018].} Combined occurrence record and Maxent habitat modeling map for \textit{M. franko} [JF2018], as indicated in the legend.}
@@
 	\begin{sideways}
-		\includegraphics[height=0.8\textwidth]{sculptilis.pdf}
+		%\includegraphics[height=0.8\textwidth]{sculptilis.pdf}
 		\end{sideways}

### 2018-03-20 tex/manuscript.tex
full draft with all figs and text
only measurements need to be added
added measurements

--- 2018-03-15 tex/manuscript.tex
@@
 \usepackage{nameref}
+\usepackage{epstopdf}
 \newcolumntype{m}[1]{D{.}{~}{#1}}
@@
 			\paragraph{Habitus}
-				Length \# mm, width \# mm, length/width ratio \#, widest at anterior \# of elytra.
+				Length 3.76 mm, width 1.76 mm, length/width ratio 2.14, widest at anterior 1/3 of elytra.
 				Integument orange-brown to black. 
@@
 			\paragraph{Rostrum}
-				Length \# mm, anterior portion \# broader than long, rostrum/pronotum length ratio \#, rostrum length/width ratio \#.
+				Length 0.54 mm, anterior portion 1.5-2\x broader than long, rostrum/pronotum length ratio 0.57, rostrum length/width ratio 1.10.
 				Separation of rostrum from head generally obscure. 
@@
 				Nasal plate defined by Y-shaped, impressed lines, convex, integument partially covered with white scales.
-				Margins of mandibular incision directed \#\td outward dorsally in frontal view. 
+				Margins of mandibular incision directed ca. 15\td outward dorsally in frontal view. 
 				Ventrolateral sulci strongly defined, beginning as a narrow sulcus posteriad of insertion point of mandibles, running parallel to scrobe, terminating in a ventral fovea.
@@
 			\paragraph{Pronotum}
-				Length/width ratio \#; widest near midpoint. 
+				Length/width ratio 0.88; widest near midpoint. 
 				Anterior margin slightly arcuate, lateral margins curved and widening into a bulge just anteriad of midpoint of pronotum, posterior margin straight, with a slight mesal incurvature. 
@@
 			\paragraph{Legs}
-				Profemur/pronotum length ratio \#; profemur with distal 1/5 produced ventrally as a rounded projection covering tibial joint; condyle of tibial articulation occupying 4/5 of distal surface and 1/5 length of femur.
-				Protibia/profemur length ratio \#; protibial apex with ventral setal comb recessed in an incurved groove; mucro present as a large, black, sub-triangular, medially-projected tooth, which is approximately equilateral and whose sides are sub-equal in length to surrounding set{\ae}.
+				Profemur/pronotum length ratio 1.04; profemur with distal 1/5 produced ventrally as a rounded projection covering tibial joint; condyle of tibial articulation occupying 4/5 of distal surface and 1/5 length of femur.
+				Protibia/profemur length ratio 0.93; protibial apex with ventral setal comb recessed in an incurved groove; mucro present as a large, black, sub-triangular, medially-projected tooth, which is approximately equilateral and whose sides are sub-equal in length to surrounding set{\ae}.
 				Protarsus with tarsomere III 1.25\x as long as II; wider than long. 
@@
 			\paragraph{Elytra}
-				Length/width ratio \#; widest at anterior 1/3; anterior margins jointly almost 2\x wider than posterior margin of pronotum and strongly produced dorsally from margin of pronotum; lateral margins evenly rounded until posterior 1/3, more strongly rounded and converging thereafter.
+				Length/width ratio 2.66; widest at anterior 1/3; anterior margins jointly almost 2\x wider than posterior margin of pronotum and strongly produced dorsally from margin of pronotum; lateral margins evenly rounded until posterior 1/3, more strongly rounded and converging thereafter.
 				Posterior declivity angled at nearly 85\td to main body axis.
@@
 			\paragraph{Habitus}
-				Length \# mm, width \# mm, length/width ratio \#, widest at anterior 1/3-1/4 of elytra.
+				Length 3.10-3.30 mm, width 1.38-1.44 mm, length/width ratio 2.25-2.29, widest at anterior 1/3-1/4 of elytra.
 				Integument orange-brown to black. 
@@
 			\paragraph{Rostrum}
-				Length \# mm, anterior portion \# broader than long, rostrum/pronotum length ratio \#, rostrum length/width ratio \#.
+				Length 0.46-0.48 mm, anterior portion 1.75-2.25\x broader than long, rostrum/pronotum length ratio 0.58-0.59, rostrum length/width ratio 1.21-1.26.
 				Separation of rostrum from head generally obscure. 
@@
 				Nasal plate defined by broad, V-shaped, shallowly impressed lines, anteromesally slightly convex, integument partially covered with white scales. 
-				Margins of mandibular incision directed \#\td outward dorsally in frontal view. 
+				Margins of mandibular incision directed ca. 15\td outward dorsally in frontal view. 
 				Ventrolateral sulci weakly defined (or entirely absent in some specimens) as a broad concavity dorsad of insertion point of mandibles, running parallel to scrobe, becoming flatter posteriorly and disappearing ventrally.
@@
 			\paragraph{Pronotum}
-				Length/width ratio \#; widest near anterior 1/3, between anterior constriction and midpoint. 
+				Length/width ratio 0.84-0.86; widest near anterior 1/3, between anterior constriction and midpoint. 
 				Anterior margin arcuate, lateral margins curved and widening into a slight bulge just anteriad of midpoint of pronotum, posterior margin straight, with a slight mesal incurvature. 
@@
 			\paragraph{Legs}
-				Profemur/pronotum length ratio \#; profemur with distal 1/5 produced ventrally as a sub-rectangular projection covering tibial joint; condyle of tibial articulation occupying 4/5 of distal surface and 1/5 length of femur.
-				Protibia/profemur length ratio \#; protibial apex with ventral setal comb recessed in a subtly incurved groove; mucro present as a large, black, sub-triangular, medially-projected tooth, which is approximately equilateral and whose sides are sub-equal in length to surrounding set{\ae}.
+				Profemur/pronotum length ratio 1.01-1.02; profemur with distal 1/5 produced ventrally as a sub-rectangular projection covering tibial joint; condyle of tibial articulation occupying 4/5 of distal surface and 1/5 length of femur.
+				Protibia/profemur length ratio 0.86-0.89; protibial apex with ventral setal comb recessed in a subtly incurved groove; mucro present as a large, black, sub-triangular, medially-projected tooth, which is approximately equilateral and whose sides are sub-equal in length to surrounding set{\ae}.
 				Protarsus with tarsomere III 2\x as long as II; wider than long. 
@@
 			\paragraph{Elytra}
-				Length/width ratio \#; widest at anterior 1/3-1/4; anterior margins jointly 1.5\x wider than posterior margin of pronotum; lateral margins sub-parallel to slightly rounded after anterior 1/3, more strongly rounded and converging in posterior 1/3.
+				Length/width ratio 3.08-3.20; widest at anterior 1/3-1/4; anterior margins jointly 1.5\x wider than posterior margin of pronotum; lateral margins sub-parallel to slightly rounded after anterior 1/3, more strongly rounded and converging in posterior 1/3.
 				Posterior declivity angled at 70-85\td to main body axis.
@@
 			\paragraph{Habitus}
-				Length \# mm, width \# mm, length/width ratio \#.
-Rostrum length \# mm, rostrum/pronotum length ratio \#, rostrum length/width ratio \#.
-Pronotum length/width ratio \#.
-Profemur/pronotum length ratio \#, protibia/profemur length ratio \#.
-Elytra length/width ratio \#.
+				Length 2.47-2.81 mm, width 0.99-1.24 mm, length/width ratio 2.27-2.49.
+Rostrum length 0.30-0.42 mm, rostrum/pronotum length ratio 0.44-0.53, rostrum length/width ratio 1.00-1.08.
+Pronotum length/width ratio 0.91-1.00.
+Profemur/pronotum length ratio 0.87-0.90, protibia/profemur length ratio 0.87-0.97.
+Elytra length/width ratio 3.00-3.10.
 			\paragraph{Elytra}
@@
 			\paragraph{{\AE}deagus}
-				Length/width ratio \#; lateral margins very slightly converging posteriorly, abruptly constricted and more strongly converging in apical 1/5.
+				Length/width ratio 2.78-3.16; lateral margins very slightly converging posteriorly, abruptly constricted and more strongly converging in apical 1/5.
 				Pedon in lateral view becoming gradually narrower posteriorly in anterior 1/2, ventral margins in posterior 1/2 abruptly curving to meet dorsal margins at a rounded apical point.
@@
 			\paragraph{Habitus}
-				Length \# mm, width \# mm, length/width ratio \#, widest at anterior 1/5 of elytra.
+				Length 3.39-3.70 mm, width 1.33-1.58 mm, length/width ratio 2.34-2.55, widest at anterior 1/5 of elytra.
 				Integument orange-brown to black.
@@
 			\paragraph{Rostrum}
-				Length \# mm, anterior portion \# broader than long, rostrum/pronotum length ratio \#, rostrum length/width ratio \#.
+				Length 0.50-0.59 mm, anterior portion ca. 1.5\x broader than long, rostrum/pronotum length ratio 0.66-0.67, rostrum length/width ratio 1.43-1.48.
 				Separation of rostrum from head generally obscure. 
@@
 				Nasal plate defined by Y-shaped, impressed lines, convex, integument covered with white scales.
-				Margins of mandibular incision directed \#\td outward dorsally in frontal view. 
+				Margins of mandibular incision directed ca. 15-20\td outward dorsally in frontal view. 
 				Ventrolateral sulci strongly defined, beginning as a narrow sulcus posteriad of insertion point of mandibles, running parallel to scrobe, terminating in a ventral fovea.
@@
 			\paragraph{Pronotum}
-				Length/width ratio \#; widest near anterior 2/5.
+				Length/width ratio 0.85-0.87; widest near anterior 2/5.
 				Anterior margin arcuate, subtly incurved mesally, and somewhat produced dorsally; anterior constriction broad, posterior margin slightly arcuate.
@@
 			\paragraph{Legs}
-				Profemur/pronotum length ratio \#; profemur with distal 1/6 produced ventrally as a slightly rounded, sub-rectangular projection covering tibial joint; condyle of tibial articulation occupying 4/5 of distal surface and 1/6 length of femur.
-				Protibia/profemur length ratio \#; protibial apex with ventral setal comb recessed in a subtly incurved groove; mucro not apparent. 
+				Profemur/pronotum length ratio 0.92-1.03; profemur with distal 1/6 produced ventrally as a slightly rounded, sub-rectangular projection covering tibial joint; condyle of tibial articulation occupying 4/5 of distal surface and 1/6 length of femur.
+				Protibia/profemur length ratio 0.87-0.93; protibial apex with ventral setal comb recessed in a subtly incurved groove; mucro not apparent. 
 				Protarsus with tarsomere III 1.5\x as long as II; wider than long. 
@@
 			\paragraph{Elytra}
-				Length/width ratio \#; widest at anterior 1/5; anterior margins jointly 1.5-2\x wider than posterior margin of pronotum; lateral margins gently converging after anterior 1/5, more strongly converging in posterior 1/4.
+				Length/width ratio 3.12-3.16; widest at anterior 1/5; anterior margins jointly 1.5-2\x wider than posterior margin of pronotum; lateral margins gently converging after anterior 1/5, more strongly converging in posterior 1/4.
 				Posterior declivity angled at 65-70\td to main body axis.
@@
 			\paragraph{Habitus}
-				Length \# mm, width \# mm, length/width ratio \#.
-Rostrum length \# mm, rostrum/pronotum length ratio \#, rostrum length/width ratio \#.
-Pronotum length/width ratio \#.
-Profemur/pronotum length ratio \#, protibia/profemur length ratio \#.
-Elytra length/width ratio \#.
+				Length 3.10 mm, width 1.22 mm, length/width ratio 2.54.
+Rostrum length 0.53 mm, rostrum/pronotum length ratio 0.65, rostrum length/width ratio 1.66.
+Pronotum length/width ratio 0.99.
+Profemur/pronotum length ratio 1.01, protibia/profemur length ratio 0.82.
+Elytra length/width ratio 3.18.
 			\paragraph{Elytra}
@@
 			\paragraph{{\AE}deagus}
-				Length/width ratio \#; lateral margins parallel, more strongly converging in region of ostium. 
+				Length/width ratio 7.00; lateral margins parallel, more strongly converging in region of ostium. 
 				In lateral view, width of pedon even throughout in anterior 2/3, ventral margins in posterior 1/3 becoming straight towards apex, then curving to meet dorsal margins at a sharp apical point; apex acutely angulate.
@@
 			\paragraph{Habitus}
-				Length \# mm, width \# mm, length/width ratio \#, widest at anterior 1/6 of elytra.
+				Length 3.46-3.62 mm, width 1.42-1.54 mm, length/width ratio 2.35-2.44, widest at anterior 1/6 of elytra.
 				Integument orange-brown to black.
@@
 			\paragraph{Rostrum}
-				Length \# mm, anterior portion \# broader than long, rostrum/pronotum length ratio \#, rostrum length/width ratio \#.
+				Length 0.49-0.50 mm, anterior portion 2.25-2.5\x broader than long, rostrum/pronotum length ratio 0.58-0.62, rostrum length/width ratio 1.26-1.32.
 				Separation of rostrum from head generally obscure. 
@@
 				Nasal plate lacking distinct impressions, having instead a poorly defined anteromesal convexity, integument completely and evenly covered with white scales. 
-				Margins of mandibular incision directed \#\td outward dorsally in frontal view. 
+				Margins of mandibular incision directed ca. 25-30\td outward dorsally in frontal view. 
 				Ventrolateral sulci weakly defined as a broad concavity dorsad of insertion point of mandibles, running parallel to scrobe, becoming flatter posteriorly and disappearing ventrally.
@@
 			\paragraph{Pronotum}
-				Length/width ratio \#; widest near anterior 2/5; somewhat globular. 
+				Length/width ratio 0.88-0.89; widest near anterior 2/5; somewhat globular. 
 				Anterior margin arcuate, but feebly incurved mesally, lateral margins evenly curved and widening into a bulge just anteriad of midpoint of pronotum, posterior margin straight, with a slight mesal incurvature.
@@
 			\paragraph{Legs}
-				Profemur/pronotum length ratio \#; profemur with distal 1/5 produced ventrally as a sub-rectangular projection covering tibial joint; condyle of tibial articulation occupying 4/5 of distal surface and 1/5 length of femur.
-				Protibia/profemur length ratio \#; protibial apex with ventral setal comb recessed in a subtly incurved groove; mucro present as an acute, medially-projected tooth, which is approximately equal in length to surrounding set{\ae}.
+				Profemur/pronotum length ratio 0.90-0.96; profemur with distal 1/5 produced ventrally as a sub-rectangular projection covering tibial joint; condyle of tibial articulation occupying 4/5 of distal surface and 1/5 length of femur.
+				Protibia/profemur length ratio 0.86-0.91; protibial apex with ventral setal comb recessed in a subtly incurved groove; mucro present as an acute, medially-projected tooth, which is approximately equal in length to surrounding set{\ae}.
 				Protarsus with tarsomere III 2\x as long as II; wider than long. 
@@
 			\paragraph{Elytra}
-				Length/width ratio \#; widest at anterior 1/6; anterior margins jointly 1.5-2\x wider than posterior margin of pronotum; lateral margins nearly straight and sub-parallel after anterior 1/5, converging in posterior 1/3.
+				Length/width ratio 3.03-3.21; widest at anterior 1/6; anterior margins jointly 1.5-2\x wider than posterior margin of pronotum; lateral margins nearly straight and sub-parallel after anterior 1/5, converging in posterior 1/3.
 				Posterior declivity angled at 70-75\td to main body axis.
@@
 	\begin{sideways}
-		\includegraphics[height=0.75\textwidth]{tree.pdf}
+		\includegraphics[height=0.75\textwidth]{tree.eps}
 	\end{sideways}
@@
 	\centering
-	\includegraphics[width=\textwidth]{summary.pdf}
+	\includegraphics[width=\textwidth]{summary.png}
 	\caption{\textbf{Summary map of distributions of new species of \textit{Minyomerus} [JF2018].} Combined occurrence record and Maxent habitat modeling map for four newly-described species of \textit{Minyomerus} [JF2018], as indicated in the legend.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{tylotos_ampullaceus.pdf}
+	\includegraphics[width=\textwidth]{tylotos_ampullaceus.png}
 	\caption{\textbf{Distributions of \textit{M.
@@
 	\centering
-	\includegraphics[width=\textwidth]{franko.pdf}
+	\includegraphics[width=\textwidth]{franko.png}
 	\caption{\textbf{Distributions of \textit{M. franko} [JF2018].} Combined occurrence record and Maxent habitat modeling map for \textit{M. franko} [JF2018], as indicated in the legend.}
@@
 	\begin{sideways}
-		\includegraphics[height=0.8\textwidth]{sculptilis.pdf}
+		\includegraphics[height=0.8\textwidth]{sculptilis.png}
 		\end{sideways}

### 2018-05-07 tex/manuscript.tex
Nico edits

@@
 
-\title{Descriptions of four new species of \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz, 2015 (Coleoptera: Curculionid{\ae}), with notes on their distribution and phylogeny}
+\title{Descriptions of four new species of \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz, 2018 (Coleoptera: Curculionidae), with notes on their distribution and phylogeny}
 
@@
 
-%\keywords{Biogeography, cladistics, concept taxonomy, desert, Entiminae, \textit{Minyomerus}, new species, provenance, weevils} - KEYWORDS PROVIDED DURING SUBMISSION.
+%\keywords{Biogeography, cladistics, concept taxonomy, desert, Entiminae, \textit{Minyomerus}, new species, Region Connection Calculus, weevils} - KEYWORDS PROVIDED DURING SUBMISSION.
 
 \begin{abstract}
-	This contribution adopts the taxonomic concept annotation and alignment approach. 
-	Accordingly, and where indicated, previous and newly inferred meanings of taxonomic names are individuated according to one specific source.
-	Articulations among these concepts and pairwise, logically consistent alignments of original and revisionary classifications are also provided, in addition to conventional nomenclatural provenance information.
-	Descriptions of four species belonging to the broad-nosed weevil genera \textit{Minyomerus} Horn, 1876 sec.
-Jansen \& Franz, 2015 (Curculionidae [non-focal]: Entiminae [non-focal]: Tanymecini [non-focal]) are presented.
-	Prior to this study, \textit{Minyomerus} sec. Jansen \& Franz, 2015 contained 17 species species distributed throughout the desert and plains regions of North America.
-	We thoroughly describe these four species as new to science: \textit{M.
-ampullaceus} sec.
-Jansen \& Franz (2015) (henceforth: [JF2015]), sp.
-n., \textit{M.
-franko} [JF2015], sp.
-n., \textit{M.
-sculptilis} [JF2015], sp.
-n., and \textit{M.
-tylotos} [JF2015], sp.
-n.
-	A cladistic analysis using 52 morphological characters of 26 terminal taxa (5/21 outgroup/ingroup) yielded a single most-parsimonious cladogram (L = 99, CI = 60, RI = 80). 
-	The analysis supports the monophyly of Minyomerus [JF2015] with eight unreversed synapomorphies, in corroboration of prior work.
-	Accordingly, each of the four new species is placed within \textit{Minyomerus} [JF2015], and their species-group placement, possible biogeographic origins, and natural history are discussed in detail.
+	This contribution adopts the taxonomic concept approach, including the use of \textit{taxonomic concept labels} (name sec.
+[\textit{according to}] source) and Region Connection Calculus (RCC--5) articulations and alignments.
+	Prior to this study, the broad-nosed weevil genus \textit{Minyomerus} Horn, 1876 sec.
+Jansen \& Franz, 2015 (Curculionidae [non-focal]: Entiminae [non-focal]: Tanymecini [non-focal]) contained 17 species distributed throughout the desert and plains regions of North America.
+	In this revision of \textit{Minyomerus} sec.
+Jansen \& Franz, 2018, we describe the following four species as new to science: \textit{Minyomerus ampullaceus} sec.
+Jansen \& Franz, 2018 (henceforth: [JF2018]), \textbf{new species,} \textit{Minyomerus franko} [JF2018], \textbf{new species,} \textit{Minyomerus sculptilis} [JF2018], \textbf{new species,} and \textit{Minyomerus tylotos} [JF2018], \textbf{new species.}
+	The four new species are added to, and integrated with, the preceding revision, and an updated key and phylogeny of \textit{Minyomerus} [JF2018] are presented. 
+	A cladistic analysis using 52 morphological characters of 26 terminal taxa (5/21 outgroup/ingroup) yielded a single most-parsimonious cladogram (Length = 99 steps, Consistency Index = 60, Retention Index = 80).
+	The analysis reaffirms the monophyly of \textit{Minyomerus} [JF2018] with eight unreversed synapomorphies.
+	The species-group placements, possible biogeographic origins, and natural history of the new species are discussed in detail.
 \end{abstract}
@@
 \section*{Introduction}\label{sec:intro}
-	The weevil genus \textit{Minyomerus} Horn, 1876 [JF2015] is currently assigned to the tribe Tanymecini Lacordaire, 1863 [non-focal], subtribe Tanymecina Lacoirdaire, 1863 [non-focal] (Curculionid{\ae} [non-focal]: Entimin{\ae} [non-focal] - higher-level classification in accordance with \citealt{alonso1999} and \citealt{bouchard2011}).
-	A recent phylogenetic revision of the genus recognized a total of 17 described species distributed throughout the desert and plains regions of North America \citep{jansen2015}.
-
-	Members of the genus \textit{Minyomerus} [JF2015] are phytophagous, and may be found on a variety of host plants, especially the creosote bush (\textit{Larrea tridentata} (DC.) Coville [non-focal; Zygophyllaceae [non-focal]), broomweed (\textit{Gutierrezia lagasca} [non-focal; Asteraceae [non-focal), sagebrush (\textit{Artemisia} Linnaeus [non-focal]; Asteraceae [non-focal]), and occasionally on other various Asteraceae [non-focal] \citep{jansen2015}.
-	While many species appear to be generalists, the adults are consistently observed on the leaves and branches of the host feeding on the leaf tissue; all other life stages remain unknown.
-	Species of this genus are commonly found in deserts throughout western North America, including the Mojave, Sonoran, Chihuahuan, and Great Basin Deserts; however, their range extends throughout the semi-arid regions of the Great Plains, the Colorado Plateau, and Baja California, M\'{e}xico \citep{obrien1982, jansen2015}.
+	This phylogenetic revision follows \citet{jansen2015} in the use of the taxonomic concept approach; see \citet{fp2009, fea2016a, fea2016b}. Accordingly:
+
+	\begin{enumerate}[itemsep=-0.4em]
+		\item \textit{Taxonomic concept labels} -- i.e., the taxonomic name sec.
+(\textit{according to}) author or source (year) -- are used whenever we identify one specific usage of the taxonomic name.
+Examples: \textit{Minyomerus} Horn, 1876 sec.
+Jansen \& Franz, 2015 (henceforth: [JF2015]) and \textit{Minyomerus} Horn, 1876 sec.
+Jansen \& Franz, 2018 (henceforth: [JF2018]).
+We also employ this convention to express nomenclatural relationships.
+		\item Solely the taxonomic name -- without the sec.
+annotation -- is used to refer to the cumulative history (origin to present) of taxonomic concept labels in which that name participates.
+Example: \textit{Minyomerus} Horn, 1876.
+		\item The annotation [non-focal] is added to taxonomic names whose meanings are not under scrutiny in the present context; such as names for higher-level weevil groups and associated plants (exempting common names).
+Example: Tanymecini Lacordaire, 1863 [non-focal].
+	\end{enumerate}
+
+	The weevil genus \textit{Minyomerus} Horn, 1876 [JF2018] remains currently assigned to the tribe Tanymecini Lacordaire, 1863 [non-focal], subtribe Tanymecina Lacoirdaire, 1863 [non-focal] (Curculionidae [non-focal]: Entiminae [non-focal] -- higher-level classification in accordance with \citealt{alonso1999} and \citealt{bouchard2011}).
+	A recent phylogenetic revision of the \textit{Minyomerus} [JF2015] recognized a total of 17 described species, distributed throughout the desert and plains regions of North America \citep{jansen2015}.
+
+	Members of the genus \textit{Minyomerus} [JF2018] are phytophagous, and may be found on a variety of host plants, especially the creosote bush \textit{Larrea tridentata} (DC) Coville [non-focal] (Zygophyllaceae [non-focal]), broomweed \textit{Gutierrezia} Lagasca [non-focal] (Asteraceae [non-focal]), sagebrush \textit{Artemisia} Linnaeus [non-focal] (Asteraceae [non-focal]), and occasionally on other various members of Asteraceae [non-focal] \citep{jansen2015}.
+	While many species appear to be generalists, the adults are consistently observed on the leaves and branches of the host, feeding on the leaf tissue. All other life stages remain unknown.
+	Species of \textit{Minyomerus} [2018] are commonly found in deserts throughout western North America; including the Mojave, Sonoran, Chihuahuan, and Great Basin Deserts.
+However, their distributional range extends throughout the semi-arid regions of the Great Plains, the Colorado Plateau, and Baja California, M\'{e}xico \citep{obrien1982, jansen2015}.
 	The adults are flightless, as the hind wings and associated flight structures of all species are either greatly reduced or not readily apparent in dissection.
 
-	\textit{Minyomerus} [JF2015] belongs to the broad-nosed weevils, subfamily Entimin{\ae} [non-focal], on the basis of having a short, broad rostrum and dehiscent mandibular process \citep{marvaldi1997, anderson2002, oberprieler2007, oberprieler2014, marvaldi2014}.
-	They are clothed in appressed, circular scales, generally in earth-tones from white to dark brown, with sub-recumbent to erect, interspersed setiform scales (`set{\ae}') arranged in rows on the elytral intervals, and can range in length from 2.8 to 6.0 mm \citep{jansen2015}.
-	The genus has been classified in the tribe Tanymecini [non-focal] based on the presence of post-ocular vibriss{\ae} that project anteriorly from the anterior prothoracic margin, although the exact placement and sister taxa of this genus within the tribe are currently unknown \citep{howden1959, howden1970, howden1982, jansen2015}.
-
-	The genus is diagnosed by a unique combination of synapomorphic traits, described by \citet{jansen2015}, and as follows:
+	\textit{Minyomerus} [JF2018] belongs to the broad-nosed weevils, subfamily Entiminae [non-focal], on the basis of having a short, broad rostrum and dehiscent mandibular process \citep{marvaldi1997, anderson2002, oberprieler2007, oberprieler2014, marvaldi2014}.
+	The adults are clothed in appressed, circular scales, generally in earth-tones from white to dark brown, with sub-recumbent to erect, interspersed setiform scales ("setae") arranged in rows on the elytral intervals.
+Their length can range from 2.8 mm to 6.0 mm \citep{jansen2015}.
+	The genus has been classified in the tribe Tanymecini [non-focal] based on the presence of post-ocular vibrissae that project anteriorly from the anterior prothoracic margin, although the exact placement and sister taxa of this genus within the tribe are currently unknown \citep{howden1959, howden1970, howden1982, jansen2015}.
+
+	\textit{Minyomerus} [JF2015] was circumscribed by a unique combination of synapomorphic traits, described by \citet{jansen2015} as follows:
 
@@
 		\item The head is directed slightly ventrally.
-		\item The metatibial apex lacks setiform bristles yet displays bristles that are shorter to sub-equal in length to the surrounding set{\ae} and conical to lamelliform.
-		\item The mesotarsi are slightly shorter than the mesotibi{\ae}.
-		\item All tarsi lack pads of setiform set{\ae} but have stout, spiniform set{\ae}.
+		\item The metatibial apex lacks setiform bristles yet displays bristles that are shorter to sub-equal in length to the surrounding setae and conical to lamelliform.
+		\item The mesotarsi are slightly shorter than the mesotibiae.
+		\item All tarsi lack pads of setiform setae but have stout, spiniform setae.
 	\end{enumerate}
 
-	The following additional characters are useful for identifying members of \textit{Minyomerus} [JF2015], especially when differentiating the former from other genera of Tanymecini [non-focal] that may be found together in the same desert habitats, viz.
+	The following additional characters are useful for identifying members of \textit{Minyomerus} [JF2018], especially when differentiating the former from other genera of Tanymecini [non-focal] that may be found together in the same desert habitats; viz.
 \textit{Isodrusus} Sharp, 1911 [non-focal], \textit{Isodacrys} Sharp, 1911 [non-focal], and \textit{Pandeleteinus} Champion, 1911 [non-focal] (see also \citealt{anderson2002}):
@@
 	\begin{enumerate} [itemsep=-0.4em]
-		\item The intercoxal process of the prosternum is medially divided into two halves, with the procox{\ae} apparently contiguous in most.
+		\item Taehe intercoxal process of the prosternum is medially divided into two halves, with the procoxae apparently contiguous in most.
 		\item The elytral humeri are rounded rather than angled and protruding.
 		\item The profemora are not dilated and lack spines.
-		\item The protibi{\ae} are ventrally excavated by a longitudinal groove or concavity.
+		\item The protibiae are ventrally excavated by a longitudinal groove or concavity.
 		\item A distinct scrobe is present and directed ventrad of the eye, with a more or less apparent tooth formed by an overhang of the dorsal margin.
@@
 
-	Following the publication of a monographic revision of \textit{Minyomerus} [JF2015], we have discovered four additional undescribed species, known to us only from limited numbers of specimens, yet well circumscribed by the generic delimitation of the genus.
-	As such, the addition of these new species \emph{does not} alter the definition of the genus (see \textbf{\nameref{sec:results}}), and we retain the taxonomic concept previously specified by \citet{jansen2015} when referring to this definition.
-	For ease of legibility, especially when discussing differences in clade composition when comparing between this and previous work, we use the notation [JF2015] and [JF2018] to specify taxon concepts sec.
-Jansen \& Franz, 2015 and sec.
-Jansen \& Franz, 2018, respectively.
-	Specifically, all clades inferred in this work will be designated according to the concept [JF2018], \emph{unless} there is perfect congruence (viz.
-synapomorphies and clade composition) with a clade previously resolved by \citet{jansen2015}, in which case the identifier [JF2015] will be retained.
-	While this is the case for all of the previously described species, and a few select clades, we differentiate the newly inferred clade corresponding to the genus, and including the herein described species, as \textit{Minyomerus} [JF2018].
-
-	Here we describe the four newly found species and provide images of the holotypes and of dissected genitalia for the purpose of identification.
-	We additionally conduct a morphological phylogenetic analysis of the genus to clarify the placement of these new taxa within \textit{Minyomerus} [JF2015], based on the analysis provided in our previous work.
-	An emended identification key to the species of \textit{Minyomerus} [JF2015] is given along with an updated checklist of the genus.
-	Where possible, we make note of host-plant records and briefly consider the geographic distribution of the herein described species.
-	A more extensive discussion of the habits, distribution, and delimitation of the genus (and all of its constituent species) can found in the generic revision \citep{jansen2015}.
+	Following the publication of a monographic revision of \textit{Minyomerus} [JF2015], we have discovered four additional, undescribed species.
+These are known to us only from limited numbers of specimens, yet are well circumscribed by -- i.e., intensionally included in \citep{fp2009} -- the recent generic delimitation of \textit{Minyomerus} [JF2015].
+	In other words, the addition of these new species \emph{has not} required altering the intensional, property-based definition of the genus-level concept as circumscribed in \citet{jansen2015} (see \textbf{\nameref{sec:results}}).
+Our RCC--5 alignments (see \textbf{\nameref{sec:alignments}}) reflect this genus-level concept congruence while also showing which classificatory and phylogenetic structures have changed (Figs.~\ref{fig:align1}-\ref{fig:align3}).
+	The precise use of the taxonomic concept labels in accordance with either [JF2015] or [JF2018] is meant to minimize the creation of new taxonomic concept labels (to counter label "inflation"; see \citet{fp2009}), while reflecting explicitly \emph{which} taxonomic concepts we consider as relevantly new and unique to the present study.
+
+	Here we describe the four newly found species of \textit{Minyomerus} [JF2018] and provide images of the holotypes and of dissected genitalia for the purpose of identification.
+	We additionally conduct a morphological phylogenetic analysis of the genus to clarify the placement of these new taxa within \textit{Minyomerus} [JF2018], based on the analysis provided in our previous work.
+	An emended identification key to the species of \textit{Minyomerus} [JF2018] is given, along with an updated species checklist.
+	Where possible, we make note of host-plant records, and briefly discuss the geographic distributions of the herein described species.
+	A more extensive discussion of the habits, distribution, and delimitation of the \textit{Minyomerus} [JF2015] and all of its constituent species is provided in \citep{jansen2015}.
 
 \section*{Materials and Methods}\label{sec:methods} 
-	In order to maximize the compatibility of the new species accounts with the higher-level generic account of \textit{Minyomerus} [JF2015], the methods used in this manuscript are aligned with those of \citet{jansen2015}.
-	Here we provide an updated account of the procedures used to generate the species descriptions, distribution maps, and phylogeny herein.
-	Most importantly, we retain the format of the species descriptions, whereby we emphasize only those characters that vary significantly from the generic description, as explained below.
+	The methods used in this manuscript are generally consistent with \citet{jansen2015}. Relevant updates are detailed below. 
+	In particular, we retain the format for the species descriptions, emphasizing only those characters that vary significantly from the generic circumscription of \textit{Minyomerus} [JF2015].
 
 	\subsection*{Acquisition of museum specimens}\label{ssec:museum} 
-		The existing set of \textit{Minyomerus} [JF2015] specimens used in the revision of \citet{jansen2015} was supplemented with material from the following collections, using the codens of \citet{arnett1993}:
+		The set of specimens used in \citet{jansen2015} was supplemented with material from the following collections, using the codens of \citet{arnett1993}:
 
@@
 
-			Georeferencing of localities was performed with Google Earth \citep{google2018} and reported in decimal degrees.
+			Georeferencing of localities was performed with Google Earth \citep{google2018}, following the WGS 84 standard, and reported in decimal degrees.
 		Taxonomic names for associated host plants, as noted following each species account, are used in accordance with \citet{munz1973} and \citet{seinet2018}.
@@
 		Our systematic and descriptive approach is complementary to \citet{jansen2015}, which in turn follows \citet{franz2010a, franz2010b, franz2012}.
-		Terminology for exterior morphology is in general accordance with \citet{torre1989}.
+		The terminology for exterior morphology is in general accordance with \citet{torre1989}.
 		Additional morphological terms specific to (entimine [non-focal]) weevils were used as follows:
@@
 		The width of an individual elytron was measured in dorsal view as the maximum distance between the lateral margin and the elytral suture.
-		Other length and width measurements were also performed in dorsal orientation, using the maximum length and width of the corresponding structure (profemur, protibia, elytron, and {\ae}deagus).
-		Images of mouthparts and terminalia were produced with the Leica microscope equipment, while habitus photographs were created with a Visionary Digital Passport II sytem using a Canon EOS Mark 5D II camera.
-
-		Herein recognized species of \textit{Minyomerus} [JF2015] were delimited through application of the phylogenetic species concept \textit{sensu} \citet{wheeler2000}.
-		Species descriptions are in alphabetical order, rather than phylogetic order, for ease of use.
-		As in \citet{jansen2015}, the species descriptions in this manuscript represent unique and complementary accounts of the character states observed in each species, including their variability, but excepting those characters invariant within the genus as specified in the higher-level description of \textit{Minyomerus} [JF2015].
+		Other length and width measurements were also performed in dorsal orientation, using the maximum length and width of the corresponding structure (profemur, protibia, elytron, and aedeagus).
+		Images of mouthparts and terminalia were produced with the Leica microscope equipment, while habitus photographs were created with a Visionary Digital Passport II system using a Canon EOS Mark 5D II camera.
+
+		The herein newly recognized species of \textit{Minyomerus} [JF2018] were delimited through application of the phylogenetic species concept \textit{sensu} \citet{wheeler2000}.
+		Species descriptions are in alphabetical order, rather than phylogenetic order, for ease of use.
+		As in \citet{jansen2015}, the species descriptions represent unique, complementary accounts of the character states observed for each species, including their intra-specific variability, but excepting characters invariant within the genus-level concept of \textit{Minyomerus} [JF2015].
 		Likewise, descriptions of males emphasize characters that are variable and sufficiently different from those of the females to merit recognition.
-		The key to identifying species of \textit{Minyomerus} [JF2015] is arranged with emphasis being placed on the most readily observable diagnostic characters.
-				This manuscript is arranged with the species descriptions appearing first, followed by the key to species, and then by the phylogenetic results.
+		The key to identifying species of \textit{Minyomerus} [JF2018] is arranged with emphasis being placed on the most readily observable diagnostic characters.
+		This manuscript is arranged with the species descriptions appearing first, followed by the key to species, and then by the phylogenetic and RCC--5 alignment results.
 
@@
 		Because generic relationships in the Tanymecini [non-focal] remain unresolved, we selected a relatively far-removed taxon to root the cladogram that would nevertheless display states applicable to the ingroup for characters under consideration \citep{rieppel2007, franz2014}.
-		To this end we used the North American species \textit{Sitona californicus} (Fahr{\ae}us, 1840) [non-focal], of the tribe Sitonini Gistel, 1856 [non-focal].
+		To this end we used the North American species \textit{Sitona californicus} (Fahraeus, 1840) [non-focal], of the tribe Sitonini Gistel, 1856 [non-focal].
 
@@
 
+	\subsection*{Taxonomic annotations and RCC--5}\label{ssec:taxanno} 
+		In accordance with \citet{jansen2015}, we use the symbol "=" to indicate nomenclatural synonymy (objective/subjective); and the RCC--5 symbols \{$==$, $>$, $<$, $><$, !\} indicate taxonomic concept articulations.
+The annotations (INT) and (OST) indicate intensional and ostensive readings of articulations, and AND is used to connect multiple simultaneously recognized provenance relationships.
+		Two \emph{intensional} alignments are produced as part of this revision, i.e., one that captures the non-/congruence of \textit{Minyomerus} [JF2018] versus \textit{Minyomerus} [JF2015] represented as rank-only classifications (Fig.~\ref{fig:align1}), and another that represents these as fully bifurcated phylogenies with newly assigned clade concept labels, shown in whole-concept resolution (Fig.~\ref{fig:align2}) and in split-concept resolution (Fig.~\ref{fig:align3}); see \citet{fea2018}.
+
+		A detailed breakdown of our alignment approach and outcomes using an RCC--5 logic reasoner toolkit \citep{chen2014} is provided in the \textbf{Supplemental Information, SI1 to SI4}.
+For further information, see also \citet{jansen2015, fea2016a, fea2016b}.
+
 	\subsection*{Species distribution modeling}\label{ssec:dismo} 
-		We used the modeling program Maxent, Version 3.4, to generate habitat models for the species of Minyomerus [JF2015] (Figs.~\ref{fig:map_summary}-\ref{fig:map_sculptilis}) based on documented occurrence records \citep{phillips2004, phillips2006, elith2011}.
+		We used the modeling program Maxent, Version 3.4, to generate habitat models for the species of Minyomerus [JF2018] (Figs.~\ref{fig:map_summary}-\ref{fig:map_sculptilis}) based on documented occurrence records \citep{phillips2004, phillips2006, elith2011}.
 		The default settings were adjusted to \texttt{Max number background points = 100,000} and \texttt{Iterations = 10}.
@@
 		\subsubsection*{Diagnosis}
-			\textit{Minyomerus ampullaceus} is best differentiated from other congenerics by its unique body shape, which most prominently features a strongly constricted, sub-cylindrical pronotum and greatly protuberant elytra; this combination gives the species a distinctly flask- or bottle-shaped appearance.
-			Due to the relatively poor condition of the scales and set{\ae} of the holotype, color and setation cannot be reliably used for identification.
-			Fortunately, the elytra themselves are unique in shape, and diagnostic, together nearly 2\x the width of the pronotum at their widest point, and nearly 3/4\x as wide as long in dorsal view.
+			\textit{Minyomerus ampullaceus} [JF2018] is best differentiated from other congenerics by its unique body shape, which most prominently features a strongly constricted, sub-cylindrical pronotum and greatly protuberant elytra; this combination gives the species a distinctly flask- or bottle-shaped appearance.
+			Due to the relatively poor condition of the scales and setae of the holotype, color and setation cannot be reliably used for identification.
+			However, the elytra themselves are unique in shape, and diagnostic, together nearly 2\x the width of the pronotum at their widest point, and nearly 3/4\x as wide as long in dorsal view.
 			In lateral view the anterior and posterior declivities of the elytra are strongly abrupt, and nearly vertical; most notably, the anterior margin of the elytra projects strongly and characteristically dorsad of its articulation with the posterior pronotal margin.
@@
 				Scales with variously interspersed colors ranging from slightly off-white to beige to yellow. 
-				Set{\ae} recumbent to sub-recumbent, white to brown in color.
+				Setae recumbent to sub-recumbent, white to brown in color.
 			\paragraph{Mandibles}
-				Partially covered with white, slightly opalescent scales, with 3 longer set{\ae}, and 1 shorter seta between these.
+				Partially covered with white, slightly opalescent scales, with 3 longer setae, and 1 shorter seta between these.
 			\paragraph{Rostrum}
@@
 				Dorsal outline of rostrum nearly square, anterior half of dorsal surface mesally concave, posterior half coarsely but shallowly punctate to rugose. 
-				Rostrum in lateral view nearly square; apical margin broadly bisinuate and emarginate, with 2 pairs of large vibriss{\ae}. 
+				Rostrum in lateral view nearly square; apical margin broadly bisinuate and emarginate, with 2 pairs of large vibrissae. 
 				Nasal plate defined by Y-shaped, impressed lines, convex, integument partially covered with white scales.
@@
 				Ventrolateral sulci strongly defined, beginning as a narrow sulcus posteriad of insertion point of mandibles, running parallel to scrobe, terminating in a ventral fovea.
-			\paragraph{Antenn{\ae}}
+			\paragraph{Antennae}
 				Small tooth formed by overhanging dorsal margin of scrobe directly ventrad of margin of eye.
@@
 				Anterior margin slightly arcuate, lateral margins curved and widening into a bulge just anteriad of midpoint of pronotum, posterior margin straight, with a slight mesal incurvature. 
-				Pronotum in lateral view with set{\ae} that reach beyond anterior margin by 1/2 of their length; these set{\ae} becoming evenly longer and more erect laterally, reaching a maximum length equal to 1/2 of length of eye.
-				Anterolateral margin with a reduced tuft of 6-7 post-ocular vibriss{\ae} present, emerging near ventral 1/2 of eye, and stopping just below ventral margin of eye; vibriss{\ae} sub-equal in length at 1/3 of anterior-posterior length of eye, except for three vibriss{\ae} achieving a maximum length similar to anterior-posterior length of eye.
+				Pronotum in lateral view with setae that reach beyond anterior margin by 1/2 of their length; these setae becoming evenly longer and more erect laterally, reaching a maximum length equal to 1/2 of length of eye.
+				Anterolateral margin with a reduced tuft of 6-7 post-ocular vibrissae present, emerging near ventral 1/2 of eye, and stopping just below ventral margin of eye; vibrissae sub-equal in length at 1/3 of anterior-posterior length of eye, except for three vibrissae achieving a maximum length similar to anterior-posterior length of eye.
 			\paragraph{Scutellum}
@@
 				Profemur/pronotum length ratio 1.04; profemur with distal 1/5 produced ventrally as a rounded projection covering tibial joint; condyle of tibial articulation occupying 4/5 of distal surface and 1/5 length of femur.
-				Protibia/profemur length ratio 0.93; protibial apex with ventral setal comb recessed in an incurved groove; mucro present as a large, black, sub-triangular, medially-projected tooth, which is approximately equilateral and whose sides are sub-equal in length to surrounding set{\ae}.
+				Protibia/profemur length ratio 0.93; protibial apex with ventral setal comb recessed in an incurved groove; mucro present as a large, black, sub-triangular, medially-projected tooth, which is approximately equilateral and whose sides are sub-equal in length to surrounding setae.
 				Protarsus with tarsomere III 1.25\x as long as II; wider than long. 
-				Metatibial apex with almond shaped convexity ringed by 10 short, spiniform set{\ae}.
+				Metatibial apex with almond shaped convexity ringed by 10 short, spiniform setae.
 			\paragraph{Elytra}
@@
 				Posterior declivity angled at nearly 85\td to main body axis.
-Elytra with 10 complete stri{\ae}; stri{\ae} shallow; punctures faint beneath appressed scales, separated by 5-7\x their diameter; intervals very slightly elevated.
+Elytra with 10 complete striae; striae shallow; punctures faint beneath appressed scales, separated by 5-7\x their diameter; intervals very slightly elevated.
 			\paragraph{Abdominal sterna}
@@
 		\subsubsection*{Etymology}
-			Named in reference to the shape of the body in dorsal view, which appears bottle-shaped due to the large elytra and comparatively cylindrical pronotum; ampullaceus = flasklike; Latin adjective \citep{brown1956}.
+			Named in reference to the shape of the body in dorsal view, which appears bottle-shaped due to the large elytra and comparatively cylindrical pronotum -- \textit{ampullaceus} = "flasklike"; Latin adjective \citep{brown1956}.
 		\subsubsection*{Material examined}
@@
 			No host plant associations have been documented.
-			The label indicates ``Geococcyx calif''; this is presumably a reference to \textit{Geococcyx californianus} (Lesson, 1829 [non-focal]; Cuculid{\ae} [non-focal]), the Greater Roadrunner, although it is unclear if the specimen was found on or near one of these birds (either living, dead, or in a nest).
-			\textit{Minyomerus} species are only known to be phytophagous, not parasitic, phoretic, or necrophagous, so we believe that this specimen was most likely found in a nest, and was present there only incidentally because the nest was constructed in the host plant of this specimen \citep{jansen2015}.
+			The label indicates ``Geococcyx calif''; this is presumably a reference to \textit{Geococcyx californianus} (Lesson, 1829) [non-focal] (Cuculidae [non-focal]), the Greater Roadrunner, although it is unclear if the specimen was found on or near one of these birds (either living, dead, or in a nest).
+			Species of \textit{Minyomerus} [JF2018] are only known to be phytophagous, not parasitic, phoretic, or necrophagous.
+Hence we believe that this specimen was most likely found in a nest, and was present there only incidentally because the nest was constructed in the host plant of this specimen \citep{jansen2015}.
 			It is unknown whether this species is parthenogenetic.
@@
 		\subsubsection*{Diagnosis}
-			\textit{Minyomerus franko} is readily distinguished from other congenerics by the strikingly long set{\ae} of the anterior margin of the pronotum, which project laterally up to 80\td from the longitudinal axis of the body and achieve a maximum length at least equaling the diameter of the eye.
-			In addition, the set{\ae} lining the dorsal margin of the ocular impression are elongate and reach a length equal to 1/2 - 3/4\x the diameter of the eye.
+			\textit{Minyomerus franko} [JF2018] is readily distinguished from other congenerics by the strikingly long setae of the anterior margin of the pronotum, which project laterally up to 80\td from the longitudinal axis of the body and achieve a maximum length at least equaling the diameter of the eye.
+			In addition, the setae lining the dorsal margin of the ocular impression are elongate and reach a length equal to 1/2 - 3/4\x the diameter of the eye.
 			The spermatheca has a short, somewhat bulbous corpus, with the ramus sub-equal in size and perpendicular to the corpus, and the collum is strongly recurved along the basal 1/3 of its length.
-			The {\ae}deagus is relatively short and wide, and is abruptly constricted in the apical 1/5 of its length, thereafter tapered to a rounded point.
+			The aedeagus is relatively short and wide, and is abruptly constricted in the apical 1/5 of its length, thereafter tapered to a rounded point.
 		\subsubsection*{Description of female}
@@
 				Scales with variously interspersed colors ranging from slightly off-white or beige to manila/tan to dark coffee brown, in some specimens appearing semi-translucent (in others opaque). 
-				Set{\ae} linear to slightly apically explanate, appearing minutely spatulate, sub-recumbent to sub-erect, white or brown in color.
+				Setae linear to slightly apically explanate, appearing minutely spatulate, sub-recumbent to sub-erect, white or brown in color.
 			\paragraph{Mandibles}
-				Covered with white scales, with 3 longer set{\ae}, and 1-2 shorter set{\ae} between these.
-			\paragraph{Maxill{\ae}}
+				Covered with white scales, with 3 longer setae, and 1-2 shorter setae between these.
+			\paragraph{Maxillae}
 				Cardo bifurcate at base with an inner angle typically between 90–120\td, arms of equal length, inner (mesal) arm nearly 1.5\x thicker than outer arm, both arms of bifurcation equal in length to apically outcurved arm, glabrous.
@@
 				Galeo-lacinial complex nearly extending to apex of maxillary palpomere II; complex mesally membranous, laterally sclerotized, with sharp demarcation of sclerotized region separating palpiger from galeo-lacinial complex; setose in membranous area just adjacent to sclerotized
-region, set{\ae} covering 2/3 of dorsal surface area; dorsally with 7 apicomesal lacinial teeth; ventrally with 4 reduced lacinial teeth. 
+region, setae covering 2/3 of dorsal surface area; dorsally with 7 apicomesal lacinial teeth; ventrally with 4 reduced lacinial teeth. 
 				Palpiger with a single lateral seta, otherwise glabrous and evenly sclerotized throughout.
 			\paragraph{Maxillary palps}
-				I apically oblique, apical end forming a 45\td angle with base, with 2 apical set{\ae}; II sub-cylindrical, with 1 apical seta.
+				I apically oblique, apical end forming a 45\td angle with base, with 2 apical setae; II sub-cylindrical, with 1 apical seta.
 			\paragraph{Labium}
@@
 				Dorsal outline of rostrum sub-rectangular, anterior half of dorsal surface feebly impressed, posterior half coarsely but shallowly punctate to rugose. 
-				Rostrum in lateral view nearly square; apical margin bisinuate and emarginate , with 2 large vibriss{\ae}. 
+				Rostrum in lateral view nearly square; apical margin bisinuate and emarginate , with 2 large vibrissae. 
 				Nasal plate defined by broad, V-shaped, shallowly impressed lines, anteromesally slightly convex, integument partially covered with white scales. 
@@
 				Rostrum ventrally lacking sulci at corners of oral cavity.
-			\paragraph{Antenn{\ae}}
+			\paragraph{Antennae}
 				Small tooth formed by overhanging dorsal margin of scrobe anterior to margin of eye by 1/5 of length of eye.
 				Scape nearly extending to posterior 1/4 of eye.
-				Terminal funicular antennomere lacking appressed scales, having instead a covering of apically-directed pubescence with interspersed sub-erect set{\ae}.
+				Terminal funicular antennomere lacking appressed scales, having instead a covering of apically-directed pubescence with interspersed sub-erect setae.
 				Club nearly 3\x as long as wide.
@@
 				Anterior margin arcuate, lateral margins curved and widening into a slight bulge just anteriad of midpoint of pronotum, posterior margin straight, with a slight mesal incurvature. 
-				Pronotum in lateral view with set{\ae} that reach just beyond anterior margin, angled laterally at 45-80\td to longitudinal axis, and strikingly long; these set{\ae} becoming evenly longer and more angled laterally, reaching a maximum length nearly equal to length of eye.
-				Anterolateral margin with a reduced tuft of 5 post-ocular vibriss{\ae} present, emerging near ventral 1/2 of eye, and stopping just below ventral margin of eye; vibriss{\ae} sub-equal in length at 1/3\x anterior-posterior length of eye, except for one vibrissa achieving a maximum length similar to anterior-posterior length of eye.
+				Pronotum in lateral view with setae that reach just beyond anterior margin, angled laterally at 45-80\td to longitudinal axis, and strikingly long; these setae becoming evenly longer and more angled laterally, reaching a maximum length nearly equal to length of eye.
+				Anterolateral margin with a reduced tuft of 5 post-ocular vibrissae present, emerging near ventral 1/2 of eye, and stopping just below ventral margin of eye; vibrissae sub-equal in length at 1/3\x anterior-posterior length of eye, except for one vibrissa achieving a maximum length similar to anterior-posterior length of eye.
 			\paragraph{Scutellum}
@@
 				Profemur/pronotum length ratio 1.01-1.02; profemur with distal 1/5 produced ventrally as a sub-rectangular projection covering tibial joint; condyle of tibial articulation occupying 4/5 of distal surface and 1/5 length of femur.
-				Protibia/profemur length ratio 0.86-0.89; protibial apex with ventral setal comb recessed in a subtly incurved groove; mucro present as a large, black, sub-triangular, medially-projected tooth, which is approximately equilateral and whose sides are sub-equal in length to surrounding set{\ae}.
+				Protibia/profemur length ratio 0.86-0.89; protibial apex with ventral setal comb recessed in a subtly incurved groove; mucro present as a large, black, sub-triangular, medially-projected tooth, which is approximately equilateral and whose sides are sub-equal in length to surrounding setae.
 				Protarsus with tarsomere III 2\x as long as II; wider than long. 
-				Metatibial apex with almond shaped convexity ringed by 8-9 short, spiniform set{\ae}.
+				Metatibial apex with almond shaped convexity ringed by 8-9 short, spiniform setae.
 			\paragraph{Elytra}
@@
 				Posterior declivity angled at 70-85\td to main body axis.
-Elytra with 10 complete stri{\ae}; stri{\ae} shallow; punctures faint beneath appressed scales, separated by 5-7\x their diameter; intervals very slightly elevated.
+Elytra with 10 complete striae; striae shallow; punctures faint beneath appressed scales, separated by 5-7\x their diameter; intervals very slightly elevated.
 			\paragraph{Abdominal sterna}
 				Ventrite III anteromesally incurved around a fovea located mesally on anterior margin, posterior margin elevated and set off from IV along lateral 1/3s of its length. 
-				Sternum VII mesally 1/2\x as long as wide; set{\ae} darkening, lengthening, and becoming more erect in posterior 2/3; anterior margin weakly curved.
+				Sternum VII mesally 1/2\x as long as wide; setae darkening, lengthening, and becoming more erect in posterior 2/3; anterior margin weakly curved.
 			\paragraph{Tergum}
@@
 			\paragraph{Abdominal sterna}
-				Sternum VII 2/5-1/2 \x as long as wide, posterior margin arcuate mesally.
+				Sternum VII 2/5-1/2\x as long as wide, posterior margin arcuate mesally.
 			\paragraph{Tergum}
@@
 			\paragraph{Sternum IX}
-				Spiculum gastrale 2\x length of {\ae}deagal pedon. Laminar al{\ae} located on lateral 1/4 of posterior margin.
-			\paragraph{{\AE}deagus}
+				Spiculum gastrale 2\x length of aedeagal pedon. Laminar alae located on lateral 1/4 of posterior margin.
+			\paragraph{Aedeagus}
 				Length/width ratio 2.78-3.16; lateral margins very slightly converging posteriorly, abruptly constricted and more strongly converging in apical 1/5.
@@
 		\subsubsection*{Etymology}
-			Named in reference to the long, somewhat unkempt, erect set{\ae} on the anterior margin of the pronotum; franko = free; Old High-German adjective \citep{brown1956}.
+			Named in reference to the long, somewhat unkempt, erect setae on the anterior margin of the pronotum-- \textit{franko} = "free"; Old High-German adjective \citep{brown1956}.
 		\subsubsection*{Material examined}
 			\paragraph{Holotype}
-				\female~``MEX: S.L.P 1 km N.; Entronque El Huizache; 1493 m 2.VI.87; R. Anderson, \underline{\smash{Sph{\ae}ralcea}}; \underline{\smash{hastula}} A. Gray'' (\texttt{\textbf{CMNC}}).
+				\female~``MEX: S.L.P 1 km N.; Entronque El Huizache; 1493 m 2.VI.87; R. Anderson, \underline{\smash{Sphaeralcea}}; \underline{\smash{hastula}} A. Gray'' [non-focal] (\texttt{\textbf{CMNC}}).
 			\paragraph{Paratypes}
@@
 				``MEXICO: San Luis Potosi; Entronque el Hulzache; 2 June 1987; R. Turnbow'' (\texttt{\textbf{CMNC}}: 1 \female, 1 \male);
-				``MEXICO:Tamaulipas; 8.8 mi. ne. Jaumave; October 10, 1973; Gaumer \& Clark'' (\texttt{\textbf{TAMU}}: 2\female);
-				``9 mi east Santo; Domingo, S.L.P.,; Mexico~~~XI-14-68; Veryl V. Board'' (\texttt{\textbf{TAMU}}: 2 \male).
+				``MEXICO: Tamaulipas; 8.8 mi. ne. Jaumave; October 10, 1973; Gaumer \& Clark'' (\texttt{\textbf{TAMU}}: 2\female);
+				``9 mi east Santo; Domingo, S.L.P.,; Mexico~XI-14-68; Veryl V. Board'' (\texttt{\textbf{TAMU}}: 2 \male).
 		\subsubsection*{Distribution}
-			This species has been found in San Luis Potos\'{i} and Tamaulipas (M\'{e}xico).
-			It is likely to be found throughout the Chihuahuan Desert and arid regions of south-central M\'{e}xico based on habitat similarity (Fig.~\ref{fig:map_franko}).
+			This species has been found in San Luis Potos\'{i} and Tamaulipas (Mexico).
+			It is likely to be found throughout the Chihuahuan Desert and arid regions of south-central Mexico based on habitat similarity (Fig.~\ref{fig:map_franko}).
 		\subsubsection*{Natural history}
-			Associated with spear globemallow (\textit{Sph{\ae}ralcea hastulata} A. Gray [non-focal]; Malvace{\ae} [non-focal]).
+			Associated with spear globemallow \textit{Sphaeralcea hastulata} A. Gray [non-focal] (Malvaceae [non-focal]).
 
@@
 		\subsubsection*{Diagnosis}
-			\textit{Minyomerus sculptilis} is best distinguished from other congenerics, especially \textit{Minyomerus imberbus} Jansen \& Franz, 2015 [JF2015], by a combination of characters, as follows.
-			The interspersed set{\ae} on the body are linear and either brown or white.
-			The anterior margin of the pronotum bears a reduced tuft of post-ocular vibriss{\ae}.
+			\textit{Minyomerus sculptilis} [JF2018] is best distinguished from other congenerics, especially \textit{Minyomerus imberbus} Jansen \& Franz, 2015 [JF2015], by a combination of characters, as follows.
+			The interspersed setae on the body are linear and either brown or white.
+			The anterior margin of the pronotum bears a reduced tuft of post-ocular vibrissae.
 			The head is barely elevated between the eyes.
@@
 			Both the corpus and cornu terminate in large, hood-shaped, explanate projections equal in size to the ramus.
-			The {\ae}deagus is elongate, acutely angulate, and narrowing towards the apex more strongly in the region of the ostium.
+			The aedeagus is elongate, acutely angulate, and narrowing towards the apex more strongly in the region of the ostium.
 		\subsubsection*{Description of female}
@@
 				Scales with variously interspersed colors ranging from slightly off-white or beige to golden brown to dark coffee brown.
-				Set{\ae} sub-recumbent to sub-erect, white to brown in color.
+				Setae sub-recumbent to sub-erect, white to brown in color.
 			\paragraph{Mandibles}
-				Covered with white scales, with 3 longer set{\ae}, and 1 shorter seta between these.
+				Covered with white scales, with 3 longer setae, and 1 shorter seta between these.
 			\paragraph{Rostrum}
@@
 				Dorsal outline of rostrum nearly square, anterior half of dorsal surface mesally concave, posterior half coarsely but shallowly punctate to rugose. 
-				Rostrum in lateral view nearly square; apical margin bisinuate and emarginate, with 2 pairs of large vibriss{\ae}. 
+				Rostrum in lateral view nearly square; apical margin bisinuate and emarginate, with 2 pairs of large vibrissae. 
 				Nasal plate defined by Y-shaped, impressed lines, convex, integument covered with white scales.
@@
 				Ventrolateral sulci strongly defined, beginning as a narrow sulcus posteriad of insertion point of mandibles, running parallel to scrobe, terminating in a ventral fovea.
-			\paragraph{Antenn{\ae}}
+			\paragraph{Antennae}
 				Dorsal margin of scrobe overhanging broadly (not forming a minute tooth).
 				Funicle slightly longer than scape.
-				Scape extending Brassicace{\ae}  to posterior 1/4 of eye.
+				Scape extending Brassicaceae  to posterior 1/4 of eye.
 				Club nearly 3\x as long as wide.
@@
 				Anterior margin arcuate, subtly incurved mesally, and somewhat produced dorsally; anterior constriction broad, posterior margin slightly arcuate.
-				Pronotum in lateral view with set{\ae} that reach beyond anterior margin; these set{\ae} becoming slightly longer and more erect laterally.
-				Anterolateral margin with a reduced tuft of 3-6 post-ocular vibriss{\ae} present, emerging near ventral 1/2 of eye, and stopping just below ventral margin of eye; vibriss{\ae} varying in length from 1/2\x anterior-posterior length of eye to a maximum length similar to anterior-posterior length of eye.
+				Pronotum in lateral view with setae that reach beyond anterior margin; these setae becoming slightly longer and more erect laterally.
+				Anterolateral margin with a reduced tuft of 3-6 post-ocular vibrissae present, emerging near ventral 1/2 of eye, and stopping just below ventral margin of eye; vibrissae varying in length from 1/2\x anterior-posterior length of eye to a maximum length similar to anterior-posterior length of eye.
 			\paragraph{Scutellum}
@@
 				Protarsus with tarsomere III 1.5\x as long as II; wider than long. 
-				Metatibial apex with almond shaped convexity ringed by 10-12 short, spiniform set{\ae}.
+				Metatibial apex with almond shaped convexity ringed by 10-12 short, spiniform setae.
 			\paragraph{Elytra}
@@
 				Posterior declivity angled at 65-70\td to main body axis.
-Elytra with 10 complete stri{\ae}; stri{\ae} broadly sculpted; punctures faint beneath appressed scales, separated by 5-7\x their diameter; intervals elevated, with every second interval, beginning at elytral suture, more strongly raised than adjacent intervals.
+Elytra with 10 complete striae; striae broadly sculpted; punctures faint beneath appressed scales, separated by 5-7\x their diameter; intervals elevated, with every second interval, beginning at elytral suture, more strongly raised than adjacent intervals.
 			\paragraph{Abdominal sterna}
@@
 			\paragraph{Abdominal sterna}
-				Sternum VII 1/2 \x as long as wide, posterior margin feebly arcuate mesally.
+				Sternum VII 1/2\x as long as wide, posterior margin feebly arcuate mesally.
 			\paragraph{Tergum}
@@
 				Consisting of 2 sub-triangular sclerites; antero-laterally with a sharply-pointed projection as long as anterior-posterior length of triangular portion of sclerite.
-			\paragraph{{\AE}deagus}
+			\paragraph{Aedeagus}
 				Length/width ratio 7.00; lateral margins parallel, more strongly converging in region of ostium. 
@@
 		\subsubsection*{Etymology}
-			Named in reference to the elevated elytral intervals, which give this species a sculpted appearance; sculptilis = sculpted; Latin adjective \citep{brown1956}.
+			Named in reference to the elevated elytral intervals, which give this species a sculpted appearance -- \textit{sculptilis} = "sculpted"; Latin adjective \citep{brown1956}.
 		\subsubsection*{Material examined}
 			\paragraph{Holotype}
-				\female~``Burley, Idaho; \#7, 5-20-32; \underline{A.} \underline{tridentata}; David E. Fox'' (\texttt{\textbf{USNM}}).
+				\female~``Burley, Idaho; \#7, 5-20-32; \underline{A.}[\textit{rtemisia}] \underline{tridentata} [non-focal]; David E. Fox'' (\texttt{\textbf{USNM}}).
 			\paragraph{Paratypes}
-				``Milner, Idaho; \#5a, 7-9-31; S. pestifer; David E. Fox'' (\texttt{\textbf{USNM}}: 1 \female);
-				``Hazelton, Ida; \#10~~~4/29/30; N. altissma'' (\texttt{\textbf{USNM}}: 1 \male)
+				``Milner, Idaho; \#5a, 7-9-31; \textit{S.}[\textit{alsola}] \textit{pestifer}; David E. Fox'' (\texttt{\textbf{USNM}}: 1 \female);
+				``Hazelton, Ida; \#10~~~4/29/30; \textit{N.}[\textit{orta}] \textit{altissma}'' (\texttt{\textbf{USNM}}: 1 \male)
 		\subsubsection*{Distribution}
@@
 		\subsubsection*{Natural history}
-			Associated with big sagebrush (\textit{Artemisia tridentata} Nutt.
-[non-focal]; Asterace{\ae} [non-focal]), tumbleweed (\textit{Salsola tragus} L.
-[non-focal]; Amaranthace{\ae} [non-focal]), tall tumblemustard (\textit{Sisymbrium altissimum} L.
-[non-focal]; Brassicace{\ae} [non-focal]).
+			Associated with big sagebrush \textit{Artemisia tridentata} Nutt.
+[non-focal] (Asteraceae [non-focal]), tumbleweed \textit{Salsola tragus} L.
+[non-focal] (= \textit{Salsola pestifer} A.
+Nelson [non-focal]) (Amaranthaceae [non-focal]), and tall tumblemustard \textit{Sisymbrium altissimum} L.
+[non-focal] (= \textit{Norta altissima} (L.) Britt.
+[non-focal]) (Brassicaceae [non-focal]).
 
@@
 		\subsubsection*{Diagnosis}
-			\textit{Minyomerus tylotos} is most readily distinguished from other congenerics by a combination of characters, as follows.
+			\textit{Minyomerus tylotos} [JF2018] is most readily distinguished from other congenerics by a combination of characters, as follows.
 			The nasal plate lacks distinct impressions, having instead a poorly defined anteromesal convexity completely and evenly covered with white scales.
 			The frons is protuberant and moderately punctate.
-			The entire body, including the legs, head, and venter, are clothed with brown, linear to minutely apically expanded set{\ae}, which are of similar length throughout and appear distinctly undifferentiated and uniform across body regions.
+			The entire body, including the legs, head, and venter, are clothed with brown, linear to minutely apically expanded setae, which are of similar length throughout and appear distinctly undifferentiated and uniform across body regions.
 			The body is somewhat bulky, with the pronotum protuberant laterally and globular in dorsal view.
-			The set{\ae} lining the anterodorsal margin of the pronotum uniquely apically explanate, with a longitudinal, medial, ridge-like portion that tapers to either side apicolaterally (visible at high magnification).
+			The setae lining the anterodorsal margin of the pronotum uniquely apically explanate, with a longitudinal, medial, ridge-like portion that tapers to either side apicolaterally (visible at high magnification).
 			The lateral margins of the elytra are protuberant anteriorly and sub-parallel along the between anterior 1/5 and posterior 1/3 of their length.
@@
 				Scales with variously interspersed colors ranging from slightly off-white or beige to manila/tan to dark coffee brown, in some specimens appearing semi-translucent (in others opaque).
-				Set{\ae} linear to apically explanate, appearing minutely spatulate, sub-recumbent to sub-erect, tan to brown in color.
+				Setae linear to apically explanate, appearing minutely spatulate, sub-recumbent to sub-erect, tan to brown in color.
 			\paragraph{Mandibles}
-				Covered with white scales, with 2-3 longer set{\ae}, and 1-3 shorter set{\ae} between these.
-			\paragraph{Maxill{\ae}}
+				Covered with white scales, with 2-3 longer setae, and 1-3 shorter setae between these.
+			\paragraph{Maxillae}
 				Cardo bifurcate at base with an inner angle of ca. 90\td, arms roughly equal in length and width, arms of bifurcation equal in length to apically outcurved arm. 
 				Stipes sub-rectangular, 1.5\x wider than long, roughly equal in width to inner arm of bifurcation of cardo, glabrous. 
-				Galeo-lacinial complex nearly extending to apex of maxillary palpomere I; complex mesally membranous, laterally sclerotized, with sharp demarcation of sclerotized region separating palpiger from galeo-lacinial complex; setose in membranous area just adjacent to sclerotized region, set{\ae} covering 1/2 of dorsal surface area; dorsally with 5 apicomesal lacinial teeth; ventrally with 3 reduced lacinial teeth.
+				Galeo-lacinial complex nearly extending to apex of maxillary palpomere I; complex mesally membranous, laterally sclerotized, with sharp demarcation of sclerotized region separating palpiger from galeo-lacinial complex; setose in membranous area just adjacent to sclerotized region, setae covering 1/2 of dorsal surface area; dorsally with 5 apicomesal lacinial teeth; ventrally with 3 reduced lacinial teeth.
 				Palpiger with a single lateral seta, otherwise glabrous, anterior 1/2 membranous, posteriorly sclerotized.
 			\paragraph{Maxillary palps}
-				I apically oblique, apical end forming a 45\td angle with base, with 2 apical set{\ae}; II sub-cylindrical, with 1 apical seta.
+				I apically oblique, apical end forming a 45\td angle with base, with 2 apical setae; II sub-cylindrical, with 1 apical seta.
 			\paragraph{Labium}
@@
 				Dorsal outline of rostrum nearly square, anterior half of dorsal surface feebly impressed, posterior half coarsely but shallowly punctate to rugose. 
-				Rostrum in lateral view nearly square; apical margin strongly bisinuate and emarginate, appearing medially notched, with 2 large vibriss{\ae}. 
+				Rostrum in lateral view nearly square; apical margin strongly bisinuate and emarginate, appearing medially notched, with 2 large vibrissae. 
 				Nasal plate lacking distinct impressions, having instead a poorly defined anteromesal convexity, integument completely and evenly covered with white scales. 
@@
 				Rostrum ventrally with sub-parallel sulci beginning at corners of oral cavity and continuing halfway to back of head.
-			\paragraph{Antenn{\ae}}
+			\paragraph{Antennae}
 				Minute tooth formed by overhanging dorsal margin of scrobe anterior to margin of eye by 1/3 of length of eye.
 				Scape extending to posterior margin of eye.
-				Terminal funicular antennomere lacking appressed scales, having instead a covering of apically-directed pubescence with interspersed sub-erect set{\ae}.
+				Terminal funicular antennomere lacking appressed scales, having instead a covering of apically-directed pubescence with interspersed sub-erect setae.
 				Club nearly 3\x as long as wide.
@@
 				Anterior margin arcuate, but feebly incurved mesally, lateral margins evenly curved and widening into a bulge just anteriad of midpoint of pronotum, posterior margin straight, with a slight mesal incurvature.
-				Pronotum in lateral view with transverse ventrolateral sulci strongly excavated and distinctly sculptured; with short, recumbent to sub-erect set{\ae} that barely attain or reach just beyond anterior margin; these set{\ae} becoming shorter and more erect laterally, reaching a maximum length nearly equal to length of eye; dorsally, these set{\ae} become uniquely apically explanate, with a longitudinal, medial, ridge-like portion that tapers to either side apicolaterally.
+				Pronotum in lateral view with transverse ventrolateral sulci strongly excavated and distinctly sculptured; with short, recumbent to sub-erect setae that barely attain or reach just beyond anterior margin; these setae becoming shorter and more erect laterally, reaching a maximum length nearly equal to length of eye; dorsally, these setae become uniquely apically explanate, with a longitudinal, medial, ridge-like portion that tapers to either side apicolaterally.
 				Anterolateral margin with a single ocular vibrissa present, emerging near ventral margin of eye; vibrissa achieving a maximum length of 2/5 of anterior-posterior length of eye.
@@
 				Profemur/pronotum length ratio 0.90-0.96; profemur with distal 1/5 produced ventrally as a sub-rectangular projection covering tibial joint; condyle of tibial articulation occupying 4/5 of distal surface and 1/5 length of femur.
-				Protibia/profemur length ratio 0.86-0.91; protibial apex with ventral setal comb recessed in a subtly incurved groove; mucro present as an acute, medially-projected tooth, which is approximately equal in length to surrounding set{\ae}.
+				Protibia/profemur length ratio 0.86-0.91; protibial apex with ventral setal comb recessed in a subtly incurved groove; mucro present as an acute, medially-projected tooth, which is approximately equal in length to surrounding setae.
 				Protarsus with tarsomere III 2\x as long as II; wider than long. 
-				Metatibial apex with weakly projecting, poorly defined, narrow convexity laterally flanged by 5 short, spiniform set{\ae}.
+				Metatibial apex with weakly projecting, poorly defined, narrow convexity laterally flanged by 5 short, spiniform setae.
 			\paragraph{Elytra}
@@
 				Posterior declivity angled at 70-75\td to main body axis.
-Elytra with 10 complete stri{\ae}; stri{\ae} broadly sculpted; punctures broad and faint beneath appressed scales, separated by 4-5\x their diameter; intervals elevated.
+Elytra with 10 complete striae; striae broadly sculpted; punctures broad and faint beneath appressed scales, separated by 4-5\x their diameter; intervals elevated.
 			\paragraph{Abdominal sterna}
 				Ventrite III anteromesally incurved around a fovea located mesally on anterior margin, posterior margin elevated and set off from IV along lateral 3/8s of its length. 
-				Sternum VII mesally 2/3\x as long as wide; set{\ae} slightly lengthening, and becoming medially directed in posterior 1/3; anterior margin weakly curved; posterior margin distinctly incurved mesally, appearing broadly notched; surface of sternite concave, appearing broadly foveate, immediately anteriad of marginal incurvature.
+				Sternum VII mesally 2/3\x as long as wide; setae slightly lengthening, and becoming medially directed in posterior 1/3; anterior margin weakly curved; posterior margin distinctly incurved mesally, appearing broadly notched; surface of sternite concave, appearing broadly foveate, immediately anteriad of marginal incurvature.
 			\paragraph{Tergum}
 				Tergum VII mesally incurved.
-				Pygidium sub-cylindrical; medial 1/3 of anterior 2/3 of pygidium less sclerotized, with a patch of very short, fine set{\ae}.
+				Pygidium sub-cylindrical; medial 1/3 of anterior 2/3 of pygidium less sclerotized, with a patch of very short, fine setae.
 			\paragraph{Sternum VIII}
@@
 			\paragraph{Ovipositor}
-				Coxites as long as broad; styli with 3 set{\ae} near the base.
+				Coxites as long as broad; styli with 3 setae near the base.
 			\paragraph{Spermatheca}
@@
 		\subsubsection*{Etymology}
-			Named in reference to the short, apically explanate set{\ae} interspersed throughout the dorsum, which give this species a distinctly ``knobbed'' appearance; tylotos = knobby; Greek adjective \citep{brown1956}.
+			Named in reference to the short, apically explanate setae interspersed throughout the dorsum, which give this species a distinctly ``knobbed'' appearance; \textit{tylotos} -- knobby; Greek adjective \citep{brown1956}.
 		\subsubsection*{Material examined}
@@
 \section*{Checklist of Species}\label{sec:checklist}
+	RCC--5 articulations are provided in \textbf{bold font.} See \citet{jansen2015} for alignments of \textit{Minyomerus} concepts published from 1831 to 2015.
+
 	\begin{tabbing}
 		\quad \= \quad \= = \= \kill
-		\textit{Minyomerus} Horn, 1876: 17\\
-				\> \> = \textit{Elissa} Casey, 1888: 271\\
+		\textbf{\textit{Minyomerus}} Horn, 1876: 17 sec. Jansen \& Franz (2018)\\
+				\> \>  \textbf{== (INT)} AND \textbf{$>$ (OST)} \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz (2015)\\
+				\> \>  \textbf{$>$} AND = \textit{Elissa} Casey, 1888: 271 sec. Casey (1888)\\
 				\> \> \> (synonymized by Kissinger, 1964: 30)\\
-				\> \> = \textit{Pseudelissa} Casey, 1888: 273\\
+				\> \>  \textbf{$>$} AND = \textit{Pseudelissa} Casey, 1888: 273 sec. Casey (1888)\\
 				\> \> \> (synonymized by Pierce, 1909: 359)\\
-				\> \> = \textit{Piscatopus} Sleeper, 1960: 84\\
+				\> \> \textbf{$>$} AND = \textit{Piscatopus} Sleeper, 1960: 84 sec. Sleeper (1960)\\
 				\> \> \> (synonymized by Jansen \& Franz, 2015: 12)\\
-			\> \textit{microps} (Say, 1831: 9) [redescribed by Jansen \& Franz, 2015: 45]\\
-				\> \> = \textit{Minyomerus innocuus} Horn, 1876: 18\\
+			\> \textbf{\textit{microps}} (Say, 1831: 9) sec. Jansen \& Franz (2015) [redescribed, p. 45]\\
+				\> \> \textbf{== (INT)} AND \textbf{$>$ (OST)} AND = \textit{Minyomerus innocuus} Horn, 1876: 18 sec. Horn (1876)\\
 				\> \> \> [former type of \textit{Minyomerus}, designated by Pierce, 1913: 400]\\
 				\> \> \> (synonymized by Jansen \& Franz, 2015: 45)\\
-				\> \> = \textit{Thylacites microps} Say, 1831: 9\\
+				\> \> \textbf{== (INT)} AND \textbf{$>$ (OST)} AND = \textit{Thylacites microps} Say, 1831: 9 sec. Say (1831)\\
 				\> \> \> (transferred to \textit{Minyomerus} on the authority of Buchanan \textit{in litt.}\\
 				\> \> \> by Blackwelder and Blackwelder, 1948: 46)\\
-				\> \> = \textit{Thylacites microsus} Boheman, 1833: 523\\
+				\> \> \textbf{== (INT)} AND \textbf{$>$ (OST)} AND = \textit{Thylacites microsus} Boheman, 1833: 523 sec. Boheman (1833)\\
 				\> \> \> (synonymized by LeConte, 1859: 286)\\
-			\> \textit{{\ae}riballux} Jansen \& Franz, 2015: 52\\
-			\> \textit{ampullaceus} \textbf{sp. nov.}\\
-			\> \textit{bulbifrons} Jansen \& Franz, 2015: 81\\
-			\> \textit{caseyi} (Sharp, 1891: 151) [redescribed by Jansen \& Franz, 2015: 66]\\
-				\> \> = \textit{Pseudelissa caseyi} Sharp, 1891: 151\\
-				\> \> \> (genus synonymized by Pierce, 1909: 359)\\
-			\> \textit{conicollis} Green, 1920: 194 [redescribed by Jansen \& Franz, 2015: 33]\\
-			\> \textit{constrictus} (Casey, 1888: 272) [redescribed by Jansen \& Franz, 2015: 22]\\
-				\> \> = \textit{Elissa constricta} Casey, 1888: 272\\
-				\> \> \> (genus synonymized by Kissinger, 1964: 30)\\
-			\> \textit{cracens} Jansen \& Franz, 2015: 61\\
-			\> \textit{franko} \textbf{sp. nov.}\\
-			\> \textit{gravivultus} Jansen \& Franz, 2015: 92\\
-			\> \textit{griseus} (Sleeper, 1960: 84) [redescribed by Jansen \& Franz, 2015: 96]\\
-				\> \> = \textit{Piscatopus griseus} Sleeper, 1960: 84\\
-				\> \> \> (genus synonymized by Jansen \& Franz, 2015: 96)\\
-			\> \textit{imberbus} Jansen \& Franz, 2015: 18\\
-			\> \textit{languidus} Horn, 1876: 18 [redescribed by Jansen \& Franz, 2015: 40]\\
-				\> \> = \textit{Pseudelissa cinerea} Casey, 1888: 274\\
+			\> \textbf{\textit{aeriballux}} Jansen \& Franz, 2015: 52 sec. Jansen \& Franz (2015)\\
+			\> \textbf{\textit{ampullaceus}} \textbf{sp. nov.} sec. Jansen \& Franz (2018)\\
+			\> \textbf{\textit{bulbifrons}} Jansen \& Franz, 2015: 81 sec. Jansen \& Franz (2015)\\
+			\> \textbf{\textit{caseyi}} (Sharp, 1891: 151) sec. Jansen \& Franz (2015) [redescribed, p. 66]\\
+				\> \> \textbf{==} AND = \textit{Pseudelissa caseyi} Sharp, 1891: 151 sec. Sharp (1891)\\
+				\> \> \> (generic name synonymized by Pierce, 1909: 359)\\
+			\> \textbf{\textit{conicollis}} Green, 1920: 194 sec. Jansen \& Franz (2015) [redescribed, p. 33]\\
+			\> \textbf{\textit{constrictus}} (Casey, 1888: 272) sec. Jansen \& Franz (2015) [redescribed, p. 22]\\
+				\> \> \textbf{==} AND = \textit{Elissa constricta} Casey, 1888: 272 sec. Casey (1888)\\
+				\> \> \> (generic name synonymized by Kissinger, 1964: 30)\\
+			\> \textbf{\textit{cracens}} Jansen \& Franz, 2015: 61 sec. Jansen \& Franz (2015)\\
+			\> \textbf{\textit{franko}} \textbf{sp. nov.} sec. Jansen \& Franz (2018)\\
+			\>\textbf{ \textit{gravivultus}} Jansen \& Franz, 2015: 92 sec. Jansen \& Franz (2015)\\
+			\> \textbf{\textit{griseus}} (Sleeper, 1960: 84) sec. Jansen \& Franz (2015) [redescribed, p. 96]\\
+				\> \> \textbf{==} AND = \textit{Piscatopus griseus} Sleeper, 1960: 84 sec. Sleeper (1960)\\
+				\> \> \> (generic name synonymized by Jansen \& Franz, 2015: 96)\\
+			\> \textbf{\textit{imberbus}} Jansen \& Franz, 2015: 18 sec. Jansen \& Franz (2015)\\
+			\> \textbf{\textit{languidus}} Horn, 1876: 18 sec. Jansen \& Franz (2015) [redescribed, p. 40]\\
+				\> \> \textbf{== (INT)} AND \textbf{$>$ (OST)} \textit{Minyomerus languidus} Horn, 1876: 18 sec. Horn (1876)\\
+				\> \> \textbf{==} AND = \textit{Pseudelissa cinerea} Casey, 1888: 274 sec. Casey (1888)\\
 				\> \> \> (synonymized by Pierce, 1909: 359)\\
-			\> \textit{laticeps} (Casey, 1888: 272) [redescribed by Jansen \& Franz, 2015: 27]\\
-				\> \> = \textit{Elissa laticeps} Casey, 1888: 272\\
-				\> \> \> (genus synonymized by Kissinger, 1964: 30)\\
-			\> \textit{politus} Jansen \& Franz, 2015: 86\\
-			\> \textit{puticulatus} Jansen \& Franz, 2015: 75\\
-			\> \textit{reburrus} Jansen \& Franz, 2015: 57\\
-			\> \textit{rutellirostris} Jansen \& Franz, 2015: 103\\
-			\> \textit{sculptilis} \textbf{sp. nov.}\\
-			\> \textit{trisetosus} Jansen \& Franz, 2015: 71\\
-			\> \textit{tylotos} \textbf{sp. nov.}\\
+			\> \textbf{\textit{laticeps}} (Casey, 1888: 272) sec. Jansen \& Franz (2015) [redescribed, p. 27]\\
+				\> \> \textbf{==} AND = \textit{Elissa laticeps} Casey, 1888: 272 sec. Casey (1888)\\
+				\> \> \> (generic name synonymized by Kissinger, 1964: 30)\\
+			\> \textbf{\textit{politus}} Jansen \& Franz, 2015: 86 sec. Jansen \& Franz (2015)\\
+			\> \textbf{\textit{puticulatus}} Jansen \& Franz, 2015: 75 sec. Jansen \& Franz (2015)\\
+			\> \textbf{\textit{reburrus}} Jansen \& Franz, 2015: 57 sec. Jansen \& Franz (2015)\\
+			\> \textbf{\textit{rutellirostris}} Jansen \& Franz, 2015: 103 sec. Jansen \& Franz (2015)\\
+			\> \textbf{\textit{sculptilis}} \textbf{sp. nov.} sec. Jansen \& Franz (2018)\\
+			\> \textbf{\textit{trisetosus}} Jansen \& Franz, 2015: 71 sec. Jansen \& Franz (2015)\\
+			\> \textbf{\textit{tylotos}} \textbf{sp. nov.} sec. Jansen \& Franz (2018)\\
 	\end{tabbing}
 
-\section*{Identification Key}\label{sec:idkey}
+\section*{Species Identification Key}\label{sec:idkey}
 	\begin{xtabular}{@{}
@@
 
-		{1} & {Procox{\ae} apparently separate, with intercoxal processes touching or very nearly so}{\dotfill}{\textbf{2}}\\
-		{--} & {Procox{\ae} apparently contiguous, with intercoxal processes short and not touching}{\dotfill}{\textbf{3}}\\
-
-		{2~(1)} & {Rostrum approximately square and as wide as head in dorsal view; ramus of spermatheca basally narrow, forming a stalk that tapers into an apical bulb}{\breakfill}{\textbf{\textit{Minyomerus rutellirostris} Jansen \& Franz, 2015 [JF2015]}}\\
-		{--} & {Rostrum approximately trapezoidal and narrower than the head in dorsal view; ramus of spermatheca cylindrical, somewhat bulbous, and basally constricted}{\breakfill}{\textbf{\textit{Minyomerus griseus} (Sleeper, 1960) [JF2015]}}\\
-
-		{3~(1)} & {Anterior margin of pronotum bearing a full, well-developed tuft of 10 or more ocular vibriss{\ae}; anterolateral margins of prementum explanate, angular, and posteriorly declivous, with a distinctly hexagonal appearance}{\dotfill}{\textbf{4}}\\
-		{--} & {Ocular vibriss{\ae} reduced in number or length; anterior margins of prementum not explanate and declivous, typically with a pentagonal appearance}{\dotfill}{\textbf{5}}\\
+		{1} & {Procoxae apparently separate, with intercoxal processes touching or very nearly so}{\dotfill}{\textbf{2}}\\
+		{--} & {Procoxae apparently contiguous, with intercoxal processes short and not touching}{\dotfill}{\textbf{3}}\\
+
+		{2~(1)} & {Rostrum approximately square and as wide as head in dorsal view; ramus of spermatheca basally narrow, forming a stalk that tapers into an apical bulb}{\breakfill}{\textbf{\textit{Minyomerus rutellirostris} [JF2015]}}\\
+		{--} & {Rostrum approximately trapezoidal and narrower than the head in dorsal view; ramus of spermatheca cylindrical, somewhat bulbous, and basally constricted}{\breakfill}{\textbf{\textit{Minyomerus griseus} [JF2015]}}\\
+
+		{3~(1)} & {Anterior margin of pronotum bearing a full, well-developed tuft of 10 or more ocular vibrissae; anterolateral margins of prementum explanate, angular, and posteriorly declivous, with a distinctly hexagonal appearance}{\dotfill}{\textbf{4}}\\
+		{--} & {Ocular vibrissae reduced in number or length; anterior margins of prementum not explanate and declivous, typically with a pentagonal appearance}{\dotfill}{\textbf{5}}\\
 
 		{4~(3)} & {Head very wide and only somewhat swollen between eyes; rostrum ca.
-4\x wider than long in dorsal view; pronotum in dorsal view cylindrical; elytral set{\ae} short, brown, and sub-recumbent; ramus of spermatheca stalked and with apical bulb abruptly constricted, not tapering at point of connection to stalk}{\dotfill}{\textbf{\textit{Minyomerus laticeps} (Casey, 1888) [JF2015]}}\\
-		{--} & {Head and rostrum typical (rostrum 2-3\x wider than long in dorsal view); pronotum in dorsal view somewhat globular, with a strong anterior constriction; elytral set{\ae} short and setiform, especially near disk; spermatheca without basal stalk}{\breakfill}{\textbf{\textit{Minyomerus constrictus} (Casey, 1888) [JF2015]}}\\
-
-		{5~(3)} & {Metatibial apex strongly convex, with set{\ae} similar in length to those of remainder of leg, somewhat lighter in color and translucent, and slightly lamelliform; head somewhat conical in form, rounded between the eyes; elytral set{\ae} copious, not in uniform rows on intervals, instead appearing in offset rows, especially near elytral suture and declivity}{\dotfill}{\textbf{6}}\\
-		{--} & {Metatibial apex oblique or weakly convex, with set{\ae} short and conical in appearance; head roughly quadrate; elytral set{\ae} in relatively uniform rows on elytra, not strongly offset}{\dotfill}{\textbf{7}}\\
-
-		{6~(5)} & {Elytral stri{\ae} deeply and distinctly punctate, appearing pin-striped; elytra without obvious humeri, gradually widening posteriorly; ramus of spermatheca elongate, annulate, and sub-apically situated on corpus}{\dotfill}{\mbox{\textbf{\textit{Minyomerus {\ae}riballux} Jansen \& Franz, 2015 [JF2015]}}}\\
-		{--} & {Elytral stri{\ae} punctate, with punctures somewhat obscured by appressed scales; elytra somewhat pyriform, with weak, but obviously present humeri; ramus of spermatheca elongate, somewhat swollen, and sub-apically situated on corpus}{\breakfill}{\textbf{\textit{Minyomerus reburrus} Jansen \& Franz, 2015 [JF2015]}}\\
-
-		{7~(5)} & {Elytra very strongly convex in lateral view; anterior margin of pronotum wider than posterior margin; spermatheca comma-shaped, with ramus reduced, apically flattened and sub-contiguous with the collum; {\ae}deagal pedon membranous ventrally, and not fully sclerotized}{\breakfill}{\textbf{\textit{Minyomerus conicollis} Green, 1920 [JF2015]}}\\
-		{--} & {Elytra only somewhat convex to nearly flat in lateral view; anterior margin of pronotum similar in length to posterior margin; spermatheca variable; {\ae}deagal pedon fully sclerotized}{\breakfill}{\textbf{8}}\\
+4\x wider than long in dorsal view; pronotum in dorsal view cylindrical; elytral setae short, brown, and sub-recumbent; ramus of spermatheca stalked and with apical bulb abruptly constricted, not tapering at point of connection to stalk}{\dotfill}{\textbf{\textit{Minyomerus laticeps} [JF2015]}}\\
+		{--} & {Head and rostrum typical (rostrum 2-3\x wider than long in dorsal view); pronotum in dorsal view somewhat globular, with a strong anterior constriction; elytral setae short and setiform, especially near disk; spermatheca without basal stalk}{\breakfill}{\textbf{\textit{Minyomerus constrictus} [JF2015]}}\\
+
+		{5~(3)} & {Metatibial apex strongly convex, with setae similar in length to those of remainder of leg, somewhat lighter in color and translucent, and slightly lamelliform; head somewhat conical in form, rounded between the eyes; elytral setae copious, not in uniform rows on intervals, instead appearing in offset rows, especially near elytral suture and declivity}{\dotfill}{\textbf{6}}\\
+		{--} & {Metatibial apex oblique or weakly convex, with setae short and conical in appearance; head roughly quadrate; elytral setae in relatively uniform rows on elytra, not strongly offset}{\dotfill}{\textbf{7}}\\
+
+		{6~(5)} & {Elytral striae deeply and distinctly punctate, appearing pin-striped; elytra without obvious humeri, gradually widening posteriorly; ramus of spermatheca elongate, annulate, and sub-apically situated on corpus}{\dotfill}{\mbox{\textbf{\textit{Minyomerus aeriballux} [JF2015]}}}\\
+		{--} & {Elytral striae punctate, with punctures somewhat obscured by appressed scales; elytra somewhat pyriform, with weak, but obviously present humeri; ramus of spermatheca elongate, somewhat swollen, and sub-apically situated on corpus}{\breakfill}{\textbf{\textit{Minyomerus reburrus} [JF2015]}}\\
+
+		{7~(5)} & {Elytra very strongly convex in lateral view; anterior margin of pronotum wider than posterior margin; spermatheca comma-shaped, with ramus reduced, apically flattened and sub-contiguous with the collum; aedeagal pedon membranous ventrally, and not fully sclerotized}{\breakfill}{\textbf{\textit{Minyomerus conicollis} [JF2015]}}\\
+		{--} & {Elytra only somewhat convex to nearly flat in lateral view; anterior margin of pronotum similar in length to posterior margin; spermatheca variable; aedeagal pedon fully sclerotized}{\breakfill}{\textbf{8}}\\
 
@@
 
-		{9~(8)} & {Set{\ae} of elytral disc a mix of shorter, brown set{\ae} and longer, more erect, white set{\ae}}{\dotfill}{\textbf{10}}\\
-		{--} & {Set{\ae} of elytral disc uniform}{\dotfill}{\textbf{12}}\\
-
-		{10~(9)} & {Anterior margin of pronotum bearing strikingly long set{\ae}, which project laterally up to 80\td from longitudinal body axis and at least equal to diameter of eye;	spermatheca with short, somewhat bulbous corpus, ramus sub-equal in size and perpendicular to corpus, and collum strongly recurved along basal 1/3 of its length; {\ae}deagal pedon relatively short and wide, and abruptly constricted in apical 1/5, thereafter tapered to rounded point}{\breakfill}{\textbf{\textit{Minyomerus franko} [JF2018], sp.
+		{9~(8)} & {Setae of elytral disc a mix of shorter, brown setae and longer, more erect, white setae}{\dotfill}{\textbf{10}}\\
+		{--} & {Setae of elytral disc uniform}{\dotfill}{\textbf{12}}\\
+
+		{10~(9)} & {Anterior margin of pronotum bearing strikingly long setae, which project laterally up to 80\td from longitudinal body axis and at least equal to diameter of eye;	spermatheca with short, somewhat bulbous corpus, ramus sub-equal in size and perpendicular to corpus, and collum strongly recurved along basal 1/3 of its length; aedeagal pedon relatively short and wide, and abruptly constricted in apical 1/5, thereafter tapered to rounded point}{\breakfill}{\textbf{\textit{Minyomerus franko} [JF2018], sp.
 n.}}\\
-		{--} & {Anterior margin of pronotum bearing set{\ae} more strongly directed anteriorly and never as long as diameter of eye; spermatheca variable; {\ae}deagal pedon, where known, narrow and expanded laterally in region of ostium}{\dotfill}{\textbf{11}}\\
-
-		{11~(10)} & {Set{\ae} apically explanate, appearing somewhat spatulate; corpus of spermatheca uniquely elongate, ramus short and cylindrical}{\dotfill}{\textbf{\textit{Minyomerus caseyi} (Sharp, 1891) [JF2015]}}\\
-		{--} & {Set{\ae} linear; corpus of spermatheca typical, ramus bulbous and basally constricted}{\breakfill}{\textbf{\textit{Minyomerus trisetosus} Jansen \& Franz, 2015 [JF2015]}}\\
-
-		{12~(9)} & {Anterior margin of pronotum lined with linear set{\ae} that extend anteriorly beyond margin by half their length}{\dotfill}{\textbf{13}}\\
-		{--} & {Anterior margin of pronotum lacking set{\ae}, or with set{\ae} that do not extend far beyond margin}{\breakfill}{\textbf{14}}\\
-
-		{13~(12)} & {Lateral margins of gular cavity strongly rounded, never straight, and slightly longer than posterior margin; frons weakly projected between eyes; appressed scales on elytra without opalescent sheen; nasal plate with or without metallic reflections; lamina of spiculum ventrale sclerotized throughout}{\dotfill}{\textbf{\textit{Minyomerus languidus} Horn, 1876 [JF2015]}}\\
-		{--} & {Lateral margins of gular cavity nearly straight, and not longer than posterior margin; frons strongly projected between eyes; appressed scales with strong opalescent sheen; nasal plate with metallic reflections; lamina of spiculum ventrale with a membranous region present medially between laminar arm}{\dotfill}{\textbf{\textit{Minyomerus gravivultus} Jansen \& Franz, 2015 [JF2015]}}\\
-
-		{14~(12)} & {Elytra each 4-5\x as long as broad in dorsal view, strongly punctate; elytra constricted anteriad of humeri, narrower than the pronotum, widening thereafter near the humeri; spermatheca with the corpus somewhat bulbous, and the ramus either flattened somewhat or slightly elongate}{\breakfill}{\textbf{\textit{Minyomerus cracens} Jansen \& Franz, 2015 [JF2015]}}\\
+		{--} & {Anterior margin of pronotum bearing setae more strongly directed anteriorly and never as long as diameter of eye; spermatheca variable; aedeagal pedon, where known, narrow and expanded laterally in region of ostium}{\dotfill}{\textbf{11}}\\
+
+		{11~(10)} & {Setae apically explanate, appearing somewhat spatulate; corpus of spermatheca uniquely elongate, ramus short and cylindrical}{\dotfill}{\textbf{\textit{Minyomerus caseyi} [JF2015]}}\\
+		{--} & {Setae linear; corpus of spermatheca typical, ramus bulbous and basally constricted}{\breakfill}{\textbf{\textit{Minyomerus trisetosus} [JF2015]}}\\
+
+		{12~(9)} & {Anterior margin of pronotum lined with linear setae that extend anteriorly beyond margin by half their length}{\dotfill}{\textbf{13}}\\
+		{--} & {Anterior margin of pronotum lacking setae, or with setae that do not extend far beyond margin}{\breakfill}{\textbf{14}}\\
+
+		{13~(12)} & {Lateral margins of gular cavity strongly rounded, never straight, and slightly longer than posterior margin; frons weakly projected between eyes; appressed scales on elytra without opalescent sheen; nasal plate with or without metallic reflections; lamina of spiculum ventrale sclerotized throughout}{\dotfill}{\textbf{\textit{Minyomerus languidus} [JF2015]}}\\
+		{--} & {Lateral margins of gular cavity nearly straight, and not longer than posterior margin; frons strongly projected between eyes; appressed scales with strong opalescent sheen; nasal plate with metallic reflections; lamina of spiculum ventrale with a membranous region present medially between laminar arm}{\dotfill}{\textbf{\textit{Minyomerus gravivultus} [JF2015]}}\\
+
+		{14~(12)} & {Elytra each 4-5\x as long as broad in dorsal view, strongly punctate; elytra constricted anteriad of humeri, narrower than the pronotum, widening thereafter near the humeri; spermatheca with the corpus somewhat bulbous, and the ramus either flattened somewhat or slightly elongate}{\breakfill}{\textbf{\textit{Minyomerus cracens} [JF2015]}}\\
 		{--} & {Elytra not so elongate, variably punctate; elytra lacking basal constriction; spermatheca variable}{\dotfill}{\textbf{15}}\\
 
-		{15~(14)} & {Elytral stri{\ae} with large, obvious punctures}{\dotfill}{\textbf{16}}\\
-		{--} & {Elytral stri{\ae} without evident punctures}{\dotfill}{\textbf{17}}\\
-
-		{16~(15)} & {Frons strongly protuberant; elytra in lateral view convex dorsally; spermatheca with corpus possessing an annulate, rectate projection nearly 1/2\x length of ramus; {\ae}deagal pedon evenly curving towards apex; {\ae}deagal flagellum with spiriform apical sclerite that spirals counterclockwise and of equal length to {\ae}deagal pedon}{\breakfill}{\textbf{\textit{Minyomerus bulbifrons} Jansen \& Franz, 2015 [JF2015]}}\\
-		{--} & {Frons not so protuberant; elytra in lateral view nearly flat dorsally; spermatheca with corpus possessing an annulate, rectate projection nearly 2/3\x length of the ramus; {\ae}deagal pedon narrow and elongate; {\ae}deagal flagellum with very minute apical sclerite}{\breakfill}{\textbf{\textit{Minyomerus puticulatus} Jansen \& Franz, 2015 [JF2015]}}\\
+		{15~(14)} & {Elytral striae with large, obvious punctures}{\dotfill}{\textbf{16}}\\
+		{--} & {Elytral striae without evident punctures}{\dotfill}{\textbf{17}}\\
+
+		{16~(15)} & {Frons strongly protuberant; elytra in lateral view convex dorsally; spermatheca with corpus possessing an annulate, rectate projection nearly 1/2\x length of ramus; aedeagal pedon evenly curving towards apex; aedeagal flagellum with spiriform apical sclerite that spirals counterclockwise and of equal length to aedeagal pedon}{\breakfill}{\textbf{\textit{Minyomerus bulbifrons} [JF2015]}}\\
+		{--} & {Frons not so protuberant; elytra in lateral view nearly flat dorsally; spermatheca with corpus possessing an annulate, rectate projection nearly 2/3\x length of the ramus; aedeagal pedon narrow and elongate; aedeagal flagellum with very minute apical sclerite}{\breakfill}{\textbf{\textit{Minyomerus puticulatus} [JF2015]}}\\
 
@@
 
-		{18~(17)} & {Nasal plate defined by inversely V-shaped, impressed lines; spermatheca with the ramus elongate and apically swollen, corpus possessing an annulate, rectate projection nearly 1/2\x length of the ramus, and cornu evenly recurved throughout its length; {\ae}deagal flagellum with a spiriform apical sclerite that spirals clockwise and of equal length to pedon}{\breakfill}{\textbf{\textit{Minyomerus politus} Jansen \& Franz, 2015 [JF2015]}}\\
+		{18~(17)} & {Nasal plate defined by inversely V-shaped, impressed lines; spermatheca with the ramus elongate and apically swollen, corpus possessing an annulate, rectate projection nearly 1/2\x length of the ramus, and cornu evenly recurved throughout its length; aedeagal flagellum with a spiriform apical sclerite that spirals clockwise and of equal length to pedon}{\breakfill}{\textbf{\textit{Minyomerus politus} [JF2015]}}\\
 		{--} & {Nasal plate lacking distinct impressions; spermatheca with ramus basally tapered with a short stalk, corpus narrow and lacking an annulate rectate bulb, and cornu with an abrupt apical curve; males not known}{\dotfill}{\textbf{\textit{Minyomerus tylotos} [JF2018], sp.
@@
 
-		{19~(17)} & {Ventrolateral sulci weakly defined as a notch ventrad of antennal insertion, or absent entirely; intervals broadly sculpted and raised, and stri{\ae} not punctate; body generally robust in overall quality; appressed scales uniformly beige and gray, with a
+		{19~(17)} & {Ventrolateral sulci weakly defined as a notch ventrad of antennal insertion, or absent entirely; intervals broadly sculpted and raised, and striae not punctate; body generally robust in overall quality; appressed scales uniformly beige and gray, with a
 distinctly ‘crusty’ appearance; spematheca with ramus and collum appearing
-as two subcontiguous, apically invaginated bulbs}{\dotfill}{\textbf{\textit{Minyomerus microps} (Say, 1831) [JF2015]}}\\
+as two subcontiguous, apically invaginated bulbs}{\dotfill}{\textbf{\textit{Minyomerus microps} [JF2015]}}\\
 		{--} & {Ventrolateral sulci deeply and distinctly defined along their entire length; intervals, if raised, only sculpted along lateral faces of elytra, not on disk; body usually not markedly robust; appressed scales either translucent or otherwise typical of genus, not beige and crusted; spermatheca distincly sinuate, with well defined, protruding ramus}{\dotfill}{\textbf{20}}\\
 
-		{20~(19)} & {Elytra with very minute set{\ae}, only perceptible at high magnification; lateral faces of elytra with intervals not noticeably raised; ramus of spermatheca elongate, cylindrical, and slightly thinner than corpus, cornu strongly recurved in basal half with uniquely sinuate appearance, both corpus and cornu with hood-like projections shorter than ramus; males not known}{\breakfill}{\textbf{\textit{Minyomerus imberbus} Jansen \& Franz, 2015 [JF2015]}}\\
-		{--} & {Elytra with easily visible, linear set{\ae}; lateral faces of elytra with intervals raised; ramus of spermatheca bulbous, basally tapered, and similar in width to corpus, cornu strongly recurved, but short in basal half with uniquely sinuate appearance, both corpus and cornu with hood-like projections longer than ramus; {\ae}deagal pedon narrow and cylindrical, apically tapered}{\breakfill}{\textbf{\textit{Minyomerus sculptilis} [JF2018], sp.
+		{20~(19)} & {Elytra with very minute setae, only perceptible at high magnification; lateral faces of elytra with intervals not noticeably raised; ramus of spermatheca elongate, cylindrical, and slightly thinner than corpus, cornu strongly recurved in basal half with uniquely sinuate appearance, both corpus and cornu with hood-like projections shorter than ramus; males not known}{\breakfill}{\textbf{\textit{Minyomerus imberbus} [JF2015]}}\\
+		{--} & {Elytra with easily visible, linear setae; lateral faces of elytra with intervals raised; ramus of spermatheca bulbous, basally tapered, and similar in width to corpus, cornu strongly recurved, but short in basal half with uniquely sinuate appearance, both corpus and cornu with hood-like projections longer than ramus; aedeagal pedon narrow and cylindrical, apically tapered}{\breakfill}{\textbf{\textit{Minyomerus sculptilis} [JF2018], sp.
 n.}}\\
@@
 	These characters are comprised of all 46 characters included in the revision of \textit{Minyomerus} [JF2015], plus an additional 6 characters intended to identify putative sister taxa to the newly described species.
-	Parsimony analysis returned a single, most-parsimonious cladogram (henceforth MPT) with a length (L) of 99 steps, a consistency index (CI) of 60 and a retention index (RI) of 80 \citep{farris1989}.
+	Parsimony analysis returned a single, most-parsimonious cladogram (henceforth MPT) with a length (L) of 99 steps, a consistency index (CI) of 60 and a retention index (RI) of 80 \citep{farris1989}; see Figs.~\ref{fig:tree1}-\ref{fig:tree2}.
 	TNT (Tree Analysis Using New Technology) was used to confirm that the shortest tree had been found \citep{goloboff2008}.
-	The most-parsimonious cladogram is shown in Fig.~\ref{fig:tree}, with relative and absolute Bremer support values (see also \textbf{\nameref{sec:methods}: \nameref{ssec:phylo}}) mapped along the left side of each branch; nodes with bootstrap support above 0.95 are marked with a ``*'' symbol to the right of each node.
+	The most-parsimonious cladogram is shown in Fig.~\ref{fig:tree1}, with relative and absolute Bremer support values (see also \textbf{\nameref{sec:methods}: \nameref{ssec:phylo}}) mapped along the left side of each branch; nodes with bootstrap support above 0.95 are marked with a ``*'' symbol to the right of each node.
+In a complementary graph, we show the herein used clade concept labels (Fig.~\ref{fig:tree2}).
 
@@
 Includes all species of \textit{Minyomerus} [JF2015], newly designated species, and select outgroup taxa.
-All multistate characters coded as additive, except for character 33.
+All multi-state characters coded as additive, except for character 33.
 The symbol ``–'' denotes inapplicable character states, whereas ``?'' denotes missing information (see also text).}
@@
     	\footnotesize
-    	\begin{tabular}{m{11.10}|l}
+    	\begin{tabular}{m{8.25}|l}
       	\toprule
-      	\multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Taxon{\textbackslash}Character}}} 
+      	\multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Taxon {\textbackslash} Character}}} 
       														& ~~~~0~~~~~1~~~~~1~~~~~2~~~~~2~~~~~3~~~~~3~~~~~4~~~~~4~~~~~5~~~\\
@@
       	\midrule
-      	Sitona.californicus       & 00-00~?????~00000~00000~00000~00000~00---~-0---~--???~?????~??\\
-      	Pandeleteius.cinereus     & 11000~?????~01000~00001~01000~00100~00000~000-0~00???~?????~??\\
-      	Pandeleteinus.subcancer   & 11000~?????~01000~00001~01010~00100~00000~000-0~00???~?????~??\\
-				Isodrusus.debilis         & 11000~?????~01000~00001~01011~00100~00000~000-0~00???~?????~??\\
-				Isodacrys.buchanani       & 11000~?????~01000~00001~01011~00101~00000~000-0~00???~?????~??\\
-				Minyomerus.constrictus    & 21100~00010~02110~01002~00011~11211~00000~00000~00000~01010~00\\
-				Minyomerus.laticeps       & 21100~00010~02110~01002~00011~11211~00000~00000~00000~01010~00\\
-				Minyomerus.imberbus       & 21100~?????~02010~11002~10011~11211~01001~00000~00???~?????~??\\
-				Minyomerus.sculptilis     & 21100~?????~02010~11002~10011~11211~01001~00000~00001~00000~10\\
-				Minyomerus.conicollis     & 21100~00000~02010~11002~10011~10211~00001~10000~01000~00000~00\\
-				Minyomerus.languidus      & 21000~11100~02010~11002~10011~10211~00001~10000~?????~?????~??\\
-				Minyomerus.microps        & 21001~11101~02110~11002~10011~10211~00001~10000~10???~?????~??\\
-				Minyomerus.tylotos        & 21001~11101~02110~11002~10011~10211~00001~10000~00???~?????~??\\
-				Minyomerus.cracens        & 21000~11101~02020~11112~10011~11211~00001~10001~00000~10010~10\\
-				Minyomerus.ampullaceus    & 21000~?????~02020~11??2~10011~11211~00001~11001~00???~?????~??\\
-				Minyomerus.{\textnormal{\textit{{\ae}}}}riballux  
-																	& 22000~11101~12020~11012~10011~20211~00001~11001~10000~00000~01\\
-				Minyomerus.reburrus       & 22000~11101~12020~11112~10011~20211~00001~11021~00???~?????~??\\
-				Minyomerus.franko         & 21110~10100~02020~11002~10011~11211~00001~10011~10010~00000~01\\
-				Minyomerus.caseyi         & 21110~00101~02020~11112~10011~11211~00001~10101~10010~10010~01\\
-				Minyomerus.trisetosus     & 21110~00101~02020~11012~10011~10211~00001~10101~10???~?????~??\\
-				Minyomerus.gravivultus    & 21100~11101~02120~11002~10011~10211~00111~10000~??010~00000~11\\
-				Minyomerus.griseus        & 21100~10101~02120~01002~10111~11211~00111~10000~00010~01100~10\\
-				Minyomerus.rutellirostris & 21100~10101~02120~11002~10111~11211~00111~10000~00010~01100~10\\
-				Minyomerus.puticulatus    & 21000~11101~02020~11012~10011~11211~10101~10010~01011~01000~11\\
-				Minyomerus.bulbifrons     & 21000~11101~02021~11112~10011~10211~10101~10000~01110~01001~01\\
-				Minyomerus.politus        & 21000~?????~02021~11112~10011~10211~10101~10010~01111~01001~11\\
+      				Sitona.californicus $ [non-focal]$    & 00-00~?????~00000~00000~00000~00000~00---~-0---~--???~?????~??\\
+      				Pandeleteius.cinereus $ [non-focal]$    & 11000~?????~01000~00001~01000~00100~00000~000-0~00???~?????~??\\
+      				Pandeleteinus.subcancer $ [non-focal]$    & 11000~?????~01000~00001~01010~00100~00000~000-0~00???~?????~??\\
+				Isodrusus.debilis $ [non-focal]$    & 11000~?????~01000~00001~01011~00100~00000~000-0~00???~?????~??\\
+				Isodacrys.buchanani $ [non-focal]$    & 11000~?????~01000~00001~01011~00101~00000~000-0~00???~?????~??\\
+				Minyomerus.constrictus $ [JF2015]$    & 21100~00010~02110~01002~00011~11211~00000~00000~00000~01010~00\\
+				Minyomerus.laticeps $ [JF2015]$      & 21100~00010~02110~01002~00011~11211~00000~00000~00000~01010~00\\
+				Minyomerus.imberbus $ [JF2015]$      & 21100~?????~02010~11002~10011~11211~01001~00000~00???~?????~??\\
+				Minyomerus.sculptilis $ [JF2018]$    & 21100~?????~02010~11002~10011~11211~01001~00000~00001~00000~10\\
+				Minyomerus.conicollis $ [JF2015]$    & 21100~00000~02010~11002~10011~10211~00001~10000~01000~00000~00\\
+				Minyomerus.languidus $ [JF2015]$     & 21000~11100~02010~11002~10011~10211~00001~10000~?????~?????~??\\
+				Minyomerus.microps $ [JF2015]$       & 21001~11101~02110~11002~10011~10211~00001~10000~10???~?????~??\\
+				Minyomerus.tylotos $ [JF2018]$       & 21001~11101~02110~11002~10011~10211~00001~10000~00???~?????~??\\
+				Minyomerus.cracens $ [JF2015]$       & 21000~11101~02020~11112~10011~11211~00001~10001~00000~10010~10\\
+				Minyomerus.ampullaceus $ [JF2018]$   & 21000~?????~02020~11??2~10011~11211~00001~11001~00???~?????~??\\
+				Minyomerus.aeriballux $ [JF2015]$   & 22000~11101~12020~11012~10011~20211~00001~11001~10000~00000~01\\
+				Minyomerus.reburrus $ [JF2015]$      & 22000~11101~12020~11112~10011~20211~00001~11021~00???~?????~??\\
+				Minyomerus.franko $ [JF2018]$        & 21110~10100~02020~11002~10011~11211~00001~10011~10010~00000~01\\
+				Minyomerus.caseyi $ [JF2015]$        & 21110~00101~02020~11112~10011~11211~00001~10101~10010~10010~01\\
+				Minyomerus.trisetosus $ [JF2015]$    & 21110~00101~02020~11012~10011~10211~00001~10101~10???~?????~??\\
+				Minyomerus.gravivultus $ [JF2015]$    & 21100~11101~02120~11002~10011~10211~00111~10000~??010~00000~11\\
+				Minyomerus.griseus $ [JF2015]$       & 21100~10101~02120~01002~10111~11211~00111~10000~00010~01100~10\\
+				Minyomerus.rutellirostris $ [JF2015]$ & 21100~10101~02120~11002~10111~11211~00111~10000~00010~01100~10\\
+				Minyomerus.puticulatus $ [JF2015]$    & 21000~11101~02020~11012~10011~11211~10101~10010~01011~01000~11\\
+				Minyomerus.bulbifrons $ [JF2015]$     & 21000~11101~02021~11112~10011~10211~10101~10000~01110~01001~01\\
+				Minyomerus.politus $ [JF2015]$        & 21000~?????~02021~11112~10011~10211~10101~10010~01111~01001~11\\
       	\bottomrule
@@
 Coded as additive due to alignment of character states with the preferred phylogeny.
-Coding as non-additive in isolation or in unison with other additive multistate characters does not affect polarization of the character/states or alter the phylogeny.
+Coding as non-additive in isolation or in unison with other additive multi-state characters does not affect polarization of the character/states or alter the phylogeny.
 State 1 is a synapomorphy for the tanymecine clade [non-focal], whereas state 2 is a synapomorphy for \textit{Minyomerus} [JF2018].
 
-		\item Habitus, arrangement of elytral set{\ae}: (0) variously interspersed; (1) arranged in single-file rows on elytral intervals; (2) arranged non-uniformly on elytral intervals.
+		\item Habitus, arrangement of elytral setae: (0) variously interspersed; (1) arranged in single-file rows on elytral intervals; (2) arranged non-uniformly on elytral intervals.
 Coded as additive due to alignment of character states with the preferred phylogeny.
-Coding as non-additive in isolation or in unison with other additive multistate characters does not affect polarization of the character/states or alter the phylogeny.
+Coding as non-additive in isolation or in unison with other additive multi-state characters does not affect polarization of the character/states or alter the phylogeny.
 State 1 is a synapomorphy for the tanymecine clade [non-focal], whereas state 2 is a synapomorphy the \textit{M.
-{\ae}riballux} - \textit{M.
-reburrus} clade [JF2018].
-
-		\item Habitus, lateral elytral set{\ae} and ventral set{\ae} differentiated from set{\ae} of elytral disc: (0) absent; (1) present.
+aeriballux}--\textit{M.
+reburrus} clade [JF2015].
+
+		\item Habitus, lateral elytral setae and ventral setae differentiated from setae of elytral disc: (0) absent; (1) present.
 Homoplasy for \textit{Minyomerus} [JF2018], with a reversal (state 0) in the \textit{M.
-languidus} – \textit{M.
-politus} clade [JF2018], subsequent convergent gain (state 1) in the \textit{M.
-franko} - \textit{M.
-politus} clade, and convergent reversal (state 0) in the \textit{M.
-puticulatus} – \textit{M.
-politus} clade [JF2018] (ci = 25; ri = 70).
-
-	 	\item Habitus, rows of elytral set{\ae} with larger white set{\ae} randomly interspersed among smaller brown set{\ae}: (0) absent; (1) present.
-Synapomorphy for the \textit{M.
-franko} – \textit{M.
-trisetosus} clade [JF2018].
+aeriballux}--\textit{M.
+languidus} clade [JF2015], subsequent convergent gain (state 1) in the \textit{M.
+bulbifrons}--\textit{M.
+caseyi} clade [JF2018], and convergent reversal (state 0) in the \textit{M.
+bulbifrons}--\textit{M.
+puticalutus} clade [JF2015] (ci = 25; ri = 70).
+
+	 	\item Habitus, rows of elytral setae with larger white setae randomly interspersed among smaller brown setae: (0) absent; (1) present.
+Synapomorphy for the \textit{M.
+caseyi}--\textit{M.
+franko} clade [JF2018].
 Changed from \citet{jansen2015}, where \textit{M.
-rutellirostris} [JF2015] was previously coded as having this character; however, the white elytral set{\ae} of this species are not randomly interspersed, but follow a distinct, and uniquely derived, pattern where every other interval contains a row of such set{\ae}.
+rutellirostris} [JF2015] was previously coded as having this character; however, the white elytral setae of this species are not randomly interspersed, but follow a distinct, and uniquely derived, pattern where every other interval contains a row of such setae.
 
@@
 Synapomorphy for the \textit{M.
-microps} – \textit{M.
+microps}--\textit{M.
 tylotos} clade [JF2018].
@@
 Synapomorphy for the \textit{M.
-languidus} – \textit{M.
-politus} clade [JF2018], with a single reversal in the \textit{M.
-caseyi} – \textit{M.
-trisetosus} clade [JF2018] (ci = 50; ri = 75).
+aeriballux}--\textit{M.
+languidus} clade [JF2015], with a single reversal in the  \textit{M.
+caseyi}--\textit{M.
+trisetosus} clade [JF2015] (ci = 50; ri = 75).
 
@@
 Synapomorphy for the \textit{M.
-languidus} – \textit{M.
-politus} clade [JF2018], with independent reversals in the \textit{M.
-franko} – \textit{M.
-trisetosus} clade [JF2018] and \textit{M.
-griseus} – \textit{M.
-rutellirostris} clade [JF2018], respectively (ci = 33; ri = 71).
-
-	 	\item Prementum, anterolateral margins simple, unexpanded: (0) absent; (1) present. Synapomorphy for the \textit{M. languidus} – \textit{M. politus} clade [JF2018].
+aeriballux}--\textit{M.
+languidus} clade [JF2015], with independent reversals in the \textit{M.
+caseyi}--\textit{M.
+franko} clade [JF2018] and \textit{M.
+griseus}--\textit{M.
+rutellirostris} clade [JF2015], respectively (ci = 33; ri = 71).
+
+	 	\item Prementum, anterolateral margins simple, unexpanded: (0) absent; (1) present. Synapomorphy for the \textit{M. aeriballux}--\textit{M. languidus} clade [JF2015].
 
@@
 ACCTRAN optimization preferred (see \citealt{agnarsson2008}), therefore inferred as a synapomorphy for the \textit{M.
-constrictus} – \textit{M.
-laticeps} clade [JF2018].
+constrictus}--\textit{M.
+laticeps} clade [JF2015].
 
@@
 Synapomorphy for the \textit{M.
-microps} – \textit{M.
-politus} clade [JF2018], with a single reversal in \textit{M.
+aeriballux}--\textit{M.
+microps} clade [JF2015], with a single reversal in \textit{M.
 franko} [JF2018] (ci = 50; ri = 75).
 
-	 	\item Rostrum, form in dorsal view: (0) approximately quadrate; (1) somewhat conical, medially convex. Synapomorphy for the \textit{M. {\ae}riballux} – \textit{M. reburrus} clade [JF2018].
-
-	 	\item Rostrum, form of nasal plate and demarcation of epistoma: (0) with three parallel, longitudinal carin{\ae}, and surface planar between these; (1) with a sharp, narrow, chevron-shaped carina demarcating epistoma; (2) with a broad, scale-covered, chevron-shaped carina demarcating epistoma.
+	 	\item Rostrum, form in dorsal view: (0) approximately quadrate; (1) somewhat conical, medially convex. Synapomorphy for the \textit{M. aeriballux}--\textit{M. reburrus} clade [JF2015].
+
+	 	\item Rostrum, form of nasal plate and demarcation of epistoma: (0) with three parallel, longitudinal carinae, and surface planar between these; (1) with a sharp, narrow, chevron-shaped carina demarcating epistoma; (2) with a broad, scale-covered, chevron-shaped carina demarcating epistoma.
 Coded as additive due to alignment of character states with preferred phylogeny.
-Coding as non-additive in isolation or in unison with other additive multistate characters does not affect polarization of the character/states or alter the phylogeny.
+Coding as non-additive in isolation or in unison with other additive multi-state characters does not affect polarization of the character/states or alter the phylogeny.
 State 1 is a synapomorphy for the tanymecine clade [non-focal], whereas state 2 is a synapomorphy for \textit{Minyomerus} [JF2018].
@@
 Convergently present in the \textit{M.
-constrictus} – \textit{M.
-laticeps} clade [JF2018], the \textit{M.
-microps} - \textit{M.
+constrictus}--\textit{M.
+laticeps} clade [JF2015], the \textit{M.
+microps}--\textit{M.
 tylotos} clade [JF2018], and the \textit{M.
-gravivultus} – \textit{M.
-rutellirostris} clade [JF2015] (ci = 33; ri = 60).
+gravivultus}--\textit{M.
+griseus} clade [JF2015] (ci = 33; ri = 60).
 
@@
 Coded as additive due to alignment of character states with preferred phylogeny.
-Coding as non-additive in isolation or in unison with other additive multistate characters does not affect polarization of the character/states or alter the phylogeny.
+Coding as non-additive in isolation or in unison with other additive multi-state characters does not affect polarization of the character/states or alter the phylogeny.
 Synapomorphy for \textit{Minyomerus} [JF2018] (state 1) and the \textit{M.
-cracens} – \textit{M.
-politus} clade [JF2018] (state 2), respectively.
+aeriballux}--\textit{M.
+cracens} clade [JF2015] (state 2), respectively.
 
@@
 Synapomorphy for the \textit{M.
-bulbifrons} – \textit{M.
-politus} clade [JF2018].
+bulbifrons}--\textit{M.
+politus} clade [JF2015].
 
@@
 Synapomorphy for the \textit{M.
-imberbus} – \textit{M.
-politus} clade [JF2018], with a single reversal in \textit{M.
+aeriballux}--\textit{M.
+languidus} clade [JF2015], with a single reversal in \textit{M.
 griseus} [JF2015] (ci = 50, ri = 85).
@@
 caseyi} [JF2015], and the \textit{M.
-bulbifrons} – \textit{M.
-politus} clade [JF2018] (ci = 25; ri = 25).
+bulbifrons}--\textit{M.
+politus} clade [JF2015] (ci = 25; ri = 25).
 
@@
 Synapomorphy for the \textit{M.
-cracens} – \textit{M.
-politus} clade [JF2018] with independent reversals in \textit{M.
+aeriballux}--\textit{M.
+cracens} clade [JF2018] with independent reversals in \textit{M.
 franko} [JF2018] and the \textit{M.
-gravivultus} – \textit{M.
-rutellirostris} clade [JF2015] (ci = 33; ri = 71).
+gravivultus}--\textit{M.
+griseus} clade [JF2015] (ci = 33; ri = 71).
 
@@
 Coded as additive due to alignment of character states with preferred phylogeny.
-Coding as non-additive in isolation or in unison with other additive multistate characters does not affect polarization of the character/states or alter the phylogeny.
+Coding as non-additive in isolation or in unison with other additive multi-state characters does not affect polarization of the character/states or alter the phylogeny.
 State 1 is a synapomorphy for the tanymecine clade [non-focal], whereas state 2 is a synapomorphy for \textit{Minyomerus} [JF2018].
 
-	 	\item Pronotum, condition of post-ocular vibriss{\ae}: (0) present in a well-developed tuft of 10 or more setae; (1) present in a reduced tuft of 3-7 set{\ae}.
-Synapomorphy for the \textit{M.
-imberbus} - \textit{M.
-politus} clade.
+	 	\item Pronotum, condition of post-ocular vibrissae: (0) present in a well-developed tuft of 10 or more setae; (1) present in a reduced tuft of 3-7 setae.
+Synapomorphy for the \textit{M.
+aeriballux}--\textit{M.
+imberbus} clade [JF2018].
 
@@
 
-	 	\item Prosternum, intercoxal process divided at midpoint between cox{\ae}, but both anterior and posterior processes extending completely between procox{\ae} and contiguous with each other: (0) absent; (1) present.
-Synapomorphy for the \textit{M.
-griseus} – \textit{M.
+	 	\item Prosternum, intercoxal process divided at midpoint between coxae, but both anterior and posterior processes extending completely between procoxae and contiguous with each other: (0) absent; (1) present.
+Synapomorphy for the \textit{M.
+griseus}--\textit{M.
 rutellirostris} clade [JF2015].
 
-	 	\item Legs, fore femora not swollen in comparison to other legs: (0) absent; (1) present. Synapomorphy for the \textit{P. subcancer} – \textit{M. politus} clade [non-focal].
-
-	 	\item Legs, sculpture of ventral surface of protibi{\ae}: (0) evenly convex throughout; (1) with a longitudinal groove or concavity.
-Synapomorphy for the \textit{I.
-debilis}–\textit{M.
-politus} clade [JF2018].
-
-	 	\item Legs, setation of metatibial apex: (0) bristles at least as long as surrounding set{\ae} and setiform; (1) bristles shorter than surrounding set{\ae} and conical; (2) bristles sub-equal in length to surrounding set{\ae} and somewhat lamelliform.
+	 	\item Legs, fore femora not swollen in comparison to other legs: (0) absent; (1) present. Synapomorphy for the \textit{M. aeriballux}--\textit{P. subcancer} clade [non-focal].
+
+	 	\item Legs, sculpture of ventral surface of protibiae: (0) evenly convex throughout; (1) with a longitudinal groove or concavity.
+Synapomorphy for the \textit{M.
+aeriballux}--\textit{I.
+debilis} clade [non-focal].
+
+	 	\item Legs, setation of metatibial apex: (0) bristles at least as long as surrounding setae and setiform; (1) bristles shorter than surrounding setae and conical; (2) bristles sub-equal in length to surrounding setae and somewhat lamelliform.
 Coded as additive due to alignment of character states with preferred phylogeny, and the appearance of being a transformation series.
-Coding as non-additive in isolation or in unison with other additive multistate characters does not affect polarization of the character/states or alter the phylogeny.
+Coding as non-additive in isolation or in unison with other additive multi-state characters does not affect polarization of the character/states or alter the phylogeny.
 Synapomorphy for \textit{Minyomerus} [JF2018] (state 1) and the \textit{M.
-{\ae}riballux} – \textit{M.
-reburrus} clade [JF2018] (state 2), respectively.
+aeriballux}--\textit{M.
+reburrus} clade [JF2015] (state 2), respectively.
 
@@
 ACCTRAN optimization preferred (see \citealt{agnarsson2008}), therefore inferred as a synapomorphy for \textit{Minyomerus} [JF2018] with a reversal (state 0) in the \textit{M.
-conicollis} - \textit{M.
-politus} clade [JF2018], then a convergent gain (state 1) in the \textit{M.
-cracens} – \textit{M.
-politus} clade [JF2018], with independent reversals (state 0) in the \textit{M.
-{\ae}riballux} – \textit{M.
-reburrus} clade [JF2018], \textit{M.
-trisetosus} [JF2015], \textit{M.
-gravivultus} [JF2015], and the \textit{M.
-bulbifrons} - \textit{M.
-politus} clade [JF2018] (ci = 14; ri = 40).
-
-		\item Legs, relative length of mesotarsi to mesotibi{\ae}: (0) tarsi much shorter than tibi{\ae}; (1) tarsi at least equal in length to tibi{\ae}; (2) tarsi slightly shorter than tibi{\ae}.
+aeriballux}--\textit{M.
+conicollis} clade [JF2015], then a convergent gain (state 1) in the \textit{M.
+aeriballux}--\textit{M.
+bulbifrons} clade [JF2018], with independent reversals (state 0) in the \textit{M.
+aeriballux}--\textit{M.
+reburrus} clade [JF2015], \textit{M.
+gravivultus} [JF2015], \textit{M.
+trisetosus} [JF2015], and the \textit{M.
+bulbifrons}--\textit{M.
+politus} clade [JF2015] (ci = 14; ri = 40).
+
+		\item Legs, relative length of mesotarsi to mesotibiae: (0) tarsi much shorter than tibiae; (1) tarsi at least equal in length to tibiae; (2) tarsi slightly shorter than tibiae.
 Coded as additive due to alignment of character states with preferred phylogeny.
-Coding as non-additive in isolation or in unison with other additive multistate characters does not affect polarization of the character/states or alter the phylogeny.
+Coding as non-additive in isolation or in unison with other additive multi-state characters does not affect polarization of the character/states or alter the phylogeny.
 State 1 is a synapomorphy for the tanymecine clade [non-focal], whereas state 2 is a synapomorphy for \textit{Minyomerus} [JF2018].
@@
 
-		\item Elytra, humeral angle rounded, not projected: (0) absent; (1) present. Synapomorphy for the \textit{I. buchanani} – \textit{M. politus} clade [non-focal].
-
-		\item Female terminalia, spermatheca with apical cylindrical bulb on corpus: (0) absent; (1) present. Synapomorphy for the \textit{M. puticulatus} – \textit{M. politus} clade [JF2018].
-
-		\item Female terminalia, corpus of spermatheca sinuate: (0) absent; (1) present. Synapomorphy for the \textit{M. imberbus} - \textit{M. sculptilis} clade [JF2018].
+		\item Elytra, humeral angle rounded, not projected: (0) absent; (1) present. Synapomorphy for the \textit{M. aeriballux}--\textit{I. buchanani} clade [non-focal].
+
+		\item Female terminalia, spermatheca with apical cylindrical bulb on corpus: (0) absent; (1) present. Synapomorphy for the \textit{M. bulbifrons}--\textit{M. puticulatus} clade [JF2015].
+
+		\item Female terminalia, corpus of spermatheca sinuate: (0) absent; (1) present. Synapomorphy for the \textit{M. imberbus}--\textit{M. sculptilis} clade [JF2018].
 
@@
 Synapomorphy for the \textit{M.
-gravivultus} – \textit{M.
-politus} clade [JF2018].
+gravivultus}--\textit{M.
+griseus} clade [JF2015].
 
@@
 Synapomorphy for the \textit{M.
-gravivultus} – \textit{M.
-rutellirostris} clade [JF2015].
+gravivultus}--\textit{M.
+griseus} clade [JF2015].
 
@@
 Synapomorphy for the \textit{M.
-imberbus} – \textit{M.
-politus} clade [JF2018].
+aeriballux}--\textit{M.
+imberbus} clade [JF2015].
 
@@
 Synapomorphy for the \textit{M.
-conicollis} – \textit{M.
-politus} clade [JF2018].
+aeriballux}--\textit{M.
+conicollis} clade [JF2015].
 
@@
 Synapomorphy for the \textit{M.
-ampullaceus} - \textit{M.
-reburrus} clade [JF2018].
+aeriballux}--\textit{M.
+ampullaceus} clade [JF2018].
 
@@
 Synapomorphy for the \textit{M.
-caseyi} – \textit{M.
-trisetosus} clade [JF2018].
+caseyi}--\textit{M.
+trisetosus} clade [JF2015].
 
@@
 franko} [JF2018] and the \textit{M.
-puticulatus} – \textit{M.
-politus} clade [JF2018] (state 1), with a single reversal in \textit{M.
+bulbifrons}--\textit{M.
+puticulatus} clade [JF2015] (state 1), with a single reversal in \textit{M.
 bulbifrons} [JF2015] (state 0).
@@
 Synapomorphy for the \textit{M.
-cracens} – \textit{M.
-politus} clade [JF2018], with a single reversal in the \textit{M.
-gravivultus} - \textit{M.
-politus} clade [JF2018] (ci = 50, ri = 83).
+aeriballux}--\textit{M.
+cracens} clade [JF2015], with a single reversal in the \textit{M.
+gravivultus}--\textit{M.
+griseus} clade [JF2015] (ci = 50, ri = 83).
 
@@
 Convergently present in \textit{M.
-microps} [JF2015], \textit{M.
-{\ae}riballux} [JF2015], and the \textit{M.
-franko} – \textit{M.
+aeriballux} [JF2015], \textit{M.
+microps} [JF2015], and the \textit{M.
+caseyi}--\textit{M.
 trisetosus} clade [JF2018] (ci = 33; ri = 50).
@@
 conicollis} [JF2015] and the \textit{M.
-puticulatus} – \textit{M.
-politus} clade [JF2018] (ci = 50; ri = 66).
-
-		\item Male terminalia, apical sclerite of {\ae}deagal flagellum elongate-spiriform: (0) absent; (1) present. Synapomorphy for the \textit{M. bulbifrons} – \textit{M. politus} clade [JF2018].
-
-		\item Male terminalia, style of spiculum gastrale with an anterior ventral flange: (0) absent; (1) present. Synapomorphy for the \textit{M. franko} – \textit{M. politus} clade [JF2018].
+bulbifrons}--\textit{M.
+puticulatus} clade [JF2015] (ci = 50; ri = 66).
+
+		\item Male terminalia, apical sclerite of aedeagal flagellum elongate-spiriform: (0) absent; (1) present. Synapomorphy for the \textit{M. bulbifrons}--\textit{M. politus} clade [JF2015].
+
+		\item Male terminalia, style of spiculum gastrale with an anterior ventral flange: (0) absent; (1) present. Synapomorphy for the \textit{M. bulbifrons}--\textit{M. caseyi} clade [JF2018].
 
@@
 ACCTRAN optimization preferred (see \citealt{agnarsson2008}), therefore inferred as convergent gains in the \textit{M.
-imberbus} - \textit{M.
+imberbus}--\textit{M.
 sculptilis} clade [JF2018] and the \textit{M.
-puticulatus} – \textit{M.
-politus} clade [JF2018], with a reversal in \textit{M.
+bulbifrons}--\textit{M.
+puticulatus} clade [JF2015], with a reversal in \textit{M.
 bulbifrons} [JF2015] (ci = 33; ri = 0).
@@
 cracens} [JF2015] and the \textit{M.
-caseyi} – \textit{M.
-trisetosus} clade [JF2018] (ci = 50, ri = 0).
+caseyi}--textit{M.
+trisetosus} clade [JF2015] (ci = 50, ri = 0).
 
@@
 ACCTRAN optimization preferred (see \citealt{agnarsson2008}), therefore convergently present in the \textit{M.
-constrictus} – \textit{M.
-laticeps} clade [JF2018] and the \textit{M.
-gravivultus} – \textit{M.
-politus} clade [JF2018] with a reversal in \textit{M.
+constrictus}--\textit{M.
+laticeps} clade [JF2015] and the \textit{M.
+bulbifrons}--\textit{M.
+gravivultus} clade [JF2015] with a reversal in \textit{M.
 gravivultus} [JF2015] (ci = 33; ri = 66).
 
-		\item Male terminalia, tergum VII approximately 4\x as long as broad: (0) absent; (1) present. Synapomorphy for the \textit{M. griseus} – \textit{M. rutellirostris} clade [JF2018].
-
-		\item Male terminalia, {\ae}deagal pedon expanded laterally around ostium: (0) absent; (1) present.
+		\item Male terminalia, tergum VII approximately 4\x as long as broad: (0) absent; (1) present. Synapomorphy for the \textit{M. griseus}--\textit{M. rutellirostris} clade [JF2015].
+
+		\item Male terminalia, aedeagal pedon expanded laterally around ostium: (0) absent; (1) present.
 ACCTRAN optimization preferred (see \citealt{agnarsson2008}), therefore convergently present in the \textit{M.
-constrictus} – \textit{M.
-laticeps} clade [JF2018], \textit{M.
-cracens}, and the \textit{M.
-caseyi} –\textit{ M.
-trisetosus} clade [JF2018] (ci = 33; ri = 33).
-
-		\item Male terminalia, {\ae}deagal pedon broad basally, evenly tapering toward apex: (0) absent; (1) present. Synapomorphy for the \textit{M. bulbifrons} – \textit{M. politus} clade [JF2018].
-
-		\item Male terminalia, {\ae}deagal pedon medially sclerotized along dorsum: (0) absent; (1) present.
+constrictus}--\textit{M.
+laticeps} clade [JF2015], \textit{M.
+cracens} [JF2015], and the \textit{M.
+caseyi}--\textit{ M.
+trisetosus} clade [JF2015] (ci = 33; ri = 33).
+
+		\item Male terminalia, aedeagal pedon broad basally, evenly tapering toward apex: (0) absent; (1) present. Synapomorphy for the \textit{M. bulbifrons}--\textit{M. politus} clade [JF2015].
+
+		\item Male terminalia, aedeagal pedon medially sclerotized along dorsum: (0) absent; (1) present.
 ACCTRAN optimization preferred (see \citealt{agnarsson2008}), therefore convergently present in the \textit{M.
-imberbus} - \textit{M.
-sculptilis} clade [JF2018], \textit{M.
-cracens}, [JF2015] and the \textit{M.
-gravivultus} – \textit{M.
-politus} clade [JF2018], with a reversal in \textit{M.
+imberbus}--\textit{M.
+sculptilis} clade [JF2015], \textit{M.
+cracens} [JF2015], and the \textit{M.
+bulbifrons}--\textit{M.
+gravivultus} clade [JF2015], with a reversal in \textit{M.
 bulbifrons} [JF2015] (ci = 25; ri = 50).
 
-		\item Male terminalia, width of connection between apodemes of {\ae}deagal tegmen: (0) wider than base of apodeme; (1) narrower than base of apodeme.
-Synapomorphy for the \textit{M.
-ampullaceus} – \textit{M.
-politus} clade [JF2018] , with a single reversal in the \textit{M.
-griseus} – \textit{M.
-rutellirostris clade} [JF2018] (ci = 50; ri = 83).
+		\item Male terminalia, width of connection between apodemes of aedeagal tegmen: (0) wider than base of apodeme; (1) narrower than base of apodeme.
+Synapomorphy for the \textit{M.
+aeriballux}--\textit{M.
+bulbifrons} clade [JF2018] , with a single reversal in the \textit{M.
+griseus}--\textit{M.
+rutellirostris clade} [JF201] (ci = 50; ri = 83).
 	\end{enumerate}
 
+\section*{RCC--5 Alignments}\label{sec:alignments}
+	Details of our RCC--5 alignment approached are given in free text form in the \textbf{Supplemental Information SI1}, which also describes the content of the data input and output files.
+	The latter, in turn, are appended in .txt, .csv, and .pdf format in the \textbf{Supplemental Information SI2 to S4}.
+	All shown alignments are \emph{intensional} in the sense of \citet{fp2009}, and thus maximize high-level concept congruence where indicated, and in spite of non-congruent lower-level concept sampling.
+
+	The first, classification-based alignment (Fig.~\ref{fig:align1}) is simple and straightforward to interpret (see also \textbf{Supplemental Information SI2}). 
+	We obtain high-level congruence among the concepts \textit{Minyomerus} [JF2018] and \textit{Minyomerus} [JF2015], where 17 species-level concepts are retained from \citet{jansen2015} and four species-level concepts are added in the current revision.
+	The coverage constraint is relaxed for \textit{Minyomerus} [JF2015], thus allowing the four new species-level concepts to be subsumed under this parent.
+	This is based on our assertion that they fall under the generic character circumscription of \citet{jansen2015}.
+
+	The following two Figs.~\ref{fig:align2}-\ref{fig:align3} show fully bifurcated, multi-phylogeny alignments of the same reasoner toolkit input, but resolved as whole concepts versus split concepts, respectively.
+	In Fig.~\ref{fig:align2} (\textbf{Supplemental Information SI3}), we observe that the phylogenetic placements of \emph{two} of the four new species-level concepts cause significant non-congruence in the alignment, resulting in seven overlapping RCC--5 articulations.
+	\textit{Minyomerus franko} [JF2018] is subsumed under the \textit{M.
+caseyi}--\textit{M.
+franko} clade [JF2018], which is intensionally congruent with the \textit{M.
+caseyi}--\textit{M.
+trisetosus} clade [JF2015].
+	In other words, this placement is not the source of non-congruence in the alignment.
+	Similarly, the placement of \textit{M. tylotos} [JF2018] into the new \textit{M. microps}--\textit{M. tylotos} clade [JF2018] is not conflicting in an intensional sense.
+	At the next, more inclusive level, this addition "resolves" into the congruent \textit{M. aeriballux}--\textit{M. microps} clade [JF2018]/[JF2015].
+
+	In contrast, the placement of \textit{M.
+ampullaceus} [JF2018] "inside" of \textit{M.
+cracens} [JF2015] in the current phylogeny, generates five overlapping articulations among as many (five) non-congruent concept regions positioned 1-2 levels above these species-level concepts.
+	The conflict is resolved in the next, more inclusive and congruent region of the \textit{M.
+aeriballux}--\textit{M.
+cracens} clade [JF2018] $==$ \textit{M.
+aeriballux}--\textit{M.
+bulbifrons} clade [JF2015]
+
+	The placements of the previously circumscribed \textit{M.
+imberbus} [JF2015] and the new species-level concept \textit{M.
+sculptilis} [JF2018] - in relation to the congruent clade \textit{M.
+constrictus}--\textit{M.
+laticeps} [JF2018]/[JF2015] - cause two additional instances of overlap (Fig.~\ref{fig:align2}).
+	In the current phylogeny, \textit{M. imberbus} [JF2015] is sister to \textit{M. sculptilis} [JF2018], and placed "inside" of the \textit{M. constrictus}--\textit{M. laticeps} clade [JF2018]/[JF2015].
+	However, in the preceding phylogeny sec. Jansen \& Franz (2015), \textit{M. imberbus} [JF2015] is non-congruently included in the \textit{M. constrictus}--\textit{M. imberbus} clade [JF2015].
+	This conflict is only resolved at the level of \textit{Minyomerus} [JF2018]/[JF2015].
+
+	Figure ~\ref{fig:align3} (\textbf{Supplemental Information SI4}) shows that the inclusion of the four new species-level concepts in the \textit{Minyomerus} [JF2018] phylogeny generates five split-concept regions for which there are no adequate labels in either input phylogeny.
+	These labels correspond to the overlapping articulations mentioned above; in particular the non-congruent assignments of \textit{M.
+ampullaceus} [JF2018], \textit{M.
+cracens} [JF2018], and \textit{M.
+sculptilis} [JF2018].
+	The phylogenetic character evidence for these placements and relationships are discussed in the following sections.
+
 \section*{Discussion}\label{sec:disc}
-	\subsection*{Parallels with prior work}\label{ssec:same}
-		The most-parsimonious cladogram of this work (Fig.~\ref{fig:tree}) exhibits important differences compared to that of \citet{jansen2015} with respect relationships between species groups, in large part due to the unique character combinations present in the newly-added taxa \citep{rieppel2007, franz2014}.
-		Nonetheless, we resolve three key clades with strong support, also inferred by and in corroboration with \citet{jansen2015}, as follows:
+	\subsection*{Relationships to the previous revision}\label{ssec:same}
+		The differences of the current phylogeny (Figs.~\ref{fig:tree1}-\ref{fig:tree2}) in relation to that of \citet{jansen2015} are in large part due to the unique character combinations present in the newly added species \citep{rieppel2007, franz2014}.
+		Nonetheless, three main clades are resolved with strong support, and further corroborate the topology of \citet{jansen2015}, as follows:
 		\begin{enumerate}
-			\item The genus \textit{Minyomerus} [JF2018] is well-supported by the same eight synapomorphies identified by \citet{jansen2015}, as specified in the Introduction of this manuscript (Bremer support value [henceforth: bsv] = 10, relative fit difference [henceforth: rfd] = 95; Bootstrap [henceforth: boot] = 100).
-			\item The species \textit{M.
-griseus} [JF2015], formerly of the monotypic genus \textit{Piscatopus} sec.
-Sleeper (1960), forms a well-supported clade with \textit{M.
+			\item \textit{Minyomerus} [JF2018] is strongly supported by the same eight synapomorphies identified in \citet{jansen2015}.
+These are reiterated in the Introduction (Bremer support value [henceforth: bsv] = 10, relative fit difference [henceforth: rfd] = 95; Bootstrap [henceforth: boot] = 100).
+			\item \textit{Minyomerus griseus} [JF2015] forms a well-supported clade with \textit{M.
 rutellirostris} [JF2015] (bsv = 4, rfd = 77, boot = 96).
 These taxa jointly share the same two synapomorphies (chars.
-23:1 and 48:1) provided in \citet{jansen2015}: (1) the intercoxal process is divided at the midpoint between the cox{\ae}, but has both the anterior and posterior processes extending completely between the procox{\ae} and contiguous with each other; and (2) the male tergum VII is nearly 4\x as long as broad, respectively.
+23:1 and 48:1) provided in \citet{jansen2015}: (1) the intercoxal process is divided at the midpoint between the coxae, but has both the anterior and posterior processes extending completely between the procoxae and contiguous with each other; and (2) the male tergum VII is nearly 4\x as long as broad, respectively.
 In addition, the \textit{M.
-gravivultus} - \textit{M.
-griseus} [JF2015] clade (bsv = 3, rfd = 60), as resolved in the current cladogram, is perfectly congruent with that of \citet{jansen2015}.
-This clade is nested within \textit{Minyomerus} [JF2018], in support of the classificatory emendations made by \citet{jansen2015}, whereby the genus \textit{Piscatopus} sec.
-Sleeper (1960) was invalidated as a junior synonym of \textit{Minyomerus} [JF2015].
-			\item The genus \textit{Minyomerus} [JF2018] is nested within a well-supported clade of Tanymecini [non-focal] (boot = 100).
-However we note, in agreement with \citet{jansen2015}, that significant further work is needed to assess the phylogenetic relationships between all genera presently assigned to the Tanymecini [non-focal] \citep{alonso1999}.
+gravivultus}--\textit{M.
+griseus} [JF2015] clade (bsv = 3, rfd = 60), as resolved in the current cladogram, is congruent with that of \citet{jansen2015}.
+			\item \textit{Minyomerus} [JF2018] is nested within a well-supported clade of Tanymecini [non-focal] (boot = 100).
+However, further work is needed to assess the phylogenetic relationships between all genera presently assigned to the Tanymecini [non-focal] \citep{alonso1999}.
 		\end{enumerate}
@@
 	\subsection*{Intrageneric relationships}\label{ssec:diff}
-		While some species groups inferred by \citet{jansen2015} remain intact, but with different character alignment, internal topology, or their placement within the genus, others are entirely different; we identify these major topological and compositional phylogenetic differences here.
-
-		Within \textit{Minyomerus} [JF2018], and beginning at the basal-most node and proceeding nodewise apically, the first major incongruence with \textit{Minyomerus} [JF2015] is the placement of \textit{M.
+		Within \textit{Minyomerus} [JF2018], beginning at the earliest-bifurcating node and proceeding towards the leaves, the first major incongruence with \textit{Minyomerus} [JF2015] is the placement of \textit{M.
 imberbus} [JF2015].
-		This species was sister to the \textit{M.
-constrictus} - \textit{M.
-laticeps} [JF2015] clade (corresponding to ``\textit{Elissa}'' sec.
-Casey (1888), but see \citealt{jansen2015}), forming a clade sister to the \textit{M.
-conicollis} - \textit{M.
-rutellirostriss} clade [JF2015].
-		By contrast, the present analysis places \textit{M.
-imberbus} [JF2015] in a clade with \textit{M.
-sculptilis} [JF2015] (see below: \textbf{\nameref{ssec:place}}), sister to \textit{M.
-conicollis} - \textit{M.
-politus} [JF2018] clade.
-		The inferred \textit{M.
-imberbus} - \textit{M.
-politus} [JF2018] clade (bsf = 2, rfd = 50) is supported by three synapomorphies: (1) presence of a transverse constriction across the posterior of the frons (char 16: 1); (2) presence of a reduced tuft of post-ocular vibriss{\ae} (char.
+		This species was sister to the \textit{M. constrictus}--\textit{M. laticeps} [JF2015] clade, which in turn was sister to the \textit{M. aeruballux}--\textit{M. conicollis} clade [JF2015].
+		The present analysis places \textit{M. imberbus} [JF2015] in a clade with \textit{M. sculptilis} [JF2018] (see \textbf{\nameref{ssec:place}}).
+		The \textit{M.
+aeriballux}--\textit{M.
+imberbus} clade [JF2018] (bsf = 2, rfd = 50) is supported by three synapomorphies: (1) presence of a transverse constriction across the posterior of the frons (char.
+16: 1); (2) presence of a reduced tuft of post-ocular vibrissae (char.
 21: 1); and (3) a mesally obscure lamina of the spiculum ventrale in the female (char.
@@
 
-		The MPT of the current analysis is thereafter topologically identical to that of \citet{jansen2015} until the \textit{M.
-cracens} - \textit{M.
-politus} [JF2018] clade, and the \textit{M.
-ampullaceus} - \textit{M.
-politus} clade, which correspond compositionally and topologically to the \textit{M.
-{\ae}riballux} - \textit{M.
-rutellirostris} [JF2015] clade, respectively.
-		In \textit{Minyomerus} [JF2015], \textit{M.
-cracens} was placed sister to the \textit{M.
-caseyi} - \textit{M.
-trisetosus} [JF2015] clade, forming a clade sister to the \textit{M.
-{\ae}riballus} - \textit{M.
-reburrus} [clade]; this larger \textit{M.
-{\ae}riballux} - \textit{M.
-trisetosus} [JF2015] clade was then sister to the \textit{M.
-puticulatus} - \textit{M.
-rutellirostris} [2015] clade.
-		We instead resolve \textit{M.
+		We resolve \textit{M.
 cracens} [JF2015] as sister to the \textit{M.
-ampullaceus} - \textit{M.
-politus} [JF2018] clade, inclusively supported by three synapomorphies: (1) presence of a strongly punctate sulcus posteriad of the nasal plate (char.
-14: 2); (2) presence of broad scales on the terminal funicular segment of the antenn{\ae}(char.
+aeriballux}--\textit{M.
+bulbifrons} [JF2018] clade, inclusively supported by three synapomorphies: (1) presence of a strongly punctate sulcus posteriad of the nasal plate (char.
+14: 2); (2) presence of broad scales on the terminal funicular segment of the antennae(char.
 19: 1); and (3) absence of a medial, anteriorly-directed, sclerotized process on the coxites of the ovipositor (char.
@@
 
-		Moreover, the \textit{M.
-ampullaceus} - \textit{M.
-politus} [JF2018] clade approximately corresponds to the topological position of the \textit{M.
-{\ae}riballux} - \textit{M.
-rutellirostris} [JF2015] clade and exhibits comparatively different internal relationships between species groups, while maintaining similar composition and topology within these groups.
-		Specifically, the relative positions of the \textit{M.
-{\ae}riballux} - \textit{M.
-reburrus} [JF2015] clade and the \textit{M.
-caseyi} - \textit{M.
-trisetosus} [JF2015] have changed from being sister clades (excepting the placement of \textit{M.
-cracens} [JF2015]), such that the \textit{M.
-ampullaceus} - \textit{M.
-reburrus} [JF2018] clade is correspondingly inferred as sister to the clade comprised of the \textit{M.
-franko} - \textit{M.
-trisetosus} [JF2018] clade and the \textit{M.
-gravivultus} - \textit{M.
-politus} [JF2018] clade, the latter of which has not changed in composition or internal topology.
-
 		The \textit{M.
-ampullaceus} - \textit{M.
-politus} [JF2018] clade is supported by a single synapomorphy: the width of the connection between the apodemes of the {\ae}deagal tegmen is narrower than the base of the apodeme (char.
+aeriballux}--\textit{M.
+bulbifrons} [JF2018] clade is weakly supported by a single synapomorphy: the width of the connection between the apodemes of the aedeagal tegmen is narrower than the base of the apodeme (char.
 52: 1).
 		Within this clade, the position of the \textit{M.
-franko} - \textit{M.
-politus} [JF2018] clade as separate from and sister to the \textit{M.
-ampullaceus} - \textit{M.
-reburrus} [JF2018] clade, is supported by a single synapomorphy and a single homoplasious character, namely: (1) presence of an anterior ventral flange on the style of the spiculum gastrale (char.
-44: 1, synapomorphy), and (2) differentiation of the set{\ae} on the lateral portion of the elytra and on the venter from the set{\ae} on the elytral disc (char.
-3: 1, homoplasy).
-
-	\subsection*{Phylogenetic placement of newly described species}\label{ssec:place}
-		The clades within \textit{Minyomerus} [JF2018] not addressed in the preceding section are identical in topology and composition to those of \textit{Minyomerus} [JF2015], except for the addition of newly described species.
-		Here we describe explicitly the phylogenetic placement of these species, and the characters supporting these newly-inferred relationships.
-		We additionally discuss, where possible, similarities in biogeographic extent of each species with putative sister taxa, based on the results of species distribution modeling (see Figs.~\ref{fig:map_summary}-\ref{fig:map_sculptilis}).
+bulbifrons}--\textit{M.
+caseyi} clade [JF2018] clade as separate from, and sister to, the \textit{M.
+aeriballux}--\textit{M.
+ampullaceus} clade [JF2018], is supported by one synapomorphy and one homoplasious character, namely: (1) presence of an anterior ventral flange on the style of the spiculum gastrale (char.
+44: 1 -- synapomorphic), and (2) differentiation of the setae on the lateral portion of the elytra and on the venter from the setae on the elytral disc (char.
+3: 1 -- homoplasious).
+
+	\subsection*{Placement of newly described species}\label{ssec:place}
+		Clades within \textit{Minyomerus} [JF2018] not addressed in the preceding section are identical in topology and composition to those of \textit{Minyomerus} [JF2015], except for the addition of newly described species.
+		Here we assess the phylogenetic placements of these species.
+		We also discuss similarities in the biogeographic range of each species, in relation to the putative sister taxa, based on the results of species distribution modeling (see Figs.~\ref{fig:map_summary}-\ref{fig:map_sculptilis}).
 
 		\subsubsection*{Minyomerus sculptilis \textnormal{\bfseries[JF2018]}}
-			\textit{M. sculptilis} [JF2018] is inferred as sister to \textit{M. imberbus} [JF2015].
-			The resulting \textit{M.
-imberbus} - \textit{M.
-sculptilis} [JF2018] clade (bsv = 3, rfd = 72) is supported by a single synapomorphy and two homoplasious characters: (1) corpus of spermatheca sinuate (char.
-32: 1, synapomorphy); (2) lamina of spiculum gastrale in male longer than broad and anteriorly extended along style (char.
-45: 1, homoplasy); and (3) {\ae}deagal pedon medially sclerotized along dorsum (char.
-51: 1, homoplasy).
+			\textit{Myniomerus sculptilis} [JF2018] is inferred as sister to \textit{M. imberbus} [JF2015].
+			The \textit{M.
+imberbus}--\textit{M.
+sculptilis} clade [JF2018] (bsv = 3, rfd = 72) is supported by a single synapomorphy and two homoplasious characters: (1) corpus of spermatheca sinuate (char.
+32: 1 -- synapomorphic); (2) lamina of spiculum gastrale in male longer than broad and anteriorly extended along style (char.
+45: 1 -- homoplasious); and (3) aedeagal pedon medially sclerotized along dorsum (char.
+51: 1 -- homoplasious).
 			In addition to these characters, \textit{M.
-sculptilis} [JF2018] and \textit{M.
-imberbus} generally share very similar exterior morphology, which can make separating these two species difficult, especially in old, damaged, or worn specimens.
-
-			While \textit{M.
-sculptilis} [JF2018] is associated with big sagebrush (\textit{Artemisia tridentata} Nutt.
-[non-focal]; Asterace{\ae} [non-focal]), tumbleweed (\textit{Salsola tragus} L.
-[non-focal]; Amaranthace{\ae} [non-focal]), tall tumblemustard (\textit{Sisymbrium altissimum} L.
-[non-focal]; Brassicace{\ae} [non-focal]), its sister taxon \textit{M.
-imberbus} [JF2015] is associated with budsage (\textit{Artemisia spinescens} D.C.Eaton [non-focal]; Asteraceae [non-focal]).
-			It is possible that the divergence of these two species may have been driven, in part, by the difference in host-plant preference between related species of \textit{Artemesia}, but given the generalist feeding habits of congenerics, and the limited data available on these species, we do not consider it very likely.
-			Conversely, their divergence may have resulted from a vicariance event, based on their present-day biogeographic distributions, which are separated by the eastern extension of the Columbia Plateau; \textit{M.
-sculptilis} [JF2018] appears to be endemic to the Snake River Plain to the north, while \textit{M.
-imberbus} [JF2015] has been found in the Great Basin Desert to the south.
+imberbus} [JF2015] and \textit{M.
+sculptilis} [JF2018] share a general external gestalt, which makes separating these two species difficult, especially in damaged or worn specimens.
+
+			Whereas \textit{M.
+sculptilis} [JF2018] is associated with big sagebrush (\textit{Artemisia tridentata} [non-focal], tumbleweed (\textit{Salsola tragus} [non-focal], and tall tumblemustard (\textit{Sisymbrium altissimum} [non-focal]; its sister taxon \textit{M.
+imberbus} [JF2015] is associated with budsage (\textit{Artemisia spinescens} [non-focal].
+			The divergence of these two species may have been driven in part by differences in host-plant use.
+			However, this is less likely considering the generalist feeding habits of \textit{Minyomerus} [JF2018] congenerics.
+			Conversely, their divergence may have resulted from a vicariance event, based on their present-day biogeographic distributions, which are separated by the eastern extension of the Columbia Plateau.
+			\textit{Minyomerus sculptilis} [JF2018] appears to be endemic to the Snake River Plain to the north, whereas \textit{M. imberbus} [JF2015] has been found in the Great Basin Desert to the south.
 
 		\subsubsection*{Minyomerus tylotos \textnormal{\bfseries[JF2018]}}	
-			\textit{M. tylotos} [JF2018] is inferred as the sister to \textit{M. microps} [JF2015], the type species of \textit{Minyomerus} [JF2015].
-			The resulting \textit{M.
-tylotos} - \textit{M.
-microps} [JF2018] clade (bsv = 3, rfd = 73) is supported by a single synapomorphy and a single homoplasious character: (1) elytra and pronotum generally large, protuberant, and sculpted in appearance along dorsal and lateral faces (char.
-5: 1, synapomorphy); and (2) sulcus posteriad of nasal plate broad and weakly punctate (char.
-13: 1, homoplasy).
-			In addition to these characters, \textit{M. tylotos} [JF2018] and \textit{M. microps} share a similar gestalt and uniform setation.
-
-			\textit{M.
-tylotos} [JF2018] appears to be endemic to northern Chihuahuan Desert, while \textit{M.
+			\textit{Minyomerus tylotos} [JF2018] is sister to \textit{M. microps} [JF2015].
+			The \textit{M.
+microps}--\textit{M.
+tylotos} clade [JF2018] (bsv = 3, rfd = 73) is supported by a single synapomorphy and a single homoplasious character: (1) elytra and pronotum generally large, protuberant, and sculpted in appearance along dorsal and lateral faces (char.
+5: 1 -- synapomorphic); and (2) sulcus posteriad of nasal plate broad and weakly punctate (char.
+13: 1 -- homoplasius).
+			In addition to these characters, the two species share a similar gestalt and uniform setation.
+
+			\textit{Minyomerus tylotos} [JF2018] appears to be endemic to northern Chihuahuan Desert, whereas \textit{M.
 microps} [JF2015] is widely distributed to the north throughout the Great Plains and along the Missouri River.
-			We consider it likely that \textit{M.
-microps} [JF2015] represents a northern radiation of the common ancestor of this clade, while \textit{M.
-tylotos} [JF2018] represents the ancestral distribution to the south, based on the hypothesized origin of \textit{Minyomerus} [JF2015] in the Chihuahuan Desert posited by \citet{jansen2015} (see also \citealt{wilson2010}).
+			We consider it likely that \textit{M. microps} [JF2015] represents a northern radiation of the common ancestor of this clade.
+			Conversely, \textit{M.
+tylotos} [JF2018] may represent the ancestral distribution to the south, based on the hypothesized origin of \textit{Minyomerus} [JF2018] in the Chihuahuan Desert; see \citet{jansen2015} and \citealt{wilson2010}.
 
 		\subsubsection*{Minyomerus ampullaceus \textnormal{\bfseries[JF2018]}}
-			\textit{M. ampullaceus} [JF2018] is inferred as sister to the \textit{M. {\ae}riballux} - \textit{M. reburrus} [JF2015] clade.
-			The resulting \textit{M.
-ampullaceus} - \textit{M.
-reburrus} [JF2018] clade (bsv = 1, rfd = 50) is supported by a single synapomorphy: lamina of spiculum ventrale with laminar arms basally bifurcating and sub-parallel mesally thereafter (char.
+			\textit{Minyomerus ampullaceus} [JF2018] is sister to the \textit{M. aeriballux}--\textit{M. reburrus} clade [JF2015].
+			The \textit{M.
+aeriballux}--\textit{M.
+ampullaceus} clade [JF2018] (bsv = 1, rfd = 50) is supported by a single synapomorphy: lamina of spiculum ventrale with laminar arms basally bifurcating and sub-parallel mesally thereafter (char.
 37: 1).
-			The placement of this species is tentatively based on the characteristics of a single, worn specimen, and may be subject to change if more data become available regarding the disposition of the habitus and mouthparts.
-
-			Nonetheless, the biogeographic distributions of the species in the \textit{M.
-ampullaceus} - \textit{M.
-reburrus} [JF2018] clade exhibit overlap; \textit{M.
-ampullaceus} [JF2018] is documented from Carlsbad, NM, in the western parts of the distributions of \textit{M.
-{\ae}riballux} [JF2015] and \textit{M.
-reburrus} [JF2015].
-			The divergence of the latter two species is thought to be a result of their habitat and host plant preference, given their overlapping ranges, as \textit{M.
-{\ae}riballux} [JF2015] is found in very sandy soils and on dune systems, while \textit{M.
-reburrus} [JF2015] prefers arid grasslands.
-			Without additional distribution or host plant data for \textit{M.
-ampullaceus} [JF2018], it is impossible to speculate whether the only documented locality for this species represents the center or edge of its range.
+			The placement of this species is tentative and based on the characteristics of a single, worn specimen.
+
+			Nonetheless, the biogeographic distributions of the species in the \textit{M. aeriballux}--\textit{M. ampullaceus} clade [JF2018] exhibit overlap.
+			\textit{Minyomerus ampullaceus} [JF2018] is documented from Carlsbad, New Mexico, in the western parts of the distributions of \textit{M. aeriballux} [JF2015] and \textit{M. reburrus} [JF2015]. 
+			The divergence of the latter two species is thought to be a result of their habitat and host plant preference, given their overlapping ranges.
+			\textit{Minyomerus aeriballux} [JF2015] is found in very sandy soils and on dune systems, whereas \textit{M. reburrus} [JF2015] prefers arid grasslands.
+			Without additional distributional or host plant data for \textit{M.
+ampullaceus} [JF2018], we cannot assess whether the single documented locality for this species represents the center or edge of its range.
 			However, this locality does overlap with the known range of its sister clade, suggesting that the divergence of \textit{M.
 ampullaceus} [JF2018] from the \textit{M.
-ampullaceus} - \textit{M.
-reburrus} [JF2018] clade was not a vicariance event.
+aeriballux}--\textit{M.
+ampullaceus} clade [JF2018] was not a vicariance event.
 
 		\subsubsection*{Minyomerus franko \textnormal{\bfseries[JF2018]}}
-			\textit{M. franko} [JF2018] is inferred as sister to the \textit{M. caseyi} - \textit{M. trisetosus} [JF2018] clade.
-			The resulting \textit{M.
-franko} - \textit{M.
-trisetosus} [JF2018] clade (bsv = 4, rfd = 63) is supported by a single synapomorphy and two homoplasious characters: (1) rows of set{\ae} on elytral intervals comprised of larger white set{\ae} randomly interspersed among smaller brown set{\ae}(char.
-4: 1, synapomorphy); (2) prementum lacking strong ligula and straight margins, not appearing pentagonal (char.
-7: 0, homoplasy); and (3) anterior margin of female tergum VII entirely free of sclerotized band (char.
-41: 1, homoplasy).
-			In addition to these characters, members of the \textit{M.
-franko} - \textit{M.
-trisetosus} [2018] clade share a generally similar gestalt, especially as pertains to the overall shape of the head and rostrum, and the articulation between the pronotum and elytra in dorsal and lateral view.
-			Furthermore, the interspersed white elytral set{\ae} of these three species all exhibit varying degrees of apical expansion, and can appear moderately to greatly explanate or spatulate in at least some, but not all, specimens of these species.
-
-			While \textit{M.
-franko} [JF2018] has been documented on spear globemallow (\textit{Sph{\ae}ralcea hastulata} A.
-Gray [non-focal]; Malvace{\ae} [non-focal]), \textit{M.
-trisetosus} [JF2015] is associated with broomweed (\textit{Xanthocephalum} [non-focal]; Asteraceae [non-focal]), creosote bush (\textit{Larrea tridentata} (DC.) Coville [non-focal]; Zygophyllaceae [non-focal]), and snakeweed (\textit{Gutierrezia} [non-focal]; Asteraceae [non-focal]); \textit{M.
-caseyi} has no known plant associations.
-			It is possible that the divergence of \textit{M.
-franko} [2018] may have resulted from a difference in host-plant preference, but, as stated previously, this is unlikely given the generalist feeding habits of congenerics, and the limited data available on this species.
-
-			Alternatively, the speciation sequence in the \textit{M. franko} - \textit{M. trisetosus} [JF2018] clade may correspond to vicariance events.
-			\textit{M.
-trisetosus} [JF2015] inhabits a broad swath of the northern Chihuahuan Desert, while \textit{M.
-franko} [2018] and \textit{M.
-caseyi} [2015] are exclusively encountered in the southern Chihuahuan Desert.
-			MaxEnt predicts overlapping species distributions for the latter species; however, the documented localities of these two species pertain to distinct biogeographic regions.
-			Specifically, \textit{M.
-franko} [JF2018] has only been collected in the valleys of the Sierra Madre Oriental range, while \textit{M.
-caseyi} is found along the western edge of this range, in the eastern portion of the Central Mexican Plateau.
-			Additional field data are needed to clarify the spatial extents of these species' distributions to draw more robust inferences regarding their endemicity within these regions.
+			\textit{Minyomerus franko} [JF2018] is sister to the \textit{M. caseyi}--\textit{M. trisetosus} clade [JF2015].
+			The \textit{M.
+caseyi}--\textit{M.
+franko} clade [JF2018] (bsv = 4, rfd = 63) is supported by a single synapomorphy and two homoplasious characters: (1) rows of setae on elytral intervals comprised of larger white setae randomly interspersed among smaller brown setae(char.
+4: 1 -- synapomorphic); (2) prementum lacking strong ligula and straight margins, not appearing pentagonal (char.
+7: 0 -- homoplasious); and (3) anterior margin of female tergum VII entirely free of sclerotized band (char.
+41: 1 -- homoplasious).
+			In addition to these characters, members of this clade share a generally similar gestalt, especially regarding the head and rostrum, and the articulation between the pronotum and elytra in dorsal and lateral view.
+			The interspersed, white elytral setae of these three species exhibit varying degrees of apical expansion, and can appear moderately to greatly explanate or spatulate in at least some, but not all, specimens.
+
+			\textit{Minyomerus franko} [JF2018] has been documented on spear globemallow \textit{Sphaeralcea hastulata} [non-focal].
+\textit{Minyomerus trisetosus} [JF2015] is associated with broomweed \textit{Xanthocephalum} [non-focal], creosote bush \textit{Larrea tridentata} [non-focal] and snakeweed \textit{Gutierrezia} [non-focal].
+\textit{Minyomerus caseyi} has no known plant associations.
+			It is therefore possible that the divergence of \textit{M. franko} [2018] was facilitated by differences in host-plant preference.
+			However, this remains unlikely given the generalist feeding habits of congenerics.
+
+			Alternatively, the speciation sequence in the \textit{M. caseyi}--\textit{M. franko} clade [JF2018] may correspond to vicariance events.
+			\textit{Minyomerus trisetosus} [JF2015] inhabits a broad swath of the northern Chihuahuan Desert, whereas \textit{M.
+franko} [JF2018] and \textit{M.
+caseyi} [JF2015] are exclusively encountered in the southern Chihuahuan Desert.
+			MaxEnt predicts overlapping species distributions for the latter two species.
+			However, the \emph{documented} localities of these two species pertain to distinct biogeographic regions.
+			\textit{Minyomerus franko} [JF2018] has only been collected in the valleys of the Sierra Madre Oriental range, whereas \textit{M.
+caseyi} [JF2015] is found along the western edge of this range, in the eastern portion of the Central Mexican Plateau.
+			Additional occurrence records are needed to clarify the spatial extents of these species' distributions, and thus draw more robust inferences regarding their endemicity.
 
 \section*{Acknowledgments}
-	The authors are grateful to Robert Anderson (CMNC), Ed Riley and John Oswald (TAMU), and Lourdes Chamorro (USNM) for their assistance and provision of specimens of \textit{Minyomerus} [JF2018] used in this manuscript.
+	The authors are grateful to Robert Anderson (CMNC), Ed Riley and John Oswald (TAMU), and Lourdes Chamorro (USNM) for their assistance and provision of specimens used in this revision.
 	The authors also thank Salvatore Anzaldo, Andrew Johnston, Sangmi Lee and other ASUHIC members for their assistance in procuring, treating, and maintaining specimen loans upon entry into the ASUHIC.
 	This research was funded in part by the National Science Foundation (DEB-1155984) and the United States Department of Agriculture – Agricultural Research Service (Agreement 58-1275-1-335).
+
+\section*{Supplemental information}
+		\begin{description}[itemsep=-1ex]
+			\item[\texttt{SI1}] Explanation of the RCC--5 alignment approach. File format: .pdf
+			\item[\texttt{SI2A}] Input constraints for the \textit{Minyomerus} [JF2018]/[JF2015] rank-only classification alignment. File format: .txt
+			\item[\texttt{SI2B}] Input visualization for the SI2A input. File format: .pdf
+			\item[\texttt{SI2C}] Set of 114 \textit{Maximally Informative Relations} (MIR) for the SI2A input. File format: .csv
+			\item[\texttt{SI2D}] Alignment visualization for the SI2A input. File format: .pdf
+			\item[\texttt{SI3A}] Input constraints for the \textit{Minyomerus} [JF2018]/[JF2015] phylogeny alignment -- whole-concept resolution with overlap. File format: .txt
+			\item[\texttt{SI3B}] Input visualization for the SI3A input. File format: .pdf
+			\item[\texttt{SI3C}] Set of 925 \textit{Maximally Informative Relations} (MIR) for the SI3A input. File format: .csv
+			\item[\texttt{SI3D}] Alignment visualization for the SI3A input. File format: .pdf
+			\item[\texttt{SI4A}] Input constraints for the \textit{Minyomerus} [JF2018]/[JF2015] phylogeny alignment -- split-concept resolution. File format: .txt
+			\item[\texttt{SI4B}] Input visualization for the SI4A input. File format: .pdf
+			\item[\texttt{SI4C}] Set of 925 \textit{Maximally Informative Relations} (MIR) for the SI4A input. File format: .csv
+			\item[\texttt{SI4D}] Alignment visualization for the SI4A input. File format: .pdf
+		\end{description}
 
@@
 		\item Upload pre-prints to bioR{\textchi}iv.
+		\item Make sure all Checklist nomenclatural references are included -- Green 1920, Casey 1888, Pierce 1909, etc.
 	\end{enumerate}
@@
 	\end{sideways}
-	\caption{\textbf{Dorsal view of {\ae}deagus of \textit{M. franko} [JF2018].} Genitalia of male (\male) paratype.}
+	\caption{\textbf{Dorsal view of aedeagus of \textit{M. franko} [JF2018].} Genitalia of male (\male) paratype.}
 	\label{fig:franko_aedeagus_dorsal}
@@
 	\end{sideways}
-	\caption{\textbf{Lateral view of {\ae}deagus of \textit{M. franko} [JF2018].} Genitalia of male (\male) paratype.}
+	\caption{\textbf{Lateral view of aedeagus of \textit{M. franko} [JF2018].} Genitalia of male (\male) paratype.}
 	\label{fig:franko_aedeagus_lateral}
@@
 	\end{sideways}
-	\caption{\textbf{Dorsal view of {\ae}deagus of \textit{M. sculptilis} [JF2018].} Genitalia of male (\male) paratype.}
+	\caption{\textbf{Dorsal view of aedeagus of \textit{M. sculptilis} [JF2018].} Genitalia of male (\male) paratype.}
 	\label{fig:sculptilis_aedeagus_dorsal}
@@
 	\end{sideways}
-	\caption{\textbf{Lateral view of {\ae}deagus of \textit{M. sculptilis} [JF2018].} Genitalia of male (\male) paratype.}
+	\caption{\textbf{Lateral view of aedeagus of \textit{M. sculptilis} [JF2018].} Genitalia of male (\male) paratype.}
 	\label{fig:sculptilis_aedeagus_lateral}
@@
 	\begin{sideways}
-		\includegraphics[height=0.75\textwidth]{tree.eps}
-	\end{sideways}
-	\caption{\textbf{Preferred phylogeny.} Single most parsimonious cladogram representing the preferred phylogeny of species of \textit{Minyomerus} [JF2018], and select outgroup taxa (L = 99, CI = 60, RI = 80).
+		\includegraphics[height=0.75\textwidth]{tree1.jpg}
+	\end{sideways}
+	\caption{\textbf{Preferred phylogeny -- character transitions and support.} Single most parsimonious cladogram representing the preferred phylogeny of species of \textit{Minyomerus} [JF2018], and select outgroup taxa (L = 99, CI = 60, RI = 80).
 Characters 9, 27, 39, 45 - 47, 49, and 51 are mapped under ACCTRAN optimization; all others are unambiguously optimized.
@@
 A ``*'' symbol at the right end of a branch indicates Bootstrap support greater than 0.95.}
-	\label{fig:tree}
+	\label{fig:tree1}
+\end{figure}
+
+%phylogeny
+\begin{figure}[h]
+	\centering
+	\begin{sideways}
+		\includegraphics[height=0.75\textwidth]{tree2.jpg}
+	\end{sideways}
+	\caption{\textbf{Preferred phylogeny -- clade concept labels.} Topology and species-level taxonomic concept labels as in Fig.~\ref{fig:tree1}.
+Clade concept labels, numbered 1-20, are consistently generated by using the alphabetically first epithet in each of the bifurcating sister clades.
+This method safeguards the clade concept labels against changes due simply to reorientation of leaves.
+Bold-font square brackets indicate new [JF2018] labels.
+See also \textbf{\nameref{sec:alignments}}.}
+	\label{fig:tree2}
+\end{figure}
+
+%RCC-5 alignment visualizations
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{align1.jpg}
+	\caption{\textbf{Intensional RCC--5 alignment of the rank-only classifications of \textit{Minyomerus} [JF2018]/[JF2015].} See also \citet{jansen2015} and \textbf{Supplemental Information SI2}.
+Taxonomic concept labels such as \textit{Minymerus microps} [JF2015] are abbreviated as "2015.Minyomerus\_microps".
+Relaxation of the coverage constraint is indicated with the prefix "nc\_" (no coverage).
+Congruent concept regions (T\textsubscript{2} and T\textsubscript{1}) are shown as grey rectangles, concepts regions unique to the later taxonomy (T\textsubscript{2}) are shown as green rectangles, and concept regions unique to the earlier taxonomy (T\textsubscript{1}) are shown as yellow octagons.
+Articulations of inverse proper inclusion $(<)$ and overlap $(><)$, where present, are also shown.}
+	\label{fig:align1}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{align2.jpg}
+	\caption{\textbf{Intensional RCC--5 alignment of the phylogenies of \textit{Minyomerus} [JF2018]/[JF2015] -- whole-concept resolution with overlap.} See also \textbf{Supplemental Information SI3}.
+Seven overlapping articulations are inferred.
+For further discussion, see the \textbf{\nameref{sec:alignments}} section.}
+	\label{fig:align2}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{align3.jpg}
+	\caption{\textbf{Intensional RCC--5 alignment of the phylogenies of \textit{Minyomerus} [JF2018]/[JF2015] -- split-concept resolution.} See also \textbf{Supplemental Information SI4}.
+The seven overlapping articulations of the alignment displayed Fig.~\ref{fig:align2} are resolved into their constituent split regions.
+That is, if regions A and B overlap, the three resulting split regions are labeled A\textbackslash b ("A, \emph{not} b"), A*B ("A \emph{and} B"), and B\textbackslash a ("B, \emph{not} a").
+Five split-concept regions can \emph{only} be named using this convention, and are salmon-colored in the alignment visualization.}
+	\label{fig:align3}
 \end{figure}

### 2018-05-08 tex/manuscript.tex
some edits and recompile

@@
 			It is unknown whether this species is parthenogenetic.
-
+\newpage
 \section*{Checklist of Species}\label{sec:checklist}
@@
 
+\newpage
 \section*{Species Identification Key}\label{sec:idkey}
@@
 	\begin{enumerate}[itemsep=-0.4em]
-		\item Insert measurements.
 		\item Submit names to zoobank.

### 2018-05-08 tex/manuscript.tex
final draft for submission

@@
 \usepackage{nameref}
-\usepackage{epstopdf}
+%\usepackage{epstopdf}
 \newcolumntype{m}[1]{D{.}{~}{#1}}
@@
 \section*{Introduction}\label{sec:intro}
-	This phylogenetic revision follows \citet{jansen2015} in the use of the taxonomic concept approach; see \citet{fp2009, fea2016a, fea2016b}. Accordingly:
+	This phylogenetic revision follows \citet{jansen2015} in the use of the taxonomic concept approach; see \citet{fp2009, fea2016a, fea2016b}. 
+	Accordingly:
 
 	\begin{enumerate}[itemsep=-0.4em]
-		\item \textit{Taxonomic concept labels} -- i.e., the taxonomic name sec.
-(\textit{according to}) author or source (year) -- are used whenever we identify one specific usage of the taxonomic name.
-Examples: \textit{Minyomerus} Horn, 1876 sec.
-Jansen \& Franz, 2015 (henceforth: [JF2015]) and \textit{Minyomerus} Horn, 1876 sec.
-Jansen \& Franz, 2018 (henceforth: [JF2018]).
+		\item \textit{Taxonomic concept labels} -- i.e., the taxonomic name sec. (\textit{according to}) author or source (year) -- are used whenever we identify one specific usage of the taxonomic name.
+		Examples: \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz, 2015 (henceforth: [JF2015]) and \textit{Minyomerus} Horn, 1876 sec. Jansen \& Franz, 2018 (henceforth: [JF2018]). 
 		We also employ this convention to express nomenclatural relationships. 
-		\item Solely the taxonomic name -- without the sec.
-annotation -- is used to refer to the cumulative history (origin to present) of taxonomic concept labels in which that name participates.
+		\item Solely the taxonomic name -- without the sec. annotation -- is used to refer to the cumulative history (origin to present) of taxonomic concept labels in which that name participates. 
 		Example: \textit{Minyomerus} Horn, 1876.
@@
 	The weevil genus \textit{Minyomerus} Horn, 1876 [JF2018] remains currently assigned to the tribe Tanymecini Lacordaire, 1863 [non-focal], subtribe Tanymecina Lacoirdaire, 1863 [non-focal] (Curculionidae [non-focal]: Entiminae [non-focal] -- higher-level classification in accordance with \citealt{alonso1999} and \citealt{bouchard2011}).
-	A recent phylogenetic revision of the \textit{Minyomerus} [JF2015] recognized a total of 17 described species, distributed throughout the desert and plains regions of North America \citep{jansen2015}.
+	A recent phylogenetic revision of the genus \textit{Minyomerus} [JF2015] recognized a total of 17 described species, distributed throughout the desert and plains regions of North America \citep{jansen2015}.
 
@@
 	\textit{Minyomerus} [JF2018] belongs to the broad-nosed weevils, subfamily Entiminae [non-focal], on the basis of having a short, broad rostrum and dehiscent mandibular process \citep{marvaldi1997, anderson2002, oberprieler2007, oberprieler2014, marvaldi2014}.
-	The adults are clothed in appressed, circular scales, generally in earth-tones from white to dark brown, with sub-recumbent to erect, interspersed setiform scales ("setae") arranged in rows on the elytral intervals.
-Their length can range from 2.8 mm to 6.0 mm \citep{jansen2015}.
+	The adults are clothed in appressed, circular scales, generally in earth-tones from white to dark brown, with sub-recumbent to erect, interspersed setiform scales (``setae'') arranged in rows on the elytral intervals.
+Their body length can range from 2.8 mm to 6.0 mm \citep{jansen2015}.
 	The genus has been classified in the tribe Tanymecini [non-focal] based on the presence of post-ocular vibrissae that project anteriorly from the anterior prothoracic margin, although the exact placement and sister taxa of this genus within the tribe are currently unknown \citep{howden1959, howden1970, howden1982, jansen2015}.
@@
 	\begin{enumerate} [itemsep=-0.4em]
-		\item Taehe intercoxal process of the prosternum is medially divided into two halves, with the procoxae apparently contiguous in most.
+		\item The intercoxal process of the prosternum is medially divided into two halves, with the procoxae apparently contiguous in most.
 		\item The elytral humeri are rounded rather than angled and protruding.
@@
 	Following the publication of a monographic revision of \textit{Minyomerus} [JF2015], we have discovered four additional, undescribed species.
-These are known to us only from limited numbers of specimens, yet are well circumscribed by -- i.e., intensionally included in \citep{fp2009} -- the recent generic delimitation of \textit{Minyomerus} [JF2015].
+	These are known to us only from limited numbers of specimens, yet are well circumscribed by -- i.e., intensionally included in (see \citealt{fp2009}) -- the recent generic delimitation of \textit{Minyomerus} [JF2015].
 	In other words, the addition of these new species \emph{has not} required altering the intensional, property-based definition of the genus-level concept as circumscribed in \citet{jansen2015} (see \textbf{\nameref{sec:results}}).
 	Our RCC--5 alignments (see \textbf{\nameref{sec:alignments}}) reflect this genus-level concept congruence while also showing which classificatory and phylogenetic structures have changed (Figs.~\ref{fig:align1}-\ref{fig:align3}).
-	The precise use of the taxonomic concept labels in accordance with either [JF2015] or [JF2018] is meant to minimize the creation of new taxonomic concept labels (to counter label "inflation"; see \citet{fp2009}), while reflecting explicitly \emph{which} taxonomic concepts we consider as relevantly new and unique to the present study.
+	The precise use of the taxonomic concept labels in accordance with either [JF2015] or [JF2018] is meant to minimize the creation of new taxonomic concept labels (to counter label ``inflation''; see \citet{fp2009}), while reflecting explicitly \emph{which} taxonomic concepts we consider as relevantly new and unique to the present study.
 
@@
 	Where possible, we make note of host-plant records, and briefly discuss the geographic distributions of the herein described species.
-	A more extensive discussion of the habits, distribution, and delimitation of the \textit{Minyomerus} [JF2015] and all of its constituent species is provided in \citep{jansen2015}.
+	A more extensive discussion of the habits, distribution, and delimitation of the genus \textit{Minyomerus} [JF2015] and all of its constituent species is provided in \citet{jansen2015}.
 
 \section*{Materials and Methods}\label{sec:methods} 
-	The methods used in this manuscript are generally consistent with \citet{jansen2015}. Relevant updates are detailed below. 
+	The methods used in this manuscript are generally consistent with \citet{jansen2015}.
+	Relevant updates are detailed below. 
 	In particular, we retain the format for the species descriptions, emphasizing only those characters that vary significantly from the generic circumscription of \textit{Minyomerus} [JF2015].
@@
 		The terminology for exterior morphology is in general accordance with \citet{torre1989}.
-		Additional morphological terms specific to (entimine [non-focal]) weevils were used as follows:
+		Additional morphological terms specific to broad-nosed weevils (Entiminae [non-focal]) were used as follows:
 			\citet{ting1936} and \citet{morimoto2003} for mouthparts;
@@
 
-\section*{To Do}
-	\begin{enumerate}[itemsep=-0.4em]
-		\item Submit names to zoobank.
-		\item Upload matrix data to dryad.
-		\item Upload pre-prints to bioR{\textchi}iv.
-		\item Make sure all Checklist nomenclatural references are included -- Green 1920, Casey 1888, Pierce 1909, etc.
-	\end{enumerate}
-
 \newpage
+
 \bibliography{references}
-%just references in windows, use references.bib in linux
+\nocite{*}
 

### 2018-05-09 tex/manuscript.tex
long dash to --

@@
 	The authors also thank Salvatore Anzaldo, Andrew Johnston, Sangmi Lee and other ASUHIC members for their assistance in procuring, treating, and maintaining specimen loans upon entry into the ASUHIC.
-	This research was funded in part by the National Science Foundation (DEB-1155984) and the United States Department of Agriculture – Agricultural Research Service (Agreement 58-1275-1-335).
+	This research was funded in part by the National Science Foundation (DEB-1155984) and the United States Department of Agriculture -- Agricultural Research Service (Agreement 58-1275-1-335).
 

### 2018-05-09 tex/manuscript.tex
added nomenclature subsection to methods

@@
 		Documented occurrence records are laid over the modeled habitat ranges as colored circles on their respective maps (Figs.~\ref{fig:map_amptyl}-\ref{fig:map_sculptilis}), along with vector layers of country (white) and state (gray) borders \citep{hijmans2012}.
+
+	\subsection*{Nomenclature}
+		The electronic version of this article in Portable Document Format (PDF) will represent a published work according to the International Commission on Zoological Nomenclature (ICZN), and hence the new names contained in the electronic version are effectively published under that Code from the electronic edition alone.
+		This published work and the nomenclatural acts it contains have been registered in ZooBank, the online registration system for the ICZN. 
+		The ZooBank LSIDs (Life Science Identifiers) can be resolved and the associated information viewed through any standard web browser by appending the LSID to the prefix http://zoobank.org/. 
+		The LSID for this publication is: [INSERT HERE]. The online version of this work is archived and available from the following digital repositories: PeerJ, PubMed Central and CLOCKSS.
 

### 2018-05-10 tex/manuscript.tex
supp. files and PDF allowed
move other pdfs to a gitignore folder if not wanted

@@
 		The ZooBank LSIDs (Life Science Identifiers) can be resolved and the associated information viewed through any standard web browser by appending the LSID to the prefix http://zoobank.org/. 
-		The LSID for this publication is: [INSERT HERE]. The online version of this work is archived and available from the following digital repositories: PeerJ, PubMed Central and CLOCKSS.
+		The LSID for this publication is: urn:lsid:zoobank.org:pub:0AEE5733-06D1-401F-88C9-0D5232FBFC7A.
+The online version of this work is archived and available from the following digital repositories: PeerJ, PubMed Central and CLOCKSS.
+
+Minyomerus ampullaceus: 
+Minyomerus franko: 
+Minyomerus sculptilis: 
+Minyomerus tylotos:
 
@@
 	\subsection*{\textit{Minyomerus ampullaceus} Jansen \& Franz sec. Jansen \& Franz, 2018; sp. n.}\label{ssec:amp}
+		urn:lsid:zoobank.org:act:24943E17-F20E-4E3C-A3A1-A1D4D907B48E\\
 		Figures~\ref{fig:ampullaceus_F_dorsal}-\ref{fig:ampullaceus_lamina}
@@
 	\subsection*{\textit{Minyomerus franko} Jansen \& Franz sec. Jansen \& Franz, 2018; sp. n.}\label{ssec:franko}
-		Figures~\ref{fig:franko_F_dorsal}-\ref{fig:franko_aedeagus_lateral}
+		urn:lsid:zoobank.org:act:F8C0153E-DF0E-40E0-AF31-EBEA7075D06D\\
+		Figures~\ref{fig:franko_F_dorsal}-\ref{fig:franko_aedeagus}
 		\subsubsection*{Diagnosis}
@@
 	\subsection*{\textit{Minyomerus sculptilis} Jansen \& Franz sec. Jansen \& Franz, 2018; sp. n.}\label{ssec:sculpt}
-		Figures~\ref{fig:sculptilis_F_dorsal}-\ref{fig:sculptilis_aedeagus_lateral}
+		urn:lsid:zoobank.org:act:EA0B1AD9-68F2-4409-A0F8-903B0DA0FFF9\\
+		Figures~\ref{fig:sculptilis_F_dorsal}-\ref{fig:sculptilis_aedeagus}
 		\subsubsection*{Diagnosis}
@@
 	\subsection*{\textit{Minyomerus tylotos} Jansen \& Franz sec. Jansen \& Franz, 2018; sp. n.}\label{ssec:tylotos}
+		urn:lsid:zoobank.org:act:10CD3562-5969-4BCF-ACFE-BB0E5E2BF9A6\\
 		Figures~\ref{fig:tylotos_F_dorsal}-\ref{fig:tylotos_lamina}
@@
     	\ttfamily
-    	\footnotesize
+    	\scriptsize
     	\begin{tabular}{m{8.25}|l}
@@
 		\centering
-		\includegraphics[height=\textwidth]{ampullaceus_F_dorsal.jpg}
+		\includegraphics[height=\textwidth]{figure1.jpg}
 	\end{sideways}
@@
 		\centering
-		\includegraphics[height=\textwidth]{ampullaceus_F_lateral.jpg}
+		\includegraphics[height=\textwidth]{figure2.jpg}
 	\end{sideways}
@@
 		\centering
-		\includegraphics[height=\textwidth]{ampullaceus_F_ventral.jpg}
+		\includegraphics[height=\textwidth]{figure3.jpg}
 	\end{sideways}
@@
 	\centering
-	\includegraphics[width=\textwidth]{ampullaceus_F_frontal.jpg}
+	\includegraphics[width=\textwidth]{figure4.jpg}
 	\caption{\textbf{Head and rostrum of \textit{M. ampullaceus} [JF2018].} Frontal view of female (\female) holotype.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{ampullaceus_spermatheca.jpg}
+	\includegraphics[width=\textwidth]{figure5.jpg}
 	\caption{\textbf{Spermatheca of \textit{M. ampullaceus} [JF2018].} Genitalia of female (\female) holotype.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{ampullaceus_lamina.jpg}
+	\includegraphics[width=\textwidth]{figure6.jpg}
 	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. ampullaceus} [JF2018].} Sternum VIII of female (\female) holotype.}
@@
 		\centering
-		\includegraphics[height=\textwidth]{franko_F_dorsal.jpg}
+		\includegraphics[height=\textwidth]{figure7.jpg}
 	\end{sideways}
@@
 		\centering
-		\includegraphics[height=\textwidth]{franko_F_lateral.jpg}
+		\includegraphics[height=\textwidth]{figure8.jpg}
 	\end{sideways}
@@
 		\centering
-		\includegraphics[height=\textwidth]{franko_F_ventral.jpg}
+		\includegraphics[height=\textwidth]{figure9.jpg}
 	\end{sideways}
@@
 	\centering
-	\includegraphics[width=\textwidth]{franko_F_frontal.jpg}
+	\includegraphics[width=\textwidth]{figure10.jpg}
 	\caption{\textbf{Head and rostrum of \textit{M. franko} [JF2018].} Frontal view of female (\female) holotype.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{franko_maxilla.jpg}
+	\includegraphics[width=\textwidth]{figure11.jpg}
 	\caption{\textbf{Maxilla of \textit{M. franko} [JF2018].} Dextral maxilla of female (\female) paratype.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{franko_prementum.jpg}
+	\includegraphics[width=\textwidth]{figure12.jpg}
 	\caption{\textbf{Prementum of \textit{M. franko} [JF2018].} Labium of female (\female) paratype.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{franko_spermatheca.jpg}
+	\includegraphics[width=\textwidth]{figure13.jpg}
 	\caption{\textbf{Spermatheca of \textit{M. franko} [JF2018].} Genitalia of female (\female) paratype.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{franko_lamina.jpg}
+	\includegraphics[width=\textwidth]{figure14.jpg}
 	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. franko} [JF2018].} Sternum VIII of female (\female) paratype.}
@@
 	\begin{sideways}
-		\includegraphics[width=0.95\textheight]{franko_aedeagus_dorsal.jpg}
+		\includegraphics[width=0.95\textheight]{figure15.jpg}
 	\end{sideways}
-	\caption{\textbf{Dorsal view of aedeagus of \textit{M. franko} [JF2018].} Genitalia of male (\male) paratype.}
-	\label{fig:franko_aedeagus_dorsal}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
+	\caption{\textbf{Aedeagus of \textit{M. franko} [JF2018].} Genitalia of male (\male) paratype in (A) dorsal view and (B) lateral view.}
+	\label{fig:franko_aedeagus}
+\end{figure}
+
+%M. sculptilis
+\begin{figure}[h]
 	\begin{sideways}
-		\includegraphics[width=0.95\textheight]{franko_aedeagus_lateral.jpg}
-	\end{sideways}
-	\caption{\textbf{Lateral view of aedeagus of \textit{M. franko} [JF2018].} Genitalia of male (\male) paratype.}
-	\label{fig:franko_aedeagus_lateral}
-\end{figure}
-
-%M. sculptilis
-\begin{figure}[h]
-	\begin{sideways}
-		\centering
-		\includegraphics[height=\textwidth]{sculptilis_F_dorsal.jpg}
+		\centering
+		\includegraphics[height=\textwidth]{figure16.jpg}
 	\end{sideways}
@@
 		\centering
-		\includegraphics[height=\textwidth]{sculptilis_F_lateral.jpg}
+		\includegraphics[height=\textwidth]{figure17.jpg}
 	\end{sideways}
@@
 		\centering
-		\includegraphics[height=\textwidth]{sculptilis_F_ventral.jpg}
+		\includegraphics[height=\textwidth]{figure18.jpg}
 	\end{sideways}
@@
 	\centering
-	\includegraphics[width=\textwidth]{sculptilis_F_frontal.jpg}
+	\includegraphics[width=\textwidth]{figure19.jpg}
 	\caption{\textbf{Head and rostrum of \textit{M. sculptilis} [JF2018].} Frontal view of female (\female) holotype.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{sculptilis_spermatheca.jpg}
+	\includegraphics[width=\textwidth]{figure20.jpg}
 	\caption{\textbf{Spermatheca of \textit{M. sculptilis} [JF2018].} Genitalia of female (\female) paratype.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{sculptilis_lamina.jpg}
+	\includegraphics[width=\textwidth]{figure21.jpg}
 	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. sculptilis} [JF2018].} Sternum VIII of female (\female) paratype.}
@@
 	\begin{sideways}
-		\includegraphics[width=0.95\textheight]{sculptilis_aedeagus_dorsal.jpg}
+		\includegraphics[width=0.95\textheight]{figure22.jpg}
 	\end{sideways}
-	\caption{\textbf{Dorsal view of aedeagus of \textit{M. sculptilis} [JF2018].} Genitalia of male (\male) paratype.}
-	\label{fig:sculptilis_aedeagus_dorsal}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
+	\caption{\textbf{Aedeagus of \textit{M. sculptilis} [JF2018].} Genitalia of male (\male) paratype in (A) dorsal view and (B) lateral view.}
+	\label{fig:sculptilis_aedeagus}
+\end{figure}
+
+%M. tylotos
+\begin{figure}[h]
 	\begin{sideways}
-		\includegraphics[width=0.95\textheight]{sculptilis_aedeagus_lateral.jpg}
-	\end{sideways}
-	\caption{\textbf{Lateral view of aedeagus of \textit{M. sculptilis} [JF2018].} Genitalia of male (\male) paratype.}
-	\label{fig:sculptilis_aedeagus_lateral}
-\end{figure}
-
-%M. tylotos
-\begin{figure}[h]
-	\begin{sideways}
-		\centering
-		\includegraphics[height=\textwidth]{tylotos_F_dorsal.jpg}
+		\centering
+		\includegraphics[height=\textwidth]{figure23.jpg}
 	\end{sideways}
@@
 		\centering
-		\includegraphics[height=\textwidth]{tylotos_F_lateral.jpg}
+		\includegraphics[height=\textwidth]{figure24.jpg}
 	\end{sideways}
@@
 		\centering
-		\includegraphics[height=\textwidth]{tylotos_F_ventral.jpg}
+		\includegraphics[height=\textwidth]{figure25.jpg}
 	\end{sideways}
@@
 	\centering
-	\includegraphics[width=\textwidth]{tylotos_F_frontal.jpg}
+	\includegraphics[width=\textwidth]{figure26.jpg}
 	\caption{\textbf{Head and rostrum of \textit{M. tylotos} [JF2018].} Frontal view of female (\female) holotype.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{tylotos_prementum.jpg}
+	\includegraphics[width=\textwidth]{figure27.jpg}
 	\caption{\textbf{Prementum of \textit{M. tylotos} [JF2018].} Labium of female (\female) paratype.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{tylotos_spermatheca.jpg}
+	\includegraphics[width=\textwidth]{figure28.jpg}
 	\caption{\textbf{Spermatheca of \textit{M. tylotos} [JF2018].} Genitalia of female (\female) paratype.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{tylotos_lamina.jpg}
+	\includegraphics[width=\textwidth]{figure29.jpg}
 	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. tylotos} [JF2018].} Sternum VIII of female (\female) paratype.}
@@
 	\begin{sideways}
-		\includegraphics[height=0.75\textwidth]{tree1.jpg}
+		\includegraphics[height=0.85\textwidth]{figure30.png}
 	\end{sideways}
@@
 	\begin{sideways}
-		\includegraphics[height=0.75\textwidth]{tree2.jpg}
+		\includegraphics[height=0.85\textwidth]{figure31.png}
 	\end{sideways}
@@
 	\centering
-	\includegraphics[width=\textwidth]{align1.jpg}
+	\includegraphics[width=\textwidth]{figure32.png}
 	\caption{\textbf{Intensional RCC--5 alignment of the rank-only classifications of \textit{Minyomerus} [JF2018]/[JF2015].} See also \citet{jansen2015} and \textbf{Supplemental Information SI2}.
@@
 	\centering
-	\includegraphics[width=\textwidth]{align2.jpg}
+	\includegraphics[width=\textwidth]{figure33.png}
 	\caption{\textbf{Intensional RCC--5 alignment of the phylogenies of \textit{Minyomerus} [JF2018]/[JF2015] -- whole-concept resolution with overlap.} See also \textbf{Supplemental Information SI3}.
@@
 	\centering
-	\includegraphics[width=\textwidth]{align3.jpg}
+	\includegraphics[width=\textwidth]{figure34.png}
 	\caption{\textbf{Intensional RCC--5 alignment of the phylogenies of \textit{Minyomerus} [JF2018]/[JF2015] -- split-concept resolution.} See also \textbf{Supplemental Information SI4}.
@@
 	\centering
-	\includegraphics[width=\textwidth]{summary.png}
+	\includegraphics[width=\textwidth]{figure35.png}
 	\caption{\textbf{Summary map of distributions of new species of \textit{Minyomerus} [JF2018].} Combined occurrence record and Maxent habitat modeling map for four newly-described species of \textit{Minyomerus} [JF2018], as indicated in the legend.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{tylotos_ampullaceus.png}
+	\includegraphics[width=\textwidth]{figure36.png}
 	\caption{\textbf{Distributions of \textit{M.
@@
 	\centering
-	\includegraphics[width=\textwidth]{franko.png}
+	\includegraphics[width=\textwidth]{figure37.png}
 	\caption{\textbf{Distributions of \textit{M. franko} [JF2018].} Combined occurrence record and Maxent habitat modeling map for \textit{M. franko} [JF2018], as indicated in the legend.}
@@
 	\begin{sideways}
-		\includegraphics[height=0.8\textwidth]{sculptilis.png}
+		\includegraphics[height=0.85\textwidth]{figure38.png}
 		\end{sideways}

### 2018-05-17 tex/manuscript.tex
added rough conclusion section

@@
 
+\section*{Conclusions}
+	With the characterization of the four herein described species, the Entimine genus \textit{Minyomerus} has expanded to include a total of 21 species.
+	We opine there is a strong likelihood that additional undescribed species exist throughout the North American deserts, given the endemicity of many members of the genus.
+	Furthermore, we believe that sampling in poorly-sampled locales, particularly in the northwestern United States and in northern Mexico, will yield new species and inferences into the evolutionary history of this genus.
+	Acquisition of specimens suitable for DNA extraction would be invaluable for generating a molecular phylogeny of this genus for comparison with our analysis.
+	We indicate a possible origin of \textit{Minyomerus} in central Mexico based on their current distribution; however, it is currently not possible to test this hypothesis due to a lack of fossils and molecular clock.
+	Additionally, we identify a significant gap in our understanding of the reproductive behavior of certain species we suspect to be parthenogenetic.
+	Future efforts could be targeted towards rearing and karyotyping specimens of these species to assess their reproductive biology in this context.
+	Finally, the validity of \textit{Minyomerus} as a member of the Tanymecini and its relationships to other Entimine taxa remain uncertain.
+	We therefore emphasize the need for further taxonomic treatment of broad-nosed weevils to resolve these questions.
+
 \section*{Acknowledgments}

### 2018-05-18 tex/manuscript.tex
conclusions section

--- 2018-05-10 tex/manuscript.tex
@@
 
+\section*{Conclusions}
+	Through addition of four herein described species, the entimine [non-focal] genus \textit{Minyomerus} [JF2018] is expanded to include 21 species.
+	We predict that additional undescribed species of \textit{Minyomerus} [JF2018] exist throughout the North American deserts, given the narrow endemicity patterns of many members of the genus.
+	Furthermore, we believe that sampling in poorly-sampled locales, particularly in the northwestern United States and in northern Mexico, will yield new evolutionary insights for this group.
+	New molecular data can strengthen phylogenetic hypotheses and provide estimates regarding the timing of diversification of \textit{Minyomerus} [JF2018], thereby testing our current inference of an origin in central Mexico.
+	Another research direction should focus on the reproductive behavior of certain species suspected to be parthenogenetic; including rearing and karyotyping.
+	Finally, the validity of the genus \textit{Minyomerus} [JF2018] as a member of the Tanymecini [non-focal], and its relationships to other Entiminae [non-focal], remain uncertain.
+
 \section*{Acknowledgments}

### 2018-07-31 reviews/rebuttal.tex
rebuttal and revisions

\documentclass[10pt,letterpaper]{letter}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{calc}
\newcommand{\x}{$\times$~}

\makeatletter
\newcommand{\DESCRIPTION@original@item}{}
\let\DESCRIPTION@original@item\item
\newcommand*{\DESCRIPTION@envir}{DESCRIPTION}
\newlength{\DESCRIPTION@totalleftmargin}
\newlength{\DESCRIPTION@linewidth}
\newcommand{\DESCRIPTION@makelabel}[1]{\llap{#1}}%
\newcommand{\DESCRIPTION@item}[1][]{%
  \setlength{\@totalleftmargin}%
       {\DESCRIPTION@totalleftmargin+\widthof{\textbf{#1 }}-\leftmargin}%
  \setlength{\linewidth}
       {\DESCRIPTION@linewidth-\widthof{\textbf{#1 }}+\leftmargin}%
  \par\parshape \@ne \@totalleftmargin \linewidth
  \DESCRIPTION@original@item[\textbf{#1}]%
}
\newenvironment{DESCRIPTION}
  {\list{}{\setlength{\labelwidth}{0cm}%
           \let\makelabel\DESCRIPTION@makelabel}%
   \setlength{\DESCRIPTION@totalleftmargin}{\@totalleftmargin}%
   \setlength{\DESCRIPTION@linewidth}{\linewidth}%
   \renewcommand{\item}{\ifx\@currenvir\DESCRIPTION@envir
                           \expandafter\DESCRIPTION@item
                        \else
                           \expandafter\DESCRIPTION@original@item
                        \fi}}
  {\endlist}
\makeatother

\address{M. Andrew Jansen\\School of Life Sciences\\Arizona State University\\Tempe, AZ 85287-4501} 
\signature{\underline{Contact Information}\\email: majanse1@asu.edu\\office: 1-(480)-727-9692} 
\begin{document} 
\begin{letter}{Juan J. Morrone\\Universidad Nacional Aut\'{o}noma de M\'{e}xico\\Academic Editor, PeerJ} 
	\opening{Dear Dr. Morrone,}

	We thank you for a speedy and very constructive review of our manuscript.
	In our revised resubmission, we have made a great effort to accommodate the suggestions brought up through the review, as outlined point-by-point below (line numbers refer to diff.pdf).
	The comments of the reviewers may be found at the end of this document for your reference.
	We sincerely hope that you will find these revisions fitting and satisfactory.

	\begin{enumerate}
		\item In response to Reviewer 2, we have changed all instances of the word revision (lines 28, 200, 912, and 1077) to read either ``review'' or ``study''.
		\item In response to Reviewer 2, we did not move the first paragraph and itemized explanation of the taxonomic concept approach to the \textbf{Methods} section of the manuscript; we feel that an upfront explanation of our approach, and especially the meaning of the taxonomic concept labels, is warranted to avoid confusion while reading the introduction.
		\item In response to Reviewers 2 \& 3, we have italicized the genus name \textit{Minyomerus} in line 210.
		\item In response to Reviewer 2, we have re-written the \textbf{Natural History} subsection of the description of \textit{Minyomerus ampullaceus} (lines 333--341) to indicate that the specimen most likely came from the gut contents of a roadrunner, rather than a nest, as we had originally thought.
		\item In response to Reviewer 2, we have added a statement to the \textbf{Natural History} subsection of the description of \textit{Minyomerus tylotos} (lines 467--468) to indicate that the specific epithet of the host plant was misspelled on the label of the holotype.
		\item In response to Reviewer 3, one of the female \textit{Minyomerus franko} paratypes from the CMNC has been exchanged for a female paratype of \textit{Minyomerus sculptilis} from the USNM (lines 458, 563).
		\item In response to Reviewer 3, a single space indent was removed from the species entry for \textit{Minyomerus gravivultus} in the \textbf{Checklist of Species}, after line 689.
		\item In response to Reviewer 3, lines 709--714 were moved to the \textbf{Phylogenetic analysis} subsection of the \textbf{Methods} section (lines 170--175).
		\item In response to Reviewer 3, we have added a short explanation to the \textbf{Phylogenetic analysis} subsection of the \textbf{Methods} section outlining our general approach to multi-state character coding (lines 175--178).
		\item In response to Reviewer 3, we have clarified the description of character 6 to read ``Prementum, anterior margin medially with a distinct facet, rather than a single edge edge, that continues to lateral margins'' (lines 740--741).
		\item In response to Reviewer 3, we have clarified the description of character 28 to read ``Legs, relative length of mesotarsi to mesotibiae: (0) tarsi less than 3/4\x length of tibiae; (1) tarsi at least equal in length to tibiae; (2) tarsi shorter than tibiae, but longer than 3/4\x length of tibiae.'' (lines 821--823).
		\item In response to Reviewer 3, we have checked again that the species \textit{Minyomerus tylotos} is, in fact, flightless, and found that there are indeed no traces of wings or associated flight structures in our dissected specimens, per the species description.
		\item In keeping with the submission checklist, we have moved our funding statement from the \textbf{Acknowledgments} section (lines 1079--1081) to a separate \textbf{Funding Statement} section (lines 1099--1102), ending with the sentence: ``There was no additional external funding received for this study.''
	\end{enumerate}

	Please let us know if these revisions are acceptable.
	We thank you for your time and consideration, and look forward to next steps.

	\closing{Sincerely,\\Andrew Jansen \& Nico Franz}
	\cc{Nico M. Franz}
	%\ps{adding a postscript}
	\encl{Reviewer comments and annotations}

	\newpage
	\textsc{Reviewer Comments \& Annotations}

	\textbf{Reviewer 1 (Anal\'{i}a Lanteri)}

	\emph{Basic reporting}

	The manuscript is written in clear, unambiguous and professional English language. 
	The main objective of this work is to describe four new species of the weevil genus \textit{Minyomerus} (Curculionidae, Entiminae, Tanymecini), previously revised by the authors of the article, and to integrate the new findings in an updated key and a phylogenetic analysis based on morphological characters.

	The article is well organized and the structure conforms to PeerJ Standards. 
	The introduction includes the necessary information and background on the taxon under study. The literature is well referenced and relevant.

	The taxonomic study was based on a sufficient number of specimens collected by the authors and borrowed from different entomological collections. 
	The descriptions are very detailed and the structures of diagnostic value are illustrated with very good photographs (dorsal and lateral habitus, mouthparts, sternites VIII of female, spermathecae). 
	All figures are relevant, high quality and well labeled. The literature is well referenced and relevant.

	\emph{Experimental design}

	The new species described have been registered in ZooBank, and the information on LSID’s in provided. 
	A cladistic analysis was performed on a data matrix of 52 morphological characters and 26 terminal taxa (5 outgroups and 21 ingroups), to see the position of the new species in the context of Minyomerus and related genera. The selection of characters and character states was correct. 
	The most parsimonious tree was found using TNT, and NONA was used for the optimization of the characters. 
	The tree with the characters optimized was conveniently illustrated. 
	The cladistics methods are sufficiently detailed and the information given can be replicated.
	The potential distribution of each new species was assessed applying an ecological modeling approach, using MAXENT, and was shown in maps.

	The authors adopted the taxonomic concept approach, including the use of taxonomic concept labels and Region Connection Calculus (RCC–5) articulations and alignments.
	I am not very familiar with this approach and I find it a bit confusing for reading the results, but I understand that the authors are leaders in this matter, not yet commonly used in the taxonomic papers.
	The details of the RCC–5 alignment are given in free text form in the Supplemental Information, which also describes the content of the data input and output files.

	\newpage
	\emph{Validity of the findings}

	The work provides new taxonomic information.
	The descriptions of the new species are well justified, same as the results of the cladistics analysis.
	In the discussion, the authors compared the results of the new phylogeny with those previously obtained.
	They discussed on the intrageneric relationships and the phylogenetic position of each species in a historical-biogeographic context.
	In find it interesting and not excessively speculative, however, I have some difficulties in following the indication relative to the taxonomic concept approach.

	Conclusions are well stated, linked to original research question and limited to supporting results.

	\emph{Comments for the Author}

	The paper provides new basic taxonomic information, consisting on a description of four new weevil species, rigorously described and illustrated.
	The phylogenetic placement of these species is analyzed and their geographic ranges are discussed in relation to those of their putative sister taxa, based on the results of a niche modeling analysis.
	The methods applied are classical and correct.
	All the figures are appropriate and necessary.

	In my opinion, the taxonomic concept approach applied in this paper is somewhat confusing, as well as the supplementary information relative to this subject, but I am not an expert on this matter.

	\emph{Annotated manuscript}

	An annotated manuscript was not provided.

	\newpage	
	\textbf{Reviewer 2 (Robert Anderson)}

	\emph{Basic reporting}

	This is a comprehensive, well-written followup to the authors previous paper revising the genus \textit{Minyomerus}.
	I have made a few minor comments in the text of the manuscript PDF.
	I am quite sure that the single specimen of \textit{M. ampullaceus} is from the stomach/gut contents of a roadrunner.
	The USNM was quite active in the mid 1900's in supporting identification of gut contents from various species of birds.
	I have a new \textit{Phyxelis} from Louisiana known only from USNM specimens from quail stomach contents and the weevil \textit{Glaphyrometopus ornithodorus} was described from a series of USNM specimens from meadowlark stomach contents.
	As such, the paragraph related to the natural history of this species should be rewritten.

	The phylogenetic work appears to be well supported and discussed with all characters and states well-explained.
	As the authors know, I am not a fan of the taxonomic concept approach but I can understand the authors rationale for its use.
	The authors have done a nice job of integrating the 4 new species into the key and phylogeny and presenting these results.

	\emph{Experimental design}

	See above.

	\emph{Validity of the findings}

	See above.

	\emph{Comments for the Author}

	See above.

	\emph{Annotated manuscript}

	The reviewer has also provided an annotated manuscript as part of their review:

	\begin{DESCRIPTION}
		\item[Line 17:] ``I think review is a better term here.''
		\item[Lines 28--40:] ``I think this section is best placed in the Methods section.''
		\item[Line 200:] ``italics''
		\item[Lines 320--323:] ``I am quite sure this specimen would have been taken from the stomach contents of this species of bird.
			Over the years the USNM frequently assisted with identifications of stomach contents of various bird species.
			I know of at least two other weevil species originally known only from the stomachs of meadowlark and quail.
			Given the specimen condition this fits with this proposal.''
		\item[Lines 440, 451:] ``Is hastula or hastulata correct...see above under Holotype?''
	\end{DESCRIPTION}

	\newpage

	\textbf{Reviewer 3 (Lourdes Chamorro)}

	\emph{Basic reporting}

	No comment.

	\emph{Experimental design}

	I suggested in the pdf itself that some information may need to be added in the methods section regarding additive/non-additive coding of multistate characters.

	\emph{Validity of the findings}

	No comment.

	\emph{Comments for the Author}

	This is a thorough study that aims to describe and phylogenetically place 4 new species of \textit{Minyomerus}.
	The use of occurrence data to predict distribution ranges for each species is a much welcome approach to this type of study.

	\emph{Annotated manuscript}

	The reviewer has also provided an annotated manuscript as part of their review:

	\begin{DESCRIPTION}
		\item[Line 200:] ``Italics needed.''
		\item[Line 481:] ``?''
		\item[Line 546:] ``USNM is willing to donate this specimen to CMNC in exchange for one of the CMNC paratypes of Minyomerus franko.''
		\item[Line 672:] ``Fix slight indent.''
		\item[Lines 692--697:] ``Perhaps some or all of this would be better placed under methods.''
		\item[Table 1:] ``Why coded as additive vs non-additive?
			Nevermind, I see you expand on this below under each character.
			Perhaps something alluding to this methodology should be mentioned in the methods.''
		\item[Line 723:] ``This is rather unclear.''
		\item[Line 803:] ``This is rather vague, as well as state 2.''
		\item[Figure 23:] ``Is this species flightless also?
			It seems to have much more prominent humeri than the other species in the genus.''
		\item[Figure 35:] ``Excellent!''
	\end{DESCRIPTION}
\end{letter} 
\end{document}

### 2018-07-31 tex/revised_manuscript.tex
rebuttal and revisions

--- 2018-05-18 tex/manuscript.tex
@@
 Jansen \& Franz, 2015 (Curculionidae [non-focal]: Entiminae [non-focal]: Tanymecini [non-focal]) contained 17 species distributed throughout the desert and plains regions of North America.
-	In this revision of \textit{Minyomerus} sec.
+	In this review of \textit{Minyomerus} sec.
 Jansen \& Franz, 2018, we describe the following four species as new to science: \textit{Minyomerus ampullaceus} sec.
@@
 \section*{Introduction}\label{sec:intro}
-	This phylogenetic revision follows \citet{jansen2015} in the use of the taxonomic concept approach; see \citet{fp2009, fea2016a, fea2016b}. 
+	This phylogenetic study follows \citet{jansen2015} in the use of the taxonomic concept approach; see \citet{fp2009, fea2016a, fea2016b}. 
 	Accordingly:
@@
 		The character matrix was edited and phylogenetic results viewed using the WinDada and WinClados interfaces of WinClada, respectively \citep{nixon2002}.
-		The character sequence follows that of the taxonomic descriptions.
+		Characters are numbered in accordance with descriptive sequence used in the species accounts.
+		A ``–'' symbol indicates inapplicable (character, state), whereas a ``?'' symbol indicates missing information, e.g., due to the unavailability of male specimens or insufficient specimens on hand to permit full dissections.
+		Characters 9, 27, 39, 45 - 47, 49, and 51 were mapped onto the preferred phylogeny using ACCTRAN optimization (see \citealt{agnarsson2008}), and the remaining characters had an unambiguous optimization.
+		All multi-state characters but one were coded as additive, as explained beneath the description for each character (see \textbf{\nameref{sec:results}}), based on their alignment with the preferred phylogeny.
+		Each alternative coding scheme was tested both alone and in unison with the other multi-state characters to assess their impact on the topology of the preferred phylogeny.
+
 		The most parsimonious tree and character state optimizations were inferred under parsimony using NONA \citep{goloboff1999}.
@@
 		The annotations (INT) and (OST) indicate intensional and ostensive readings of articulations, and AND is used to connect multiple simultaneously recognized provenance relationships.
-		Two \emph{intensional} alignments are produced as part of this revision, i.e., one that captures the non-/congruence of \textit{Minyomerus} [JF2018] versus \textit{Minyomerus} [JF2015] represented as rank-only classifications (Fig.~\ref{fig:align1}), and another that represents these as fully bifurcated phylogenies with newly assigned clade concept labels, shown in whole-concept resolution (Fig.~\ref{fig:align2}) and in split-concept resolution (Fig.~\ref{fig:align3}); see \citet{fea2018}.
+		Two \emph{intensional} alignments are produced as part of this review, i.e., one that captures the non-/congruence of \textit{Minyomerus} [JF2018] versus \textit{Minyomerus} [JF2015] represented as rank-only classifications (Fig.~\ref{fig:align1}), and another that represents these as fully bifurcated phylogenies with newly assigned clade concept labels, shown in whole-concept resolution (Fig.~\ref{fig:align2}) and in split-concept resolution (Fig.~\ref{fig:align3}); see \citet{fea2018}.
 
@@
 	\subsection*{Species distribution modeling}\label{ssec:dismo} 
-		We used the modeling program Maxent, Version 3.4, to generate habitat models for the species of Minyomerus [JF2018] (Figs.~\ref{fig:map_summary}-\ref{fig:map_sculptilis}) based on documented occurrence records \citep{phillips2004, phillips2006, elith2011}.
+		We used the modeling program Maxent, Version 3.4, to generate habitat models for the species of \textit{Minyomerus} [JF2018] (Figs.~\ref{fig:map_summary}-\ref{fig:map_sculptilis}) based on documented occurrence records \citep{phillips2004, phillips2006, elith2011}.
 		The default settings were adjusted to \texttt{Max number background points = 100,000} and \texttt{Iterations = 10}.
@@
 			No host plant associations have been documented.
-			The label indicates ``Geococcyx calif''; this is presumably a reference to \textit{Geococcyx californianus} (Lesson, 1829) [non-focal] (Cuculidae [non-focal]), the Greater Roadrunner, although it is unclear if the specimen was found on or near one of these birds (either living, dead, or in a nest).
-			Species of \textit{Minyomerus} [JF2018] are only known to be phytophagous, not parasitic, phoretic, or necrophagous.
-Hence we believe that this specimen was most likely found in a nest, and was present there only incidentally because the nest was constructed in the host plant of this specimen \citep{jansen2015}.
+			The label indicates ``Geococcyx calif''; this is presumably a reference to \textit{Geococcyx californianus} (Lesson, 1829) [non-focal] (Cuculidae [non-focal]), the Greater Roadrunner.
+We had initially believed that this indicated a specimen found in a roadrunner nest; however, according to our reviewers, the USNM frequently assisted with the identification of insect specimens retrieved from the stomach contents of birds, and thus the specimen was most likely retrieved from the gut contents of a roadrunner.
+This seems quite likely given the poor external condition of the specimen.
 			It is unknown whether this species is parthenogenetic.
@@
 				``MEXICO: S.L.P; 19.6 mi. n. Huizache; July 25, 1976; Peigler, Gruetzmacher,; R\&M Murray, Schaffner'' (\texttt{\textbf{CMNC}}: 1 \male);
-				``MEXICO: San Luis Potosi; Entronque el Hulzache; 2 June 1987; R. Turnbow'' (\texttt{\textbf{CMNC}}: 1 \female, 1 \male);
+				``MEXICO: San Luis Potosi; Entronque el Hulzache; 2 June 1987; R. Turnbow'' (\texttt{\textbf{USNM}}: 1 \female; \texttt{\textbf{CMNC}}: 1 \male);
 				``MEXICO: Tamaulipas; 8.8 mi. ne. Jaumave; October 10, 1973; Gaumer \& Clark'' (\texttt{\textbf{TAMU}}: 2\female);
@@
 		\subsubsection*{Natural history}
-			Associated with spear globemallow \textit{Sphaeralcea hastulata} A. Gray [non-focal] (Malvaceae [non-focal]).
+			Associated with spear globemallow \textit{Sphaeralcea hastulata} A.
+Gray [non-focal] (Malvaceae [non-focal]).
+The indication of ``Sphaeralcea hastula A.
+Gray'' is not a valid name and appears to be a misspelling of \textit{Sphaeralcea hastulata}.
 
@@
 				Funicle slightly longer than scape.
-				Scape extending Brassicaceae  to posterior 1/4 of eye.
+				Scape extending to posterior 1/4 of eye.
 				Club nearly 3\x as long as wide.
@@
 			\paragraph{Paratypes}
-				``Milner, Idaho; \#5a, 7-9-31; \textit{S.}[\textit{alsola}] \textit{pestifer}; David E. Fox'' (\texttt{\textbf{USNM}}: 1 \female);
+				``Milner, Idaho; \#5a, 7-9-31; \textit{S.}[\textit{alsola}] \textit{pestifer}; David E. Fox'' (\texttt{\textbf{CMNC}}: 1 \female);
 				``Hazelton, Ida; \#10~~~4/29/30; \textit{N.}[\textit{orta}] \textit{altissma}'' (\texttt{\textbf{USNM}}: 1 \male)
@@
 			It is unknown whether this species is parthenogenetic.
+
 \newpage
+
 \section*{Checklist of Species}\label{sec:checklist}
@@
 			\> \textbf{\textit{franko}} \textbf{sp. nov.} sec. Jansen \& Franz (2018)\\
-			\>\textbf{ \textit{gravivultus}} Jansen \& Franz, 2015: 92 sec. Jansen \& Franz (2015)\\
+			\> \textbf{\textit{gravivultus}} Jansen \& Franz, 2015: 92 sec. Jansen \& Franz (2015)\\
 			\> \textbf{\textit{griseus}} (Sleeper, 1960: 84) sec. Jansen \& Franz (2015) [redescribed, p. 96]\\
@@
 
+\newpage
 \section*{Phylogenetic Results}\label{sec:results}
@@
 	 For all characters not resolved as unreversed synapomorphies, both the individual consistency (ci) and retention (ri) indices are provided.
-	Characters are numbered in accordance with descriptive sequence used in the species accounts.
-	A ``–'' symbol indicates inapplicable (character, state), whereas a ``?'' symbol indicates missing information, e.g., due to the unavailability of male specimens or insufficient specimens on hand to permit full dissections.
-	Characters 9, 27, 39, 45 - 47, 49, and 51 were mapped onto the preferred phylogeny using ACCTRAN optimization (see \citealt{agnarsson2008}), and the remaining characters had an unambiguous optimization.
 
@@
 
-	 	\item Prementum, anterior margin forming a distinct face that continues to lateral margins: (0) absent; (1) present.
+	 	\item Prementum, anterior margin medially with a distinct facet, rather than a single edge edge, that continues to lateral margins: (0) absent; (1) present.
 Synapomorphy for the \textit{M.
@@
 
-		\item Legs, relative length of mesotarsi to mesotibiae: (0) tarsi much shorter than tibiae; (1) tarsi at least equal in length to tibiae; (2) tarsi slightly shorter than tibiae.
+		\item Legs, relative length of mesotarsi to mesotibiae: (0) tarsi less than 3/4\x length of tibiae; (1) tarsi at least equal in length to tibiae; (2) tarsi shorter than tibiae, but longer than 3/4\x length of tibiae.
 Coded as additive due to alignment of character states with preferred phylogeny.
@@
 	The first, classification-based alignment (Fig.~\ref{fig:align1}) is simple and straightforward to interpret (see also \textbf{Supplemental Information SI2}). 
-	We obtain high-level congruence among the concepts \textit{Minyomerus} [JF2018] and \textit{Minyomerus} [JF2015], where 17 species-level concepts are retained from \citet{jansen2015} and four species-level concepts are added in the current revision.
+	We obtain high-level congruence among the concepts \textit{Minyomerus} [JF2018] and \textit{Minyomerus} [JF2015], where 17 species-level concepts are retained from \citet{jansen2015} and four species-level concepts are added in the current review.
 	The coverage constraint is relaxed for \textit{Minyomerus} [JF2015], thus allowing the four new species-level concepts to be subsumed under this parent.
@@
 \section*{Acknowledgments}
-	The authors are grateful to Robert Anderson (CMNC), Ed Riley and John Oswald (TAMU), and Lourdes Chamorro (USNM) for their assistance and provision of specimens used in this revision.
+	The authors are grateful to Robert Anderson (CMNC), Ed Riley and John Oswald (TAMU), and Lourdes Chamorro (USNM) for their assistance and provision of specimens used in this study.
 	The authors also thank Salvatore Anzaldo, Andrew Johnston, Sangmi Lee and other ASUHIC members for their assistance in procuring, treating, and maintaining specimen loans upon entry into the ASUHIC.
-	This research was funded in part by the National Science Foundation (DEB-1155984) and the United States Department of Agriculture -- Agricultural Research Service (Agreement 58-1275-1-335).
 
@@
 
+\section*{Funding statement}
+	This research was funded in part by the National Science Foundation (DEB-1155984) and the United States Department of Agriculture -- Agricultural Research Service (Agreement 58-1275-1-335).
+	There was no additional external funding received for this study.
+
 \newpage

### 2018-08-10 tex/revised_manuscript.tex
Final edits 1st revision
figure names

@@
 		For example, a species endemic to the Snake River Valley of Idaho does not require a predictive model for bioclimatically similar habitats in the Chihuahuan Desert.
-		Documented occurrence records are laid over the modeled habitat ranges as colored circles on their respective maps (Figs.~\ref{fig:map_amptyl}-\ref{fig:map_sculptilis}), along with vector layers of country (white) and state (gray) borders \citep{hijmans2012}.
+		Documented occurrence records are laid over the modeled habitat ranges as colored circles on their respective maps (Figs.~\ref{fig:map_summary}-\ref{fig:map_sculptilis}), along with vector layers of country (white) and state (gray) borders \citep{hijmans2012}.
 
@@
 		\subsubsection*{Natural history}
-			Associated with spear globemallow \textit{Sphaeralcea hastulata} A.
-Gray [non-focal] (Malvaceae [non-focal]).
-The indication of ``Sphaeralcea hastula A.
-Gray'' is not a valid name and appears to be a misspelling of \textit{Sphaeralcea hastulata}.
+			Associated with spear globemallow \textit{Sphaeralcea hastulata} A. Gray [non-focal] (Malvaceae [non-focal]).
+			The indication of ``Sphaeralcea hastula A. Gray'' is not a valid name and appears to be a misspelling of \textit{Sphaeralcea hastulata} [non-focal].
 
@@
 \newpage
+%RCC-5 alignment visualizations
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{figure1.png}
+	\caption{\textbf{Intensional RCC--5 alignment of the rank-only classifications of \textit{Minyomerus} [JF2018]/[JF2015].} See also \citet{jansen2015} and \textbf{Supplemental Information SI2}.
+Taxonomic concept labels such as \textit{Minymerus microps} [JF2015] are abbreviated as "2015.Minyomerus\_microps".
+Relaxation of the coverage constraint is indicated with the prefix "nc\_" (no coverage).
+Congruent concept regions (T\textsubscript{2} and T\textsubscript{1}) are shown as grey rectangles, concepts regions unique to the later taxonomy (T\textsubscript{2}) are shown as green rectangles, and concept regions unique to the earlier taxonomy (T\textsubscript{1}) are shown as yellow octagons.
+Articulations of inverse proper inclusion $(<)$ and overlap $(><)$, where present, are also shown.}
+	\label{fig:align1}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{figure2.png}
+	\caption{\textbf{Intensional RCC--5 alignment of the phylogenies of \textit{Minyomerus} [JF2018]/[JF2015] -- whole-concept resolution with overlap.} See also \textbf{Supplemental Information SI3}.
+Seven overlapping articulations are inferred.
+For further discussion, see the \textbf{\nameref{sec:alignments}} section.}
+	\label{fig:align2}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{figure3.png}
+	\caption{\textbf{Intensional RCC--5 alignment of the phylogenies of \textit{Minyomerus} [JF2018]/[JF2015] -- split-concept resolution.} See also \textbf{Supplemental Information SI4}.
+The seven overlapping articulations of the alignment displayed Fig.~\ref{fig:align2} are resolved into their constituent split regions.
+That is, if regions A and B overlap, the three resulting split regions are labeled A\textbackslash b ("A, \emph{not} b"), A*B ("A \emph{and} B"), and B\textbackslash a ("B, \emph{not} a").
+Five split-concept regions can \emph{only} be named using this convention, and are salmon-colored in the alignment visualization.}
+	\label{fig:align3}
+\end{figure}
+
+%distribution maps
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{figure4.png}
+	\caption{\textbf{Summary map of distributions of new species of \textit{Minyomerus} [JF2018].} Combined occurrence record and Maxent habitat modeling map for four newly-described species of \textit{Minyomerus} [JF2018], as indicated in the legend.}
+	\label{fig:map_summary}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{figure5.png}
+	\caption{\textbf{Distributions of \textit{M.
+ampullaceus} [JF2018] and \textit{M.
+tylotos} [JF2018].} Combined occurrence record and Maxent habitat modeling map for \textit{M.
+ampullaceus} [JF2018] and \textit{M.
+tylotos} [JF2018], as indicated in the legend.}
+	\label{fig:map_amptyl}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{figure6.png}
+	\caption{\textbf{Distributions of \textit{M. franko} [JF2018].} Combined occurrence record and Maxent habitat modeling map for \textit{M. franko} [JF2018], as indicated in the legend.}
+	\label{fig:map_franko}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\begin{sideways}
+		\includegraphics[height=0.85\textwidth]{figure7.png}
+		\end{sideways}
+	\caption{\textbf{Distributions of \textit{M. sculptilis} [JF2018].} Combined occurrence record and Maxent habitat modeling map for \textit{M. sculptilis} [JF2018], as indicated in the legend.}
+	\label{fig:map_sculptilis}
+\end{figure}
 
@@
 		\centering
-		\includegraphics[height=\textwidth]{figure1.jpg}
+		\includegraphics[height=\textwidth]{figure8.jpg}
 	\end{sideways}
@@
 		\centering
-		\includegraphics[height=\textwidth]{figure2.jpg}
+		\includegraphics[height=\textwidth]{figure9.jpg}
 	\end{sideways}
@@
 		\centering
-		\includegraphics[height=\textwidth]{figure3.jpg}
+		\includegraphics[height=\textwidth]{figure10.jpg}
 	\end{sideways}
@@
 	\centering
-	\includegraphics[width=\textwidth]{figure4.jpg}
+	\includegraphics[width=\textwidth]{figure11.jpg}
 	\caption{\textbf{Head and rostrum of \textit{M. ampullaceus} [JF2018].} Frontal view of female (\female) holotype.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{figure5.jpg}
+	\includegraphics[width=\textwidth]{figure12.jpg}
 	\caption{\textbf{Spermatheca of \textit{M. ampullaceus} [JF2018].} Genitalia of female (\female) holotype.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{figure6.jpg}
+	\includegraphics[width=\textwidth]{figure13.jpg}
 	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. ampullaceus} [JF2018].} Sternum VIII of female (\female) holotype.}
@@
 		\centering
-		\includegraphics[height=\textwidth]{figure7.jpg}
+		\includegraphics[height=\textwidth]{figure14.jpg}
 	\end{sideways}
@@
 		\centering
-		\includegraphics[height=\textwidth]{figure8.jpg}
+		\includegraphics[height=\textwidth]{figure15.jpg}
 	\end{sideways}
@@
 		\centering
-		\includegraphics[height=\textwidth]{figure9.jpg}
+		\includegraphics[height=\textwidth]{figure16.jpg}
 	\end{sideways}
@@
 	\centering
-	\includegraphics[width=\textwidth]{figure10.jpg}
+	\includegraphics[width=\textwidth]{figure17.jpg}
 	\caption{\textbf{Head and rostrum of \textit{M. franko} [JF2018].} Frontal view of female (\female) holotype.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{figure11.jpg}
+	\includegraphics[width=\textwidth]{figure18.jpg}
 	\caption{\textbf{Maxilla of \textit{M. franko} [JF2018].} Dextral maxilla of female (\female) paratype.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{figure12.jpg}
+	\includegraphics[width=\textwidth]{figure19.jpg}
 	\caption{\textbf{Prementum of \textit{M. franko} [JF2018].} Labium of female (\female) paratype.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{figure13.jpg}
+	\includegraphics[width=\textwidth]{figure20.jpg}
 	\caption{\textbf{Spermatheca of \textit{M. franko} [JF2018].} Genitalia of female (\female) paratype.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{figure14.jpg}
+	\includegraphics[width=\textwidth]{figure21.jpg}
 	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. franko} [JF2018].} Sternum VIII of female (\female) paratype.}
@@
 	\begin{sideways}
-		\includegraphics[width=0.95\textheight]{figure15.jpg}
+		\includegraphics[width=0.95\textheight]{figure22.jpg}
 	\end{sideways}
@@
 		\centering
-		\includegraphics[height=\textwidth]{figure16.jpg}
+		\includegraphics[height=\textwidth]{figure23.jpg}
 	\end{sideways}
@@
 		\centering
-		\includegraphics[height=\textwidth]{figure17.jpg}
+		\includegraphics[height=\textwidth]{figure24.jpg}
 	\end{sideways}
@@
 		\centering
-		\includegraphics[height=\textwidth]{figure18.jpg}
+		\includegraphics[height=\textwidth]{figure25.jpg}
 	\end{sideways}
@@
 	\centering
-	\includegraphics[width=\textwidth]{figure19.jpg}
+	\includegraphics[width=\textwidth]{figure26.jpg}
 	\caption{\textbf{Head and rostrum of \textit{M. sculptilis} [JF2018].} Frontal view of female (\female) holotype.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{figure20.jpg}
+	\includegraphics[width=\textwidth]{figure27.jpg}
 	\caption{\textbf{Spermatheca of \textit{M. sculptilis} [JF2018].} Genitalia of female (\female) paratype.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{figure21.jpg}
+	\includegraphics[width=\textwidth]{figure28.jpg}
 	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. sculptilis} [JF2018].} Sternum VIII of female (\female) paratype.}
@@
 	\begin{sideways}
-		\includegraphics[width=0.95\textheight]{figure22.jpg}
+		\includegraphics[width=0.95\textheight]{figure29.jpg}
 	\end{sideways}
@@
 		\centering
-		\includegraphics[height=\textwidth]{figure23.jpg}
+		\includegraphics[height=\textwidth]{figure30.jpg}
 	\end{sideways}
@@
 		\centering
-		\includegraphics[height=\textwidth]{figure24.jpg}
+		\includegraphics[height=\textwidth]{figure31.jpg}
 	\end{sideways}
@@
 		\centering
-		\includegraphics[height=\textwidth]{figure25.jpg}
+		\includegraphics[height=\textwidth]{figure32.jpg}
 	\end{sideways}
@@
 	\centering
-	\includegraphics[width=\textwidth]{figure26.jpg}
+	\includegraphics[width=\textwidth]{figure33.jpg}
 	\caption{\textbf{Head and rostrum of \textit{M. tylotos} [JF2018].} Frontal view of female (\female) holotype.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{figure27.jpg}
+	\includegraphics[width=\textwidth]{figure34.jpg}
 	\caption{\textbf{Prementum of \textit{M. tylotos} [JF2018].} Labium of female (\female) paratype.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{figure28.jpg}
+	\includegraphics[width=\textwidth]{figure35.jpg}
 	\caption{\textbf{Spermatheca of \textit{M. tylotos} [JF2018].} Genitalia of female (\female) paratype.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{figure29.jpg}
+	\includegraphics[width=\textwidth]{figure36.jpg}
 	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. tylotos} [JF2018].} Sternum VIII of female (\female) paratype.}
@@
 	\begin{sideways}
-		\includegraphics[height=0.85\textwidth]{figure30.png}
+		\includegraphics[height=0.85\textwidth]{figure37.png}
 	\end{sideways}
@@
 	\begin{sideways}
-		\includegraphics[height=0.85\textwidth]{figure31.png}
+		\includegraphics[height=0.85\textwidth]{figure38.png}
 	\end{sideways}
@@
 \end{figure}
-
-%RCC-5 alignment visualizations
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{figure32.png}
-	\caption{\textbf{Intensional RCC--5 alignment of the rank-only classifications of \textit{Minyomerus} [JF2018]/[JF2015].} See also \citet{jansen2015} and \textbf{Supplemental Information SI2}.
-Taxonomic concept labels such as \textit{Minymerus microps} [JF2015] are abbreviated as "2015.Minyomerus\_microps".
-Relaxation of the coverage constraint is indicated with the prefix "nc\_" (no coverage).
-Congruent concept regions (T\textsubscript{2} and T\textsubscript{1}) are shown as grey rectangles, concepts regions unique to the later taxonomy (T\textsubscript{2}) are shown as green rectangles, and concept regions unique to the earlier taxonomy (T\textsubscript{1}) are shown as yellow octagons.
-Articulations of inverse proper inclusion $(<)$ and overlap $(><)$, where present, are also shown.}
-	\label{fig:align1}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{figure33.png}
-	\caption{\textbf{Intensional RCC--5 alignment of the phylogenies of \textit{Minyomerus} [JF2018]/[JF2015] -- whole-concept resolution with overlap.} See also \textbf{Supplemental Information SI3}.
-Seven overlapping articulations are inferred.
-For further discussion, see the \textbf{\nameref{sec:alignments}} section.}
-	\label{fig:align2}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{figure34.png}
-	\caption{\textbf{Intensional RCC--5 alignment of the phylogenies of \textit{Minyomerus} [JF2018]/[JF2015] -- split-concept resolution.} See also \textbf{Supplemental Information SI4}.
-The seven overlapping articulations of the alignment displayed Fig.~\ref{fig:align2} are resolved into their constituent split regions.
-That is, if regions A and B overlap, the three resulting split regions are labeled A\textbackslash b ("A, \emph{not} b"), A*B ("A \emph{and} B"), and B\textbackslash a ("B, \emph{not} a").
-Five split-concept regions can \emph{only} be named using this convention, and are salmon-colored in the alignment visualization.}
-	\label{fig:align3}
-\end{figure}
-
-%distribution maps
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{figure35.png}
-	\caption{\textbf{Summary map of distributions of new species of \textit{Minyomerus} [JF2018].} Combined occurrence record and Maxent habitat modeling map for four newly-described species of \textit{Minyomerus} [JF2018], as indicated in the legend.}
-	\label{fig:map_summary}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{figure36.png}
-	\caption{\textbf{Distributions of \textit{M.
-ampullaceus} [JF2018] and \textit{M.
-tylotos} [JF2018].} Combined occurrence record and Maxent habitat modeling map for \textit{M.
-ampullaceus} [JF2018] and \textit{M.
-tylotos} [JF2018], as indicated in the legend.}
-	\label{fig:map_amptyl}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{figure37.png}
-	\caption{\textbf{Distributions of \textit{M. franko} [JF2018].} Combined occurrence record and Maxent habitat modeling map for \textit{M. franko} [JF2018], as indicated in the legend.}
-	\label{fig:map_franko}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\begin{sideways}
-		\includegraphics[height=0.85\textwidth]{figure38.png}
-		\end{sideways}
-	\caption{\textbf{Distributions of \textit{M. sculptilis} [JF2018].} Combined occurrence record and Maxent habitat modeling map for \textit{M. sculptilis} [JF2018], as indicated in the legend.}
-	\label{fig:map_sculptilis}
-\end{figure}
 \end{document}

### 2018-08-10 reviews/editor_review.tex
editor review

\documentclass[10pt,letterpaper]{letter}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{calc}
\newcommand{\x}{$\times$~}

\makeatletter
\newcommand{\DESCRIPTION@original@item}{}
\let\DESCRIPTION@original@item\item
\newcommand*{\DESCRIPTION@envir}{DESCRIPTION}
\newlength{\DESCRIPTION@totalleftmargin}
\newlength{\DESCRIPTION@linewidth}
\newcommand{\DESCRIPTION@makelabel}[1]{\llap{#1}}%
\newcommand{\DESCRIPTION@item}[1][]{%
  \setlength{\@totalleftmargin}%
       {\DESCRIPTION@totalleftmargin+\widthof{\textbf{#1 }}-\leftmargin}%
  \setlength{\linewidth}
       {\DESCRIPTION@linewidth-\widthof{\textbf{#1 }}+\leftmargin}%
  \par\parshape \@ne \@totalleftmargin \linewidth
  \DESCRIPTION@original@item[\textbf{#1}]%
}
\newenvironment{DESCRIPTION}
  {\list{}{\setlength{\labelwidth}{0cm}%
           \let\makelabel\DESCRIPTION@makelabel}%
   \setlength{\DESCRIPTION@totalleftmargin}{\@totalleftmargin}%
   \setlength{\DESCRIPTION@linewidth}{\linewidth}%
   \renewcommand{\item}{\ifx\@currenvir\DESCRIPTION@envir
                           \expandafter\DESCRIPTION@item
                        \else
                           \expandafter\DESCRIPTION@original@item
                        \fi}}
  {\endlist}
\makeatother

\address{M. Andrew Jansen\\School of Life Sciences\\Arizona State University\\Tempe, AZ 85287-4501} 
\signature{\underline{Contact Information}\\email: majanse1@asu.edu\\office: 1-(480)-727-9692} 
\begin{document} 
\begin{letter}{Juan J. Morrone\\Universidad Nacional Aut\'{o}noma de M\'{e}xico\\Academic Editor, PeerJ} 
	\opening{Dear Dr. Morrone,}

	In response to your review of the manuscript, we have made the following changes and addressed all of the points brought up in your comments.

	\begin{enumerate}
		\item \textbf{Figure/Table Citation} -- We have rearranged and re-numbered the figures, both in-text and within the file names, as necessary, to reflect their citation order in the manuscript.
		\item \textbf{References} -- We have removed all instances of \textit{et al.} from the references section and added full author lists.
		\item \textbf{Tables} -- The only table is found in-text, within the latex source code; we added a note to the staff indicating the lines of code where the table may be found.
		\item \textbf{Figure Source Credit} -- All of the photographs were taken by the first author, so we have added a photo credit for Andrew Jansen to all of the pictures. 
		\item \textbf{Figure Permissions} -- The maps were taken from https://gadm.org/, which are freely available for use in research and academic publishing, as indicated in their license at https://gadm.org/license.html; we have copied the text of this page, as well as the web address, and placed both in a text file uploaded to the supplementary information of this work.
		\item \textbf{Supplemental File legend} -- We have added brief descriptive legends to each supplementary file.
		\item \textbf{Funding Statement} -- We have removed the funding statement; this information is now provided in the author declarations.
	\end{enumerate}

	Please let us know if these revisions are acceptable.
	Many thanks again for your time and effort to improve this manuscript.

	\closing{Sincerely,\\Andrew Jansen \& Nico Franz}
	\cc{Nico M. Franz}
	%\ps{adding a postscript}
\end{letter} 
\end{document}

### 2018-08-10 tex/revised_manuscript.tex
editor review

@@
 
-\section*{Funding statement}
-	This research was funded in part by the National Science Foundation (DEB-1155984) and the United States Department of Agriculture -- Agricultural Research Service (Agreement 58-1275-1-335).
-	There was no additional external funding received for this study.
-
 \newpage
@@
 	\end{sideways}
-	\caption{\textbf{Dorsal habitus of \textit{M. ampullaceus} [JF2018].} Image of female (\female) holotype.}
+	\caption{\textbf{Dorsal habitus of \textit{M. ampullaceus} [JF2018].} Image of female (\female) holotype. Photo credit: Andrew Jansen.}
 	\label{fig:ampullaceus_F_dorsal}
@@
 	\end{sideways}
-	\caption{\textbf{Lateral habitus of \textit{M. ampullaceus} [JF2018].} Image of female (\female) holotype.}
+	\caption{\textbf{Lateral habitus of \textit{M. ampullaceus} [JF2018].} Image of female (\female) holotype. Photo credit: Andrew Jansen.}
 	\label{fig:ampullaceus_F_lateral}
@@
 	\end{sideways}
-	\caption{\textbf{Ventral habitus of \textit{M. ampullaceus} [JF2018].} Image of female (\female) holotype.}
+	\caption{\textbf{Ventral habitus of \textit{M. ampullaceus} [JF2018].} Image of female (\female) holotype. Photo credit: Andrew Jansen.}
 	\label{fig:ampullaceus_F_ventral}
@@
 	\includegraphics[width=\textwidth]{figure11.jpg}
-	\caption{\textbf{Head and rostrum of \textit{M. ampullaceus} [JF2018].} Frontal view of female (\female) holotype.}
+	\caption{\textbf{Head and rostrum of \textit{M. ampullaceus} [JF2018].} Frontal view of female (\female) holotype. Photo credit: Andrew Jansen.}
 	\label{fig:ampullaceus_F_frontal}
@@
 	\includegraphics[width=\textwidth]{figure12.jpg}
-	\caption{\textbf{Spermatheca of \textit{M. ampullaceus} [JF2018].} Genitalia of female (\female) holotype.}
+	\caption{\textbf{Spermatheca of \textit{M. ampullaceus} [JF2018].} Genitalia of female (\female) holotype. Photo credit: Andrew Jansen.}
 	\label{fig:ampullaceus_spermatheca}
@@
 	\includegraphics[width=\textwidth]{figure13.jpg}
-	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. ampullaceus} [JF2018].} Sternum VIII of female (\female) holotype.}
+	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. ampullaceus} [JF2018].} Sternum VIII of female (\female) holotype. Photo credit: Andrew Jansen.}
 	\label{fig:ampullaceus_lamina}
@@
 	\end{sideways}
-	\caption{\textbf{Dorsal habitus of \textit{M. franko} [JF2018].} Image of female (\female) holotype.}
+	\caption{\textbf{Dorsal habitus of \textit{M. franko} [JF2018].} Image of female (\female) holotype. Photo credit: Andrew Jansen.}
 	\label{fig:franko_F_dorsal}
@@
 	\end{sideways}
-	\caption{\textbf{Lateral habitus of \textit{M. franko} [JF2018].} Image of female (\female) holotype.}
+	\caption{\textbf{Lateral habitus of \textit{M. franko} [JF2018].} Image of female (\female) holotype. Photo credit: Andrew Jansen.}
 	\label{fig:franko_F_lateral}
@@
 	\end{sideways}
-	\caption{\textbf{Ventral habitus of \textit{M. franko} [JF2018].} Image of female (\female) holotype.}
+	\caption{\textbf{Ventral habitus of \textit{M. franko} [JF2018].} Image of female (\female) holotype. Photo credit: Andrew Jansen.}
 	\label{fig:franko_F_ventral}
@@
 	\includegraphics[width=\textwidth]{figure17.jpg}
-	\caption{\textbf{Head and rostrum of \textit{M. franko} [JF2018].} Frontal view of female (\female) holotype.}
+	\caption{\textbf{Head and rostrum of \textit{M. franko} [JF2018].} Frontal view of female (\female) holotype. Photo credit: Andrew Jansen.}
 	\label{fig:franko_F_frontal}
@@
 	\includegraphics[width=\textwidth]{figure18.jpg}
-	\caption{\textbf{Maxilla of \textit{M. franko} [JF2018].} Dextral maxilla of female (\female) paratype.}
+	\caption{\textbf{Maxilla of \textit{M. franko} [JF2018].} Dextral maxilla of female (\female) paratype. Photo credit: Andrew Jansen.}
 	\label{fig:franko_maxilla}
@@
 	\includegraphics[width=\textwidth]{figure19.jpg}
-	\caption{\textbf{Prementum of \textit{M. franko} [JF2018].} Labium of female (\female) paratype.}
+	\caption{\textbf{Prementum of \textit{M. franko} [JF2018].} Labium of female (\female) paratype. Photo credit: Andrew Jansen.}
 	\label{fig:franko_prementum}
@@
 	\includegraphics[width=\textwidth]{figure20.jpg}
-	\caption{\textbf{Spermatheca of \textit{M. franko} [JF2018].} Genitalia of female (\female) paratype.}
+	\caption{\textbf{Spermatheca of \textit{M. franko} [JF2018].} Genitalia of female (\female) paratype. Photo credit: Andrew Jansen.}
 	\label{fig:franko_spermatheca}
@@
 	\includegraphics[width=\textwidth]{figure21.jpg}
-	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. franko} [JF2018].} Sternum VIII of female (\female) paratype.}
+	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. franko} [JF2018].} Sternum VIII of female (\female) paratype. Photo credit: Andrew Jansen.}
 	\label{fig:franko_lamina}
@@
 	\end{sideways}
-	\caption{\textbf{Aedeagus of \textit{M. franko} [JF2018].} Genitalia of male (\male) paratype in (A) dorsal view and (B) lateral view.}
+	\caption{\textbf{Aedeagus of \textit{M. franko} [JF2018].} Genitalia of male (\male) paratype in (A) dorsal view and (B) lateral view. Photo credit: Andrew Jansen.}
 	\label{fig:franko_aedeagus}
@@
 	\end{sideways}
-	\caption{\textbf{Dorsal habitus of \textit{M. sculptilis} [JF2018].} Image of female (\female) holotype.}
+	\caption{\textbf{Dorsal habitus of \textit{M. sculptilis} [JF2018].} Image of female (\female) holotype. Photo credit: Andrew Jansen.}
 	\label{fig:sculptilis_F_dorsal}
@@
 	\end{sideways}
-	\caption{\textbf{Lateral habitus of \textit{M. sculptilis} [JF2018].} Image of female (\female) holotype.}
+	\caption{\textbf{Lateral habitus of \textit{M. sculptilis} [JF2018].} Image of female (\female) holotype. Photo credit: Andrew Jansen.}
 	\label{fig:sculptilis_F_lateral}
@@
 	\end{sideways}
-	\caption{\textbf{Ventral habitus of \textit{M. sculptilis} [JF2018].} Image of female (\female) holotype.}
+	\caption{\textbf{Ventral habitus of \textit{M. sculptilis} [JF2018].} Image of female (\female) holotype. Photo credit: Andrew Jansen.}
 	\label{fig:sculptilis_F_ventral}
@@
 	\includegraphics[width=\textwidth]{figure26.jpg}
-	\caption{\textbf{Head and rostrum of \textit{M. sculptilis} [JF2018].} Frontal view of female (\female) holotype.}
+	\caption{\textbf{Head and rostrum of \textit{M. sculptilis} [JF2018].} Frontal view of female (\female) holotype. Photo credit: Andrew Jansen.}
 	\label{fig:sculptilis_F_frontal}
@@
 	\includegraphics[width=\textwidth]{figure27.jpg}
-	\caption{\textbf{Spermatheca of \textit{M. sculptilis} [JF2018].} Genitalia of female (\female) paratype.}
+	\caption{\textbf{Spermatheca of \textit{M. sculptilis} [JF2018].} Genitalia of female (\female) paratype. Photo credit: Andrew Jansen.}
 	\label{fig:sculptilis_spermatheca}
@@
 	\includegraphics[width=\textwidth]{figure28.jpg}
-	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. sculptilis} [JF2018].} Sternum VIII of female (\female) paratype.}
+	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. sculptilis} [JF2018].} Sternum VIII of female (\female) paratype. Photo credit: Andrew Jansen.}
 	\label{fig:sculptilis_lamina}
@@
 	\end{sideways}
-	\caption{\textbf{Aedeagus of \textit{M. sculptilis} [JF2018].} Genitalia of male (\male) paratype in (A) dorsal view and (B) lateral view.}
+	\caption{\textbf{Aedeagus of \textit{M. sculptilis} [JF2018].} Genitalia of male (\male) paratype in (A) dorsal view and (B) lateral view. Photo credit: Andrew Jansen.}
 	\label{fig:sculptilis_aedeagus}
@@
 	\end{sideways}
-	\caption{\textbf{Dorsal habitus of \textit{M. tylotos} [JF2018].} Image of female (\female) holotype.}
+	\caption{\textbf{Dorsal habitus of \textit{M. tylotos} [JF2018].} Image of female (\female) holotype. Photo credit: Andrew Jansen.}
 	\label{fig:tylotos_F_dorsal}
@@
 	\end{sideways}
-	\caption{\textbf{Lateral habitus of \textit{M. tylotos} [JF2018].} Image of female (\female) holotype.}
+	\caption{\textbf{Lateral habitus of \textit{M. tylotos} [JF2018].} Image of female (\female) holotype. Photo credit: Andrew Jansen.}
 	\label{fig:tylotos_F_lateral}
@@
 	\end{sideways}
-	\caption{\textbf{Ventral habitus of \textit{M. tylotos} [JF2018].} Image of female (\female) holotype.}
+	\caption{\textbf{Ventral habitus of \textit{M. tylotos} [JF2018].} Image of female (\female) holotype. Photo credit: Andrew Jansen.}
 	\label{fig:tylotos_F_ventral}
@@
 	\includegraphics[width=\textwidth]{figure33.jpg}
-	\caption{\textbf{Head and rostrum of \textit{M. tylotos} [JF2018].} Frontal view of female (\female) holotype.}
+	\caption{\textbf{Head and rostrum of \textit{M. tylotos} [JF2018].} Frontal view of female (\female) holotype. Photo credit: Andrew Jansen.}
 	\label{fig:tylotos_F_frontal}
@@
 	\includegraphics[width=\textwidth]{figure34.jpg}
-	\caption{\textbf{Prementum of \textit{M. tylotos} [JF2018].} Labium of female (\female) paratype.}
+	\caption{\textbf{Prementum of \textit{M. tylotos} [JF2018].} Labium of female (\female) paratype. Photo credit: Andrew Jansen.}
 	\label{fig:tylotos_prementum}
@@
 	\includegraphics[width=\textwidth]{figure35.jpg}
-	\caption{\textbf{Spermatheca of \textit{M. tylotos} [JF2018].} Genitalia of female (\female) paratype.}
+	\caption{\textbf{Spermatheca of \textit{M. tylotos} [JF2018].} Genitalia of female (\female) paratype. Photo credit: Andrew Jansen.}
 	\label{fig:tylotos_spermatheca}
@@
 	\includegraphics[width=\textwidth]{figure36.jpg}
-	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. tylotos} [JF2018].} Sternum VIII of female (\female) paratype.}
+	\caption{\textbf{Lamina of spiculum ventrale of \textit{M. tylotos} [JF2018].} Sternum VIII of female (\female) paratype. Photo credit: Andrew Jansen.}
 	\label{fig:tylotos_lamina}
